### 2016-06-07 paper/main.tex
add paper

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{bm}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

%\makeatletter
%\def\@copyrightspace{\relax}
%\makeatother

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\doi{10.475/123_4}
\doi{**.***/***}

% ISBN
%\isbn{123-4567-24-567/08/06}
\isbn{***-****-**-***/**/**}

%Conference
%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

%\acmPrice{\$15.00}

%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Full History Info Enhanced Normal States Training for High Accuracy Event Detection}

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\begin{comment}
\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
\end{comment}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
In cyberspace, it is a very challenging task to detect events accurately due to its rapid changing nature.
In our study, we find out the key to improve the accuracy lies in training the normal states well, which describe what happened and help to identify what is happening in cyberspace.
Traditional methods underestimate the normal states due to the limited training data spanning over a few time windows.
To overcome this limitation, we propose \textsc{FullReader}, a high accuracy event detection system that trains normal states better by using Wikipedia, which can be treated as an approximation of full history information source. 
In \textsc{FullReader}, 1) normal states are trained as topical word frequencies; 2) historical topical word frequencies are extracted from Wikipedia pages, categories, and their Topic-PageRank-HITS scores; 3) topical word frequencies of targeted corpus are updated incrementally by Asymmetric-Prior-LDA, using the history information as prior; 4) events are detected by monitoring the change of topical word frequencies. 
Experiments on the benchmark Edinburgh twitter corpus validate the effectiveness of our proposed \textsc{FullReader}.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc{Mathematics of computing~Bayesian computation}
\ccsdesc{Mathematics of computing~Gibbs sampling}
\ccsdesc{Information systems ~ Data analytics}
\ccsdesc{Information systems ~Data stream mining}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{Full history info; normal states initialization and maintenance; event detection; text mining;}

\section{Introduction}
Improving the accuracy of event detection in cyberspace can benefit many tasks, but it's nontrivial due to the rapid changing nature of cyberspace.

In our study, we find out that the key to improve the accuracy of event detection lies in training the normal states of the focused media/site/domain. Based on training normal states accurately, event detection task can be treated as finding terms, articles, or topics which are different from the normal states.

Our intuition is inspired from the news value theory\cite{galtung1965structure}\cite{caple2013delving}, which emphasizes the \textit{news unexpectedness} -- "the unpredictable or the rare is more newsworthy than the routine"\cite{bell1991language}, and "routine events are difficult to assimilate to the news, which favours the novel, the atypical and the unusual"\cite{montgomery2007discourse}.
Following this guideline, if the journalist knew the normal states, aka, the "routine things" of everyday better, he/she would tend to choose more unexpected news to report. 
We suppose that the ideal event detection system performs like a journalist who can find news from cyberspace with the knowledge of the normal states.

To train the normal states, the methods of existing systems can be grouped into two categories: \textit{unsupervised normal states training} and \textit{classification based normal states training}, which is illustrated by Figure \ref{fig:modelDesc:a}.

In the first category, the methods treat the normal states as clustered articles\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topics\cite{Diao:2012wj}\cite{Yan:2015wm}. 
Taking the clustering of articles\cite{Petrovic:2010uj}\cite{Wurzer:2015wq} as an example, they model the occured events as clusters, and link the incoming article with an existing event cluster or assign it as the new detected event.
The decision is based on whether the dissimilarity between the incoming article and existing event clusters is over the user-specified threshold.

And in the second category, the methods learn the normal states by given the knowledge of \textit{event trigger}\cite{Li2013JointEE}\cite{Nguyen2015EventDA} (usually a single verb or entity mentions). The normal states are trained by the labeled data appeared in a fixed time window.

Both categories of methods have achieved good performance on formal texts, but are hamppered by the diverse and rapid changing nature of cyberspace data (e.g., twitter\cite{Asur:2011tc} and reddit\cite{singer2014evolution}).
In the journalist metaphor of news value theory, they have the limited knowledge of normal states (aka "routine things") due to the limited history information used. 
More specifically,

It's difficult to represent the 
the low threshold leads to , while the high threshold leads to

They build the normal states in the evolving training window
%TODO
The second category, train the triggers\cite{Li2013JointEE}\cite{Nguyen2015EventDA}(\textit{But it has some problems here, these methods are used in event extraction, so what's the relationship between event extraction and event detection? and the fired example in \cite{Li2013JointEE}?}).

They are hamppered by the rapid changing nature of cyberspace, e.g. twitter and reddit(\textit{find out the sentences to describe the rapid changing nature}).

It is hard to handle all the cyberspace data by using limited computing resources. As a result, it have to make a trade off, only to process part of them, instead of using the whole data.

In this paper, we demonstrate that the better normal states  are learned, the better event detection system can perform.

 and \textit{full history info enhanced normal states training}.

\begin{figure*}[ht]
    \centering
    \subfigure[The first category methods\cite{Petrovic:2010uj}\cite{Wurzer:2015wq} utilize the history information appeared in an evolving training window; the second category\cite{Li2013JointEE}\cite{Nguyen2015EventDA} trains the normal states by the labeled data existed in a fixed time window. Our method intializes the normal states with full history info, and updates them incrementally. With normal states, systems detect events.]{
                \label{fig:modelDesc:a} %% label for first subfigure
                \includegraphics[height=7.4cm]{img/modelDescription.pdf}
        }
        \quad
        \quad
    \subfigure[\textsc{FullReader}'s process flow, taking \textbf{military} related events in cyberspace as an example. \textsc{FullReader} initializes the normal states as topical word frequencies from full history information about military, updates them further at the specific corpus day by day, and detects events finally.]{
                \label{fig:modelDesc:b} %% label for first subfigure
                \includegraphics[height=7.0cm]{img/systemExample.pdf}
        }    
    \caption{Overview of how event detection systems use history information (left), and an example of our \textsc{FullReader} system process flow on how to detect the military related events (right).}
    \label{fig:modelDesc}
\end{figure*}

For example, in ideal conditions an event detection system for anti-terrorism has the knowledge about the normal state such as “the words ISIS and Syria are both high-frequent, while the word Russia is not so frequent as them”. 
With the knowledge of normal state, the system for anti-terrorism can detect the event of “Russia's anti-ISIS op in Syria” as Russia appeared more frequent than the normal state and appeared with ISIS and Syria. 
After detection, the ideal event detection system also updates the normal state by considering the new coming data.

\section{Related Works}
Although \cite{Wurzer:2015wq} points out that UMass\cite{Allan:2000wu} and its variants\cite{Petrovic:2010uj}\cite{petrovic2012using}\cite{Wurzer:2015wq} are the state-of-art systems on the Event Detection task for the newswire data, these systems still suffers from the lack of accuracy to applied on more general cyberspace data, such as tweets, emails, and reddit posts. 
The underlying reason is that the normalized Topic Weighted Minimum Cost metric (\(C_{min}\)) used in the Event Detection keep balance between miss and false alarm, which cannot work well on the .
Usually these traditional systems set the ratio of cost between miss alarm and false alarm to 10, preferring recall to precision on detecting events.

Study of event detection on text stream can be divided into three ways: word frequency based, text similarity based and topic model based.

Several word frequency methods have been developed for event detection such as Discrete Fourier Transform\cite{he2007analyzingDFT}, wavelet analysis \cite{weng2011eventWavelet}.
They treat the word's document frequency along timeline as time series and do the analysis in frequency domain. 
DFT method suffers the problem that it can not locate the time point for bursty.
Wavelet analysis based method's complexity is very high, so its scalability is limited.

 Text similarity based online event detection methods\cite{petrovic2010streaming}\cite{mccreadiescalable}  suffer from the lexical variation which means different words describe the same events.
 Similarity based method can successfully detect the tweet which is retweeted by many times, but fails to find out the event which is described from many different perspectives.
 As a result, many events are duplicately detected due to their popularities, which may bury other events and overwhelm users with duplicated unwanted content.

In contrast, topic model can handle the lexical variation problem with word co-occurrence\cite{blei2003latent}.
%After \cite{blei2006dynamic} and \cite{wang2006topics} introducing time factor into topic model, a number of temporal model has been developed to different tasks.
As many events are highly related to topics, a number of methods based on topic model have been proposed for event detection, including online detection and offline detection.
Lau\cite{lau2012line} introduces an online topic model to track emerging events in microblogs.
It can deal with a massive of tweets, but it doesn't filter out the tweets related to user interests.
Diao\cite{timeUserLDA2012finding}\cite{diao2013unified} show that event detection can benefit from filtering out user interest related tweets. 
And Yan\cite{Yan:2015wm} models the bursty topic by incorporating burstiness of biterms as prior knowledge.
But they are different from ours.
As these models need the whole dataset as the input, they are offline detections, which is not scalability for large dynamic dataset such as micorblogs.
Instead, we gather user's self-description and the followings' self-description as user profile which is stable to characterize user interests. 
Based on this fine-grained user modeling information, user's long term interest related tweets and short term bursty event related tweets can be distinguished in online style, and can be efficiently applied on microblogs.

Since user modeling has the significant impact on users' activities on microblogs, the usage of user modeling has drawn attention in many research fields. 
\cite{zhao2013inferring} exploits user modeling information and network topology to infer user's role in social network.
\cite{yoshida2013toward} also introduces user modeling to community detection where some edges are not observable, but user profile can provide additional information.
Different from the above work, we do not only treat the user modeling result as an additional feature, but also an important representative factor for users, who are the source of information in microblogs.

User modeling can be carried out to obtain web users' demographics information \cite{culotta2015predicting} (e.g., gender, age, ethnicity, education, income, etc.).
Compared with demographics information, user interests' modeling can be verified more easily \cite{faralli2015large}.

  尽管文献[1]指出UMass[2] 是FSD任务中最为精确的方法，但由于在Event Detection任务中，the metric used in this method单纯的使用normalized topic weighted minimum cost并不能准确的反映出它能够很好的说明网络空间中的事件检测的准确性。其原因在于计算公式中缩小了CFa的值（一般默认的方法将miss与false alarm的cost的比值设置为10：1），因而传统的方法倾向于扩大召回率而牺牲了准确率。这样的做法在处理newswire信息时并没有太大不妥，原因在于newswire中检测出的novel story是事件的概率极大。而一般的网络空间中不仅仅包含新闻，而且覆盖了各方面的信息【参见Twevent中对twitter信息覆盖面的文献】。在此种情况下，即便是novelty story，也不一定代表了事件（具体的例子见Section实验部分）。进一步的，我们认为UMass在应用到一般的网络空间的事件检测的准确率不高的原因是UMass没有对网络空间的正常状态进行有效的训练。UMass[2]，LSH方法[3]，k-terms Hashing[1]使用聚类簇来表示cyberspace的正常状态，然而对于twitter这种覆盖面极广的社交媒体，聚类簇的方法总是不能穷尽所有正常状态。【这里的说法不是很强健】
  与UMass，LSH，kterms等在向量空间或者在此基础上的哈希值进行聚类的方法不同，timeUserLDA[4]以及BBTM[5]对网络空间中的正常状态使用topic model进行刻画，将网络空间中的topics试图按照normal topics和bursty topics进行区分。该方法能够有效的检测到被人们广泛关注的bursty topics，这些bursty topics往往是我们需要我们检测的events的一部分。然而此类方法也有明显的缺陷，由于topic model使用对称的先验，因此其topic的规模倾向于相近的大小。然而人们在同一时间内对事件的关注度有限，事件受关注的程度也是趋向于power law分布的。这样，一些较小规模的事件不能被正确的检测出。因此，此类方法的特点是准确率高，但召回率低。进一步的究其本质，是timeUserLDA、BBTM等方法没有能够准确的训练网络空间的正常状态，较小的bursty event会被吸收进正常状态中。
另一类方法是以EDCoW[6]为代表的对词频的正常状态进行训练的工作，判断the degree of burstiness of terms，然而cyberspace中常用词频率变化并不明显，因此由这类词构成的事件往往并不容易被检测到，这一结果也由[7]证实。
与我们的工作最为相近的是Twevent[7]，Twevent采用三个阶段的方式进行：tweet segment, event segment detection, event segment clustering。
Twevent 抽取tweet segment依赖于词典因而往往不能发现。。。
正常状态训练部分的相关工作。
Tedas[8], ESA[9], AIDR[10] 
TwitterMonitor[11], EDCoW[6], TwitInfo[12], Twevent[7], Leadline[13], TwiCal[14], ESA[9], Redites[15]

Twitter Trending Topic Classification
%\begin{figure}
%    \includegraphics[height=7.7cm]{img/mlab_dirichlet_alpha_effects.pdf}
%\end{figure}
We use PageRank-HITS\cite{Yan:2015wq} algorithm to update score of categories in wikipedia.

%3*4 figures
\begin{figure*}[ht]
        \centering
        \label{fig:subfig} %% label for entire figure
        \subfigure[\(\alpha=(0.25,0.25,0.25)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph0.pdf}
        }
        \subfigure[\(\alpha=(0.5,0.5,0.5)\)]{
                \label{fig:subfig:b} %% label for second subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph1.pdf}
        } 
        \subfigure[\(\alpha=(1.5,1.5,1.5)\)]{
                \label{fig:subfig:c} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph2.pdf}
        }
        \subfigure[\(\alpha=(2.5,2.5,2.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph3.pdf}
        }\hspace{1in}
        \subfigure[\(\alpha=(0.25,0.25,0.75)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph4.pdf}
        }
        \subfigure[\(\alpha=(0.5,0.5,1.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph5.pdf}
        }
        \subfigure[\(\alpha=(1.5,1.5,2.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph6.pdf}
        }
        \subfigure[\(\alpha=(2.5,2.5,3.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph7.pdf}
        }\hspace{1in}
        \subfigure[\(\alpha=(0.25,0.75,0.75)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph8.pdf}
        }
        \subfigure[\(\alpha=(0.5,1.5,1.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph9.pdf}
        }
        \subfigure[\(\alpha=(1.5,2.5,2.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph10.pdf}
        }
        \subfigure[\(\alpha=(2.5,3.5,3.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph11.pdf}
        }
        \caption{Illustration of Drichlet distribution's probabilistic density on the 3-dimensional simplex when given different priors. (a-d) (e-h) (i-l)}
\end{figure*}

\section{Method}
\textbf{User profile.} User usually describes herself or himself by a piece of short text on microblog platform.
This short text can be a continuous string or an array of hash tags, e.g., "\textit{Co-founder of Twitter, Medium, and now Co-founder and CEO of Askjelly.com}" of Biz Stone or "\textit{\#Cloud}, \textit{\#YARN}" of @hadoopchina.
Though it's easy to estimate Biz Stone's interests by his self-description text, it's not always capable of doing so because some users' are very short.
To overcome this limitation, we define \textbf{user profile} \(\bm{p_u}\) as combining user \(u\)'s self-description text with the texts provided by \(u\)'s followings. 
Taking Biz Stone as an example, he follows 696 accounts, in which there are 60 founders, 27 CEOs, 21 Google related, and 9 medium related accounts, etc. 
This example demonstrates that user profile \(p_u\) can be augmented by gathering the followings' information.

\textbf{User modeling.} 
User modeling is used to capturing user's long term interests. 
For each user profile token, .
For example, Biz Stone's long term interests can be inferred as \textit{Social Media}, \textit{Business}, and \textit{Technology} from his user profile \textit{Medium}, \textit{CEO}, and \textit{Google} respectively.

The notations used in this paper are summarized in Table \ref{symbolsInModel}.
We consider \(u\)'s user timeline as  the triple \(\{uid, \bm{p_u},\bm{w_u}\} \), where \(\bm{p_u}\) represents user \(u\)'s profile and \(\bm{w_u}=\{(tweetid, t_{ud},w_{ud})\}\) means the set of tweets posted by user \(u\).
The element of \(\bm{w_u}\) is a triple of tweet id, time stamp \(t_{ud}\) and tweet content \(\bm{w_{ud}}\).

\textbf{Event.} We define the event in the given time window \(t\) as the set of tweets denoted by \( \{ \bm{w_{te}}\}\).
The event related tweets in set \( \{ \bm{w_{te}}\}\)  hold two properties: (1) it is different from user \(u\)'s long term interests and (2) it is similar with other tweets in the set.
The task of event detection is to find out all the events in corpus.
Different methods treat the above properties in different ways: LSH based methods\cite{petrovic2010streaming} treat the difference and simliarity in word vector space; while the topic model based methods\cite{timeUserLDA2012finding} take the semantic meaning into consideration.
Under the framework of topic model, we divide the topics into user interest related topics and bursty event related topics, and further promote an online learning model UMIETM.
\subsection{Normal States' Initialization}
%TODO
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{img/normalStatesFromHistoryInfo.pdf}  
    \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
    \label{fig:modelDesc}
\end{figure}

\textbf{HITS step.}
After the above step, we obtain PageRank scores for either queries or candidate replies. To propagate such information to the other side in the query-reply bipartite graph, we perform another random walk with links between queries and replies representing the structural information of hubs and authorities. %To incorporate prior information (obtained in the PageRank step) of queries and replies, we adopt a HITS variant in \citeauthor{deng2009generalized}~\shortcite{deng2009generalized}, called Co-HITS.

Formally, the bipartite graph $G=(V,E)$ has vertexes  $V=\{V_q \cup V_r\}$, where $V_q$ are queries and $V_r$ are replies. We define the weight matrix by a relevance scoring function $\phi(q,r)$ between queries and replies. $\phi(\cdot,\cdot)$ was learned via a \textit{learning-to-rank} model similar to ~\shortcite{burges2005learning} with rich features including textual similarity, translation models, as well as {\tt word2vec} word embeddings \cite{mikolov2013distributed}. In other words, $\phi(\cdot,\cdot)$ returns the relatedness between a query and a reply in the range $(0,1)$.

Moreover, since we would like to make use of PageRank scores for queries or replies, the HITS links are judged by not only the static relevance score $\phi(\cdot,\cdot)$, but also the information given by PageRank. To be concrete, the (unnormalized) weight matrix is given by either
\begin{equation}
\text{\quad \quad\quad\quad\!}\tilde{\mathbf W}_{ij} = \phi(q_i, r_j)\cdot q_i\quad\quad\quad\text{(query$\rightarrow$reply)}
\label{eqn:w1}
\end{equation}
\begin{equation}
\text{or\quad\quad\quad} \tilde{\mathbf W}_{ij} = \phi(r_i, q_j)\cdot {r}_i\quad\quad\quad\text{(reply$\rightarrow$query)}
\label{eqn:w2}
\end{equation}
Here, $q_i$ and $r_i$ are the \textit{i}-th element in the vectors $\mathbf q$ and $\mathbf r$, which are obtained in the PageRank phase by Equations~\ref{eqn:pagerank1}--\ref{eqn:pagerank2}. If information is propagated from queries to replies, we use the former equation for weight update, and \textit{vice versa}.

The mutual-reinforcing relationship of hub and authority scores can be expressed in matrix representation as follows.
\begin{align}
\mathbf{x}^{(i+1)} &= \alpha_x\cdot \big[\tilde{\mathbf W}\big]\,\mathbf{y}^{(i)}+(1-\alpha_x)\cdot \hat{\mathbf{x}}\label{eqn:HITS2}\\
\mathbf{y}^{(i+1)} &= \alpha_y\cdot \left[\big[\tilde{\mathbf W}\big]^\top\right]\mathbf{x}^{(i)}+(1-\alpha_y)\cdot\hat{\mathbf{y}} \label{eqn:HITS1}
\end{align}
where $\mathbf x$ is query scores, $\mathbf y$ reply scores; superscripts denote the number of local iterations in HITS update.
Each column of the weights is normalized to be a valid probability. Moreover, to compute the weight for $\mathbf{y}$, the matrix $\mathbf{\tilde W}^\top$ should be first row-normalized (given by $[\mathbf{\tilde W}]^\top$); otherwise, the effect of the prior $q_i$ in Equation~\ref{eqn:w1} is ruled out by column normalization.
Notice that the transition matrix is fixed in one step of HITS, but they may also change as our algorithm proceeds like the PageRank step.

\subsection{Normal States' Maintenance}
Asymmetric-Prior-LDA
\begin{figure}[t]
    \centering
    \includegraphics[height=3.5cm]{img/NTS.eps}
    \caption{Probabilistic model for training normal states by using history information.}
    %The convolution neural network for extracting character-level representations of words. Dashed arrows indicate a dropout layer applied before character embeddings are input to CNN.}
    \label{fig:cnn}
\end{figure}

\ \ Our theme modeling, want to learn the first \(k\) topics with Wikipedia Article \(k\) topics as close as possible, and we will be Wikipedia article \(k\) before 1000 words) was added to the theme of the word frequency word in the subject a priori distribution on the.
Learning to be the first \(k\) Subject polynomial distribution of the word, referred to as \(\phi_k \), Wikipedia article \(k \) distribution of topics for \(\tau_k \), then this formalized process is expressed as: \(\ phi_k \sim Dir(\beta + \tau_k) \).
Formal presentation of the explanation is: With prior knowledge \(\tau_k \) after the theme \(\phi_k \) is no longer simply rely on symmetric priori \(\beta \), different words right is not the same weight , such as a discussion of "fashion" theme in Wikipedia, it will refer to "dress", "grand", "blue", "gold" and other words, with the asymmetric priori \(\beta + \tau_k \) after in microblogging "fashion" theme "dress" the proportion will be increased in this way so that microblogging corpus theme tends to Wikipedia topic.
\(\tau_k \) in the first \(v \) words such as formula (\ref{eq: wikiPrior}).
Where \(S_k \) as a set of candidate words: high-quality information to use Wikipedia, we extract the theme \(phi_k \ \) in the higher-word word frequency candidate set \(S_k \).
We can control set \(S_k \) in size, the size of the control is usually set for 1000.
The number of frequency \(n_{kv} \) for the word \(v \) (\ k) appears in the Wikipedia article themes of: (\ref{wikiPrior eq}).
If the word \(v \) does not appear in the candidate set \(S_k \), and then set a priori knowledge \(\tau_{kv} = 0 \), otherwise, the word frequency is proportional to \(n_{kv} \) with the prior knowledge of weight \(W\).
In the latter experiment, we will be on a priori knowledge of weights \(W \) will be discussed.

\begin{enumerate}[noitemsep]
    \item for each topic \(k \in \{1,\cdots,K\}\)，
    \begin{enumerate}
        \item word distribution on the topic \(\phi_k \sim Dirichlet(\beta+\tau_k)\).
    \end{enumerate}
    \item for each document \(d \in D\)，
    \begin{enumerate}
        \item topic distribution on the document \(\theta_d \sim Dir(\alpha)\)
        \item for each word index \(n \in \{1,\cdots,N_d\}\)，
        \begin{enumerate}
            \item word's topic assignment \(z_{dn} \sim Multinomial(\theta_d)\)，
            \item word \(w_{dn} \sim Multinomial(\phi_{z_{dn}})\)
        \end{enumerate}
    \end{enumerate}
\end{enumerate}

\begin{equation}
\label{eq:wikiPrior}
\begin{aligned}
\tau_{kv}=
\left\{ \begin{aligned}
W \frac{n_{kv}}{\sum_{v\in S_{kv}}n_{kv}} &,v\in S_{k} \\
0&,v \notin S_{k}\\
\end{aligned}\right.
\end{aligned}
\end{equation}

\begin{equation}
\label{eq:LDAgibbs}
\begin{aligned}
&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha,\beta,\tau)\\
&\ \ \propto \frac{n_{dk}+\alpha}{n_{d,.}+K\alpha}\frac{n_{kv}+\tau_{kv}+\beta}{n_{k,.}+\tau_{k,.}+V\beta}
\end{aligned}
\end{equation}

\begin{algorithm}[H]
    \caption{UPIETM batch learning algorithm} %title
    \label{alg:UPIETMbatch} %label
    \begin{algorithmic}[1] %this 1 means the showing of line number in algorithm
    \STATE initiate the topic label and the statistics
    \FOR {\(i=1:I_1\)}
        \FOR{\(u\) in  user set U}
            \FOR{\(n\) = \(1:P_u\)}
                \STATE sample profile's hidden topic \(s_{un}\) by (\ref{timeUserTagLDAIVsamplingForS})
                \STATE update \(s_{un}\), \(c^{(p)}_{u,k}\) and \(c^{(p)}_{k,v}\)
            \ENDFOR%end of n
        \ENDFOR%end of u
    \ENDFOR%end of i
    \FOR{iteration \(i=1:I_2\)}
        \FOR{\(t=1:T\)}
            \FOR{\(u\) in  user set \(U_t\)}
                \FOR{\(d\) = \(1: D_u\) }
                    \STATE{sample \(y_{ud}\) and \(z_{ud}\) by (\ref{timeUserTagLDAIVJointSamplingForY0Z}), (\ref{timeUserTagLDAIVJointSamplingForY1Z}) }
                    \IF{\(y_{ud}=0\)}
                        \STATE{update \(z_{ud}\), \(y_{ud}\), \(c^{(0)}_u\), \(c^{(0)}_{u,k}\), \(c^{(0)}_{k,v}\)}
                    \ELSE
                        \STATE{update \(z_{ud}\), \(y_{ud}\), \(c^{(1)}_u\), \(c^{(1)}_{t,k}\), \(c^{(1)}_{t,k,v}\)}
                    \ENDIF
                    \FOR{\(n\) in \(1,\cdots,N_{ud}\)}
                        \STATE{sample \(x_{udn}\) by (\ref{timeUserTagLDAIVsamplingX0}), (\ref{timeUserTagLDAIVsamplingX1}})
                        \IF{\(x_{udn}=0\)}
                            \STATE{update \(x_{udn}\), \(M^{\rho}_0\), \(c^{(B)}_v\)}
                        \ELSE
                            \STATE{update \(x_{udn}\), \(M^{\rho}_1\), \(c^{(0)}_{k,v}\), \(c^{(1)}_{t,k,v}\) }
                        \ENDIF
                    \ENDFOR%end of n
                \ENDFOR%end of d
            \ENDFOR%end of u
        \ENDFOR%end of t
    \ENDFOR%end of i
    \end{algorithmic}
\end{algorithm}

\subsection{Detecting Events from Normal States}
The state of attention of social issue k at time t in cyberspace is binary, namely at the peak or not at the peak. We denote it by hidden binary variable sk,t, which is 1 or 0. We do the inference for the hidden variable sk,t according to Poisson distribution according to Reference10,11. If the state of attention of social issue k at time t is "not at peak", then the probability density function is 
\(p([Ax_(k,t) ]|s_(k,t)=0)=e^(-μ_0 )  μ_0^([Ax_(k,t)])/([Ax_(k,t)]!)\) otherwise the probability density function is \(p([Ax_(k,t) ]|s_(k,t)=1)=e^(-μ_1 )  μ_1^([Ax_(k,t)])/([Ax_(k,t)])\)
In the above functions the symbol \(x_{k,t}\) denotes the attention of social issue k at time t , the symbol A denotes the constant, \(μ_0\) and \(μ_1\) represent the average of \([Ax_(k,t)]\) at peak and not at peak respectively. The state sk,t is inferred from \(ratio=p([Ax_(k,t) ]|s_(k,t)=0)/p([Ax_(k,t) ]|s_(k,t)=1) \).
In calculation, we use the log ratio to determine whether the attention is at peak as in equation (1). logratio>0 indicates that the attention of social issue k at time t is not at peak, otherwise at peak. As the attention xk,t is often between 0.01% and 5% in our experiment, we set the constant A in log ratio equation to be〖10〗^4。
	\(logratio=-(μ_0-μ_1 )+[Ax_(k,t)](log⁡μ_0 -log⁡μ_1)\)
After the data preprocessing, we get the air pollution state sequence\((a_t)_(t=1,…T)\) and the attention state sequence of each social issue \((s_(k,t))_(t=1,…,T;k=1…n)\), where T denotes the number of time windows.

\begin{algorithm}
\caption{Spectral Clustering Based Event Phrase Extraction}
\label{alg:eventKeywordsSearchMethod}
\KwIn{\(\mathcal{B}_{k,t},\mathcal{G}_{k,t},\tau\)}
\KwOut{\(\mathcal{C}_{k,t}\)}
\(n_{k,t}\)=number of connected component in \(\mathcal{G}_{k,t}\)\\
\For{\(n \in \{ n_{k,t}, \cdots, |\mathcal{G}_{k,t}|\}\) }{
    \(\mathcal{C}_{k,t}=SpectralClustering(\mathcal{G}_{k,t},n)\)\\
    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\tau\)}{
        return \(\mathcal{C}_{k,t}\)
    }
}
\end{algorithm}

\begin{figure}
\centering
\includegraphics[height=3cm]{img/wordClusterGraph.eps}
%todo
\caption{Hot words between the heat pattern forming word time window edge weight calculated by the PMI obtained between words, to obtain spectral clustering clustering clustering}
\label{fig: windowsBurstyWordGraph}
\end{figure}

\textbf{event} phrase Mining
% Refer to bursty.py
\ \ Microblogging mining events can be represented by a variety of ways, a single word, phrase, or topic.
Here we use the form of phrase, said event.
In this paper, the phrase indicates that the event is due to the fact that: the same period of time when there are multiple areas of internal hot words appear, a collection of hot words \(\mathcal{B}_{k, t} \) between the hot words great probability is interrelated. For example, observed "mac", "os", "lion" three words are in a state of emergency.
In fact, the state of emergency three words is to publish a new system "mac os lion" event caused by Apple, in order to find the association between words and events, we use spectral clustering based search methods.

As shown in Figure \ref{fig: windowsBurstyWordGraph} below, we will one area, a hot word of the time window and hot words between to diagram.
Hot words set \(\ mathcal {B}_{k, t} \) formed in FIG using \textbf{hot word graph} \(\mathcal {G}_{k, t} = (\mathcal{B}_{k, t}, \mathcal{E}_{k, t}) \) indicates,
\(\mathcal{E}_{k, t} = \{(a, b) | a \in \mathcal{B}_{k, t}, b \in \mathcal {B} _ {k, t }, PMI (\mathcal{D}_{k, t}, a, b)> 0 \} \), where \(PMI (\mathcal{D}_{k, t}, a, b) \) the field \(k \) time window \(t \) related microblog \(\ mathcal {D} _ {k, t} \) on the word \(a \) and the word \(b \) point metric information between each other.
% Refer to bursty.py getSimGraph () function

Given a field \(k \) and the time window \(t \), in which the number of events can not be determined in advance.
The two most extreme situations are: events coarse granularity, said the event is equal to the number of Figure \(\ mathcal {G} _ {k, t} \) in the number of connected components; events finer granularity display, event number equal to \(\ mathcal {G} _ {k, t} \) the number of points.
To do this, we use the Density to the degree of density of quantum graphs \(2 \#Edge / (\# Node \ cdot (\# Node-1)) \), the more the greater if the edge density in the range of Density in \((0,1] \).
Density can be a good indicator to determine the size indicates the event: too many unrelated phrases to put together an event can not be represented, too fine particle size, such as a single word can represent only part of the event; only in close co-occurrence of the phrase to a reasonable It indicates that the event granularity.
To this end, we have designed events phrase search algorithm \ ref {alg: eventKeywordsSearchMethod}: We try to find a reasonable number of spectral clustering Clustering \(n \), let \(n \) from a smaller value ( event corresponds to coarser granularity representation) to start the search, then the most likely cluster cluster size is too large, its performance is the clustering results in one or more small Density indicators; continue to increase the number of clusters \(n \), the event represents reduced size, reduced the size of clusters of clusters, thus making the Density index increases; when all cluster clustering Density indicators are larger than the threshold \(\tau \), the search terminates, returning clustering results \(\mathcal{C}_{k, t}\).
As the above process algorithm \ref{alg: eventKeywordsSearchMethod} description line 2 to line 5, we use in practice \(\tau = 0.6 \).
We call \(\mathcal{C}_{k, t} \) results in each cluster to cluster \textbf{event} phrase.

\textbf{detected events related to micro-blog}
\ \
By algorithm \ref{alg:eventKeywordsSearchMethod} find art \(k \) time window \ \(t \) within the \(| \mathcal{C}_{k, t} | \) events phrase later, you can also further find each event and the corresponding event phrase microblogging.
We looked at the first \(i \) events phrase \(\mathcal{C}_{k, t, i} \),
The phrase based on the number of elements distinguish the event, there are three situations: (1) the phrase event more than two hot words, he said while the event is not a phrase between any two words We have a very strong relationship between the co-occurrence, so just pay attention to the co-occurrence relationship stronger side; (2) event phrase has two hot words; (3) the event is only a hot word in the phrase.
Weibo text length is shorter, not all of the microblogging event will include the phrase \(\mathcal{C}_{k, t, i} \) in all the words.
Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\ mathcal {D} _ {k, t, i} \) in.
For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\ mathcal{D }_{k, t, i} \) in.
Ultimately, we can get the field \(k \) next time window \(t \) in the event the phrase relating to events microblogging \(\{(\mathcal{C}_{k, t, i}, \mathcal{D}_{k, t, i}) \}_{i=1}^{| \mathcal{C}_{k, t} |} \).

\section{Experiments}
\begin{figure}
        \centering
        \includegraphics[height=4.0cm]{img/pmi.pdf}
        \caption{History State Portion}
\end{figure}
\begin{table}
\centering
\caption{Normal State Training Performance}
\label{my-label}
\scalebox{0.8}{
    \begin{tabular}{|l|l|l|}
    \hline
    Model & History State & PMI \\ \hline
    LDA & None  & 1.265 \(\pm\) 0.013     \\ \hline
    BBTM\cite{Yan:2015wm} & None    & 1.467 \(\pm\) 0.017     \\ \hline
    NST\(^{(-)}\)   &   \begin{tabular}[c]{@{}l@{}}\footnotesize{Learned by LDA}\\ \footnotesize{from Wikipedia}\end{tabular} & 1.439 \(\pm\) 0.010     \\ \hline
    NST         & \begin{tabular}[c]{@{}l@{}}\footnotesize{Derived from Categories} \\\footnotesize{of Wikipedia}\end{tabular} & 1.523 \(\pm\) 0.017     \\ \hline
    \end{tabular}
}
\end{table}

\begin{table*}[ht]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|cc|cc|cc|cc|}
\hline
\multicolumn{2}{|c|}{\textit{Security}} & \multicolumn{2}{c|}{\textit{Vehicles}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Sport}} \\ 
\begin{tabular}[c]{@{}c@{}}History\\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} \\ \hline
Army & killed & aircraft & air & medical & weight & league & season \\ 
Battle & news & train & plane & patients & loss & season & win \\ 
military & \#libya & airport & flight & treatment & diet & club & team \\ 
Forces & libya & station & time & disease & pain & cup & deal \\ 
attacks & rebels & flight & ship & health & cancer & football & year \\ 
terrorist & people & pilot & news & brain & health & game & sign \\ 
troops & police & aviation & boat & cancer & lose & games & jagr \\ 
Killed & war & gear & airport & patient & tips & round & richards \\ 
soldiers & libyan & passenger & force & blood & treatment & championship & cup \\ 
commander & attack & drive & fly & body & fat & player & time \\ 
Front & u.s. & navigation & hurricane & clinical & hair & match & arsenal \\ 
Units & gaddafi & departure & navy & care & skin & division & fans \\ 
captured & army & takeoff & coast & surgery & body & win & nasri \\ 
campaign & forces & aviator & home & research & healthy & goals & city \\ 
fighting & pakistan & navigator & crash & type & surgery & teams & league \\ 
siege & afghanistan & runaway & irene & syndrome & blood & play & players \\ 
officers & military & departure & train & system & brain & stadium & player \\ 
guards & attacks & airbus & sea & medicine & acne & coach & signed \\ 
allied & troops & miles & aircraft & eye & diabetes & players & contract \\ 
lieutenant & dead & landing & jet & physician & eye & record & run \\ \hline
\end{tabular}
\end{table*}

\begin{table*}[ht]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|l|l|l|l|l|}
\hline
Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate(Duplicate \\ Event Rate)\end{tabular} \\ \hline
UMass System & 0.882 & 0.138 & 0.941 & 0. 071 \\ \hline
LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
BBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
Our Method & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
\end{tabular}
\end{table*}

\begin{table}[]
\centering
\caption{Twitter data set description}
\label{my-label}
\begin{tabular}{|l|r|}
\hline
Time range & \begin{tabular}[c]{@{}r@{}}2011/06/30\\ -2011/09/15\end{tabular} \\ \hline
Tweet number & 36,627,434 \\ \hline
Event number in Benchmark1 & 17 \\ \hline
Event number in Benchmark2 & 523 \\ \hline
\end{tabular}
\end{table}
% \begin{table}[]
% \centering
% \caption{My caption}
% \label{my-label}
% \begin{tabular}{|l|l|l|l|}
% \hline
% \multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Time \\ range\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Tweet \\ number\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Event number \\ in Benchmark1\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Event number \\ in Benchmark2\end{tabular}} \\ \hline
% \begin{tabular}[c]{@{}l@{}}2011/06/30-\\ 2011/09/15\end{tabular} & 36,627,434 & 17 & 523 \\ \hline
% \end{tabular}
% \end{table}

\begin{table*}[ht]
\centering
\caption{Events about \textit{vehicles} detected by systems between 2011-07-20 and 2011-07-30}
\label{my-label}
\begin{tabular}{|l|L{3cm}|l|c|}
\hline
\multicolumn{1}{|c|}{Date} & \multicolumn{1}{c|}{Event key words} & \multicolumn{1}{c|}{Representative event tweet} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Number of \\ event tweet\end{tabular}} \\ \hline
7/20/11 & \begin{tabular}[c]{@{}l@{}}American, Airlines, \\ order, planes\end{tabular} & \begin{tabular}[c]{@{}l@{}}NDTV: American Airlines orders 460 new planes from \\ Boeing, Airbus http://bit.ly/p1ZgYG\end{tabular} & 31 \\ \hline
7/23/11 & \begin{tabular}[c]{@{}l@{}}China, bullet, train, \\ collision\end{tabular} & \begin{tabular}[c]{@{}l@{}}China Bullet Train Collision: 33 Dead, 190 Injured \\ http://huff.to/qEq6Yx\end{tabular} & 67 \\ \hline
7/26/11 & \begin{tabular}[c]{@{}l@{}}Morocco, military, \\ plane, crash\end{tabular} & \begin{tabular}[c]{@{}l@{}}BBC News - Morocco military plane crash kills 78 \\ http://t.co/uwnLv8L\end{tabular} & 36 \\ \hline
7/27/11 & Air, Canada & \begin{tabular}[c]{@{}l@{}}Smoke in galley forces Air Canada flight back to airport. \\ Plane landed safely in Sydney, Australia after dumping fuel\end{tabular} & 48 \\ \hline
7/30/11 & \begin{tabular}[c]{@{}l@{}}Caribbean, Airlines, \\ crashes, Guyana\end{tabular} & \begin{tabular}[c]{@{}l@{}}Caribbean Airlines Jet Crash-Lands In Guyana All 163 \\ Passengers, Crew Survive http://t.co/qPVD3WJ\end{tabular} & 57 \\ \hline
\end{tabular}
\end{table*}

\begin{table*}[ht]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|l|L{3cm}|l|l|}
\hline
Date & Event key words & Representative event tweet & \begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular} \\ \hline
7/20/11 & \begin{tabular}[c]{@{}l@{}}Serbia, crimes, \\ fugitive, arrests\end{tabular} & Serbia: Serbia arrests last war crimes fugitive-TV- Reuters & 27 \\ \hline
7/20/11 & Somalia, famine & \begin{tabular}[c]{@{}l@{}}UN declares famine in Somalia. What can we do to save \\ 3.7million lives? http://bit.ly/r1Rq7R\end{tabular} & 89 \\ \hline
7/21/11 & \begin{tabular}[c]{@{}l@{}}U.S., military, \\accept, gay, \\lesbian, openly\end{tabular} & \begin{tabular}[c]{@{}l@{}}RT @cnnbrk: Pentagon is set to certify that the U.S. military \\ is prepared to accept openly gay and lesbian service members \\ \#dadt\end{tabular} & 20 \\ \hline
7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman...˙http://dlvr.it/cLbk8\end{tabular} & 557 \\ \hline
7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 \\ \hline
7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 25 \\ \hline
7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 20 \\ \hline
7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 \\ \hline
\end{tabular}
\end{table*}

\begin{figure*}
    \label{fig:algorithm}
    \includegraphics[width=1.0\textwidth]{img/screenShot.png}
\end{figure*}

\subsection{Data set}
Dataset
We conduct the empirical analysis on a twitter dataset which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}. 
Due to the developer policy of Twitter\footnote{https://dev.twitter.com/overview/terms/policy}, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{http://demeter.inf.ed.ac.uk/cross/docs/fsd\_corpus.tar.gz}.
We collect the tweets' contents according to the IDs with the help of Twitter API. 
The dataset contains 36,627,434 tweets which spans from 2011/06/30 to 2011/09/15.

Here we present the effectiveness of our proposed algorithm UMIETM and the efficiency of its online performance.
We evaluate the efficiency by perplexity, precision for event detection. 
We check the time cost and complete likelihood for efficiency.
% We are going to design the experiment to show the effectiveness of distinguishing user interests and events.
% Firstly, user profile can help to model user interests.
% In this experiment we compare to the baseline of user interest modeling\cite{sun2013serendipity}.
% Secondly, event detection can be enhanced by filtering out user interests.
%\subsection{Experiment Settings}
%We demonstrate our method can work very well on real dataset.

Weibo is a popular Chinese microblogging service\footnote{http://en.wikipedia.org/wiki/Sina\_Weibo/}.
We crawl weibo data by  its public API\footnote{http://open.weibo.com/} from Jan 2012 to Dec 2012.
To improve the quality of analyzing on tweets, we do necessary pre-processing: (1) splitting dataset by week, (2) segmenting Chinese words, (3) removing stop words and low frequency words whose document frequency in its time window is less than 3, (4) removing tweets whose token number is less than 3.
To model user interests better,  we remove users from dataset who has less than 2 hashtags in profile.
After pre-processing we get 252 thousand users, 16 million tweets and 251 million tweet tokens listed in Table \ref{statisticsOfDataset}.

We compare our model UMIETM with twitterLDA, timeUserLDA, Author-LDA, and our model's variant IETM.
Author-LDA combines the tweets posted by same author into a single document, then run standard LDA on the assembled tweets.
TwitterLDA is designed for topic modeling on twitter.
We compare with Author-LDA and TwitterLDA for confirming the significance of distinguishing user interests from events in microblog.
TimeUserLDA is designed for retrospective event detection in microblog, and considers to distinguish events from user interests.
We compare with timeUserLDA to show the impact of user profile.
The variant IETM (\textit{Interest and Event Topic Model}) models user's interests and events without the help of user profiles.
%UMIETM benifits from modeling user profiles.

%To demonstrate the necessary of user profiles, we compare it to its variant IETM (Interest and Event Topic Model) which only consider the tweets shown in figure \ref{fig:IETM}.
%IETM also run in online learning way.

We set the asymmetric \(\alpha\) and symmetric \(\beta=0.01\) for UMIETM, where \(\alpha\) will be optimized by Gibbs EM algorithm\cite{wallach2008structured}.
\(\alpha=0.1\), \(\beta=0.01\) are set for all remaining models. 
After cross validation we find that UMIETM and IETM perform best on \(K=90\) and \(E=30\), \(\kappa=0.01\).
To compare equally, we set the same topic number for Author-LDA, twitterLDA, timeUserLDA (which means when we run models offline on 1 time window, we shall set 120 topics for all, and 150 topics on 2 time windows and so on).

To verify the role of user profiles played, we set UMIETM(-) as the degradation of UMIETM, which take symmetric prior \(\alpha\).

In this subsection, we illustrate the performance of UMIETM in which user profile is considered.

\textbf{Quantitative Measure.}
We initialize UMIETM and IETM by batch learning on data from first week to third week, then run them in online learning way from fourth week to ninth week.
On each week we calculate their perplexities\cite{wallach2009evaluation}, where \(perplexity(D_{test})=\exp{\{-\frac{\sum_{u=1}^{U}\sum_{d=1}^{D_u}\log{p(w_{ud})}}{\sum_{u=1}^{U}\sum_{d=1}^{D_u}N_{ud}}\}}\) and \(p(w_{ud})=(1-\pi_u)\sum_{k=1}^{K}\theta_{uk}\prod_{n=1}^{N_{ud}}(\phi_{s,w_{udn}}(1-\rho)+\phi_{k,w_{udn}}\rho)+\pi_u \sum_{k=1}^{K}\eta_{t,k}\prod_{n=1}^{N_{ud}}(\phi_{s,w_{udn}}(1-\rho)+\phi_{k,w_{udn}}\rho)\).
The others are trained from first week to third week, and the held out perplexities are calculated on data from fourth week to ninth week.
TimeUserLDA and IETM's perplexities are smaller than User-LDA, twitterLDA as they both consider distinguishing user interests from events.

In Table \ref{tab:heldoutPerplexity} the perplexity of UMIETM is 3107.8, and much smaller than others. It demonstrates that user profile is significant for tweet stream's modeling.

In Table \ref{tab:metrics}, we evaluate the events detected by models. We asked the annotators to label the event with score 1, and non-event related topic as 0. 
The precision and recall is illustrated, where UMIETM(-) performs slightly better than IETM. 
And UMIETM outperforms UMIETM(-) in detecting high quality event. 
A reasonable analysis is that UMIETM uses the profile information sufficiently by asymmetric priors. 
In this way, we also prove that the well exploiting of user profile information is important to model user interests and events on tweets. 
%\subsubsection{Precision of Event Detection}

\textbf{Case Study} 
Some events detected by our UMIETM model are shown in Table \ref{fig:event}.
Comparing with UMIETM, timeUserLDA fails to discover the \textit{shoddy construction} event in the second week, while IETM reports this event as \textit{bi, women, elegant, adoption, engineering, reed}. Obviously IETM fails to distinguish this event from user interests.
UMIETM filters users' interests like \textit{bi, women, elegant, adoption} using their profile {\#baby, \#women}, and detect the event.
\subsection{Efficiency}
We implement our methods on mallet\footnote{http://mallet.cs.umass.edu/dist/mallet-2.0.7.tar.gz}, and run them on Linux server with 8 cores(2.00GHz) and 64GB memory.
In this subsection, we verify the convergence and online performance of our online learning algorithm.

\textbf{Convergence.}
The convergence of algorithm is vital in real time streaming environment. 
UMIETM needs several Gibbs sweeps to find out the optimal parameters of model.
But the size of data is usually large even spitted into time windows.
The time complexity of UMIETM is \(O(I_1K|P|+I_2K|W|+I_2E|W|)\) given in section \ref{subsec:online}.
It suggests that the more iterations Gibbs sampling have to do, the less efficiently our model performs. 
Fortunately UMIETM is very economic to its stable state and does not need so much iterations.
As suggested by \cite{wallach2009rethinking} and \cite{jian2014factorOfTopicModel}, we choose LDA with asymmetric priors as baseline, which is much more comparable than standard LDA on microblog dataset.
We run UMIETM on the first three time windows. 
Correspondingly we only use the tweets in these time windows for LDA with asymmetric priors.
Burn-in period is set to 20 and optimize interval also 20, which means the priors are optimized every 20 iterations as the red curve in Fig \ref{fig:completeLoglikelihood}.

One of the criteria for stopping Gibbs sampling is that the complete log likelihood is stabilized.
We stop UMIETM after 50 iterations since the complete log likelihood only increases 0.02\% in last iteration.
It will take LDA(asymmetric priors) 300 minutes to run 1000 iterations, and 20 minutes per 10 iterations for UMIETM.
There is a trade-off between the effectiveness by more iterations and efficiency by less,  we set the iteration number as 10 in online setting.
After 10 iterations the UMIETM's complete log likelihood will increase no more than 0.2\%.
% \subsubsection{Soundness}
% As the online learning for UMIETM is an approximated version of batch learning for UMIETM, the soundness should be confirmed before applying it in the real enviroment.
%[todo] We also want to show that online learning for UMIETM does not  sacrifice the accuracy. 
%Comapring the held out perplexity.

\textbf{Online Performance.}
%Figure \ref{fig:completeLoglikelihood} shows that the log likelihood increases less than 0.1\% after 12 iterations.
%Our experiment shows UMIETM has good convergence that the complete log likelihood increases less than 0.15\% after 10 iterations.
As verified in the above subsection \textit{Convergence}, we run 10 Gibbs sweeps for each time window in online learning phase.
When UMIETM is implemented in online way, it doesn't have to revisit the tweets in previous windows. 
So its time cost in each window is proportional to the data size of current window  as shown in Figure \ref{fig:onlinelearningResult}.
In average, online UMIETM can process five thousand tokens per second.
%Memory cost grows slightly and the increased memory cost only depends on the size of vocabulary.

LSH based event detection on microblogs is used by \cite{petrovic2010streaming},\cite{mccreadiescalable}. 
The former one detects events as the cluster of tweets by LSH, and the latter one extends this method on distributed machines. 
They both only use the cosine similarity without considering semantic meaning of words. 
So LSH based method may split the same event into clusters of similar tweets.
However LSH based method reports 10578 events in 7th time window, and 10901 events in 8th window. 
The other problem of LSH based event detection method is that the bad design may lead unstable performance. 
The tweets are mapped into LSH defined space in a skew way which is illustrated in Fig \ref{fig:onlinelearningResult}.
The other comparison is timeUserLDA which is designed for retrospective event detction. 
The purple line in Fig \ref{fig:onlinelearningResult} goes up straightly as timeUserLDA has to revisit previous tweets to make a decision whether the tweet is event related. 
The perplexity of online UMIETM on the 11 time window in Fig \ref{fig:onlinelearningResult} is \(3036.44\pm397.14\). 
And the average precision of detecting high quality event is 0.22.
Both indicators demonstrate that UMIETM can perform well in online learning way. 
\subsection{Application on Reddit}

\section{Conclusions \& Future Work}
Microbiolog is mixed with user interests and external events.
The quality of event detection in microblog depends on how we distinguish them.
We exploit user profile to discover events by filtering out user interest-related tweets.
We further treat the arriving data as stream and run the detection in online learning style.
The experiments demonstrates that our method is effective and efficient for online event detection in microblogs.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paperbib}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\end{document}

### 2016-06-08 paper/main.tex
add abstract

@@
 
-\title{Full History Info Enhanced Normal States Training for High Accuracy Event Detection}
+\title{Normal States Training for High Accuracy Event Detection}
 
@@
 \begin{abstract}
-In cyberspace, it is a very challenging task to detect events accurately due to its rapid changing nature.
-In our study, we find out the key to improve the accuracy lies in training the normal states well, which describe what happened and help to identify what is happening in cyberspace.
-Traditional methods underestimate the normal states due to the limited training data spanning over a few time windows.
-To overcome this limitation, we propose \textsc{FullReader}, a high accuracy event detection system that trains normal states better by using Wikipedia, which can be treated as an approximation of full history information source.
-In \textsc{FullReader}, 1) normal states are trained as topical word frequencies; 2) historical topical word frequencies are extracted from Wikipedia pages, categories, and their Topic-PageRank-HITS scores; 3) topical word frequencies of targeted corpus are updated incrementally by Asymmetric-Prior-LDA, using the history information as prior; 4) events are detected by monitoring the change of topical word frequencies.
-Experiments on the benchmark Edinburgh twitter corpus validate the effectiveness of our proposed \textsc{FullReader}.
+In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
+For humanbeing, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
+In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumalation of happened things.
+In \textsc{NSDetector}, 1) balanced for effectiveness and efficiency, normal states are trained as topical words and their frequencies; 2) historical topical word frequencies are initialized from knowledge base with chi-squared test; 3) topical word frequencies on targeted corpus are maintened by KB-Prior-LDA, using the normal states in knowledge base as prior; 4) events are detected by monitoring the change of topical word frequencies.
+Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
+And further experiments on \textit{reddit} and \textit{arXiv} also demonstrate that \textsc{NSDetector} can be easily adapted on other cyberspace datasets.
+%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.
 \end{abstract}
+
+%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.
 
@@
 
-\keywords{Full history info; normal states initialization and maintenance; event detection; text mining;}
+\keywords{normal states initialization and maintenance; event detection;}
 
@@
 
-\begin{figure*}[ht]
-    \centering
-    \subfigure[The first category methods\cite{Petrovic:2010uj}\cite{Wurzer:2015wq} utilize the history information appeared in an evolving training window; the second category\cite{Li2013JointEE}\cite{Nguyen2015EventDA} trains the normal states by the labeled data existed in a fixed time window.
-Our method intializes the normal states with full history info, and updates them incrementally.
-With normal states, systems detect events.]{
-                \label{fig:modelDesc:a} %% label for first subfigure
-                \includegraphics[height=7.4cm]{img/modelDescription.pdf}
-        }
-        \quad
-        \quad
-    \subfigure[\textsc{FullReader}'s process flow, taking \textbf{military} related events in cyberspace as an example.
-\textsc{FullReader} initializes the normal states as topical word frequencies from full history information about military, updates them further at the specific corpus day by day, and detects events finally.]{
-                \label{fig:modelDesc:b} %% label for first subfigure
+\begin{figure}
+    \label{fig:modelDesc}
     \includegraphics[height=7.0cm]{img/systemExample.pdf}
-        }    
-    \caption{Overview of how event detection systems use history information (left), and an example of our \textsc{FullReader} system process flow on how to detect the military related events (right).}
-    \label{fig:modelDesc}
-\end{figure*}
+    \caption{\textsc{NSDetector}'s process flow, taking \textbf{military} related events in cyberspace as an example.
+\textsc{FullReader} initializes the normal states as topical word frequencies from full history information about military, updates them further at the specific corpus day by day, and detects events finally.}
+\end{figure}
 
@@
 Compared with demographics information, user interests' modeling can be verified more easily \cite{faralli2015large}.
-
-  尽管文献[1]指出UMass[2] 是FSD任务中最为精确的方法，但由于在Event Detection任务中，the metric used in this method单纯的使用normalized topic weighted minimum cost并不能准确的反映出它能够很好的说明网络空间中的事件检测的准确性。其原因在于计算公式中缩小了CFa的值（一般默认的方法将miss与false alarm的cost的比值设置为10：1），因而传统的方法倾向于扩大召回率而牺牲了准确率。这样的做法在处理newswire信息时并没有太大不妥，原因在于newswire中检测出的novel story是事件的概率极大。而一般的网络空间中不仅仅包含新闻，而且覆盖了各方面的信息【参见Twevent中对twitter信息覆盖面的文献】。在此种情况下，即便是novelty story，也不一定代表了事件（具体的例子见Section实验部分）。进一步的，我们认为UMass在应用到一般的网络空间的事件检测的准确率不高的原因是UMass没有对网络空间的正常状态进行有效的训练。UMass[2]，LSH方法[3]，k-terms Hashing[1]使用聚类簇来表示cyberspace的正常状态，然而对于twitter这种覆盖面极广的社交媒体，聚类簇的方法总是不能穷尽所有正常状态。【这里的说法不是很强健】
-  与UMass，LSH，kterms等在向量空间或者在此基础上的哈希值进行聚类的方法不同，timeUserLDA[4]以及BBTM[5]对网络空间中的正常状态使用topic model进行刻画，将网络空间中的topics试图按照normal topics和bursty topics进行区分。该方法能够有效的检测到被人们广泛关注的bursty topics，这些bursty topics往往是我们需要我们检测的events的一部分。然而此类方法也有明显的缺陷，由于topic model使用对称的先验，因此其topic的规模倾向于相近的大小。然而人们在同一时间内对事件的关注度有限，事件受关注的程度也是趋向于power law分布的。这样，一些较小规模的事件不能被正确的检测出。因此，此类方法的特点是准确率高，但召回率低。进一步的究其本质，是timeUserLDA、BBTM等方法没有能够准确的训练网络空间的正常状态，较小的bursty event会被吸收进正常状态中。
-另一类方法是以EDCoW[6]为代表的对词频的正常状态进行训练的工作，判断the degree of burstiness of terms，然而cyberspace中常用词频率变化并不明显，因此由这类词构成的事件往往并不容易被检测到，这一结果也由[7]证实。
-与我们的工作最为相近的是Twevent[7]，Twevent采用三个阶段的方式进行：tweet segment, event segment detection, event segment clustering。
-Twevent 抽取tweet segment依赖于词典因而往往不能发现。。。
-正常状态训练部分的相关工作。
-Tedas[8], ESA[9], AIDR[10] 
-TwitterMonitor[11], EDCoW[6], TwitInfo[12], Twevent[7], Leadline[13], TwiCal[14], ESA[9], Redites[15]
 
@@
 \ \ Our theme modeling, want to learn the first \(k\) topics with Wikipedia Article \(k\) topics as close as possible, and we will be Wikipedia article \(k\) before 1000 words) was added to the theme of the word frequency word in the subject a priori distribution on the.
-Learning to be the first \(k\) Subject polynomial distribution of the word, referred to as \(\phi_k \), Wikipedia article \(k \) distribution of topics for \(\tau_k \), then this formalized process is expressed as: \(\ phi_k \sim Dir(\beta + \tau_k) \).
+Learning to be the first \(k\) Subject polynomial distribution of the word, referred to as \(\phi_k \), Wikipedia article \(k \) distribution of topics for \(\tau_k \), then this formalized process is expressed as: \(\ \phi_k \sim Dir(\beta + \tau_k) \).
 Formal presentation of the explanation is: With prior knowledge \(\tau_k \) after the theme \(\phi_k \) is no longer simply rely on symmetric priori \(\beta \), different words right is not the same weight , such as a discussion of "fashion" theme in Wikipedia, it will refer to "dress", "grand", "blue", "gold" and other words, with the asymmetric priori \(\beta + \tau_k \) after in microblogging "fashion" theme "dress" the proportion will be increased in this way so that microblogging corpus theme tends to Wikipedia topic.
@@
 \end{equation}
-
+\begin{comment}
 \begin{algorithm}[H]
@@
 \end{algorithm}
+\end{comment}
 
@@
 \hline
-\multicolumn{2}{|c|}{\textit{Security}} & \multicolumn{2}{c|}{\textit{Vehicles}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Sport}} \\ 
+\multicolumn{2}{|c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Sport}} \\ 
 \begin{tabular}[c]{@{}c@{}}History\\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} \\ \hline
@@
 \centering
-\caption{My caption}
+\caption{Events about \textit{military} detected by systems between 2011-07-20 and 2011-07-30}
 \label{my-label}
@@
     \includegraphics[width=1.0\textwidth]{img/screenShot.png}
+    \caption{An illustration of the time series of Military related states on Twitter dataset from 2011-06-30 to 2011-09-15.}
 \end{figure*}

### 2016-06-12 runDDLDA.sh
set model parameters

@@ -21,7 +21,7 @@ echo "vocabulary size is $vocabulary_size"
 
 #vocabulary_size=272472
 #wikiPortions="0 0.1 0.2 0.4 0.8 1.6 3.2 6.4 12.8 25.6 51.2"
-wikiPortions="3.2"
+wikiPortions="6.4"
 roundArray="0"
 for portion in ${wikiPortions}
 do 

### 2016-06-12 src/ietm/LDAWithPrior.java

@@ -19,6 +19,7 @@ import usertagmodel.PrintUtil;
 import usertagmodel.UserInstancePlus;
 import waleking.util.MyFile;
 import cc.mallet.types.Alphabet;
+import cc.mallet.types.Dirichlet;
 import cc.mallet.util.Randoms;
 
 import common.LogUtil;
@@ -32,7 +33,8 @@ import common.LogUtil;
 public class LDAWithPrior implements Serializable {
 	private static final long serialVersionUID = -3335514051631979791L;
 	// prior parameters
-	public double alpha = 0.1;
+	public double[] alpha;
+    public double alphaSum=0;
 	public double beta = 0.005;
 
 	// dataset related
@@ -63,6 +65,15 @@ public class LDAWithPrior implements Serializable {
 	 */
 	public transient Zu[][][] z;// \vec{z}_{t,u,d}
 	public transient Ndk[][][] ndk;// \vec{n}_{t,u,d}
+
+    /**
+     * statistics for hyper parmaters' estimation
+     */
+    private int maxTokenNums=0;
+    private transient int[] oneDocTopicCounts;//temporal histogram of topic related token's number
+    private transient int[] docLengthCounts; // histogram of document sizes
+    private transient int[][] topicDocCounts; // histogram of document/topic counts
+
 
 	/**
 	 * hidden topic of user's tweets
@@ -154,7 +165,7 @@ public class LDAWithPrior implements Serializable {
 			}
 			interestTokenPerTopic[k] = toInitIETM.interestTokenPerTopic[k];
 		}
-
+        //update prior knowledge from wiki.topics
 		String filename = "wiki.topics";
 		MyFile reader = new MyFile(filename, "r");
 		String line = reader.readln();
@@ -220,6 +231,9 @@ public class LDAWithPrior implements Serializable {
 				for (int d = 0; d < tweetNum; d++) {
 					ArrayList<Integer> tweet = userInstance.getTweets().get(d).tweetContent;
 					int tweetLength = tweet.size();
+                    if(tweetLength>maxTokenNums){
+                        maxTokenNums=tweetLength;
+                    }
 					this.z[t][u][d] = new Zu(tweetLength);
 					this.ndk[t][u][d] = new Ndk(this.topicNumber);
 
@@ -237,473 +251,541 @@ public class LDAWithPrior implements Serializable {
 			}// end of user
 
 		}// end of t (timeWindowList.size())
+        
 	}// end of randomAssighHiddenTopics
 
[…]

### 2016-06-12 wiki_topics.py

@@ -6,7 +6,11 @@ def loadFeatures(filename):
     d=dict()
     sum=0
     for line in open(filename,"r"):
-        word,chi2=line.strip().split("\t")
+        if("\t" in line):
+            word,chi2=line.strip().split("\t")
+        else:
+            word,chi2=line.strip().split(" ")
+
         chi2=float(chi2)
         sum=sum+chi2
         d[word]=chi2

### 2016-06-13 background_topics.py
add background.topics

@@ -1,0 +1,30 @@
+#generate background.topics from ~/git/wiki_processor/data/features/other_features.txt
+import os
+from operator import itemgetter
+
+def loadBackgroundFeatures(filename):
+    d=dict()
+    sum=0
+    for line in open(filename,"r"):
+        if("\t" in line):
+            word,chi2=line.strip().split("\t")
+        else:
+            word,chi2=line.strip().split(" ")
+
+        chi2=float(chi2)
+        sum=sum+chi2
+        d[word]=chi2
+
+    for word in d:
+        d[word]=d[word]/sum
+    return d
+
+
+
+backgroundTopicsFile=open("background.topics","w")
+d=loadBackgroundFeatures("../wiki_processor/data/features/other_features.txt")
+sortedWords=sorted(d.items(),key=itemgetter(1),reverse=True)
+for t in sortedWords:
+    word,score=t
+    backgroundTopicsFile.write("%s\t%s\n" % (word,score))
+backgroundTopicsFile.close()

### 2016-06-13 paper/main.tex
solve the problem of how to start the model

@@
 &p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha,\beta,\tau)\\
-&\ \ \propto \frac{n_{dk}+\alpha}{n_{d,.}+K\alpha}\frac{n_{kv}+\tau_{kv}+\beta}{n_{k,.}+\tau_{k,.}+V\beta}
+&\ \ \propto (n_{dk}+\alpha)\frac{n_{kv}+\tau_{kv}+\beta}{n_{k,.}+\tau_{k,.}+V\beta}
 \end{aligned}

### 2016-06-13 src/ietm/LDAWithPrior.java

@@ -40,6 +40,7 @@ public class LDAWithPrior implements Serializable {
 	// dataset related
 	public int tweetVSize = 0;
 	public int topicNumber = 0;
+    public int wikiTopicNumber=0;
 	public int userNumber = 0;
 	public int timeWindowNum = 0;
 
@@ -50,6 +51,8 @@ public class LDAWithPrior implements Serializable {
 
 	// user interest related
 	public int[][] iCkv;// c^{0}_{k,v}
+    //word vector
+    public double[][] wordVecs;
 
 	// additional prior knowledge
 	public double[][] tau;
@@ -142,7 +145,9 @@ public class LDAWithPrior implements Serializable {
 				"Before adding wikipedia's alphabet. size(alphabet)="
 						+ trainingData.tweetAlphabet.size());
 
-		buildWikiAlphabet(trainingData.tweetAlphabet);
+        //the alphabet of background.topics includes the alphabet of wiki.topics
+        String[] extraFilesForTopics=new String[]{"wiki.topics","background.topics"};
+		buildExtraAlphabet(extraFilesForTopics,trainingData.tweetAlphabet);
 
 		LogUtil.logger().info(
 				"After adding wikipedia's alphabet. size(alphabet)="
@@ -178,6 +183,9 @@ public class LDAWithPrior implements Serializable {
 			if (!line.equals("")) {
 				String[] array = line.split("\t");
 				int topicId = Integer.parseInt(array[0].split("topic")[1]);
+                if(topicId+1>this.wikiTopicNumber){
+                    this.wikiTopicNumber=topicId+1;
+                }
 				String word = array[1];
 				float prob = Float.parseFloat(array[2]);
 
@@ -213,11 +221,59 @@ public class LDAWithPrior implements Serializable {
 		return toInitIETM;
 	}
 
-	public void randomAssignHiddenTopics(TimeWindowListPlus timeWindows) {
-		// random assign tag's topic
-		double[] topicWeights = new double[this.topicNumber];
-		Arrays.fill(topicWeights, (double) 1 / (double) this.topicNumber);
 
+	/**
+	 * init toInitIETM by background.topics
+	 * 
+	 * @param toInitIETM
+	 * @param alphabet
+	 */
+	public LDAWithPrior initByWikiBackgroundTopics(LDAWithPrior toInitIETM,TimeWindowListPlus trainingData,float wikiWeight) {
+
+        //update prior knowledge from wiki.topics
[…]

### 2016-06-13 background_topics.py
remove background topics

@@ -1,30 +1,0 @@
-#generate background.topics from ~/git/wiki_processor/data/features/other_features.txt
-import os
-from operator import itemgetter
-
-def loadBackgroundFeatures(filename):
-    d=dict()
-    sum=0
-    for line in open(filename,"r"):
-        if("\t" in line):
-            word,chi2=line.strip().split("\t")
-        else:
-            word,chi2=line.strip().split(" ")
-
-        chi2=float(chi2)
-        sum=sum+chi2
-        d[word]=chi2
-
-    for word in d:
-        d[word]=d[word]/sum
-    return d
-
-
-
-backgroundTopicsFile=open("background.topics","w")
-d=loadBackgroundFeatures("../wiki_processor/data/features/other_features.txt")
-sortedWords=sorted(d.items(),key=itemgetter(1),reverse=True)
-for t in sortedWords:
-    word,score=t
-    backgroundTopicsFile.write("%s\t%s\n" % (word,score))
-backgroundTopicsFile.close()

### 2016-06-13 src/ietm/LDAWithPrior.java
set the model parameters

@@ -400,11 +400,16 @@ public class LDAWithPrior implements Serializable {
         }
     }
 
-    public String traceICkv() {
+    public String traceICkv(TimeWindowListPlus timeWindowList) {
         int topic = 0;
         StringBuffer sb = new StringBuffer();
-        for (int v = 0; v < 80; v++) {
+        for (int v = 0; v < 200; v++) {
             sb.append(this.iCkv[topic][v]).append(" ");
+        }
+        for (int v=0;v<200;v++) {
+            if(this.iCkv[topic][v]>0){
+               sb.append(timeWindowList.tweetAlphabet.lookupObject(v)).append(" ");
+            }
         }
         return sb.toString().trim();
     }
@@ -570,7 +575,7 @@ public class LDAWithPrior implements Serializable {
                 }// end of sampling tweet's topic
             }// end of sampling user u's information
         }// end of sampling time window t's information
-        LogUtil.logger().error(traceICkv());
+        LogUtil.logger().error(traceICkv(timeWindowList));
     }
 
     /**
@@ -725,7 +730,7 @@ public class LDAWithPrior implements Serializable {
         LDAWithPrior unInitedUserEventLDA = new LDAWithPrior();
         unInitedUserEventLDA.init(trainingData,
                 DefaultGlobalValueTweets.topicNum);
-        LogUtil.logger().error(unInitedUserEventLDA.traceICkv());
+        LogUtil.logger().error(unInitedUserEventLDA.traceICkv(trainingData));
 
         LDAWithPrior userEventLDA = unInitedUserEventLDA.initByWikipedia(
                 unInitedUserEventLDA, trainingData, wikiWeight);
@@ -735,7 +740,7 @@ public class LDAWithPrior implements Serializable {
         userEventLDA.updateWordVecs(isInit,trainingData);
         userEventLDA.randomAssignHiddenTopics(trainingData);
 
-        LogUtil.logger().error(userEventLDA.traceICkv());
+        LogUtil.logger().error(userEventLDA.traceICkv(trainingData));
 
         long start = System.currentTimeMillis();
         for (int i = 0; i < DefaultGlobalValueTweets.trainIterationNum; i++) {

### 2016-06-14 paper/main.tex
add tikz files

@@
 
-\section{Method}
+\section{Proposed Method}
+\subsection{Initialization of Normal States}
 \textbf{User profile.} User usually describes herself or himself by a piece of short text on microblog platform.
@@
 \left\{ \begin{aligned}
-W \frac{n_{kv}}{\sum_{v\in S_{kv}}n_{kv}} &,v\in S_{k} \\
+W \frac{f_{kv}}{\sum_{v\in S_{kv}}f_{kv}} &,v\in S_{k} \\
 0&,v \notin S_{k}\\
@@
 As shown in Figure \ref{fig: windowsBurstyWordGraph} below, we will one area, a hot word of the time window and hot words between to diagram.
-Hot words set \(\ mathcal {B}_{k, t} \) formed in FIG using \textbf{hot word graph} \(\mathcal {G}_{k, t} = (\mathcal{B}_{k, t}, \mathcal{E}_{k, t}) \) indicates,
+Hot words set \(\ mathcal{B}_{k, t} \) formed in FIG using \textbf{hot word graph} \(\mathcal {G}_{k, t} = (\mathcal{B}_{k, t}, \mathcal{E}_{k, t}) \) indicates,
 \(\mathcal{E}_{k, t} = \{(a, b) | a \in \mathcal{B}_{k, t}, b \in \mathcal {B} _ {k, t }, PMI (\mathcal{D}_{k, t}, a, b)> 0 \} \), where \(PMI (\mathcal{D}_{k, t}, a, b) \) the field \(k \) time window \(t \) related microblog \(\ mathcal {D} _ {k, t} \) on the word \(a \) and the word \(b \) point metric information between each other.

### 2016-06-14 paper/model/lda_tikz.tex
add tikz files

\documentclass{standalone}

%\url{}
\usepackage{tikz}
\usepackage{comment}
\usepackage{bm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makeatletter
\def\grd@save@target#1{%
  \def\grd@target{#1}}
\def\grd@save@start#1{%
  \def\grd@start{#1}}
\tikzset{
  grid with coordinates/.style={
    to path={%
      \pgfextra{%
        \edef\grd@@target{(\tikztotarget)}%
        \tikz@scan@one@point\grd@save@target\grd@@target\relax
        \edef\grd@@start{(\tikztostart)}%
        \tikz@scan@one@point\grd@save@start\grd@@start\relax
        \draw[minor help lines] (\tikztostart) grid (\tikztotarget);
        \draw[major help lines] (\tikztostart) grid (\tikztotarget);
        \grd@start
        \pgfmathsetmacro{\grd@xa}{\the\pgf@x/1cm}
        \pgfmathsetmacro{\grd@ya}{\the\pgf@y/1cm}
        \grd@target
        \pgfmathsetmacro{\grd@xb}{\the\pgf@x/1cm}
        \pgfmathsetmacro{\grd@yb}{\the\pgf@y/1cm}
        \pgfmathsetmacro{\grd@xc}{\grd@xa + \pgfkeysvalueof{/tikz/grid with coordinates/major step}}
        \pgfmathsetmacro{\grd@yc}{\grd@ya + \pgfkeysvalueof{/tikz/grid with coordinates/major step}}
        \foreach \x in {\grd@xa,\grd@xc,...,\grd@xb}
        \node[anchor=north] at (\x,\grd@ya) {\pgfmathprintnumber{\x}};
        \foreach \y in {\grd@ya,\grd@yc,...,\grd@yb}
        \node[anchor=east] at (\grd@xa,\y) {\pgfmathprintnumber{\y}};
      }
    }
  },
  minor help lines/.style={
    help lines,
    step=\pgfkeysvalueof{/tikz/grid with coordinates/minor step}
  },
  major help lines/.style={
    help lines,
    line width=\pgfkeysvalueof{/tikz/grid with coordinates/major line width},
    step=\pgfkeysvalueof{/tikz/grid with coordinates/major step}
  },
  grid with coordinates/.cd,
  minor step/.initial=.2,
  major step/.initial=1,
  major line width/.initial=2pt,
}

\makeatother
\begin{document}
\begin{tikzpicture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%coordination system below
\begin{comment}
\draw[help lines,step=.2] (-2,-2) grid (7,4);
\draw[help lines,line width=.6pt,step=1] (-2,-2) grid (7,4);
\foreach \x in {-2,-1,0,1,2,3,4,5,6,7}
 \node[anchor=north] at (\x,-2) {\x};
\foreach \y in {-2,-1,0,1,2,3,4}
 \node[anchor=east] at (-2,\y) {\y};
\end{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%your code below
\node (u) at (-1.2,0) [circle, draw, inner sep=0pt, minimum size=0.8cm] {\bm{$u$}};
\node (m) at (0,0) [circle, draw, inner sep=0pt, minimum size=0.8cm] {\bm{$m$}};
\node (theta) at (1.5,0) [circle, draw, inner sep=0pt, minimum size=0.8cm] {\bm{$\theta_d$}};
\node (z) at (3,0) [circle, draw, inner sep=0pt, minimum size=0.8cm] {$z_{dn}$};
\node (w) at (4.5,0) [fill=gray!30,circle, draw, inner sep=0pt, minimum size=0.8cm] {$w_{dn}$};

\node (alpha) at (0,1.5) [circle, draw, inner sep=0pt, minimum size=0.8cm] {$\alpha$};
\node (b) at (1.5,1.5) [circle, draw, inner sep=0pt, minimum size=0.8cm] {\bm{$\beta$}};
\node (phi) at (3,1.5) [circle, draw, inner sep=0pt, minimum size=0.8cm] {\bm{$\phi_k$}};
\node (tau) at (4.5,1.5) [fill=gray!30,circle, draw, inner sep=0pt, minimum size=0.8cm] {\bm{$\tau_k$}};

\draw[->] (alpha) -- (m);
\draw[->] (u) -- (m);
\draw[->] (m) -- (theta);
\draw[->] (b.east) -- (phi.west);

\draw[->] (theta.east) -- (z.west);
\draw[->] (z.east) -- (w.west);
\draw[->] (phi) -- (w);
\draw[->] (tau.west) -- (phi.east);

%D related
\draw (0.8,-.8) rectangle (5.8,.8);

%N related
\draw (2.2,-.6) rectangle (5.4,0.6);

%K related
\draw (2.2,1) rectangle (5.4,2);

\node at (5.6,-.6) {\scriptsize $D$};
\node at (5.1,-.4) {\scriptsize $N_d$};
\node at (5.1,1.2) {\scriptsize $K$};
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{tikzpicture}

\end{document}

### 2016-06-16 paper/ieeeFormat.tex
add ieee format version

--- 2016-06-14 paper/main.tex
@@
 
-\documentclass{sig-alternate-05-2015}
+%\documentclass{sig-alternate-05-2015}
+\documentclass[conference,compsoc]{IEEEtran}
+\usepackage{comment}
 \usepackage{subfigure}
@@
 \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
-\usepackage{algorithm}
-\usepackage{algorithmic}
+%\usepackage{algorithm}
 \usepackage{bm}
+\usepackage{graphics}
+\usepackage{graphicx}
+\usepackage{amsmath} 
+\usepackage{amssymb}
 
@@
 
-%\makeatletter
-%\def\@copyrightspace{\relax}
-%\makeatother
-
 \begin{document}
 
-% Copyright
-\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-%\doi{10.475/123_4}
-\doi{**.***/***}
-
-% ISBN
-%\isbn{123-4567-24-567/08/06}
-\isbn{***-****-**-***/**/**}
-
-%Conference
-%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
-
-%\acmPrice{\$15.00}
-
-%
-% --- Author Metadata here ---
-%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
-% --- End of Author Metadata ---
-
 \title{Normal States Training for High Accuracy Event Detection}
-
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-\begin{comment}
-\numberofauthors{8} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-\alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
-% 2nd. author
-\alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
-% 3rd. author
-\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Lawrence P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
-       \email{lleipuner@researchlabs.org}
-% 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
-}
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-\date{30 July 1999}
-\end{comment}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
 
@@
 In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
-For humanbeing, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
-In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumalation of happened things.
-In \textsc{NSDetector}, 1) balanced for effectiveness and efficiency, normal states are trained as topical words and their frequencies; 2) historical topical word frequencies are initialized from knowledge base with chi-squared test; 3) topical word frequencies on targeted corpus are maintened by KB-Prior-LDA, using the normal states in knowledge base as prior; 4) events are detected by monitoring the change of topical word frequencies.
+For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
+In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things.
+%TODO
+In \textsc{NSDetector}, 1) balanced for effectiveness and efficiency, normal states are trained as topical words and their chi-squared scores, and initialized by knowledge base; 2) topical word frequencies on targeted corpus within the time window are learned by NS-Prior-LDA, using the normal states as prior; 3) events are detected by monitoring the change of topical word frequencies; 4) normal states are further maintained by detected events incrementally.
 Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
-And further experiments on \textit{reddit} and \textit{arXiv} also demonstrate that \textsc{NSDetector} can be easily adapted on other cyberspace datasets.
+And further experiments on \textit{reddit} also demonstrate that \textsc{NSDetector} can be easily adapted on other cyberspace datasets.
 %\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.
@@
 %\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>  
-\end{CCSXML}
-
-\ccsdesc{Mathematics of computing~Bayesian computation}
-\ccsdesc{Mathematics of computing~Gibbs sampling}
-\ccsdesc{Information systems ~ Data analytics}
-\ccsdesc{Information systems ~Data stream mining}
-
-%
-% End generated code
-%
-
-%
-%  Use this command to print the description
-%
-\printccsdesc
-
-% We no longer use \terms command
-%\terms{Theory}
-
-\keywords{normal states initialization and maintenance; event detection;}
 
@@
     \label{fig:modelDesc}
-    \includegraphics[height=7.0cm]{img/systemExample.pdf}
+    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
     \caption{\textsc{NSDetector}'s process flow, taking \textbf{military} related events in cyberspace as an example.
@@
 \section{Proposed Method}
+\begin{algorithm}
+\caption{Overview of \textsc{NSDetector}}
+\label{alg:overviewNSDetector}
+\KwIn{Knowledge Base's structure \(G^{(0)}\), \(G^{(1)}\), and content \(G^{(2)}\), }
+\KwOut{Events}
+\(n_{k,t}\)=number of connected component in \(\mathcal{G}_{k,t}\)\\
+\For{\(n \in \{ n_{k,t}, \cdots, |\mathcal{G}_{k,t}|\}\) }{
+    \(\mathcal{C}_{k,t}=SpectralClustering(\mathcal{G}_{k,t},n)\)\\
+    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\tau\)}{
+        return \(\mathcal{C}_{k,t}\)
+    }
+}
+\end{algorithm}
+
 \subsection{Initialization of Normal States}
@@
 \subsection{Normal States' Initialization}
+\begin{algorithm}
+\caption{Normal States' Initialization from Knowledge Base}
+\label{alg:normalStatesInit}
+\KwIn{Taxonomy's Directed Acyclic Graph \(G^{(0)}\), Category-Page Bipartite Graph \(G^{(1)}\), Page-Content Bipartite Graph \(G^{(2)}\), topic related category node \(c\)}
+\KwOut{Normal states \(\bm{f}_c\) on topic \(c\)}
+\(Pages(c)\leftarrow \varnothing\)\\
+\(SuccessorNodes(c) \leftarrow \) Breadth-first-search(\(G^{(0)},c\))\\
+\For{\(node \in SuccessorNodes(c)\)}{
+    \(Pages(c) \leftarrow Pages(c) \cup G^{(1)}.neighbours(node)\)\\
+}
+\(WordFrequencyTable(c) \leftarrow \) do word count on the text contents of \(Pages(c)\) \\
+\(WordFrequencyTable(All) \leftarrow \) do word count on the text contents of all pages in \(G^{(2)}\).\\
+\For{word \(w\) in WordFrequencyTable(All).keys()}{
+    \(\tau_{c,w} \leftarrow \) \(w\)'s chi-square score on \(WordFrequencyTable(c)\) and \(WordFrequencyTable(All)\).
+}
+\Return{\(\bm{f}_c\)}
+\end{algorithm}
+
+\cite{faralli2015large} propose the Twixonomy Graph.
+
 %TODO
@@
     \centering
-    \includegraphics[width=1.0\columnwidth]{img/normalStatesFromHistoryInfo.pdf}  
+    \includegraphics[width=1.0\columnwidth]{img/initializationExample.pdf}  
     \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
@@
 
-\textbf{HITS step.}
-After the above step, we obtain PageRank scores for either queries or candidate replies.
-To propagate such information to the other side in the query-reply bipartite graph, we perform another random walk with links between queries and replies representing the structural information of hubs and authorities.
-%To incorporate prior information (obtained in the PageRank step) of queries and replies, we adopt a HITS variant in \citeauthor{deng2009generalized}~\shortcite{deng2009generalized}, called Co-HITS.
-
-Formally, the bipartite graph $G=(V,E)$ has vertexes  $V=\{V_q \cup V_r\}$, where $V_q$ are queries and $V_r$ are replies.
-We define the weight matrix by a relevance scoring function $\phi(q,r)$ between queries and replies.
-$\phi(\cdot,\cdot)$ was learned via a \textit{learning-to-rank} model similar to ~\shortcite{burges2005learning} with rich features including textual similarity, translation models, as well as {\tt word2vec} word embeddings \cite{mikolov2013distributed}.
-In other words, $\phi(\cdot,\cdot)$ returns the relatedness between a query and a reply in the range $(0,1)$.
-
-Moreover, since we would like to make use of PageRank scores for queries or replies, the HITS links are judged by not only the static relevance score $\phi(\cdot,\cdot)$, but also the information given by PageRank.
-To be concrete, the (unnormalized) weight matrix is given by either
-\begin{equation}
-\text{\quad \quad\quad\quad\!}\tilde{\mathbf W}_{ij} = \phi(q_i, r_j)\cdot q_i\quad\quad\quad\text{(query$\rightarrow$reply)}
-\label{eqn:w1}
-\end{equation}
-\begin{equation}
-\text{or\quad\quad\quad} \tilde{\mathbf W}_{ij} = \phi(r_i, q_j)\cdot {r}_i\quad\quad\quad\text{(reply$\rightarrow$query)}
-\label{eqn:w2}
-\end{equation}
-Here, $q_i$ and $r_i$ are the \textit{i}-th element in the vectors $\mathbf q$ and $\mathbf r$, which are obtained in the PageRank phase by Equations~\ref{eqn:pagerank1}--\ref{eqn:pagerank2}.
-If information is propagated from queries to replies, we use the former equation for weight update, and \textit{vice versa}.
-
-The mutual-reinforcing relationship of hub and authority scores can be expressed in matrix representation as follows.
-\begin{align}
-\mathbf{x}^{(i+1)} &= \alpha_x\cdot \big[\tilde{\mathbf W}\big]\,\mathbf{y}^{(i)}+(1-\alpha_x)\cdot \hat{\mathbf{x}}\label{eqn:HITS2}\\
-\mathbf{y}^{(i+1)} &= \alpha_y\cdot \left[\big[\tilde{\mathbf W}\big]^\top\right]\mathbf{x}^{(i)}+(1-\alpha_y)\cdot\hat{\mathbf{y}} \label{eqn:HITS1}
-\end{align}
-where $\mathbf x$ is query scores, $\mathbf y$ reply scores; superscripts denote the number of local iterations in HITS update.
-Each column of the weights is normalized to be a valid probability.
-Moreover, to compute the weight for $\mathbf{y}$, the matrix $\mathbf{\tilde W}^\top$ should be first row-normalized (given by $[\mathbf{\tilde W}]^\top$); otherwise, the effect of the prior $q_i$ in Equation~\ref{eqn:w1} is ruled out by column normalization.
-Notice that the transition matrix is fixed in one step of HITS, but they may also change as our algorithm proceeds like the PageRank step.
-
 \subsection{Normal States' Maintenance}
-Asymmetric-Prior-LDA
+KB-Prior-LDA
 \begin{figure}[t]
     \centering
-    \includegraphics[height=3.5cm]{img/NTS.eps}
+    \includegraphics[width=1.0\columnwidth]{model/lda_tikz.pdf}
     \caption{Probabilistic model for training normal states by using history information.}
@@
 
-\begin{enumerate}[noitemsep]
-    \item for each topic \(k \in \{1,\cdots,K\}\)，
-    \begin{enumerate}
-        \item word distribution on the topic \(\phi_k \sim Dirichlet(\beta+\tau_k)\).
-    \end{enumerate}
-    \item for each document \(d \in D\)，
-    \begin{enumerate}
-        \item topic distribution on the document \(\theta_d \sim Dir(\alpha)\)
-        \item for each word index \(n \in \{1,\cdots,N_d\}\)，
-        \begin{enumerate}
-            \item word's topic assignment \(z_{dn} \sim Multinomial(\theta_d)\)，
-            \item word \(w_{dn} \sim Multinomial(\phi_{z_{dn}})\)
-        \end{enumerate}
-    \end{enumerate}
-\end{enumerate}
+\begin{table}[!htbp]
+\begin{tabular}{l}
+1. Draw corpus prior distribution \(\bm{m} \sim Dir(\alpha \bm{u})\), where \(\bm{u}\)\\
+ \ \ \ \ is the uniform distribution. \\
+2. For each topic \(k \in \{1,\cdots,K\}\),\\
+\ \ \ \ (a) word distribution on the topic \(\bm{\phi_k} \sim Dir(\bm{\beta}+ \bm{\tau_k})\). \\
+
+3. For each document index \(d \in \{1,...,D\}\), \\
+\ \ \ \ (a) topic distribution on the document \(\theta_d \sim Dir(\bm{m})\), \\
+\ \ \ \ (b) for each word index \(n \in \{1,\cdots,N_d\}\),\\
+\ \ \ \ \ \ \ \ i. word's topic assignment \(z_{dn} \sim Multinomial(\theta_d)\), \\
+\ \ \ \ \ \ \ \ ii. word \(w_{dn} \sim Multinomial(\phi_{z_{dn}})\). \\
+\end{tabular}
+\end{table}
 
@@
 \left\{ \begin{aligned}
-W \frac{f_{kv}}{\sum_{v\in S_{kv}}f_{kv}} &,v\in S_{k} \\
-0&,v \notin S_{k}\\
+\lambda \frac{f_{kv}}{\sum_{v\in S_{kv}}f_{kv}} &,v\in S_{k}\ and  \ k \leq K_{\bm{KB}} \\
+0&,v \notin S_{k} \ or \ k > K_{\bm{KB}} \\
 \end{aligned}\right.
@@
 \begin{equation}
-\label{eq:LDAgibbs}
+\label{eq:initProbability}
+\begin{aligned}
+\hat{q}_{k|v}=
+\left\{ \begin{aligned}
+\frac{\tau_{kv}}{\sum_{k=1}^{K}\tau_{kv}} &,\sum_{k}\tau_{kv}>0 \\
+0&, \sum_{k}\tau_{kv}=0 \ and \ k \leq K_{\bm{KB}} \\
+1/(K-K_{\bm{KB}})&,\sum_{k}\tau_{kv}=0 \ and \ k > K_{\bm{KB}}
+\end{aligned}\right.
+\end{aligned}
+\end{equation}
+
+\begin{equation}
+\label{eq:KBPriorLDAgibbs}
 \begin{aligned}
 &p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha,\beta,\tau)\\
-&\ \ \propto (n_{dk}+\alpha)\frac{n_{kv}+\tau_{kv}+\beta}{n_{k,.}+\tau_{k,.}+V\beta}
+&\ \ \propto (n^{(d)}_{dk}+\alpha m_k)\frac{n^{(w)}_{kv}+\tau_{kv}+\beta}{n^{(w)}_{k,.}+\tau_{k,.}+V\beta}
 \end{aligned}
 \end{equation}
-\begin{comment}
-\begin{algorithm}[H]
-    \caption{UPIETM batch learning algorithm} %title
-    \label{alg:UPIETMbatch} %label
-    \begin{algorithmic}[1] %this 1 means the showing of line number in algorithm
-    \STATE initiate the topic label and the statistics
-    \FOR {\(i=1:I_1\)}
-        \FOR{\(u\) in  user set U}
-            \FOR{\(n\) = \(1:P_u\)}
-                \STATE sample profile's hidden topic \(s_{un}\) by (\ref{timeUserTagLDAIVsamplingForS})
-                \STATE update \(s_{un}\), \(c^{(p)}_{u,k}\) and \(c^{(p)}_{k,v}\)
-            \ENDFOR%end of n
-        \ENDFOR%end of u
-    \ENDFOR%end of i
-    \FOR{iteration \(i=1:I_2\)}
-        \FOR{\(t=1:T\)}
-            \FOR{\(u\) in  user set \(U_t\)}
-                \FOR{\(d\) = \(1: D_u\) }
-                    \STATE{sample \(y_{ud}\) and \(z_{ud}\) by (\ref{timeUserTagLDAIVJointSamplingForY0Z}), (\ref{timeUserTagLDAIVJointSamplingForY1Z}) }
-                    \IF{\(y_{ud}=0\)}
-                        \STATE{update \(z_{ud}\), \(y_{ud}\), \(c^{(0)}_u\), \(c^{(0)}_{u,k}\), \(c^{(0)}_{k,v}\)}
-                    \ELSE
-                        \STATE{update \(z_{ud}\), \(y_{ud}\), \(c^{(1)}_u\), \(c^{(1)}_{t,k}\), \(c^{(1)}_{t,k,v}\)}
-                    \ENDIF
-                    \FOR{\(n\) in \(1,\cdots,N_{ud}\)}
-                        \STATE{sample \(x_{udn}\) by (\ref{timeUserTagLDAIVsamplingX0}), (\ref{timeUserTagLDAIVsamplingX1}})
-                        \IF{\(x_{udn}=0\)}
-                            \STATE{update \(x_{udn}\), \(M^{\rho}_0\), \(c^{(B)}_v\)}
-                        \ELSE
-                            \STATE{update \(x_{udn}\), \(M^{\rho}_1\), \(c^{(0)}_{k,v}\), \(c^{(1)}_{t,k,v}\) }
-                        \ENDIF
-                    \ENDFOR%end of n
-                \ENDFOR%end of d
-            \ENDFOR%end of u
-        \ENDFOR%end of t
-    \ENDFOR%end of i
-    \end{algorithmic}
+
+\begin{algorithm}
+\caption{NS-Prior-LDA Learning Algorithm}
+\label{alg:gibbsSamplingKBPriorLDA}
+\KwIn{Document sequences \(\bm{w_{1:D}}\), and normal states \(\bm{f}_{1:K_{\bm{KB}}}\)}
+\KwOut{The sufficient statistics \(\bm{n^{(d)}}\), \(\bm{n^{(w)}}\)}
+\medskip
+\tcc{Initialization of NS-Prior-LDA Learning}
+\For{\(d=1:D\)}{
+    \For{\(n=1:N_d\)}{
+        \(v=w_{dn}\), sample \(z_{dn}=k\) accroding to Eq(\ref{eq:wikiPrior})(\ref{eq:initProbability}).\\
+        Update the sufficient statistics \(n^{(d)}_{d,k}\), \(n^{(w)}_{k,v}\).\\
+            }
+        }
+\medskip
+\For{\(i= 1:I\)}{
+    \tcc{E-Step of NS-Prior-LDA Learning}
+    \For{\(i=1:I_E\)}{
+        \For{\(d=1:D\)}{
+            \For{\(n=1:N_d\)}{
+                Set \(v=w_{dn}\), and reset the sufficient statistics \(n^{(d)}_{d,z_{dn}}\), \(n^{(w)}_{z_{dn},v}\).\\
+                Resample \(z_{dn}=k\) accroding to Eq(\ref{eq:wikiPrior})(\ref{eq:KBPriorLDAgibbs}).\\
+                Update the sufficient statistics \(n^{(d)}_{d,k}\), \(n^{(w)}_{k,v}\).\\
+            }
+        }
+    }
+    \medskip
+    \tcc{M-Step of NS-Prior-LDA Learning}
+    Optimize \(\alpha \bm{m}\) by the fixed-point iteration\cite{wallach2008structured}. 
+}
+\Return{\(\bm{n^{(d)}}\), \(\bm{n^{(w)}}\)}
 \end{algorithm}
-\end{comment}
+
+\cite{wallach2008structured}\footnote{\url{https://github.com/mimno/Mallet/blob/master/src/cc/mallet/types/Dirichlet.java}}
 

### 2016-06-17 paper/ieeeFormat.tex
I.1

@@
-% This is "sig-alternate.tex" V2.1 April 2013
-% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
-%
-% This example file demonstrates the use of the 'sig-alternate.cls'
-% V2.5 LaTeX2e document class file. It is for those submitting
-% articles to ACM Conference Proceedings WHO DO NOT WISH TO
-% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
-% The 'sig-alternate.cls' file will produce a similar-looking,
-% albeit, 'tighter' paper resulting in, invariably, fewer pages.
-%
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V2.5) produces:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) NO page numbers
-%
-% as against the acm_proc_article-sp.cls file which
-% DOES NOT produce 1) thru' 3) above.
-%
-% Using 'sig-alternate.cls' you have control, however, from within
-% the source .tex file, over both the CopyrightYear
-% (defaulted to 200X) and the ACM Copyright Data
-% (defaulted to X-XXXXX-XX-X/XX/XX).
-% e.g.
-% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
-% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
-%
-% ---------------------------------------------------------------------------------------------------------------
-% This .tex source is an example which *does* use
-% the .bib file (from which the .bbl file % is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission, you *NEED* to 'insert'
-% your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% ================= IF YOU HAVE QUESTIONS =======================
-% Questions regarding the SIGS styles, SIGS policies and
-% procedures, Conferences etc. should be sent to
-% Adrienne Griscti (griscti@acm.org)
-%
-% Technical questions _only_ to
-% Gerald Murray (murray@hq.acm.org)
-% ===============================================================
-%
-% For tracking purposes - this is V2.0 - May 2012
-
-%\documentclass{sig-alternate-05-2015}
 \documentclass[conference,compsoc]{IEEEtran}
@@
 %\usepackage{algorithm}
-\usepackage{bm}
+\usepackage{bm}%used for bm
 \usepackage{graphics}
 \usepackage{graphicx}
-\usepackage{amsmath} 
-\usepackage{amssymb}
+\usepackage{amsmath} %used for maths symbols
+\usepackage{amssymb}%used for empty set symbol
+
+%used for quotes
+\usepackage{epigraph}
+\setlength\epigraphwidth{\columnwidth}
+\setlength\epigraphrule{0pt}
 
@@
 \section{Introduction}
-Improving the accuracy of event detection in cyberspace can benefit many tasks, but it's nontrivial due to the rapid changing nature of cyberspace.
+%\textit{``To study the abnormal is the best way of understanding the normal."}---William James
+%\textit{``The unpredictable or the rare is more newsworthy than the routine."}---Allan Bell
+
+%The event detection task always tries to find out the newsworthy messages from cyberspace. 
+With the increasing of cyberspace data nowadays, there is a growing need for detecting events accurately.
+Detecting events can mainly benifit the following three folds: (1) understanding what happened in the corpus without checking every single document manually, and generating the timeline to get a bird's eye view of the corpus\cite{ge2015bring}; (2) being aware what is happening currently, which helps to deal with emergencies\cite{hughes2009twitter}\cite{sakaki2010earthquake}; (3) adding detected events and their types as extra structured data information to organize the unstructured text corpus\cite{ritter2012open}.
 
@@
 We suppose that the ideal event detection system performs like a journalist who can find news from cyberspace with the knowledge of the normal states.
+
+They build the normal states in the evolving training window
+%TODO
+
+They are hamppered by the rapid changing nature of cyberspace, e.g. twitter and reddit(\textit{find out the sentences to describe the rapid changing nature}).
+
+It is hard to handle all the cyberspace data by using limited computing resources. As a result, it have to make a trade off, only to process part of them, instead of using the whole data.
+
+In this paper, we demonstrate that the better normal states  are learned, the better event detection system can perform.
+
+ and \textit{full history info enhanced normal states training}.
+
+\begin{figure}
+    \label{fig:modelDesc}
+    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
+    \caption{\textsc{NSDetector}'s process flow, taking \textbf{military} related events in cyberspace as an example.
+\textsc{NSDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
+\end{figure}
+
+For example, in ideal conditions an event detection system for anti-terrorism has the knowledge about the normal state such as “the words ISIS and Syria are both high-frequent, while the word Russia is not so frequent as them”.
+With the knowledge of normal state, the system for anti-terrorism can detect the event of “Russia's anti-ISIS op in Syria” as Russia appeared more frequent than the normal state and appeared with ISIS and Syria.
+After detection, the ideal event detection system also updates the normal state by considering the new coming data.
+
+\section{Related Works}
 
@@
 
-It's difficult to represent the 
-the low threshold leads to , while the high threshold leads to
-
-They build the normal states in the evolving training window
-%TODO
 The second category, train the triggers\cite{Li2013JointEE}\cite{Nguyen2015EventDA}(\textit{But it has some problems here, these methods are used in event extraction, so what's the relationship between event extraction and event detection?
@@
 
-They are hamppered by the rapid changing nature of cyberspace, e.g. twitter and reddit(\textit{find out the sentences to describe the rapid changing nature}).
-
-It is hard to handle all the cyberspace data by using limited computing resources. As a result, it have to make a trade off, only to process part of them, instead of using the whole data.
-
-In this paper, we demonstrate that the better normal states  are learned, the better event detection system can perform.
-
- and \textit{full history info enhanced normal states training}.
-
-\begin{figure}
-    \label{fig:modelDesc}
-    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
-    \caption{\textsc{NSDetector}'s process flow, taking \textbf{military} related events in cyberspace as an example.
-\textsc{FullReader} initializes the normal states as topical word frequencies from full history information about military, updates them further at the specific corpus day by day, and detects events finally.}
-\end{figure}
-
-For example, in ideal conditions an event detection system for anti-terrorism has the knowledge about the normal state such as “the words ISIS and Syria are both high-frequent, while the word Russia is not so frequent as them”.
-With the knowledge of normal state, the system for anti-terrorism can detect the event of “Russia's anti-ISIS op in Syria” as Russia appeared more frequent than the normal state and appeared with ISIS and Syria.
-After detection, the ideal event detection system also updates the normal state by considering the new coming data.
-
-\section{Related Works}
 Although \cite{Wurzer:2015wq} points out that UMass\cite{Allan:2000wu} and its variants\cite{Petrovic:2010uj}\cite{petrovic2012using}\cite{Wurzer:2015wq} are the state-of-art systems on the Event Detection task for the newswire data, these systems still suffers from the lack of accuracy to applied on more general cyberspace data, such as tweets, emails, and reddit posts.
@@
 \subsection{Initialization of Normal States}
-\textbf{User profile.} User usually describes herself or himself by a piece of short text on microblog platform.
-This short text can be a continuous string or an array of hash tags, e.g., "\textit{Co-founder of Twitter, Medium, and now Co-founder and CEO of Askjelly.com}" of Biz Stone or "\textit{\#Cloud}, \textit{\#YARN}" of @hadoopchina.
-Though it's easy to estimate Biz Stone's interests by his self-description text, it's not always capable of doing so because some users' are very short.
-To overcome this limitation, we define \textbf{user profile} \(\bm{p_u}\) as combining user \(u\)'s self-description text with the texts provided by \(u\)'s followings. 
-Taking Biz Stone as an example, he follows 696 accounts, in which there are 60 founders, 27 CEOs, 21 Google related, and 9 medium related accounts, etc. 
-This example demonstrates that user profile \(p_u\) can be augmented by gathering the followings' information.
-
-\textbf{User modeling.} 
-User modeling is used to capturing user's long term interests. 
-For each user profile token, .
-For example, Biz Stone's long term interests can be inferred as \textit{Social Media}, \textit{Business}, and \textit{Technology} from his user profile \textit{Medium}, \textit{CEO}, and \textit{Google} respectively.
-
-The notations used in this paper are summarized in Table \ref{symbolsInModel}.
-We consider \(u\)'s user timeline as  the triple \(\{uid, \bm{p_u},\bm{w_u}\} \), where \(\bm{p_u}\) represents user \(u\)'s profile and \(\bm{w_u}=\{(tweetid, t_{ud},w_{ud})\}\) means the set of tweets posted by user \(u\).
-The element of \(\bm{w_u}\) is a triple of tweet id, time stamp \(t_{ud}\) and tweet content \(\bm{w_{ud}}\).
-
-\textbf{Event.} We define the event in the given time window \(t\) as the set of tweets denoted by \( \{ \bm{w_{te}}\}\).
-The event related tweets in set \( \{ \bm{w_{te}}\}\)  hold two properties: (1) it is different from user \(u\)'s long term interests and (2) it is similar with other tweets in the set.
-The task of event detection is to find out all the events in corpus.
-Different methods treat the above properties in different ways: LSH based methods\cite{petrovic2010streaming} treat the difference and simliarity in word vector space; while the topic model based methods\cite{timeUserLDA2012finding} take the semantic meaning into consideration.
-Under the framework of topic model, we divide the topics into user interest related topics and bursty event related topics, and further promote an online learning model UMIETM.
-\subsection{Normal States' Initialization}
 \begin{algorithm}
@@
 \label{alg:gibbsSamplingKBPriorLDA}
-\KwIn{Document sequences \(\bm{w_{1:D}}\), and normal states \(\bm{f}_{1:K_{\bm{KB}}}\)}
+\KwIn{Documents \(\mathcal{D}\) (a.k.a., \(\bm{w_{1:D}}\)), and normal states \(\bm{f}_{1:K_{\bm{KB}}}\)}
 \KwOut{The sufficient statistics \(\bm{n^{(d)}}\), \(\bm{n^{(w)}}\)}
-\medskip
-\tcc{Initialization of NS-Prior-LDA Learning}
+\tcc{Initialization of NS-Prior-LDA}
 \For{\(d=1:D\)}{
     \For{\(n=1:N_d\)}{
-        \(v=w_{dn}\), sample \(z_{dn}=k\) accroding to Eq(\ref{eq:wikiPrior})(\ref{eq:initProbability}).\\
+        \(v=w_{dn}\), sample \(z_{dn}=k\) as Eq(\ref{eq:wikiPrior})(\ref{eq:initProbability}).\\
         Update the sufficient statistics \(n^{(d)}_{d,k}\), \(n^{(w)}_{k,v}\).\\
@@
         }
-\medskip
 \For{\(i= 1:I\)}{
-    \tcc{E-Step of NS-Prior-LDA Learning}
+    \tcc{E-Step of NS-Prior-LDA}
     \For{\(i=1:I_E\)}{
@@
                 Set \(v=w_{dn}\), and reset the sufficient statistics \(n^{(d)}_{d,z_{dn}}\), \(n^{(w)}_{z_{dn},v}\).\\
-                Resample \(z_{dn}=k\) accroding to Eq(\ref{eq:wikiPrior})(\ref{eq:KBPriorLDAgibbs}).\\
+                Resample \(z_{dn}=k\) as Eq(\ref{eq:wikiPrior})(\ref{eq:KBPriorLDAgibbs}).\\
                 Update the sufficient statistics \(n^{(d)}_{d,k}\), \(n^{(w)}_{k,v}\).\\
@@
     }
-    \medskip
-    \tcc{M-Step of NS-Prior-LDA Learning}
+    \tcc{M-Step of NS-Prior-LDA}
     Optimize \(\alpha \bm{m}\) by the fixed-point iteration\cite{wallach2008structured}. 
 }
-\Return{\(\bm{n^{(d)}}\), \(\bm{n^{(w)}}\)}
+\Return{\(\bm{n^{(w)}}\)}
 \end{algorithm}
@@
 \label{my-label}
-\scalebox{0.8}{
+\scalebox{1.0}{
     \begin{tabular}{|l|l|l|}
@@
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{paperbib}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
+\bibliographystyle{unsrt}
+\bibliography{paperbib}
+
 \end{document}

### 2016-06-17 paper/ieeeFormat.tex
fix figure 6

@@
 \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
-%\usepackage{algorithm}
+\usepackage{algorithmic}
+
 \usepackage{bm}%used for bm
@@
 \usepackage{amssymb}%used for empty set symbol
+\usepackage{url}
 
@@
 Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
-And further experiments on \textit{reddit} also demonstrate that \textsc{NSDetector} can be easily adapted on other cyberspace datasets.
 %\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.
@@
 %The event detection task always tries to find out the newsworthy messages from cyberspace. 
-With the increasing of cyberspace data nowadays, there is a growing need for detecting events accurately.
+With the increasing of cyberspace data, there is a growing need for detecting events accurately.
 Detecting events can mainly benifit the following three folds: (1) understanding what happened in the corpus without checking every single document manually, and generating the timeline to get a bird's eye view of the corpus\cite{ge2015bring}; (2) being aware what is happening currently, which helps to deal with emergencies\cite{hughes2009twitter}\cite{sakaki2010earthquake}; (3) adding detected events and their types as extra structured data information to organize the unstructured text corpus\cite{ritter2012open}.
+
+Considering the importance of event detection on the cyberspace data, researchers have have made many efforts, including checking the and the . Therefore, the existing methods are ... and
 
@@
 We suppose that the ideal event detection system performs like a journalist who can find news from cyberspace with the knowledge of the normal states.
-
-They build the normal states in the evolving training window
-%TODO
-
-They are hamppered by the rapid changing nature of cyberspace, e.g. twitter and reddit(\textit{find out the sentences to describe the rapid changing nature}).
-
-It is hard to handle all the cyberspace data by using limited computing resources. As a result, it have to make a trade off, only to process part of them, instead of using the whole data.
-
-In this paper, we demonstrate that the better normal states  are learned, the better event detection system can perform.
-
- and \textit{full history info enhanced normal states training}.
 
@@
 \section{Related Works}
+\subsection{Event Detection}
 
-To train the normal states, the methods of existing systems can be grouped into two categories: \textit{unsupervised normal states training} and \textit{classification based normal states training}, which is illustrated by Figure \ref{fig:modelDesc:a}.
+To train the normal states, the methods of existing systems can be grouped into unsupervised methods and supervised methods based on whether they .
 
@@
 As these models need the whole dataset as the input, they are offline detections, which is not scalability for large dynamic dataset such as micorblogs.
-Instead, we gather user's self-description and the followings' self-description as user profile which is stable to characterize user interests. 
-Based on this fine-grained user modeling information, user's long term interest related tweets and short term bursty event related tweets can be distinguished in online style, and can be efficiently applied on microblogs.
+\subsection{Knowledge Base}
 
-Since user modeling has the significant impact on users' activities on microblogs, the usage of user modeling has drawn attention in many research fields. 
-\cite{zhao2013inferring} exploits user modeling information and network topology to infer user's role in social network.
-\cite{yoshida2013toward} also introduces user modeling to community detection where some edges are not observable, but user profile can provide additional information.
-Different from the above work, we do not only treat the user modeling result as an additional feature, but also an important representative factor for users, who are the source of information in microblogs.
+%Twitter Trending Topic Classification
+%We use PageRank-HITS\cite{Yan:2015wq} algorithm to update score of categories in wikipedia.
 
-User modeling can be carried out to obtain web users' demographics information \cite{culotta2015predicting} (e.g., gender, age, ethnicity, education, income, etc.).
-Compared with demographics information, user interests' modeling can be verified more easily \cite{faralli2015large}.
-
-Twitter Trending Topic Classification
-%\begin{figure}
-%    \includegraphics[height=7.7cm]{img/mlab_dirichlet_alpha_effects.pdf}
-%\end{figure}
-We use PageRank-HITS\cite{Yan:2015wq} algorithm to update score of categories in wikipedia.
-
-%3*4 figures
+%3*4 figures, 0-11 is reorganized in the following order: 0, 1, 4, 5, 8, 9;
+%2, 3, 6, 7, 10, 11;
 \begin{figure*}[ht]
@@
         \label{fig:subfig} %% label for entire figure
-        \subfigure[\(\alpha=(0.25,0.25,0.25)\)]{
+        \subfigure[\((0.25,0.25,0.25)\)]{
                 \label{fig:subfig:a} %% label for first subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph0.pdf}
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph0.pdf}
         }
-        \subfigure[\(\alpha=(0.5,0.5,0.5)\)]{
+        \subfigure[\((0.5,0.5,0.5)\)]{
                 \label{fig:subfig:b} %% label for second subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph1.pdf}
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph1.pdf}
         } 
-        \subfigure[\(\alpha=(1.5,1.5,1.5)\)]{
+        \subfigure[\((1.5,1.5,1.5)\)]{
                 \label{fig:subfig:c} %% label for third subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph2.pdf}
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph4.pdf}
         }
-        \subfigure[\(\alpha=(2.5,2.5,2.5)\)]{
+        \subfigure[\((2.5,2.5,2.5)\)]{
                 \label{fig:subfig:a} %% label for first subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph3.pdf}
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph5.pdf}
+        }
+        \subfigure[\((0.25,0.25,0.75)\)]{
+                \label{fig:subfig:d} %% label for third subfigure
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph8.pdf}
+        }
+        \subfigure[\((0.5,0.5,1.5)\)]{
+                \label{fig:subfig:d} %% label for third subfigure
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph9.pdf}
         }\hspace{1in}
-        \subfigure[\(\alpha=(0.25,0.25,0.75)\)]{
+        \subfigure[\((1.5,1.5,2.5)\)]{
                 \label{fig:subfig:d} %% label for third subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph4.pdf}
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph2.pdf}
         }
-        \subfigure[\(\alpha=(0.5,0.5,1.5)\)]{
+        \subfigure[\((2.5,2.5,3.5)\)]{
+                \label{fig:subfig:a} %% label for first subfigure
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph3.pdf}
+        }
+        \subfigure[\((0.25,0.75,0.75)\)]{
                 \label{fig:subfig:d} %% label for third subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph5.pdf}
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph6.pdf}
         }
-        \subfigure[\(\alpha=(1.5,1.5,2.5)\)]{
+        \subfigure[\((0.5,1.5,1.5)\)]{
                 \label{fig:subfig:d} %% label for third subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph6.pdf}
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph7.pdf}
         }
-        \subfigure[\(\alpha=(2.5,2.5,3.5)\)]{
+        \subfigure[\((1.5,2.5,2.5)\)]{
+                \label{fig:subfig:d} %% label for third subfigure
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph10.pdf}
+        }
+        \subfigure[\((2.5,3.5,3.5)\)]{
                 \label{fig:subfig:a} %% label for first subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph7.pdf}
+                \includegraphics[height=2.14cm]{img/croppedDirichletGraph11.pdf}
         }\hspace{1in}
-        \subfigure[\(\alpha=(0.25,0.75,0.75)\)]{
-                \label{fig:subfig:d} %% label for third subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph8.pdf}
-        }
-        \subfigure[\(\alpha=(0.5,1.5,1.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph9.pdf}
-        }
-        \subfigure[\(\alpha=(1.5,2.5,2.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph10.pdf}
-        }
-        \subfigure[\(\alpha=(2.5,3.5,3.5)\)]{
-                \label{fig:subfig:a} %% label for first subfigure
-                \includegraphics[height=3.21cm]{img/croppedDirichletGraph11.pdf}
-        }
         \caption{Illustration of Drichlet distribution's probabilistic density on the 3-dimensional simplex when given different priors. (a-d) (e-h) (i-l)}
@@
 %TODO
+
 \begin{figure}
     \centering
-    \includegraphics[width=1.0\columnwidth]{img/initializationExample.pdf}  
+    \includegraphics[width=.85\columnwidth]{img/initializationExample.pdf}  
     \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
@@
     \centering
-    \includegraphics[width=1.0\columnwidth]{model/lda_tikz.pdf}
+    \includegraphics[width=0.75\columnwidth]{model/lda_tikz.pdf}
     \caption{Probabilistic model for training normal states by using history information.}
@@
 
+\begin{scriptsize}
 \begin{equation}
@@
 \end{equation}
+\end{scriptsize}
 
+\begin{scriptsize}
 \begin{equation}
@@
 \end{equation}
+\end{scriptsize}
 
@@
 \label{alg:eventKeywordsSearchMethod}
-\KwIn{\(\mathcal{B}_{k,t},\mathcal{G}_{k,t},\tau\)}
+\KwIn{\(\mathcal{B}_{k,t},\mathcal{G}_{k,t},\rho\)}
 \KwOut{\(\mathcal{C}_{k,t}\)}
@@
     \(\mathcal{C}_{k,t}=SpectralClustering(\mathcal{G}_{k,t},n)\)\\
-    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\tau\)}{
+    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\rho\)}{
         return \(\mathcal{C}_{k,t}\)
@@
         \includegraphics[height=4.0cm]{img/pmi.pdf}
-        \caption{History State Portion}
+        \caption{The quality of all twitter topics learned by NS-Prior-LDA increases with normal states weight (\(\lambda\)) before \(\lambda=12.8\).
+The optimized PMI is gained with moderate normal states weight when considering topics \(k\leq K_{\bm{KB}}\) and topics \(k > K_{\bm{KB}}\) together.}
 \end{figure}
+
 \begin{table}
 \centering
-\caption{Normal State Training Performance}
-\label{my-label}
-\scalebox{1.0}{
+\caption{NS-Prior-LDA's Performance on the evaluation metric PMI}
     \begin{tabular}{|l|l|l|}
@@
     BBTM\cite{Yan:2015wm} & None    & 1.467 \(\pm\) 0.017     \\ \hline
-    NST\(^{(-)}\)   &   \begin{tabular}[c]{@{}l@{}}\footnotesize{Learned by LDA}\\ \footnotesize{from Wikipedia}\end{tabular} & 1.439 \(\pm\) 0.010     \\ \hline
-    NST         & \begin{tabular}[c]{@{}l@{}}\footnotesize{Derived from Categories} \\\footnotesize{of Wikipedia}\end{tabular} & 1.523 \(\pm\) 0.017     \\ \hline
+    NS-Prior-LDA\(^{(-)}\)   &   \begin{tabular}[c]{@{}l@{}}\footnotesize{Learned by LDA}\\ \footnotesize{from Wikipedia}\end{tabular} & 1.439 \(\pm\) 0.010     \\ \hline
+    NS-Prior-LDA         & \begin{tabular}[c]{@{}l@{}}\footnotesize{Derived from Categories} \\\footnotesize{of Wikipedia}\end{tabular} & 1.523 \(\pm\) 0.017     \\ \hline
     \end{tabular}
-}
+\label{tbl:NS-Prior-LDA}
 \end{table}
@@
 \multicolumn{2}{|c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Sport}} \\ 
-\begin{tabular}[c]{@{}c@{}}History\\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} \\ \hline
+\begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} \\ \hline
 Army & killed & aircraft & air & medical & weight & league & season \\ 
@@
 \label{my-label}
+\subtable[Twitter Dataset Statistics]{
+\begin{tabular}{|l|r|}
+\hline
+Time range & \begin{tabular}[c]{@{}l@{}}2011/06/30\\ -2011/09/15\end{tabular} \\ \hline
+Tweet Number & 36,627,434 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Event Number \\ in Benchmark1\end{tabular} & 27 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Event Number \\ in Benchmark2\end{tabular} & 523 \\ \hline
+\end{tabular}
+}\quad \quad
+\subtable[Event Detection Results]{
     \begin{tabular}{|l|l|l|l|l|}
@@
     Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate(Duplicate \\ Event Rate)\end{tabular} \\ \hline
-UMass System & 0.882 & 0.138 & 0.941 & 0. 071 \\ \hline
+    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
     LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
@@
     BBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
-Our Method & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
+    \textsc{NSDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
     \end{tabular}
+}
 \end{table*}
 
-\begin{table}[]
-\centering
-\caption{Twitter data set description}
-\label{my-label}
-\begin{tabular}{|l|r|}
-\hline
-Time range & \begin{tabular}[c]{@{}r@{}}2011/06/30\\ -2011/09/15\end{tabular} \\ \hline
-Tweet number & 36,627,434 \\ \hline
-Event number in Benchmark1 & 17 \\ \hline
-Event number in Benchmark2 & 523 \\ \hline
-\end{tabular}
-\end{table}
 % \begin{table}[]
@@
 Due to the developer policy of Twitter\footnote{https://dev.twitter.com/overview/terms/policy}, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{http://demeter.inf.ed.ac.uk/cross/docs/fsd\_corpus.tar.gz}.
-We collect the tweets' contents according to the IDs with the help of Twitter API. 
+We collected the tweets' contents according to the IDs with the help of Twitter API. 
+Though it's mentioned that there are 90 million tweets, due to the limit of twitter API w
 The dataset contains 36,627,434 tweets which spans from 2011/06/30 to 2011/09/15.
+
+%TODO
+The benchmark of Edinburgh contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}}.
 

### 2016-06-21 paper/ieeeFormat.tex
add 20 news group

@@
 \usepackage{url}
+\usepackage{xcolor}% or package color
 
@@
 With the increasing of cyberspace data, there is a growing need for detecting events accurately.
-Detecting events can mainly benifit the following three folds: (1) understanding what happened in the corpus without checking every single document manually, and generating the timeline to get a bird's eye view of the corpus\cite{ge2015bring}; (2) being aware what is happening currently, which helps to deal with emergencies\cite{hughes2009twitter}\cite{sakaki2010earthquake}; (3) adding detected events and their types as extra structured data information to organize the unstructured text corpus\cite{ritter2012open}.
+Detecting events can mainly benefit the following three folds: (1) understanding what happened in the corpus without checking every single document manually, and generating the timeline to get a bird's eye view of the corpus\cite{ge2015bring}; (2) being aware what is happening currently, which helps to deal with emergencies\cite{hughes2009twitter}\cite{sakaki2010earthquake}; (3) adding detected events and their types as extra structured data information to organize the unstructured text corpus\cite{ritter2012open}.
 
@@
 In the first category, the methods treat the normal states as clustered articles\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topics\cite{Diao:2012wj}\cite{Yan:2015wm}.
-Taking the clustering of articles\cite{Petrovic:2010uj}\cite{Wurzer:2015wq} as an example, they model the occured events as clusters, and link the incoming article with an existing event cluster or assign it as the new detected event.
+Taking the clustering of articles\cite{Petrovic:2010uj}\cite{Wurzer:2015wq} as an example, they model the occurred events as clusters, and link the incoming article with an existing event cluster or assign it as the new detected event.
 The decision is based on whether the dissimilarity between the incoming article and existing event clusters is over the user-specified threshold.
@@
 
-Both categories of methods have achieved good performance on formal texts, but are hamppered by the diverse and rapid changing nature of cyberspace data (e.g., twitter\cite{Asur:2011tc} and reddit\cite{singer2014evolution}).
+Both categories of methods have achieved good performance on formal texts, but are hampered by the diverse and rapid changing nature of cyberspace data (e.g., twitter\cite{Asur:2011tc} and reddit\cite{singer2014evolution}).
 In the journalist metaphor of news value theory, they have the limited knowledge of normal states (aka "routine things") due to the limited history information used. 
@@
 They treat the word's document frequency along timeline as time series and do the analysis in frequency domain. 
-DFT method suffers the problem that it can not locate the time point for bursty.
-Wavelet analysis based method's complexity is very high, so its scalability is limited.
+DFT method suffers the problem that it can not locate the time point for bursty, while wavelet analysis based method's complexity is very high, which limits its scalability.
 
- Text similarity based online event detection methods\cite{petrovic2010streaming}\cite{mccreadiescalable}  suffer from the lexical variation which means different words describe the same events.
+ Text similarity based online event detection methods\cite{petrovic2010streaming}\cite{mccreadie2013scalable}  suffer from the lexical variation which means different words describe the same events.
  Similarity based method can successfully detect the tweet which is retweeted by many times, but fails to find out the event which is described from many different perspectives.
@@
 But they are different from ours.
-As these models need the whole dataset as the input, they are offline detections, which is not scalability for large dynamic dataset such as micorblogs.
+As these models need the whole dataset as the input, they are offline detections, which is not scalability for large dynamic dataset such as microblogs.
 \subsection{Knowledge Base}
@@
         \subfigure[\((0.25,0.25,0.25)\)]{
-                \label{fig:subfig:a} %% label for first subfigure
+                \label{fig:subfig:a} %% label for first subfigure a
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph0.pdf}
@@
         \subfigure[\((0.5,0.5,0.5)\)]{
-                \label{fig:subfig:b} %% label for second subfigure
+                \label{fig:subfig:b} %% label for second subfigure b
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph1.pdf}
         } 
-        \subfigure[\((1.5,1.5,1.5)\)]{
-                \label{fig:subfig:c} %% label for third subfigure
+        \subfigure[\((0.25,0.25,0.75)\)]{
+                \label{fig:subfig:c} %% label for third subfigure c
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph4.pdf}
         }
-        \subfigure[\((2.5,2.5,2.5)\)]{
-                \label{fig:subfig:a} %% label for first subfigure
+        \subfigure[\((0.5,0.5,1.5)\)]{
+                \label{fig:subfig:a} %% label for first subfigure d
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph5.pdf}
         }
-        \subfigure[\((0.25,0.25,0.75)\)]{
-                \label{fig:subfig:d} %% label for third subfigure
+        \subfigure[\((0.25,0.75,0.75)\)]{
+                \label{fig:subfig:d} %% label for third subfigure e
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph8.pdf}
         }
-        \subfigure[\((0.5,0.5,1.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure
+        \subfigure[\((0.5,1.5,1.5)\)]{
+                \label{fig:subfig:d} %% label for third subfigure f
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph9.pdf}
         }\hspace{1in}
-        \subfigure[\((1.5,1.5,2.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure
+        \subfigure[\((1.5,1.5,1.5)\)]{
+                \label{fig:subfig:d} %% label for third subfigure g
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph2.pdf}
         }
-        \subfigure[\((2.5,2.5,3.5)\)]{
-                \label{fig:subfig:a} %% label for first subfigure
+        \subfigure[\((2.5,2.5,2.5)\)]{
+                \label{fig:subfig:a} %% label for first subfigure h
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph3.pdf}
         }
-        \subfigure[\((0.25,0.75,0.75)\)]{
-                \label{fig:subfig:d} %% label for third subfigure
+        \subfigure[\((1.5,1.5,2.5)\)]{
+                \label{fig:subfig:d} %% label for third subfigure i
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph6.pdf}
         }
-        \subfigure[\((0.5,1.5,1.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure
+        \subfigure[\((2.5,2.5,3.5)\)]{
+                \label{fig:subfig:d} %% label for third subfigure j
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph7.pdf}
@@
         \subfigure[\((1.5,2.5,2.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure
+                \label{fig:subfig:d} %% label for third subfigure k
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph10.pdf}
@@
         \subfigure[\((2.5,3.5,3.5)\)]{
-                \label{fig:subfig:a} %% label for first subfigure
+                \label{fig:subfig:a} %% label for first subfigure l
                 \includegraphics[height=2.14cm]{img/croppedDirichletGraph11.pdf}
         }\hspace{1in}
-        \caption{Illustration of Drichlet distribution's probabilistic density on the 3-dimensional simplex when given different priors. (a-d) (e-h) (i-l)}
+        \caption{Illustration of Dirichlet distribution's probabilistic density on the 3-dimensional simplex when given different priors.
+(a,b,g,h) the left four subfigures illustrate the probabilistic density when given the symetric priors for Dirichlet distribution; (c,d,i,j) the central subfigures illustrate the probablistic density given ; (e,f,k,l) }
 \end{figure*}
@@
 \subsection{Initialization of Normal States}
+In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
 \begin{algorithm}
@@
 \label{alg:normalStatesInit}
+
 \KwIn{Taxonomy's Directed Acyclic Graph \(G^{(0)}\), Category-Page Bipartite Graph \(G^{(1)}\), Page-Content Bipartite Graph \(G^{(2)}\), topic related category node \(c\)}
@@
 \begin{aligned}
-&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha,\beta,\tau)\\
+&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha\bm{m},\beta,\tau)\\
 &\ \ \propto (n^{(d)}_{dk}+\alpha m_k)\frac{n^{(w)}_{kv}+\tau_{kv}+\beta}{n^{(w)}_{k,.}+\tau_{k,.}+V\beta}
@@
 \centering
-\caption{NS-Prior-LDA's Performance on the evaluation metric PMI}
-    \begin{tabular}{|l|l|l|}
+\caption{The PMI of twitter topics learned by NS-Prior-LDA, its variant, and other baselines}
+    \begin{tabular}{|l|l|c|}
     \hline
-    Model & History State & PMI \\ \hline
+    Model & Prior Knowledge & PMI \\ \hline
     LDA & None  & 1.265 \(\pm\) 0.013     \\ \hline
     BBTM\cite{Yan:2015wm} & None    & 1.467 \(\pm\) 0.017     \\ \hline
-    NS-Prior-LDA\(^{(-)}\)   &   \begin{tabular}[c]{@{}l@{}}\footnotesize{Learned by LDA}\\ \footnotesize{from Wikipedia}\end{tabular} & 1.439 \(\pm\) 0.010     \\ \hline
-    NS-Prior-LDA         & \begin{tabular}[c]{@{}l@{}}\footnotesize{Derived from Categories} \\\footnotesize{of Wikipedia}\end{tabular} & 1.523 \(\pm\) 0.017     \\ \hline
+    NS-Prior-LDA\(^{(-)}\)   &   \begin{tabular}[c]{@{}l@{}}\footnotesize{Words in categories simply}\\ \footnotesize{extracted from Wikipedia}\end{tabular} & 1.439 \(\pm\) 0.010     \\ \hline
+    NS-Prior-LDA         & \begin{tabular}[c]{@{}l@{}}\footnotesize{Normal states initialized} \\\footnotesize{from wikipedia}\end{tabular} & 1.523 \(\pm\) 0.017     \\ \hline
     \end{tabular}
@@
 \label{my-label}
-\begin{tabular}{|cc|cc|cc|cc|}
+\scalebox{0.88}{
+\begin{tabular}{|cc|cc|cc|cc|cc|cc|}
 \hline
-\multicolumn{2}{|c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Sport}} \\ 
-\begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} \\ \hline
-Army & killed & aircraft & air & medical & weight & league & season \\ 
-Battle & news & train & plane & patients & loss & season & win \\ 
-military & \#libya & airport & flight & treatment & diet & club & team \\ 
-Forces & libya & station & time & disease & pain & cup & deal \\ 
-attacks & rebels & flight & ship & health & cancer & football & year \\ 
-terrorist & people & pilot & news & brain & health & game & sign \\ 
-troops & police & aviation & boat & cancer & lose & games & jagr \\ 
-Killed & war & gear & airport & patient & tips & round & richards \\ 
-soldiers & libyan & passenger & force & blood & treatment & championship & cup \\ 
-commander & attack & drive & fly & body & fat & player & time \\ 
-Front & u.s. & navigation & hurricane & clinical & hair & match & arsenal \\ 
-Units & gaddafi & departure & navy & care & skin & division & fans \\ 
-captured & army & takeoff & coast & surgery & body & win & nasri \\ 
-campaign & forces & aviator & home & research & healthy & goals & city \\ 
-fighting & pakistan & navigator & crash & type & surgery & teams & league \\ 
-siege & afghanistan & runaway & irene & syndrome & blood & play & players \\ 
-officers & military & departure & train & system & brain & stadium & player \\ 
-guards & attacks & airbus & sea & medicine & acne & coach & signed \\ 
-allied & troops & miles & aircraft & eye & diabetes & players & contract \\ 
-lieutenant & dead & landing & jet & physician & eye & record & run \\ \hline
+\multicolumn{2}{|c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Middle East}} & \multicolumn{2}{c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Mobile Phones}} & \multicolumn{2}{c|}{\textit{Video Games}} \\
+\begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} \\
+\hline
+aircraft & air\scriptsize(3253) & health & weight\scriptsize(16344) & al & \textcolor{red}{\textit{\#syria}}\scriptsize(4212) & army & killed\scriptsize(4055)  & android & iphone\scriptsize (13674) & game & games\scriptsize(8812) \\
+air & plane & patients & loss & israel & \textcolor{red}{\textit{\#bahrain}} & military & news & mobile & apple & player & liked \\ 
+airport & flight & medical & diet & iran & people & air & \textcolor{red}{\textit{\#libya}}\scriptsize(3503) & nokia & android & playstation & free \\ 
+flight & time & disease & health & arab & israel & command & libya & ios & app & gameplay & xbox \\
+airline & airlines & treatment & cancer & israeli & police & force & rebels & phone & ipad & nintendo & 360 \\
+airlines & news & hospital & lose & egypt & \textcolor{red}{\textit{\#libya}}\scriptsize(2557) & regiment & people & samsung & samsung & games & playing \\
+aviation & boat & patient & fat & egyptian & \#egypt & forces & police & game & mobile & players & played \\
+flying & airport & clinical & tips & ibn & news & squadron & war & app & blackberry & xbox &iphone\scriptsize(2820)\\
+pilot & force & symptoms & treatment & jerusalem & \#israel & infantry & libyan & iphone & tablet & mode & time\\
+squadron & fly & cancer & body & syria & world & battle & attack & htc & apps & arcade & \textcolor{red}{\textit{ps3}}\\
+flights & hurricane & cells & healthy & iraq & syria & commander & u.s. & smartphone & free & wii & trailer\\
+pilots & navy & blood & study & palestinian & protest & ship & gaddafi & phones & \#android & multiplayer & online\\
+raf & flying & therapy & pain & syrian & israeli & corps & army & blackberry & htc & sega & hours\\
+airways & aircraft & drug & exercise & iranian & egypt & navy & forces & apps & google & console & ipad\\
+fighter & \textcolor{red}{\textit{irene}} & medicine & \#health & ottoman & al & brigade & pakistan & ipad & galaxy & enemies & app\\
+boeing & crew & brain & natural & islamic & syrian & battalion & afghanistan & gsm & ios & characters & player\\
+runway & sky & care & disease & iraqi & protesters & lieutenant & military & lte & store & playable & wii\\
+force & crash & syndrome & acne & abu & arab & aircraft & attacks & symbian & windows & character & ops\\
+crashed & jet & infection & hair & jewish & rights & officer & troops & devices & mac & video & download\\
+flew & pilot & disorder & surgery & persian & libya & naval & dead & smartphones & phones & graphics & nintendo\\
+\hline
 \end{tabular}
+}
 \end{table*}
@@
 
-% \begin{table}[]
-% \centering
-% \caption{My caption}
-% \label{my-label}
-% \begin{tabular}{|l|l|l|l|}
-% \hline
-% \multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Time \\ range\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Tweet \\ number\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Event number \\ in Benchmark1\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Event number \\ in Benchmark2\end{tabular}} \\ \hline
-% \begin{tabular}[c]{@{}l@{}}2011/06/30-\\ 2011/09/15\end{tabular} & 36,627,434 & 17 & 523 \\ \hline
-% \end{tabular}
-% \end{table}
-
 \begin{table*}[ht]
@@
 \multicolumn{1}{|c|}{Date} & \multicolumn{1}{c|}{Event key words} & \multicolumn{1}{c|}{Representative event tweet} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Number of \\ event tweet\end{tabular}} \\ \hline
-7/20/11 & \begin{tabular}[c]{@{}l@{}}American, Airlines, \\ order, planes\end{tabular} & \begin{tabular}[c]{@{}l@{}}NDTV: American Airlines orders 460 new planes from \\ Boeing, Airbus http://bit.ly/p1ZgYG\end{tabular} & 31 \\ \hline
-7/23/11 & \begin{tabular}[c]{@{}l@{}}China, bullet, train, \\ collision\end{tabular} & \begin{tabular}[c]{@{}l@{}}China Bullet Train Collision: 33 Dead, 190 Injured \\ http://huff.to/qEq6Yx\end{tabular} & 67 \\ \hline
+7/20/11 & \begin{tabular}[c]{@{}l@{}}American, airlines, \\ order, planes\end{tabular} & \begin{tabular}[c]{@{}l@{}}NDTV: American Airlines orders 460 new planes from \\ Boeing, Airbus http://bit.ly/p1ZgYG\end{tabular} & 31 \\ \hline
 7/26/11 & \begin{tabular}[c]{@{}l@{}}Morocco, military, \\ plane, crash\end{tabular} & \begin{tabular}[c]{@{}l@{}}BBC News - Morocco military plane crash kills 78 \\ http://t.co/uwnLv8L\end{tabular} & 36 \\ \hline
-7/27/11 & Air, Canada & \begin{tabular}[c]{@{}l@{}}Smoke in galley forces Air Canada flight back to airport. \\ Plane landed safely in Sydney, Australia after dumping fuel\end{tabular} & 48 \\ \hline
-7/30/11 & \begin{tabular}[c]{@{}l@{}}Caribbean, Airlines, \\ crashes, Guyana\end{tabular} & \begin{tabular}[c]{@{}l@{}}Caribbean Airlines Jet Crash-Lands In Guyana All 163 \\ Passengers, Crew Survive http://t.co/qPVD3WJ\end{tabular} & 57 \\ \hline
+7/27/11 & air, Canada & \begin{tabular}[c]{@{}l@{}}Smoke in galley forces Air Canada flight back to airport. \\ Plane landed safely in Sydney, Australia after dumping fuel\end{tabular} & 48 \\ \hline
+7/30/11 & \begin{tabular}[c]{@{}l@{}}Caribbean, airlines, \\ crashes, Guyana\end{tabular} & \begin{tabular}[c]{@{}l@{}}Caribbean Airlines Jet Crash-Lands In Guyana All 163 \\ Passengers, Crew Survive http://t.co/qPVD3WJ\end{tabular} & 57 \\ \hline
 \end{tabular}
@@
 
-\subsection{Data set}
-Dataset
-We conduct the empirical analysis on a twitter dataset which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}.
+\subsection{Data set and experiment settings}
+\textbf{Data set.} We conduct the empirical analysis on a twitter dataset which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}.
 Due to the developer policy of Twitter\footnote{https://dev.twitter.com/overview/terms/policy}, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{http://demeter.inf.ed.ac.uk/cross/docs/fsd\_corpus.tar.gz}.
 We collected the tweets' contents according to the IDs with the help of Twitter API.
-Though it's mentioned that there are 90 million tweets, due to the limit of twitter API w
-The dataset contains 36,627,434 tweets which spans from 2011/06/30 to 2011/09/15.
 
 %TODO
-The benchmark of Edinburgh contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}}.
+The benchmark \textit{Edinburgh twitter corpus} contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}} and 90 million tweets.
+Though we cannot get the whole dataset due to the limit of Twitter API, after neccessary pre-processing, our rebuilt dataset still contains 36,627,434 tweets, which spans identically from 2011/06/30 to 2011/09/15, and also covers 27 labeled events.
+More details of the original dataset are described in \cite{petrovic2010edinburgh}.
+
+20-newsgroup\footnote{http://qwone.com/~jason/20Newsgroups/}
+
+\textbf{Benchmark1} The first set of the ground truth about events in the corpus are provided by \cite{petrovic2013can}, which is mentioned above. 
+And 27 events ...
+
+\textbf{Benchmark2} here.
+
+\textbf{Normal States Initialization} here.
+
+\textbf{Baseline}
+
+UMass System
+
+LSH
+
+TimeUserLDA
+
+Twevent
+
+EDCoW
+
+BBTM
+
+\textbf{Model Setting}
+
+\subsection{Validity of Normal States}
+\textbf{Topic Coherence} \cite{roder2015exploring}
+\subsection{Topical Words Learned by NS-Prior-LDA}
+\textbf{PMI}
+\subsection{Evaluation of Detected Events}
+\textbf{Precision} Precision@Benchmark1, Precision@Benchmark2
+
+\textbf{Recall}
+
+\textbf{Accuracy}
+
+\textbf{DERate(Duplicate Event Rate)}
+\subsection{Case Study}
 
@@
 We check the time cost and complete likelihood for efficiency.
-% We are going to design the experiment to show the effectiveness of distinguishing user interests and events.
-% Firstly, user profile can help to model user interests.
-% In this experiment we compare to the baseline of user interest modeling\cite{sun2013serendipity}.
-% Secondly, event detection can be enhanced by filtering out user interests.
-%\subsection{Experiment Settings}
-%We demonstrate our method can work very well on real dataset.
 
-Weibo is a popular Chinese microblogging service\footnote{http://en.wikipedia.org/wiki/Sina\_Weibo/}.
-We crawl weibo data by  its public API\footnote{http://open.weibo.com/} from Jan 2012 to Dec 2012.
-To improve the quality of analyzing on tweets, we do necessary pre-processing: (1) splitting dataset by week, (2) segmenting Chinese words, (3) removing stop words and low frequency words whose document frequency in its time window is less than 3, (4) removing tweets whose token number is less than 3.
-To model user interests better,  we remove users from dataset who has less than 2 hashtags in profile.
-After pre-processing we get 252 thousand users, 16 million tweets and 251 million tweet tokens listed in Table \ref{statisticsOfDataset}.
+To improve the quality of analyzing on tweets, we do necessary pre-processing: (1) splitting dataset by week, (2) segmenting Chinese words, (3) removing stop words and low frequency words whose document frequency in its time window is less than 3.
 
@@
 The variant IETM (\textit{Interest and Event Topic Model}) models user's interests and events without the help of user profiles.
-%UMIETM benifits from modeling user profiles.
-
-%To demonstrate the necessary of user profiles, we compare it to its variant IETM (Interest and Event Topic Model) which only consider the tweets shown in figure \ref{fig:IETM}.
-%IETM also run in online learning way.
 
@@
 After 10 iterations the UMIETM's complete log likelihood will increase no more than 0.2\%.
-% \subsubsection{Soundness}
-% As the online learning for UMIETM is an approximated version of batch learning for UMIETM, the soundness should be confirmed before applying it in the real enviroment.
-%[todo] We also want to show that online learning for UMIETM does not  sacrifice the accuracy. 
-%Comapring the held out perplexity.
 
 \textbf{Online Performance.}
-%Figure \ref{fig:completeLoglikelihood} shows that the log likelihood increases less than 0.1\% after 12 iterations.
-%Our experiment shows UMIETM has good convergence that the complete log likelihood increases less than 0.15\% after 10 iterations.
 As verified in the above subsection \textit{Convergence}, we run 10 Gibbs sweeps for each time window in online learning phase.

### 2016-07-02 paper/ieeeFormat.tex
add 20newsgroups and their categories in wiki

@@
 \section{Experiments}
+\subsection{Effects of Normal States Initialization}
+We use 20newsgroups\cite{lang1995newsweeder} dataset\footnote{http://qwone.com/~jason/20Newsgroups} to check the effects of normal states initialization.
+\begin{table}[]
+\centering
+\caption{My caption}
+\label{my-label}
+\begin{tabular}{|l|l|}
+\hline
+comp.graphics            & Category:Computer graphics      \\ \hline
+comp.os.ms-windows.misc  & Category:Microsoft Windows      \\ \hline
+comp.sys.ibm.pc.hardware & Category:IBM personal computers \\ \hline
+comp.sys.mac.hardware    & Category:Macintosh computers    \\ \hline
+comp.windows.x           & Category:X Window System        \\ \hline
+rec.autos                & Category:Automobiles            \\ \hline
+rec.motorcycles          & Category:Motorcycles            \\ \hline
+rec.sport.baseball       & Category:Baseball               \\ \hline
+rec.sport.hockey         & Category:Hockey                 \\ \hline
+sci.crypt                & Category:Cryptography           \\ \hline
+sci.electronics          & Category:Electronics            \\ \hline
+sci.med                  & Category:Medicine               \\ \hline
+sci.space                & Category:Outer space            \\ \hline
+misc.forsale             & Category:Sales                  \\ \hline
+talk.politics.misc       & Category:Politics               \\ \hline
+talk.politics.guns       & Category:Gun politics          \\ \hline
+talk.politics.mideast    & Category:Middle East           \\ \hline
+talk.religion.misc       & Category:Religion               \\ \hline
+alt.atheism              & Category:Atheism                \\ \hline
+soc.religion.christian   & Category:Christians             \\ \hline
+\end{tabular}
+\end{table}
+
 \begin{figure}

### 2016-07-08 paper/ieeeFormat.tex
before modifying

@@
 We use 20newsgroups\cite{lang1995newsweeder} dataset\footnote{http://qwone.com/~jason/20Newsgroups} to check the effects of normal states initialization.
+
+What's NPMI? maybe can refer to \cite{Aletras2013EvaluatingTC}\cite{Rder2015ExploringTS}\footnote{https://github.com/AKSW/Palmetto}.
 \begin{table}[]
@@
 The optimized PMI is gained with moderate normal states weight when considering topics \(k\leq K_{\bm{KB}}\) and topics \(k > K_{\bm{KB}}\) together.}
+\end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=1.0\columnwidth]{img/NPMI.pdf}
+        \caption{NPMI}
 \end{figure}
@@
 
-Here we present the effectiveness of our proposed algorithm UMIETM and the efficiency of its online performance.
-We evaluate the efficiency by perplexity, precision for event detection. 
-We check the time cost and complete likelihood for efficiency.
-
-To improve the quality of analyzing on tweets, we do necessary pre-processing: (1) splitting dataset by week, (2) segmenting Chinese words, (3) removing stop words and low frequency words whose document frequency in its time window is less than 3.
-
-We compare our model UMIETM with twitterLDA, timeUserLDA, Author-LDA, and our model's variant IETM.
-Author-LDA combines the tweets posted by same author into a single document, then run standard LDA on the assembled tweets.
-TwitterLDA is designed for topic modeling on twitter.
-We compare with Author-LDA and TwitterLDA for confirming the significance of distinguishing user interests from events in microblog.
-TimeUserLDA is designed for retrospective event detection in microblog, and considers to distinguish events from user interests.
-We compare with timeUserLDA to show the impact of user profile.
-The variant IETM (\textit{Interest and Event Topic Model}) models user's interests and events without the help of user profiles.
-
-We set the asymmetric \(\alpha\) and symmetric \(\beta=0.01\) for UMIETM, where \(\alpha\) will be optimized by Gibbs EM algorithm\cite{wallach2008structured}.
-\(\alpha=0.1\), \(\beta=0.01\) are set for all remaining models. 
-After cross validation we find that UMIETM and IETM perform best on \(K=90\) and \(E=30\), \(\kappa=0.01\).
-To compare equally, we set the same topic number for Author-LDA, twitterLDA, timeUserLDA (which means when we run models offline on 1 time window, we shall set 120 topics for all, and 150 topics on 2 time windows and so on).
-
-To verify the role of user profiles played, we set UMIETM(-) as the degradation of UMIETM, which take symmetric prior \(\alpha\).
-
-In this subsection, we illustrate the performance of UMIETM in which user profile is considered.
-
-\textbf{Quantitative Measure.}
-We initialize UMIETM and IETM by batch learning on data from first week to third week, then run them in online learning way from fourth week to ninth week.
-On each week we calculate their perplexities\cite{wallach2009evaluation}, where \(perplexity(D_{test})=\exp{\{-\frac{\sum_{u=1}^{U}\sum_{d=1}^{D_u}\log{p(w_{ud})}}{\sum_{u=1}^{U}\sum_{d=1}^{D_u}N_{ud}}\}}\) and \(p(w_{ud})=(1-\pi_u)\sum_{k=1}^{K}\theta_{uk}\prod_{n=1}^{N_{ud}}(\phi_{s,w_{udn}}(1-\rho)+\phi_{k,w_{udn}}\rho)+\pi_u \sum_{k=1}^{K}\eta_{t,k}\prod_{n=1}^{N_{ud}}(\phi_{s,w_{udn}}(1-\rho)+\phi_{k,w_{udn}}\rho)\).
-The others are trained from first week to third week, and the held out perplexities are calculated on data from fourth week to ninth week.
-TimeUserLDA and IETM's perplexities are smaller than User-LDA, twitterLDA as they both consider distinguishing user interests from events.
-
-In Table \ref{tab:heldoutPerplexity} the perplexity of UMIETM is 3107.8, and much smaller than others. It demonstrates that user profile is significant for tweet stream's modeling.
-
-In Table \ref{tab:metrics}, we evaluate the events detected by models. We asked the annotators to label the event with score 1, and non-event related topic as 0. 
-The precision and recall is illustrated, where UMIETM(-) performs slightly better than IETM. 
-And UMIETM outperforms UMIETM(-) in detecting high quality event. 
-A reasonable analysis is that UMIETM uses the profile information sufficiently by asymmetric priors. 
-In this way, we also prove that the well exploiting of user profile information is important to model user interests and events on tweets. 
-%\subsubsection{Precision of Event Detection}
-
-\textbf{Case Study} 
-Some events detected by our UMIETM model are shown in Table \ref{fig:event}.
-Comparing with UMIETM, timeUserLDA fails to discover the \textit{shoddy construction} event in the second week, while IETM reports this event as \textit{bi, women, elegant, adoption, engineering, reed}.
-Obviously IETM fails to distinguish this event from user interests.
-UMIETM filters users' interests like \textit{bi, women, elegant, adoption} using their profile {\#baby, \#women}, and detect the event.
-\subsection{Efficiency}
-We implement our methods on mallet\footnote{http://mallet.cs.umass.edu/dist/mallet-2.0.7.tar.gz}, and run them on Linux server with 8 cores(2.00GHz) and 64GB memory.
-In this subsection, we verify the convergence and online performance of our online learning algorithm.
-
-\textbf{Convergence.}
-The convergence of algorithm is vital in real time streaming environment. 
-UMIETM needs several Gibbs sweeps to find out the optimal parameters of model.
-But the size of data is usually large even spitted into time windows.
-The time complexity of UMIETM is \(O(I_1K|P|+I_2K|W|+I_2E|W|)\) given in section \ref{subsec:online}.
-It suggests that the more iterations Gibbs sampling have to do, the less efficiently our model performs. 
-Fortunately UMIETM is very economic to its stable state and does not need so much iterations.
-As suggested by \cite{wallach2009rethinking} and \cite{jian2014factorOfTopicModel}, we choose LDA with asymmetric priors as baseline, which is much more comparable than standard LDA on microblog dataset.
-We run UMIETM on the first three time windows. 
-Correspondingly we only use the tweets in these time windows for LDA with asymmetric priors.
-Burn-in period is set to 20 and optimize interval also 20, which means the priors are optimized every 20 iterations as the red curve in Fig \ref{fig:completeLoglikelihood}.
-
-One of the criteria for stopping Gibbs sampling is that the complete log likelihood is stabilized.
-We stop UMIETM after 50 iterations since the complete log likelihood only increases 0.02\% in last iteration.
-It will take LDA(asymmetric priors) 300 minutes to run 1000 iterations, and 20 minutes per 10 iterations for UMIETM.
-There is a trade-off between the effectiveness by more iterations and efficiency by less,  we set the iteration number as 10 in online setting.
-After 10 iterations the UMIETM's complete log likelihood will increase no more than 0.2\%.
-
-\textbf{Online Performance.}
-As verified in the above subsection \textit{Convergence}, we run 10 Gibbs sweeps for each time window in online learning phase.
-When UMIETM is implemented in online way, it doesn't have to revisit the tweets in previous windows. 
-So its time cost in each window is proportional to the data size of current window  as shown in Figure \ref{fig:onlinelearningResult}.
-In average, online UMIETM can process five thousand tokens per second.
-%Memory cost grows slightly and the increased memory cost only depends on the size of vocabulary.
-
-LSH based event detection on microblogs is used by \cite{petrovic2010streaming},\cite{mccreadiescalable}. 
-The former one detects events as the cluster of tweets by LSH, and the latter one extends this method on distributed machines. 
-They both only use the cosine similarity without considering semantic meaning of words. 
-So LSH based method may split the same event into clusters of similar tweets.
-However LSH based method reports 10578 events in 7th time window, and 10901 events in 8th window. 
-The other problem of LSH based event detection method is that the bad design may lead unstable performance. 
-The tweets are mapped into LSH defined space in a skew way which is illustrated in Fig \ref{fig:onlinelearningResult}.
-The other comparison is timeUserLDA which is designed for retrospective event detction. 
-The purple line in Fig \ref{fig:onlinelearningResult} goes up straightly as timeUserLDA has to revisit previous tweets to make a decision whether the tweet is event related. 
-The perplexity of online UMIETM on the 11 time window in Fig \ref{fig:onlinelearningResult} is \(3036.44\pm397.14\). 
-And the average precision of detecting high quality event is 0.22.
-Both indicators demonstrate that UMIETM can perform well in online learning way. 
 \subsection{Application on Reddit}

### 2016-07-15 paper/ieeeFormat.tex
before coling

@@
 
+%主动感知的
 \title{Normal States Training for High Accuracy Event Detection}
@@
 %TODO
-In \textsc{NSDetector}, 1) balanced for effectiveness and efficiency, normal states are trained as topical words and their chi-squared scores, and initialized by knowledge base; 2) topical word frequencies on targeted corpus within the time window are learned by NS-Prior-LDA, using the normal states as prior; 3) events are detected by monitoring the change of topical word frequencies; 4) normal states are further maintained by detected events incrementally.
+In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
 Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
@@
 \section{Proposed Method}
-\begin{algorithm}
-\caption{Overview of \textsc{NSDetector}}
-\label{alg:overviewNSDetector}
-\KwIn{Knowledge Base's structure \(G^{(0)}\), \(G^{(1)}\), and content \(G^{(2)}\), }
-\KwOut{Events}
-\(n_{k,t}\)=number of connected component in \(\mathcal{G}_{k,t}\)\\
-\For{\(n \in \{ n_{k,t}, \cdots, |\mathcal{G}_{k,t}|\}\) }{
-    \(\mathcal{C}_{k,t}=SpectralClustering(\mathcal{G}_{k,t},n)\)\\
-    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\tau\)}{
-        return \(\mathcal{C}_{k,t}\)
-    }
-}
-\end{algorithm}
+\begin{table}
+\begin{tabular}{|p{0.1\columnwidth}|p{0.8\columnwidth}|} \hline
+\(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \hline
+\(G^{(1)}\) & Category-Page Bipartite Graph in Knowledge Base\\ \hline
+\(G^{(2)}\) & Page-Content Bipartite Graph in Knowledge Base\\ \hline
+\(c\) & topic related category node in \(G^{(0)}\) and \(G^{(1)}\) \\ \hline
+\(K_{\bm{KB}}\) & number of pre-defined topics by Knowledge Base \\ \hline
+\(f_{c,w}\) & word \(w\)'s normal state (chi-square score) in category \(c\) \\ \hline
+\(\lambda\) & normal state weight in  NS-Prior-LDA\\ \hline
+\(\tau_{c,w}\) & word \(w\)'s prior knowledge confidence for topic \(c\) in NS-Prior-LDA\\ \hline
+\(S_c\) & topic \(c\)'s all normal states related words \\ \hline
+\(K\) & number of topics in NS-Prior-LDA such as \(K>K_{\bm{KB}}\)\\ \hline
+\(\mathcal{B}_{c, t}\)  & hot words set detected from topic \(k\) at time \(t\)  \\ \hline
+\(\mathcal{G}_{c, t}\)  & hot word graph constructed from \(\mathcal{B}_{c, t}\) \\ \hline
+\(\mathcal{C}_{c,t,i}\) & event \(i\)-th related words in topic \(c\) at time \(t\) \\ \hline
+\(\mathcal{D}_{c,t,i}\) & event \(i\)-th related tweets in topic \(c\) at time \(t\) \\ \hline
+\(\rho\) & density threshold for the sub-graph constructed by event words  \\ \hline
+
+\end{tabular}
+\label{symbolsInModel}
+\end{table}
 
@@
 \begin{algorithm}
-\caption{Normal States' Initialization from Knowledge Base}
+\caption{Normal States Initialization from Knowledge Base}
 \label{alg:normalStatesInit}
 
-\KwIn{Taxonomy's Directed Acyclic Graph \(G^{(0)}\), Category-Page Bipartite Graph \(G^{(1)}\), Page-Content Bipartite Graph \(G^{(2)}\), topic related category node \(c\)}
+\KwIn{Taxonomy's Graph \(G^{(0)}\), Category-Page Bipartite Graph \(G^{(1)}\), Page-Content Bipartite Graph \(G^{(2)}\), topic related category node \(c\)}
 \KwOut{Normal states \(\bm{f}_c\) on topic \(c\)}
 \(Pages(c)\leftarrow \varnothing\)\\
-\(SuccessorNodes(c) \leftarrow \) Breadth-first-search(\(G^{(0)},c\))\\
+DAG \(G^{(0)'} \leftarrow\) Remove Cycles of \(G^{(0)}\) by nodes' HITS-PageRank scores. \\
+\(SuccessorNodes(c) \leftarrow \) Breadth-first-traverse(\(G^{(0)},c\))\\
 \For{\(node \in SuccessorNodes(c)\)}{
@@
 \(\tau_k \) in the first \(v \) words such as formula (\ref{eq: wikiPrior}).
-Where \(S_k \) as a set of candidate words: high-quality information to use Wikipedia, we extract the theme \(phi_k \ \) in the higher-word word frequency candidate set \(S_k \).
+Where \(S_k \) as a set of candidate words: high-quality information to use Wikipedia, we extract the theme \(\phi_k \ \) in the higher-word word frequency candidate set \(S_k \).
 We can control set \(S_k \) in size, the size of the control is usually set for 1000.
@@
 The state of attention of social issue k at time t in cyberspace is binary, namely at the peak or not at the peak.
-We denote it by hidden binary variable sk,t, which is 1 or 0.
-We do the inference for the hidden variable sk,t according to Poisson distribution according to Reference10,11.
+We denote it by hidden binary variable \(s_{k,t}\), which is 1 or 0.
+We do the inference for the hidden variable \(s_{k,t}\) according to Poisson distribution according to Reference\cite{Diao:2012wj} 10,11.
 If the state of attention of social issue k at time t is "not at peak", then the probability density function is
-\(p([Ax_(k,t) ]|s_(k,t)=0)=e^(-μ_0 )  μ_0^([Ax_(k,t)])/([Ax_(k,t)]!)\) otherwise the probability density function is \(p([Ax_(k,t) ]|s_(k,t)=1)=e^(-μ_1 )  μ_1^([Ax_(k,t)])/([Ax_(k,t)])\)
-In the above functions the symbol \(x_{k,t}\) denotes the attention of social issue k at time t , the symbol A denotes the constant, \(μ_0\) and \(μ_1\) represent the average of \([Ax_(k,t)]\) at peak and not at peak respectively.
-The state sk,t is inferred from \(ratio=p([Ax_(k,t) ]|s_(k,t)=0)/p([Ax_(k,t) ]|s_(k,t)=1) \).
-In calculation, we use the log ratio to determine whether the attention is at peak as in equation (1).
-logratio>0 indicates that the attention of social issue k at time t is not at peak, otherwise at peak.
-As the attention xk,t is often between 0.01% and 5% in our experiment, we set the constant A in log ratio equation to be〖10〗^4。
-	\(logratio=-(μ_0-μ_1 )+[Ax_(k,t)](log⁡μ_0 -log⁡μ_1)\)
-After the data preprocessing, we get the air pollution state sequence\((a_t)_(t=1,…T)\) and the attention state sequence of each social issue \((s_(k,t))_(t=1,…,T;k=1…n)\), where T denotes the number of time windows.
+\(p(x_{k,t}|s_{k,t}=0)=e^{-\mu_0 }  \frac{\mu_0^{x_{k,t}}}{x_{k,t}!}\) otherwise the probability density function is \(p(x_{k,t}|s_{k,t}=0)=e^{-\mu_1 }  \frac{\mu_1^{x_{k,t}}}{x_{k,t}!}\)
+In the above functions the symbol \(x_{k,t}\) denotes the attention of social issue \(k\) at time \(t\) , the symbol A denotes the constant, \(\mu_0\) and \(\mu_1\) represent the average of \(x_{k,t}\) at peak and not at peak respectively.
+The state \(s_{k,t}\) is inferred from \(ratio=\frac{p(x_{k,t} |s_{k,t}=0)}{p(x_{k,t} |s_{k,t}=1)} \).
+In calculation, we use the log ratio to determine whether the attention is at peak as in equation (\ref{eq:logratio}).
+\(\log ratio>0 \) indicates that the attention of social issue \(k\) at time \(t\) is not at peak, otherwise at peak.
+\begin{equation}
+\label{eq:logratio}
+\log ratio=-(\mu_0-\mu_1 )+x_{k,t}(\log \mu_0 -\log⁡ \mu_1)
+\end{equation}
 
 \begin{algorithm}
+\label{alg:eventKeywordsSearchMethod}
 \caption{Spectral Clustering Based Event Phrase Extraction}
@@
 As shown in Figure \ref{fig: windowsBurstyWordGraph} below, we will one area, a hot word of the time window and hot words between to diagram.
-Hot words set \(\ mathcal{B}_{k, t} \) formed in FIG using \textbf{hot word graph} \(\mathcal {G}_{k, t} = (\mathcal{B}_{k, t}, \mathcal{E}_{k, t}) \) indicates,
-\(\mathcal{E}_{k, t} = \{(a, b) | a \in \mathcal{B}_{k, t}, b \in \mathcal {B} _ {k, t }, PMI (\mathcal{D}_{k, t}, a, b)> 0 \} \), where \(PMI (\mathcal{D}_{k, t}, a, b) \) the field \(k \) time window \(t \) related microblog \(\ mathcal {D} _ {k, t} \) on the word \(a \) and the word \(b \) point metric information between each other.
+Hot words set \(\mathcal{B}_{k, t} \) formed in FIG using \textbf{hot word graph} \(\mathcal{G}_{k, t} = (\mathcal{B}_{k, t}, \mathcal{E}_{k, t}) \) indicates,
+\(\mathcal{E}_{k, t} = \{(a, b) | a \in \mathcal{B}_{k, t}, b \in \mathcal{B}_{k, t }, PMI (\mathcal{D}_{k, t}, a, b)> 0 \} \), where \(PMI (\mathcal{D}_{k, t}, a, b) \) the field \(k \) time window \(t \) related microblog \(\mathcal{D}_{k, t} \) on the word \(a\) and the word \(b\) point metric information between each other.
 % Refer to bursty.py getSimGraph () function
 
-Given a field \(k \) and the time window \(t \), in which the number of events can not be determined in advance.
-The two most extreme situations are: events coarse granularity, said the event is equal to the number of Figure \(\ mathcal {G} _ {k, t} \) in the number of connected components; events finer granularity display, event number equal to \(\ mathcal {G} _ {k, t} \) the number of points.
+Given a field \(k\) and the time window \(t\), in which the number of events can not be determined in advance.
+The two most extreme situations are: events coarse granularity, said the event is equal to the number of Figure \(\mathcal{G}_{k, t} \) in the number of connected components; events finer granularity display, event number equal to \(\mathcal{G}_{k, t} \) the number of points.
 To do this, we use the Density to the degree of density of quantum graphs \(2 \#Edge / (\# Node \ cdot (\# Node-1)) \), the more the greater if the edge density in the range of Density in \((0,1] \).
 Density can be a good indicator to determine the size indicates the event: too many unrelated phrases to put together an event can not be represented, too fine particle size, such as a single word can represent only part of the event; only in close co-occurrence of the phrase to a reasonable It indicates that the event granularity.
-To this end, we have designed events phrase search algorithm \ ref {alg: eventKeywordsSearchMethod}: We try to find a reasonable number of spectral clustering Clustering \(n \), let \(n \) from a smaller value ( event corresponds to coarser granularity representation) to start the search, then the most likely cluster cluster size is too large, its performance is the clustering results in one or more small Density indicators; continue to increase the number of clusters \(n \), the event represents reduced size, reduced the size of clusters of clusters, thus making the Density index increases; when all cluster clustering Density indicators are larger than the threshold \(\tau \), the search terminates, returning clustering results \(\mathcal{C}_{k, t}\).
-As the above process algorithm \ref{alg: eventKeywordsSearchMethod} description line 2 to line 5, we use in practice \(\tau = 0.6 \).
+To this end, we have designed events phrase search algorithm \ref{alg:eventKeywordsSearchMethod}: We try to find a reasonable number of spectral clustering Clustering \(n \), let \(n \) from a smaller value ( event corresponds to coarser granularity representation) to start the search, then the most likely cluster cluster size is too large, its performance is the clustering results in one or more small Density indicators; continue to increase the number of clusters \(n \), the event represents reduced size, reduced the size of clusters of clusters, thus making the Density index increases; when all cluster clustering Density indicators are larger than the threshold \(\tau \), the search terminates, returning clustering results \(\mathcal{C}_{k, t}\).
+As the above process algorithm \ref{alg:eventKeywordsSearchMethod} description line 2 to line 5, we use in practice \(\rho = 0.6 \).
 We call \(\mathcal{C}_{k, t} \) results in each cluster to cluster \textbf{event} phrase.
@@
 Weibo text length is shorter, not all of the microblogging event will include the phrase \(\mathcal{C}_{k, t, i} \) in all the words.
-Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\ mathcal {D} _ {k, t, i} \) in.
-For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\ mathcal{D }_{k, t, i} \) in.
+Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\mathcal{D}_{k, t, i} \) in.
+For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\mathcal{D}_{k, t, i} \) in.
 Ultimately, we can get the field \(k \) next time window \(t \) in the event the phrase relating to events microblogging \(\{(\mathcal{C}_{k, t, i}, \mathcal{D}_{k, t, i}) \}_{i=1}^{| \mathcal{C}_{k, t} |} \).

### 2016-07-15 paper/coling2016.tex
add coling

--- 2016-07-15 paper/ieeeFormat.tex
@@
-\documentclass[conference,compsoc]{IEEEtran}
-\usepackage{comment}
-\usepackage{subfigure}
-\usepackage{enumitem}
+%
+% File coling2016.tex
+%
+% Contact: mutiyama@nict.go.jp
+%%
+%% Based on the style files for COLING-2014, which were, in turn,
+%% Based on the style files for ACL-2014, which were, in turn,
+%% Based on the style files for ACL-2013, which were, in turn,
+%% Based on the style files for ACL-2012, which were, in turn,
+%% based on the style files for ACL-2011, which were, in turn, 
+%% based on the style files for ACL-2010, which were, in turn, 
+%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
+%% based on the style files for EACL-2009 and IJCNLP-2008...
+
+%% Based on the style files for EACL 2006 by 
+%%e.agirre@ehu.es or Sergi.Balari@uab.es
+%% and that of ACL 08 by Joakim Nivre and Noah Smith
+
+\documentclass[11pt]{article}
+\usepackage{coling2016}
+\usepackage{times}
+\usepackage{url}
+\usepackage{latexsym}
+\usepackage{bm}%used for bm
 \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
 \usepackage{algorithmic}
+\usepackage{amssymb}%used for empty set symbol
+\usepackage{amsmath} %used for maths symbols
 
-\usepackage{bm}%used for bm
-\usepackage{graphics}
-\usepackage{graphicx}
-\usepackage{amsmath} %used for maths symbols
-\usepackage{amssymb}%used for empty set symbol
-\usepackage{url}
-\usepackage{xcolor}% or package color
+%\setlength\titlebox{5cm}
 
-%used for quotes
-\usepackage{epigraph}
-\setlength\epigraphwidth{\columnwidth}
-\setlength\epigraphrule{0pt}
+% You can expand the titlebox if you need extra space
+% to show all the authors. Please do not make the titlebox
+% smaller than 5cm (the original size); we will check this
+% in the camera-ready version and ask you to change it back.
 
-\usepackage{array}
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\title{Instructions for COLING-2016 Proceedings}
+
+\author{First Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\\And
+  Second Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\}
+
+\date{}
 
 \begin{document}
-
-%主动感知的
-\title{Normal States Training for High Accuracy Event Detection}
-
 \maketitle
@@
 In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things.
-%TODO
 In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
 Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
-%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.
 \end{abstract}
 
-%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.
+\section{Introduction}
+\label{intro}
 
-\section{Introduction}
-%\textit{``To study the abnormal is the best way of understanding the normal."}---William James
-%\textit{``The unpredictable or the rare is more newsworthy than the routine."}---Allan Bell
-
-%The event detection task always tries to find out the newsworthy messages from cyberspace. 
 With the increasing of cyberspace data, there is a growing need for detecting events accurately.
@@
 
-\begin{figure}
-    \label{fig:modelDesc}
-    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
-    \caption{\textsc{NSDetector}'s process flow, taking \textbf{military} related events in cyberspace as an example.
-\textsc{NSDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
-\end{figure}
-
-For example, in ideal conditions an event detection system for anti-terrorism has the knowledge about the normal state such as “the words ISIS and Syria are both high-frequent, while the word Russia is not so frequent as them”.
-With the knowledge of normal state, the system for anti-terrorism can detect the event of “Russia's anti-ISIS op in Syria” as Russia appeared more frequent than the normal state and appeared with ISIS and Syria.
-After detection, the ideal event detection system also updates the normal state by considering the new coming data.
-
 \section{Related Works}
-\subsection{Event Detection}
 
@@
 As these models need the whole dataset as the input, they are offline detections, which is not scalability for large dynamic dataset such as microblogs.
-\subsection{Knowledge Base}
 
-%Twitter Trending Topic Classification
-%We use PageRank-HITS\cite{Yan:2015wq} algorithm to update score of categories in wikipedia.
+\section{Translation of non-English Terms}
 
-%3*4 figures, 0-11 is reorganized in the following order: 0, 1, 4, 5, 8, 9;
-%2, 3, 6, 7, 10, 11;
-\begin{figure*}[ht]
-        \centering
-        \label{fig:subfig} %% label for entire figure
-        \subfigure[\((0.25,0.25,0.25)\)]{
-                \label{fig:subfig:a} %% label for first subfigure a
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph0.pdf}
-        }
-        \subfigure[\((0.5,0.5,0.5)\)]{
-                \label{fig:subfig:b} %% label for second subfigure b
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph1.pdf}
-        } 
-        \subfigure[\((0.25,0.25,0.75)\)]{
-                \label{fig:subfig:c} %% label for third subfigure c
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph4.pdf}
-        }
-        \subfigure[\((0.5,0.5,1.5)\)]{
-                \label{fig:subfig:a} %% label for first subfigure d
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph5.pdf}
-        }
-        \subfigure[\((0.25,0.75,0.75)\)]{
-                \label{fig:subfig:d} %% label for third subfigure e
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph8.pdf}
-        }
-        \subfigure[\((0.5,1.5,1.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure f
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph9.pdf}
-        }\hspace{1in}
-        \subfigure[\((1.5,1.5,1.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure g
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph2.pdf}
-        }
-        \subfigure[\((2.5,2.5,2.5)\)]{
-                \label{fig:subfig:a} %% label for first subfigure h
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph3.pdf}
-        }
-        \subfigure[\((1.5,1.5,2.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure i
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph6.pdf}
-        }
-        \subfigure[\((2.5,2.5,3.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure j
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph7.pdf}
-        }
-        \subfigure[\((1.5,2.5,2.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure k
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph10.pdf}
-        }
-        \subfigure[\((2.5,3.5,3.5)\)]{
-                \label{fig:subfig:a} %% label for first subfigure l
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph11.pdf}
-        }\hspace{1in}
-        \caption{Illustration of Dirichlet distribution's probabilistic density on the 3-dimensional simplex when given different priors.
-(a,b,g,h) the left four subfigures illustrate the probabilistic density when given the symetric priors for Dirichlet distribution; (c,d,i,j) the central subfigures illustrate the probablistic density given ; (e,f,k,l) }
-\end{figure*}
-
-\section{Proposed Method}
 \begin{table}
@@
 
-\subsection{Initialization of Normal States}
-In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
 \begin{algorithm}
@@
 \end{algorithm}
-
-\cite{faralli2015large} propose the Twixonomy Graph.
-
-%TODO
-
-\begin{figure}
-    \centering
-    \includegraphics[width=.85\columnwidth]{img/initializationExample.pdf}  
-    \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
-    \label{fig:modelDesc}
-\end{figure}
-
-\subsection{Normal States' Maintenance}
-KB-Prior-LDA
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.75\columnwidth]{model/lda_tikz.pdf}
-    \caption{Probabilistic model for training normal states by using history information.}
-    %The convolution neural network for extracting character-level representations of words. Dashed arrows indicate a dropout layer applied before character embeddings are input to CNN.}
-    \label{fig:cnn}
-\end{figure}
 
@@
 
-\cite{wallach2008structured}\footnote{\url{https://github.com/mimno/Mallet/blob/master/src/cc/mallet/types/Dirichlet.java}}
-
 \subsection{Detecting Events from Normal States}
@@
 
-\begin{figure}
-\centering
-\includegraphics[height=3cm]{img/wordClusterGraph.eps}
-%todo
-\caption{Hot words between the heat pattern forming word time window edge weight calculated by the PMI obtained between words, to obtain spectral clustering clustering clustering}
-\label{fig: windowsBurstyWordGraph}
-\end{figure}
-
 \textbf{event} phrase Mining
@@
 
-\textbf{detected events related to micro-blog}
-\ \
-By algorithm \ref{alg:eventKeywordsSearchMethod} find art \(k \) time window \ \(t \) within the \(| \mathcal{C}_{k, t} | \) events phrase later, you can also further find each event and the corresponding event phrase microblogging.
-We looked at the first \(i \) events phrase \(\mathcal{C}_{k, t, i} \),
-The phrase based on the number of elements distinguish the event, there are three situations: (1) the phrase event more than two hot words, he said while the event is not a phrase between any two words We have a very strong relationship between the co-occurrence, so just pay attention to the co-occurrence relationship stronger side; (2) event phrase has two hot words; (3) the event is only a hot word in the phrase.
-Weibo text length is shorter, not all of the microblogging event will include the phrase \(\mathcal{C}_{k, t, i} \) in all the words.
-Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\mathcal{D}_{k, t, i} \) in.
-For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\mathcal{D}_{k, t, i} \) in.
-Ultimately, we can get the field \(k \) next time window \(t \) in the event the phrase relating to events microblogging \(\{(\mathcal{C}_{k, t, i}, \mathcal{D}_{k, t, i}) \}_{i=1}^{| \mathcal{C}_{k, t} |} \).
+\section*{Acknowledgements}
 
-\section{Experiments}
-\subsection{Effects of Normal States Initialization}
-We use 20newsgroups\cite{lang1995newsweeder} dataset\footnote{http://qwone.com/~jason/20Newsgroups} to check the effects of normal states initialization.
+\begin{thebibliography}{}
 
-What's NPMI? maybe can refer to \cite{Aletras2013EvaluatingTC}\cite{Rder2015ExploringTS}\footnote{https://github.com/AKSW/Palmetto}.
-\begin{table}[]
-\centering
-\caption{My caption}
-\label{my-label}
-\begin{tabular}{|l|l|}
-\hline
-comp.graphics            & Category:Computer graphics      \\ \hline
-comp.os.ms-windows.misc  & Category:Microsoft Windows      \\ \hline
-comp.sys.ibm.pc.hardware & Category:IBM personal computers \\ \hline
-comp.sys.mac.hardware    & Category:Macintosh computers    \\ \hline
-comp.windows.x           & Category:X Window System        \\ \hline
-rec.autos                & Category:Automobiles            \\ \hline
-rec.motorcycles          & Category:Motorcycles            \\ \hline
-rec.sport.baseball       & Category:Baseball               \\ \hline
-rec.sport.hockey         & Category:Hockey                 \\ \hline
-sci.crypt                & Category:Cryptography           \\ \hline
-sci.electronics          & Category:Electronics            \\ \hline
-sci.med                  & Category:Medicine               \\ \hline
-sci.space                & Category:Outer space            \\ \hline
-misc.forsale             & Category:Sales                  \\ \hline
-talk.politics.misc       & Category:Politics               \\ \hline
-talk.politics.guns       & Category:Gun politics          \\ \hline
-talk.politics.mideast    & Category:Middle East           \\ \hline
-talk.religion.misc       & Category:Religion               \\ \hline
-alt.atheism              & Category:Atheism                \\ \hline
-soc.religion.christian   & Category:Christians             \\ \hline
-\end{tabular}
-\end{table}
+\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
+Alfred~V. Aho and Jeffrey~D. Ullman.
+\newblock 1972.
+\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
+\newblock Prentice-{Hall}, Englewood Cliffs, NJ.
 
-\begin{figure}
-        \centering
-        \includegraphics[height=4.0cm]{img/pmi.pdf}
-        \caption{The quality of all twitter topics learned by NS-Prior-LDA increases with normal states weight (\(\lambda\)) before \(\lambda=12.8\).
-The optimized PMI is gained with moderate normal states weight when considering topics \(k\leq K_{\bm{KB}}\) and topics \(k > K_{\bm{KB}}\) together.}
-\end{figure}
+\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
+{American Psychological Association}.
+\newblock 1983.
+\newblock {\em Publications Manual}.
+\newblock American Psychological Association, Washington, DC.
 
-\begin{figure}
-        \centering
-        \includegraphics[width=1.0\columnwidth]{img/NPMI.pdf}
-        \caption{NPMI}
-\end{figure}
+\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
+{Association for Computing Machinery}.
+\newblock 1983.
+\newblock {\em Computing Reviews}, 24(11):503--512.
 
-\begin{table}
-\centering
-\caption{The PMI of twitter topics learned by NS-Prior-LDA, its variant, and other baselines}
-    \begin{tabular}{|l|l|c|}
-    \hline
-    Model & Prior Knowledge & PMI \\ \hline
-    LDA & None  & 1.265 \(\pm\) 0.013     \\ \hline
-    BBTM\cite{Yan:2015wm} & None    & 1.467 \(\pm\) 0.017     \\ \hline
-    NS-Prior-LDA\(^{(-)}\)   &   \begin{tabular}[c]{@{}l@{}}\footnotesize{Words in categories simply}\\ \footnotesize{extracted from Wikipedia}\end{tabular} & 1.439 \(\pm\) 0.010     \\ \hline
-    NS-Prior-LDA         & \begin{tabular}[c]{@{}l@{}}\footnotesize{Normal states initialized} \\\footnotesize{from wikipedia}\end{tabular} & 1.523 \(\pm\) 0.017     \\ \hline
-    \end{tabular}
-\label{tbl:NS-Prior-LDA}
-\end{table}
+\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
+Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
+\newblock 1981.
+\newblock Alternation.
+\newblock {\em Journal of the Association for Computing Machinery},
+  28(1):114--133.
 
-\begin{table*}[ht]
-\centering
-\caption{My caption}
-\label{my-label}
-\scalebox{0.88}{
-\begin{tabular}{|cc|cc|cc|cc|cc|cc|}
-\hline
-\multicolumn{2}{|c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Middle East}} & \multicolumn{2}{c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Mobile Phones}} & \multicolumn{2}{c|}{\textit{Video Games}} \\
-\begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} \\
-\hline
-aircraft & air\scriptsize(3253) & health & weight\scriptsize(16344) & al & \textcolor{red}{\textit{\#syria}}\scriptsize(4212) & army & killed\scriptsize(4055)  & android & iphone\scriptsize (13674) & game & games\scriptsize(8812) \\
-air & plane & patients & loss & israel & \textcolor{red}{\textit{\#bahrain}} & military & news & mobile & apple & player & liked \\ 
-airport & flight & medical & diet & iran & people & air & \textcolor{red}{\textit{\#libya}}\scriptsize(3503) & nokia & android & playstation & free \\ 
-flight & time & disease & health & arab & israel & command & libya & ios & app & gameplay & xbox \\
-airline & airlines & treatment & cancer & israeli & police & force & rebels & phone & ipad & nintendo & 360 \\
-airlines & news & hospital & lose & egypt & \textcolor{red}{\textit{\#libya}}\scriptsize(2557) & regiment & people & samsung & samsung & games & playing \\
-aviation & boat & patient & fat & egyptian & \#egypt & forces & police & game & mobile & players & played \\
-flying & airport & clinical & tips & ibn & news & squadron & war & app & blackberry & xbox &iphone\scriptsize(2820)\\
-pilot & force & symptoms & treatment & jerusalem & \#israel & infantry & libyan & iphone & tablet & mode & time\\
-squadron & fly & cancer & body & syria & world & battle & attack & htc & apps & arcade & \textcolor{red}{\textit{ps3}}\\
-flights & hurricane & cells & healthy & iraq & syria & commander & u.s. & smartphone & free & wii & trailer\\
-pilots & navy & blood & study & palestinian & protest & ship & gaddafi & phones & \#android & multiplayer & online\\
-raf & flying & therapy & pain & syrian & israeli & corps & army & blackberry & htc & sega & hours\\
-airways & aircraft & drug & exercise & iranian & egypt & navy & forces & apps & google & console & ipad\\
-fighter & \textcolor{red}{\textit{irene}} & medicine & \#health & ottoman & al & brigade & pakistan & ipad & galaxy & enemies & app\\
-boeing & crew & brain & natural & islamic & syrian & battalion & afghanistan & gsm & ios & characters & player\\
-runway & sky & care & disease & iraqi & protesters & lieutenant & military & lte & store & playable & wii\\
-force & crash & syndrome & acne & abu & arab & aircraft & attacks & symbian & windows & character & ops\\
-crashed & jet & infection & hair & jewish & rights & officer & troops & devices & mac & video & download\\
-flew & pilot & disorder & surgery & persian & libya & naval & dead & smartphones & phones & graphics & nintendo\\
-\hline
-\end{tabular}
-}
-\end{table*}
+\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
+Dan Gusfield.
+\newblock 1997.
+\newblock {\em Algorithms on Strings, Trees and Sequences}.
+\newblock Cambridge University Press, Cambridge, UK.
 
-\begin{table*}[ht]
-\centering
-\caption{My caption}
-\label{my-label}
-\subtable[Twitter Dataset Statistics]{
-\begin{tabular}{|l|r|}
-\hline
-Time range & \begin{tabular}[c]{@{}l@{}}2011/06/30\\ -2011/09/15\end{tabular} \\ \hline
-Tweet Number & 36,627,434 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Event Number \\ in Benchmark1\end{tabular} & 27 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Event Number \\ in Benchmark2\end{tabular} & 523 \\ \hline
-\end{tabular}
-}\quad \quad
-\subtable[Event Detection Results]{
-    \begin{tabular}{|l|l|l|l|l|}
-    \hline
-    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate(Duplicate \\ Event Rate)\end{tabular} \\ \hline
-    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
-    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
-    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
-    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
-    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
-    BBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
-    \textsc{NSDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
-    \end{tabular}
-}
-\end{table*}
-
-\begin{table*}[ht]
-\centering
-\caption{Events about \textit{vehicles} detected by systems between 2011-07-20 and 2011-07-30}
-\label{my-label}
-\begin{tabular}{|l|L{3cm}|l|c|}
-\hline
-\multicolumn{1}{|c|}{Date} & \multicolumn{1}{c|}{Event key words} & \multicolumn{1}{c|}{Representative event tweet} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Number of \\ event tweet\end{tabular}} \\ \hline
-7/20/11 & \begin{tabular}[c]{@{}l@{}}American, airlines, \\ order, planes\end{tabular} & \begin{tabular}[c]{@{}l@{}}NDTV: American Airlines orders 460 new planes from \\ Boeing, Airbus http://bit.ly/p1ZgYG\end{tabular} & 31 \\ \hline
-7/26/11 & \begin{tabular}[c]{@{}l@{}}Morocco, military, \\ plane, crash\end{tabular} & \begin{tabular}[c]{@{}l@{}}BBC News - Morocco military plane crash kills 78 \\ http://t.co/uwnLv8L\end{tabular} & 36 \\ \hline
-7/27/11 & air, Canada & \begin{tabular}[c]{@{}l@{}}Smoke in galley forces Air Canada flight back to airport. \\ Plane landed safely in Sydney, Australia after dumping fuel\end{tabular} & 48 \\ \hline
-7/30/11 & \begin{tabular}[c]{@{}l@{}}Caribbean, airlines, \\ crashes, Guyana\end{tabular} & \begin{tabular}[c]{@{}l@{}}Caribbean Airlines Jet Crash-Lands In Guyana All 163 \\ Passengers, Crew Survive http://t.co/qPVD3WJ\end{tabular} & 57 \\ \hline
-\end{tabular}
-\end{table*}
-
-\begin{table*}[ht]
-\centering
-\caption{Events about \textit{military} detected by systems between 2011-07-20 and 2011-07-30}
-\label{my-label}
-\begin{tabular}{|l|L{3cm}|l|l|}
-\hline
-Date & Event key words & Representative event tweet & \begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular} \\ \hline
-7/20/11 & \begin{tabular}[c]{@{}l@{}}Serbia, crimes, \\ fugitive, arrests\end{tabular} & Serbia: Serbia arrests last war crimes fugitive-TV- Reuters & 27 \\ \hline
-7/20/11 & Somalia, famine & \begin{tabular}[c]{@{}l@{}}UN declares famine in Somalia. What can we do to save \\ 3.7million lives? http://bit.ly/r1Rq7R\end{tabular} & 89 \\ \hline
-7/21/11 & \begin{tabular}[c]{@{}l@{}}U.S., military, \\accept, gay, \\lesbian, openly\end{tabular} & \begin{tabular}[c]{@{}l@{}}RT @cnnbrk: Pentagon is set to certify that the U.S.
-military \\ is prepared to accept openly gay and lesbian service members \\ \#dadt\end{tabular} & 20 \\ \hline
-7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman...˙http://dlvr.it/cLbk8\end{tabular} & 557 \\ \hline
-7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 \\ \hline
-7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 25 \\ \hline
-7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 20 \\ \hline
-7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 \\ \hline
-\end{tabular}
-\end{table*}
-
-\begin{figure*}
-    \label{fig:algorithm}
-    \includegraphics[width=1.0\textwidth]{img/screenShot.png}
-    \caption{An illustration of the time series of Military related states on Twitter dataset from 2011-06-30 to 2011-09-15.}
-\end{figure*}
-
-\subsection{Data set and experiment settings}
-\textbf{Data set.} We conduct the empirical analysis on a twitter dataset which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}.
-Due to the developer policy of Twitter\footnote{https://dev.twitter.com/overview/terms/policy}, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{http://demeter.inf.ed.ac.uk/cross/docs/fsd\_corpus.tar.gz}.
-We collected the tweets' contents according to the IDs with the help of Twitter API.
-
-%TODO
-The benchmark \textit{Edinburgh twitter corpus} contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}} and 90 million tweets.
-Though we cannot get the whole dataset due to the limit of Twitter API, after neccessary pre-processing, our rebuilt dataset still contains 36,627,434 tweets, which spans identically from 2011/06/30 to 2011/09/15, and also covers 27 labeled events.
-More details of the original dataset are described in \cite{petrovic2010edinburgh}.
-
-20-newsgroup\footnote{http://qwone.com/~jason/20Newsgroups/}
-
-\textbf{Benchmark1} The first set of the ground truth about events in the corpus are provided by \cite{petrovic2013can}, which is mentioned above. 
-And 27 events ...
-
-\textbf{Benchmark2} here.
-
-\textbf{Normal States Initialization} here.
-
-\textbf{Baseline}
-
-UMass System
-
-LSH
-
-TimeUserLDA
-
-Twevent
-
-EDCoW
-
-BBTM
-
-\textbf{Model Setting}
-
-\subsection{Validity of Normal States}
-\textbf{Topic Coherence} \cite{roder2015exploring}
-\subsection{Topical Words Learned by NS-Prior-LDA}
-\textbf{PMI}
-\subsection{Evaluation of Detected Events}
-\textbf{Precision} Precision@Benchmark1, Precision@Benchmark2
-
-\textbf{Recall}
-
-\textbf{Accuracy}
-
-\textbf{DERate(Duplicate Event Rate)}
-\subsection{Case Study}
-
-\subsection{Application on Reddit}
-
-\section{Conclusions \& Future Work}
-Microbiolog is mixed with user interests and external events.
-The quality of event detection in microblog depends on how we distinguish them.
-We exploit user profile to discover events by filtering out user interest-related tweets.
-We further treat the arriving data as stream and run the detection in online learning style.
-The experiments demonstrates that our method is effective and efficient for online event detection in microblogs.
-
-\bibliographystyle{unsrt}
-\bibliography{paperbib}
+\end{thebibliography}
 

### 2016-07-15 paper/coling2016.tex
coling

--- 2016-07-15 paper/ieeeFormat.tex
@@
-\documentclass[conference,compsoc]{IEEEtran}
-\usepackage{comment}
-\usepackage{subfigure}
-\usepackage{enumitem}
+%
+% File coling2016.tex
+%
+% Contact: mutiyama@nict.go.jp
+%%
+%% Based on the style files for COLING-2014, which were, in turn,
+%% Based on the style files for ACL-2014, which were, in turn,
+%% Based on the style files for ACL-2013, which were, in turn,
+%% Based on the style files for ACL-2012, which were, in turn,
+%% based on the style files for ACL-2011, which were, in turn, 
+%% based on the style files for ACL-2010, which were, in turn, 
+%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
+%% based on the style files for EACL-2009 and IJCNLP-2008...
+
+%% Based on the style files for EACL 2006 by 
+%%e.agirre@ehu.es or Sergi.Balari@uab.es
+%% and that of ACL 08 by Joakim Nivre and Noah Smith
+
+\documentclass[11pt]{article}
+\usepackage{coling2016}
+\usepackage{times}
+\usepackage{url}
+\usepackage{latexsym}
+\usepackage{bm}%used for bm
 \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
 \usepackage{algorithmic}
+\usepackage{amssymb}%used for empty set symbol
+\usepackage{amsmath} %used for maths symbols
 
-\usepackage{bm}%used for bm
 \usepackage{graphics}
 \usepackage{graphicx}
-\usepackage{amsmath} %used for maths symbols
-\usepackage{amssymb}%used for empty set symbol
-\usepackage{url}
-\usepackage{xcolor}% or package color
-
-%used for quotes
-\usepackage{epigraph}
-\setlength\epigraphwidth{\columnwidth}
-\setlength\epigraphrule{0pt}
-
+\usepackage{subfigure}
 \usepackage{array}
@@
 
+%\setlength\titlebox{5cm}
+
+% You can expand the titlebox if you need extra space
+% to show all the authors. Please do not make the titlebox
+% smaller than 5cm (the original size); we will check this
+% in the camera-ready version and ask you to change it back.
+
+\title{Instructions for COLING-2016 Proceedings}
+
+\author{First Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\\And
+  Second Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\}
+
+\date{}
+
 \begin{document}
-
-%主动感知的
-\title{Normal States Training for High Accuracy Event Detection}
-
 \maketitle
@@
 We call \(\mathcal{C}_{k, t} \) results in each cluster to cluster \textbf{event} phrase.
-
-\textbf{detected events related to micro-blog}
-\ \
-By algorithm \ref{alg:eventKeywordsSearchMethod} find art \(k \) time window \ \(t \) within the \(| \mathcal{C}_{k, t} | \) events phrase later, you can also further find each event and the corresponding event phrase microblogging.
-We looked at the first \(i \) events phrase \(\mathcal{C}_{k, t, i} \),
-The phrase based on the number of elements distinguish the event, there are three situations: (1) the phrase event more than two hot words, he said while the event is not a phrase between any two words We have a very strong relationship between the co-occurrence, so just pay attention to the co-occurrence relationship stronger side; (2) event phrase has two hot words; (3) the event is only a hot word in the phrase.
-Weibo text length is shorter, not all of the microblogging event will include the phrase \(\mathcal{C}_{k, t, i} \) in all the words.
-Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\mathcal{D}_{k, t, i} \) in.
-For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\mathcal{D}_{k, t, i} \) in.
-Ultimately, we can get the field \(k \) next time window \(t \) in the event the phrase relating to events microblogging \(\{(\mathcal{C}_{k, t, i}, \mathcal{D}_{k, t, i}) \}_{i=1}^{| \mathcal{C}_{k, t} |} \).
 

### 2016-07-19 paper/ieeeFormat.tex
format table

@@
 \usepackage{xcolor}% or package color
+
+\usepackage{multirow}% for table
 
@@
 \begin{table}
-\begin{tabular}{|p{0.1\columnwidth}|p{0.8\columnwidth}|} \hline
-\(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \hline
-\(G^{(1)}\) & Category-Page Bipartite Graph in Knowledge Base\\ \hline
-\(G^{(2)}\) & Page-Content Bipartite Graph in Knowledge Base\\ \hline
-\(c\) & topic related category node in \(G^{(0)}\) and \(G^{(1)}\) \\ \hline
-\(K_{\bm{KB}}\) & number of pre-defined topics by Knowledge Base \\ \hline
-\(f_{c,w}\) & word \(w\)'s normal state (chi-square score) in category \(c\) \\ \hline
-\(\lambda\) & normal state weight in  NS-Prior-LDA\\ \hline
-\(\tau_{c,w}\) & word \(w\)'s prior knowledge confidence for topic \(c\) in NS-Prior-LDA\\ \hline
-\(S_c\) & topic \(c\)'s all normal states related words \\ \hline
-\(K\) & number of topics in NS-Prior-LDA such as \(K>K_{\bm{KB}}\)\\ \hline
-\(\mathcal{B}_{c, t}\)  & hot words set detected from topic \(k\) at time \(t\)  \\ \hline
-\(\mathcal{G}_{c, t}\)  & hot word graph constructed from \(\mathcal{B}_{c, t}\) \\ \hline
-\(\mathcal{C}_{c,t,i}\) & event \(i\)-th related words in topic \(c\) at time \(t\) \\ \hline
-\(\mathcal{D}_{c,t,i}\) & event \(i\)-th related tweets in topic \(c\) at time \(t\) \\ \hline
-\(\rho\) & density threshold for the sub-graph constructed by event words  \\ \hline
+\begin{tabular}{|c|p{0.1\columnwidth}|p{0.55\columnwidth}|} \hline
+%first part: normalization initialization
+\multirow{5}{0.18\columnwidth}{Normalization Initialization} & \(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \cline{2-3}
+& \(G^{(1)}\) & Category-Page Bipartite Graph in Knowledge Base\\ \cline{2-3}
+& \(G^{(2)}\) & Page-Content Bipartite Graph in Knowledge Base\\ \cline{2-3}
+& \(c\) & topic related category node in \(G^{(0)}\) and \(G^{(1)}\) \\ \cline{2-3}
+& \(K_{\bm{KB}}\) & number of pre-defined topics by Knowledge Base \\ \cline{2-3}
+& \(f_{c,w}\) & word \(w\)'s normal state (chi-square score) in category \(c\) \\ \hline
+%second part: normalization maintenance
+\multirow{4}{0.18\columnwidth}{Normalization Maintenance} & \(\lambda\) & normal state weight in  NS-Prior-LDA\\ \cline{2-3}
+& \(\tau_{c,w}\) & word \(w\)'s prior knowledge confidence for topic \(c\) in NS-Prior-LDA\\ \cline{2-3}
+& \(S_c\) & topic \(c\)'s all normal states related words \\ \cline{2-3}
+& \(K\) & number of topics in NS-Prior-LDA such as \(K>K_{\bm{KB}}\)\\ \hline
+%third part: event detection
+\multirow{5}{0.18\columnwidth}{Event Detection} & \(\mathcal{B}_{c, t}\)  & hot words set detected from topic \(k\) at time \(t\)  \\ \cline{2-3}
+& \(\mathcal{G}_{c, t}\)  & hot word graph constructed from \(\mathcal{B}_{c, t}\) \\ \cline{2-3}
+& \(\mathcal{C}_{c,t,i}\) & event \(i\)-th related words in topic \(c\) at time \(t\) \\ \cline{2-3}
+& \(\mathcal{D}_{c,t,i}\) & event \(i\)-th related tweets in topic \(c\) at time \(t\) \\ \cline{2-3}
+& \(\rho\) & density threshold for the sub-graph constructed by event words  \\ \hline
 
@@
 
-\subsection{Initialization of Normal States}
+\subsection{Normal States Initialization}
 In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 

### 2016-08-01 paper/ieeeFormat.tex
before rush again

@@
 
+\newtheorem{rmk}{Definition}% definition
+
 %used for quotes
@@
 %主动感知的
-\title{Normal States Training for High Accuracy Event Detection}
+\title{Is That Enough to Only Use the Recent Data to Detect Events?}
 
@@
 \begin{abstract}
+
 In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
@@
 %The event detection task always tries to find out the newsworthy messages from cyberspace. 
+In big data era, event detection is a profound, popular, but still challenging task. 
+The existing methods include
+
 With the increasing of cyberspace data, there is a growing need for detecting events accurately.
@@
 
+\cite{faralli2015large} propose the Twixonomy Graph.
+
 %Twitter Trending Topic Classification
@@
 \section{Proposed Method}
+\begin{rmk}[Normal States] 
+The normal states of the specific category is defined by a set of tuples, in which the first element is the word \(w^{(c)}_i\) related to the category \(c\), and the second element is the chi-square score \(f(c,w^{(c)}_{i})\) under the category.
+And we denote the normal states of category \(c\) as \(\bm{f}_c=\{<w^{(c)}_i,f(c,w^{(c)}_{i})>\}_{i=1,...,N_c}\).
+\end{rmk}
+
 \begin{table}
@@
 In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
+The knowledge base such as Wikipedia has the structure of classes, subclasses, instances, and the edges between them. 
+This structure usually can be represented as triples in RDF graph\cite{klyne2006rdf}, which is adopted to build DBPedia\cite{auer2007dbpedia} and YAGO\cite{suchanek2007yago} from Wikipedia.  
+But the existing computation on the RDF graph is often time consuming.
+To overcome this obtacle, we propose the new data structure \textit{normal states}, which not only utilize the structure adequately but also maintain the information about what happened and what's happening more efficiently than RDF.
+\begin{enumerate}[labelindent=\parindent,leftmargin=*]
+\item Taxonomy.
+Indicates that the classification relationship, for example, Society this classification page contains Politics classification page, further contains Military, and Society itself is included in the topic classifications Main;
+\item Category-Page Bipartite graph.
+\item Page-Content Maps.
+\end{enumerate}
+
 \begin{algorithm}
@@
 \end{algorithm}
-
-\cite{faralli2015large} propose the Twixonomy Graph.
 
@@
 \section{Conclusions \& Future Work}
-Microbiolog is mixed with user interests and external events.
-The quality of event detection in microblog depends on how we distinguish them.
-We exploit user profile to discover events by filtering out user interest-related tweets.
-We further treat the arriving data as stream and run the detection in online learning style.
-The experiments demonstrates that our method is effective and efficient for online event detection in microblogs.
 

### 2016-08-03 paper/ieeeFormat.tex
introduction version 1

@@
 %主动感知的
-\title{Is That Enough to Only Use the Recent Data to Detect Events?}
+\title{Is That Enough to Use the Recent Data to Detect Events?}
+Revealing the Important Factors on the High Accuracy Event Detection
+%点明factor是什么——能准确描述历史知识的model，该model的表述能力起码能够model概念和概念之间的联系；model应该有一个实时自学习功能，即在历史知识的基础上，能在不断到来的新数据流上更新自己的知识。（“支持”恐怖组织，“打击”恐怖组织）打击恐怖组织的topic中，通常是美国和英国、法国；但是俄罗斯突然出现在该topic的列表中，说明俄罗斯参与打击恐怖组织应该被判别为一个新的事件。需要一个精确描述历史数据中概念之间联系的例子——（找到一个立场发生变化的例子，如果能在叙利亚问题上找到很好，如果不能考虑别的例子）。
 
@@
 \begin{abstract}
+Event detection is an important task to understand what already happened and what is currently happening in the rapid evolving text stream. 
+% what happened不需要了
+% 诸多互联网的应用都迫切需要实时准确的事件检测技术。
+% 由于需要实时监测最新发生的事件，人们通常实时分析最新的数据流来检测可能发生的事件，但很遗憾这种技术的准确率远远不能支撑应用的要求。
 
-In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
-For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
-In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things.
-%TODO
+%举例之后,1这个例子说明需要哪些新技术支持——需要对历史知识有准确的描述，充分体现概念与概念之间的联系；并且能够利用新数据来更新相应的知识，以解决知识库的更新滞后于新数据的问题 2 列举related works，这些技术无法解决这个问题
+%我们的工作。
+
+%在Related Works 之前说明我们这是一个amazing的工作，同时将precision和recall都进行了提升，而一般的工作很难兼顾这一点。
+But existing methods cannot achieve high precision and high recall simultaneously. 
+The reason lies in that they only use the recent data and lack the accumulation of history knowledge. 
+We further find out that the ideal event detection method should have two properties: \textit{organizing history data well} and \textit{self-updating}.
+According to this guideline, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of history data.
 In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
@@
 %The event detection task always tries to find out the newsworthy messages from cyberspace. 
-In big data era, event detection is a profound, popular, but still challenging task. 
-The existing methods include
+In big data era, event detection is an important task to understand what already happened\cite{ge2015bring} and what is currently happening\cite{hughes2009twitter}\cite{sakaki2010earthquake} within the rapid evolving text stream.
+Although many efforts have been made, the performance still needs to be enhanced as the existing methods cannot achieve high precision and high recall simultaneously, only sacrificing the precision for the recall (such as UMass\cite{Allan:2000wu}), or otherwise (such as BBTM\cite{yan2015probabilistic}).
+To analyze the reason, we go deep into the existing two kinds of methods.
 
-With the increasing of cyberspace data, there is a growing need for detecting events accurately.
-Detecting events can mainly benefit the following three folds: (1) understanding what happened in the corpus without checking every single document manually, and generating the timeline to get a bird's eye view of the corpus\cite{ge2015bring}; (2) being aware what is happening currently, which helps to deal with emergencies\cite{hughes2009twitter}\cite{sakaki2010earthquake}; (3) adding detected events and their types as extra structured data information to organize the unstructured text corpus\cite{ritter2012open}.
+The first category of methods, including UMass\cite{Allan:2000wu} and BBTM\cite{yan2015probabilistic}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
+This kind methods can be implemented by clustering of articles\cite{Allan:2000wu}\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topic modeling\cite{Diao:2012wj}\cite{Yan:2015wm} in the recent time windows.
+Taking the clustering of articles as an example, they model the occurred events as clusters, and link the incoming article with an already existed event cluster or assign it as the new detected event.
+The decision is based on whether the dissimilarity between the incoming article and existed event clusters is over the user-specified threshold.
 
-Considering the importance of event detection on the cyberspace data, researchers have have made many efforts, including checking the and the . Therefore, the existing methods are ... and
+The reason why this kind methods cannot achive high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
+This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision.
+On the one hand, UMass\cite{Allan:2000wu} prefers the lower threshold to enlarge the recall but suffers the precision. 
+On the other hand, BBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.
 
-In our study, we find out that the key to improve the accuracy of event detection lies in training the normal states of the focused media/site/domain.
+The second category of methods thouroughly relies on the \textit{history data}. 
+The typical implementation is to train the event triggers\cite{Li2013JointEE}\cite{Nguyen2015EventDA} from history labeled data, then apply the trained model to detect the event related articles, which contain the triggers such as the word \textit{attacked} for the \textit{public security} events.
+This kind methods suffer from the loss of recall. 
+There are two reasons. 
+%没有对历史数据进行很好的组织
+(1) The model does not utilize the history data sufficiently. 
+Usually, the event trigger based method mainly focus on the event related verbs, but often ignores the other word types.
+(2) The model lacks the update mechanism. 
+It only restores the history knowledge but without updating. 
+Some new event related articles may be mistakenly filtered out because not containing previous trained triggers. 
+For example, the tweet ``Russia's intervention in Syria began in September 2015" without an event trigger, which is really related to a \textit{public security} event, may be omitted by the system.
+
+Based on the above analysis, we can make a conclusion that it's not enough to use the recent data to detect events, but not enough to only use the history data for this task either.
+We believe that the ideal event detection method should have two properties: (1) having a good mechanism to organize the history data, and being aware of what happened; (2) having the capability of self-updating, to accumlate the knowledge about what is happening.
+
+%In our study, we find out that the key to improve the accuracy of event detection lies in training the normal states of the focused media/site/domain.
 Based on training normal states accurately, event detection task can be treated as finding terms, articles, or topics which are different from the normal states.
 
-Our intuition is inspired from the news value theory\cite{galtung1965structure}\cite{caple2013delving}, which emphasizes the \textit{news unexpectedness} -- "the unpredictable or the rare is more newsworthy than the routine"\cite{bell1991language}, and "routine events are difficult to assimilate to the news, which favours the novel, the atypical and the unusual"\cite{montgomery2007discourse}.
-Following this guideline, if the journalist knew the normal states, aka, the "routine things" of everyday better, he/she would tend to choose more unexpected news to report. 
+The properties of the ideal event detection method also coincide with the news value theory\cite{galtung1965structure}\cite{caple2013delving}, which emphasizes the \textit{news unexpectedness} -- ``the unpredictable or the rare is more newsworthy than the routine"\cite{bell1991language}, and ``routine events are difficult to assimilate to the news, which favours the novel, the atypical and the unusual"\cite{montgomery2007discourse}.
+Following this guideline, if the journalist knew the normal states, aka, the ``routine things" of everyday better, he/she would tend to choose more unexpected news to report. 
 We suppose that the ideal event detection system performs like a journalist who can find news from cyberspace with the knowledge of the normal states. 
+For example, a journalist had the knowledge about the anti-terrorism as ``the words \textit{ISIS}, \textit{Syria}, \textit{America}, and \textit{France} were both high-frequent and co-occurred, while the word \textit{Russia} was not so frequent as them'' before August 2015, because ``America led the allies, including France, Germany, and United Kindom etc., to counter ISIS"\footnote{\url{https://en.wikipedia.org/wiki/American-led_intervention_in_Syria}}.
+With this knowledge about what happened and what is happening normally, the journalist can detect the event of ``Russia's anti-ISIS operation in Syria"\footnote{\url{https://en.wikipedia.org/wiki/Russian_military_intervention_in_the_Syrian_Civil_War}} when \textit{Russia} appeared more frequent than the normal and appeared with \textit{ISIS} and \textit{Syria} in September 2015.
+After detection, the journalist would update his knowledge about what happened and what's happening for anti-terrorism.
+Comparing to the other journalists who don't have the history knowledge of anti-terrorism, the journalist with that is more likely to report the above mentioned event accurately in time. 
+%Taking another example in our study for example, the tweet ``UN declares famine in Somalia (7/20/2011)"\footnote{\url{https://en.wikipedia.org/wiki/2011_East_Africa_drought}} is related to a \textit{public security} event as the famine has the potential of relating to a war.
+%Being aware of the history knowledge, such as \textit{Vietnamese Famine of 1945}\footnote{\url{https://en.wikipedia.org/wiki/Vietnamese_Famine_of_1945}}, \textit{Dutch famine of 1944-45}\footnote{\url{https://en.wikipedia.org/wiki/Dutch_famine_of_1944-45}} caused by World War II, it's possible to detect it accurately.
+
+It's very close for the ideal event detection method, which holds the previous mentioned two properties (\textit{organizing history data well} and \textit{self-updating}), to perform like the journalist who follows the news value theory.
+To implement the ideal event detection method, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things.
+In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
+
+%The experiments verifed that the
 
@@
     \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
-    \caption{\textsc{NSDetector}'s process flow, taking \textbf{military} related events in cyberspace as an example.
+    \caption{\textsc{NSDetector}'s process flow, taking \textit{public security} related events in cyberspace as an example.
 \textsc{NSDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
@@
 
-For example, in ideal conditions an event detection system for anti-terrorism has the knowledge about the normal state such as “the words ISIS and Syria are both high-frequent, while the word Russia is not so frequent as them”.
-With the knowledge of normal state, the system for anti-terrorism can detect the event of “Russia's anti-ISIS op in Syria” as Russia appeared more frequent than the normal state and appeared with ISIS and Syria.
-After detection, the ideal event detection system also updates the normal state by considering the new coming data.
+The contribution of this paper is mainly in three aspects:
+(1) it points out that the effective way to improve the accuracy of event detection is not only to use the recent data, but also need the historical data to support.
+And found that the introduction of historical data, can significantly improve the accuracy of event detection.
+(2) the a combination of historical data and recent data of the probability model NSDetector.
+The model can combines the historical data and recent events, used to determine the arrival of a new document is a new event, and update the knowledge of new events to the NSDetector, realize what happened and what is happening on the knowledge of the incremental updating.
+(3) we experiment with 30 million tweets benchmark Edinburgh twitter corpus show that our model and accuracy model is the highest compared to will improve the accuracy rate of 9\%; and the recall rate is the highest model compared to the accurate rate was increased by 1\%.
 
 \section{Related Works}
-\subsection{Event Detection}
-
-To train the normal states, the methods of existing systems can be grouped into unsupervised methods and supervised methods based on whether they .
+\textbf{Event Detection.} To train the normal states, the methods of existing systems can be grouped into unsupervised methods and supervised methods based on whether they .
 
@@
 In the journalist metaphor of news value theory, they have the limited knowledge of normal states (aka "routine things") due to the limited history information used.
-More specifically,
-
-The second category, train the triggers\cite{Li2013JointEE}\cite{Nguyen2015EventDA}(\textit{But it has some problems here, these methods are used in event extraction, so what's the relationship between event extraction and event detection?
-and the fired example in \cite{Li2013JointEE}?}).
 
@@
 
+\begin{comment}
  Text similarity based online event detection methods\cite{petrovic2010streaming}\cite{mccreadie2013scalable}  suffer from the lexical variation which means different words describe the same events.
@@
 As these models need the whole dataset as the input, they are offline detections, which is not scalability for large dynamic dataset such as microblogs.
-\subsection{Knowledge Base}
+\end{comment}
 
-\cite{faralli2015large} propose the Twixonomy Graph.
+\textbf{Knowledge Base}. \cite{faralli2015large} propose the Twixonomy Graph.
 
@@
     Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate(Duplicate \\ Event Rate)\end{tabular} \\ \hline
-    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
+    UMass System\cite{Allan:2000wu} & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
     LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
@@
 
-UMass System
+UMass System\cite{Allan:2000wu}
 
@@
 
-BBTM
+BBTM\cite{yan2015probabilistic}
 

### 2016-08-04 paper/ieeeFormat.tex
before version 2 of introduction

@@
 \usepackage{xcolor}% or package color
+
+\usepackage{makecell}
 
@@
 %主动感知的
-\title{Is That Enough to Use the Recent Data to Detect Events?}
-Revealing the Important Factors on the High Accuracy Event Detection
+%\title{Is That Enough to Use the Recent Data to Detect Events?}
+\title{Revealing the Important Factors on the High Accuracy Event Detection}
 %点明factor是什么——能准确描述历史知识的model，该model的表述能力起码能够model概念和概念之间的联系；model应该有一个实时自学习功能，即在历史知识的基础上，能在不断到来的新数据流上更新自己的知识。（“支持”恐怖组织，“打击”恐怖组织）打击恐怖组织的topic中，通常是美国和英国、法国；但是俄罗斯突然出现在该topic的列表中，说明俄罗斯参与打击恐怖组织应该被判别为一个新的事件。需要一个精确描述历史数据中概念之间联系的例子——（找到一个立场发生变化的例子，如果能在叙利亚问题上找到很好，如果不能考虑别的例子）。
@@
 To analyze the reason, we go deep into the existing two kinds of methods.
-
-The first category of methods, including UMass\cite{Allan:2000wu} and BBTM\cite{yan2015probabilistic}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
-This kind methods can be implemented by clustering of articles\cite{Allan:2000wu}\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topic modeling\cite{Diao:2012wj}\cite{Yan:2015wm} in the recent time windows.
-Taking the clustering of articles as an example, they model the occurred events as clusters, and link the incoming article with an already existed event cluster or assign it as the new detected event.
-The decision is based on whether the dissimilarity between the incoming article and existed event clusters is over the user-specified threshold.
-
-The reason why this kind methods cannot achive high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
-This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision.
-On the one hand, UMass\cite{Allan:2000wu} prefers the lower threshold to enlarge the recall but suffers the precision. 
-On the other hand, BBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.
-
-The second category of methods thouroughly relies on the \textit{history data}. 
-The typical implementation is to train the event triggers\cite{Li2013JointEE}\cite{Nguyen2015EventDA} from history labeled data, then apply the trained model to detect the event related articles, which contain the triggers such as the word \textit{attacked} for the \textit{public security} events.
-This kind methods suffer from the loss of recall. 
-There are two reasons. 
-%没有对历史数据进行很好的组织
-(1) The model does not utilize the history data sufficiently. 
-Usually, the event trigger based method mainly focus on the event related verbs, but often ignores the other word types.
-(2) The model lacks the update mechanism. 
-It only restores the history knowledge but without updating. 
-Some new event related articles may be mistakenly filtered out because not containing previous trained triggers. 
-For example, the tweet ``Russia's intervention in Syria began in September 2015" without an event trigger, which is really related to a \textit{public security} event, may be omitted by the system.
 
@@
 \section{Related Works}
-\textbf{Event Detection.} To train the normal states, the methods of existing systems can be grouped into unsupervised methods and supervised methods based on whether they .
+The first category of methods, including UMass\cite{Allan:2000wu} and BBTM\cite{yan2015probabilistic}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
+This kind methods can be implemented by clustering of articles\cite{Allan:2000wu}\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topic modeling\cite{Diao:2012wj}\cite{Yan:2015wm} in the recent time windows.
+Taking the clustering of articles as an example, they model the occurred events as clusters, and link the incoming article with an already existed event cluster or assign it as the new detected event.
+The decision is based on whether the dissimilarity between the incoming article and existed event clusters is over the user-specified threshold.
 
-In the first category, the methods treat the normal states as clustered articles\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topics\cite{Diao:2012wj}\cite{Yan:2015wm}.
-Taking the clustering of articles\cite{Petrovic:2010uj}\cite{Wurzer:2015wq} as an example, they model the occurred events as clusters, and link the incoming article with an existing event cluster or assign it as the new detected event.
-The decision is based on whether the dissimilarity between the incoming article and existing event clusters is over the user-specified threshold.
+The reason why this kind methods cannot achive high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
+This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision.
+In the journalist metaphor of news value theory, they have the limited knowledge of normal states (aka "routine things") due to the limited history information used.
+On the one hand, UMass\cite{Allan:2000wu} prefers the lower threshold to enlarge the recall but suffers the precision. 
+On the other hand, BBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.
 
-And in the second category, the methods learn the normal states by given the knowledge of \textit{event trigger}\cite{Li2013JointEE}\cite{Nguyen2015EventDA} (usually a single verb or entity mentions).
-The normal states are trained by the labeled data appeared in a fixed time window.
-
-Both categories of methods have achieved good performance on formal texts, but are hampered by the diverse and rapid changing nature of cyberspace data (e.g., twitter\cite{Asur:2011tc} and reddit\cite{singer2014evolution}).
-In the journalist metaphor of news value theory, they have the limited knowledge of normal states (aka "routine things") due to the limited history information used.
+The second category of methods thouroughly relies on the \textit{history data}. 
+The typical implementation is to train the event triggers\cite{Li2013JointEE}\cite{Nguyen2015EventDA} from history labeled data, then apply the trained model to detect the event related articles, which contain the triggers such as the word \textit{attacked} for the \textit{public security} events.
+This kind methods suffer from the loss of recall. 
+There are two reasons. 
+%没有对历史数据进行很好的组织
+(1) The model does not utilize the history data sufficiently. 
+Usually, the event trigger based method mainly focus on the event related verbs, but often ignores the other word types.
+(2) The model lacks the update mechanism. 
+It only restores the history knowledge but without updating. 
+Some new event related articles may be mistakenly filtered out because not containing previous trained triggers. 
+For example, the tweet ``Russia's intervention in Syria began in September 2015" without an event trigger, which is really related to a \textit{public security} event, may be omitted by the system.
 
@@
 
-Study of event detection on text stream can be divided into three ways: word frequency based, text similarity based and topic model based.
-
-Several word frequency methods have been developed for event detection such as Discrete Fourier Transform\cite{he2007analyzingDFT}, wavelet analysis \cite{weng2011eventWavelet}.
-They treat the word's document frequency along timeline as time series and do the analysis in frequency domain. 
-DFT method suffers the problem that it can not locate the time point for bursty, while wavelet analysis based method's complexity is very high, which limits its scalability.
-
-\begin{comment}
- Text similarity based online event detection methods\cite{petrovic2010streaming}\cite{mccreadie2013scalable}  suffer from the lexical variation which means different words describe the same events.
- Similarity based method can successfully detect the tweet which is retweeted by many times, but fails to find out the event which is described from many different perspectives.
- As a result, many events are duplicately detected due to their popularities, which may bury other events and overwhelm users with duplicated unwanted content.
-
-In contrast, topic model can handle the lexical variation problem with word co-occurrence\cite{blei2003latent}.
-%After \cite{blei2006dynamic} and \cite{wang2006topics} introducing time factor into topic model, a number of temporal model has been developed to different tasks.
-As many events are highly related to topics, a number of methods based on topic model have been proposed for event detection, including online detection and offline detection.
-Lau\cite{lau2012line} introduces an online topic model to track emerging events in microblogs.
-It can deal with a massive of tweets, but it doesn't filter out the tweets related to user interests.
-Diao\cite{timeUserLDA2012finding}\cite{diao2013unified} show that event detection can benefit from filtering out user interest related tweets. 
-And Yan\cite{Yan:2015wm} models the bursty topic by incorporating burstiness of biterms as prior knowledge.
-But they are different from ours.
-As these models need the whole dataset as the input, they are offline detections, which is not scalability for large dynamic dataset such as microblogs.
-\end{comment}
-
-\textbf{Knowledge Base}. \cite{faralli2015large} propose the Twixonomy Graph.
+%\textbf{Knowledge Base}. \cite{faralli2015large} propose the Twixonomy Graph.
 
@@
 
+\begin{rmk}[The Set of Events' Candidate Words] 
+The set of events' candidate words \(\mathcal{B}_{c,t}\) are defined by the words that belong to the category \(c\) in time \(t\), but are different from the normal states \(\bm{f}_c\). 
+\end{rmk}
+
+\begin{rmk}[Event Phrase] 
+Event phrase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occured in the set of events' cadidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happend in time \(t\) under the category \(c\).
+\end{rmk}
+
+\begin{rmk}[Event Related Articles] Event related articles \(\mathcal{D}_{c,t,i}\) are articles that relate to the \(i\)-th event in time \(t\) under the category \(c\), and correspond to the event phrase \(\mathcal{C}_{c,t,i}\).
+\end{rmk}
+
 \begin{table}
-\begin{tabular}{|c|p{0.1\columnwidth}|p{0.55\columnwidth}|} \hline
+\caption{Notations used by \textsc{NSDetector}}
+\label{tbl:notations}
+\begin{tabular}{|c|p{0.06\columnwidth}|p{0.64\columnwidth}|} \hline
 %first part: normalization initialization
-\multirow{5}{0.18\columnwidth}{Normalization Initialization} & \(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \cline{2-3}
+\multirow{5}{0.15\columnwidth}{Normal States Initialization} & \(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \cline{2-3}
 & \(G^{(1)}\) & Category-Page Bipartite Graph in Knowledge Base\\ \cline{2-3}
-& \(G^{(2)}\) & Page-Content Bipartite Graph in Knowledge Base\\ \cline{2-3}
-& \(c\) & topic related category node in \(G^{(0)}\) and \(G^{(1)}\) \\ \cline{2-3}
-& \(K_{\bm{KB}}\) & number of pre-defined topics by Knowledge Base \\ \cline{2-3}
+& \(G^{(2)}\) & Page-Content Map in Knowledge Base\\ \cline{2-3}
+& \(c\) & topic related category node in \(G^{(0)}\), \(G^{(1)}\) \\ \cline{2-3}
+& \(K_{\bm{KB}}\) & number of pre-defined topics in Knowledge Base \\ \cline{2-3}
 & \(f_{c,w}\) & word \(w\)'s normal state (chi-square score) in category \(c\) \\ \hline
 %second part: normalization maintenance
-\multirow{4}{0.18\columnwidth}{Normalization Maintenance} & \(\lambda\) & normal state weight in  NS-Prior-LDA\\ \cline{2-3}
+\multirow{4}{0.15\columnwidth}{Normal States Maintenance} & \(\lambda\) & normal state weight in  NS-Prior-LDA\\ \cline{2-3}
 & \(\tau_{c,w}\) & word \(w\)'s prior knowledge confidence for topic \(c\) in NS-Prior-LDA\\ \cline{2-3}
@@
 %third part: event detection
-\multirow{5}{0.18\columnwidth}{Event Detection} & \(\mathcal{B}_{c, t}\)  & hot words set detected from topic \(k\) at time \(t\)  \\ \cline{2-3}
+\multirow{5}{0.15\columnwidth}{Event Detection} & \(\mathcal{B}_{c, t}\)  & event words set detected from topic \(c\) at time \(t\)  \\ \cline{2-3}
 & \(\mathcal{G}_{c, t}\)  & hot word graph constructed from \(\mathcal{B}_{c, t}\) \\ \cline{2-3}
 & \(\mathcal{C}_{c,t,i}\) & event \(i\)-th related words in topic \(c\) at time \(t\) \\ \cline{2-3}
-& \(\mathcal{D}_{c,t,i}\) & event \(i\)-th related tweets in topic \(c\) at time \(t\) \\ \cline{2-3}
+& \(\mathcal{D}_{c,t,i}\) & event \(i\)-th related articles in topic \(c\) at time \(t\) \\ \cline{2-3}
 & \(\rho\) & density threshold for the sub-graph constructed by event words  \\ \hline
@@
 \begin{enumerate}[labelindent=\parindent,leftmargin=*]
-\item Taxonomy.
-Indicates that the classification relationship, for example, Society this classification page contains Politics classification page, further contains Military, and Society itself is included in the topic classifications Main;
+\item Taxonomy Graph \(G^{(0)}\). The directed edges \(G^{(0)}\) represent the class-subclass relations in the knowledge base. 
+Taking Wikipedia for example (Figure \ref{fig:NSinitializaton}), the node \textit{Main topic classifications}\footnote{\url{https://en.wikipedia.org/wiki/Category:Main_topic_classifications}} has the subclass \textit{Society}, further contains the subclass \textit{Politics}, which is the ancestor of the subclass \textit{Military}.
+This graph is constructed by Wikipedia users, and still contain
+PageRank-HITS\cite{Yan:2015wq}. 
 \item Category-Page Bipartite graph.
@@
     \includegraphics[width=.85\columnwidth]{img/initializationExample.pdf}  
-    \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
-    \label{fig:modelDesc}
+    \caption{Illustration on how to initialize normal states from wikipedia (an example on the initialization of the normal states about \textit{military}).}
+    \label{fig:NSinitializaton}
 \end{figure}
@@
 \subsection{Normal States' Maintenance}
-KB-Prior-LDA
+
+\begin{comment}
 \begin{figure}[t]
@@
     %The convolution neural network for extracting character-level representations of words. Dashed arrows indicate a dropout layer applied before character embeddings are input to CNN.}
-    \label{fig:cnn}
+    \label{fig:NS-Prior-LDA}
 \end{figure}
+\end{comment}
 
-\ \ Our theme modeling, want to learn the first \(k\) topics with Wikipedia Article \(k\) topics as close as possible, and we will be Wikipedia article \(k\) before 1000 words) was added to the theme of the word frequency word in the subject a priori distribution on the.
+\ \ Our topic modeling, want to learn the first \(k\) topics with Wikipedia Article \(k\) topics as close as possible, and we will be Wikipedia article \(k\) before 1000 words) was added to the theme of the word frequency word in the subject a priori distribution on the.
 Learning to be the first \(k\) Subject polynomial distribution of the word, referred to as \(\phi_k \), Wikipedia article \(k \) distribution of topics for \(\tau_k \), then this formalized process is expressed as: \(\ \phi_k \sim Dir(\beta + \tau_k) \).
 Formal presentation of the explanation is: With prior knowledge \(\tau_k \) after the theme \(\phi_k \) is no longer simply rely on symmetric priori \(\beta \), different words right is not the same weight , such as a discussion of "fashion" theme in Wikipedia, it will refer to "dress", "grand", "blue", "gold" and other words, with the asymmetric priori \(\beta + \tau_k \) after in microblogging "fashion" theme "dress" the proportion will be increased in this way so that microblogging corpus theme tends to Wikipedia topic.
-\(\tau_k \) in the first \(v \) words such as formula (\ref{eq: wikiPrior}).
+\(\tau_k \) in the first \(v \) words such as formula (\ref{eq:wikiPrior}).
 Where \(S_k \) as a set of candidate words: high-quality information to use Wikipedia, we extract the theme \(\phi_k \ \) in the higher-word word frequency candidate set \(S_k \).
 We can control set \(S_k \) in size, the size of the control is usually set for 1000.
-The number of frequency \(n_{kv} \) for the word \(v \) (\ k) appears in the Wikipedia article themes of: (\ref{wikiPrior eq}).
+The number of frequency \(n_{kv} \) for the word \(v \) (\ k) appears in the Wikipedia article themes.
 If the word \(v \) does not appear in the candidate set \(S_k \), and then set a priori knowledge \(\tau_{kv} = 0 \), otherwise, the word frequency is proportional to \(n_{kv} \) with the prior knowledge of weight \(W\).
@@
 
-\cite{wallach2008structured}\footnote{\url{https://github.com/mimno/Mallet/blob/master/src/cc/mallet/types/Dirichlet.java}}
+The line 12 in Algorithm \ref{alg:gibbsSamplingKBPriorLDA} is implemented according to \cite{wallach2008structured}\footnote{\url{https://github.com/mimno/Mallet/blob/master/src/cc/mallet/types/Dirichlet.java}}, which can optimize \(\alpha \bm{m}\) for promoting NS-Prior-LDA's fitting to documents \(\mathcal{D}\).
 
@@
 
+\begin{comment}
 \begin{figure}
@@
 \end{figure}
-
+\end{comment}
 \textbf{event} phrase Mining
@@
 \section{Experiments}
-\subsection{Effects of Normal States Initialization}
+\subsection{Effects of Normal States}
 We use 20newsgroups\cite{lang1995newsweeder} dataset\footnote{http://qwone.com/~jason/20Newsgroups} to check the effects of normal states initialization.
 
-What's NPMI? maybe can refer to \cite{Aletras2013EvaluatingTC}\cite{Rder2015ExploringTS}\footnote{https://github.com/AKSW/Palmetto}.
 \begin{table}[]
 \centering
-\caption{My caption}
+\caption{Normal State's cateogries corresponding to the 20-newsgroups corpus, and the F1 score on the classification task}
 \label{my-label}
@@
 alt.atheism              & Category:Atheism                \\ \hline
-soc.religion.christian   & Category:Christians             \\ \hline
+soc.religion.christian   & Category:Christians             \\ \Xhline{3\arrayrulewidth}
+LDA & 0.74\\ \hline
+BOW & 0.84\\ \hline
+doc2vec & 0.73\\ \hline
+NS-Prior-LDA & 0.89\\ \hline
 \end{tabular}
@@
         \includegraphics[width=1.0\columnwidth]{img/NPMI.pdf}
-        \caption{NPMI}
+        \caption{The comparison on NPMI\cite{Aletras2013EvaluatingTC}\cite{Rder2015ExploringTS} between LDA's topics and normal states initialized from Wikipedia}
 \end{figure}
@@
 \centering
-\caption{My caption}
+\caption{Normal States initialized from Wikipedia and topical words learned from NS-Prior-LDA}
 \label{my-label}
@@
 \centering
-\caption{My caption}
-\label{my-label}
-\subtable[Twitter Dataset Statistics]{
+\caption{Event Detection Results on Edinburgh Twitter Corpus}
+\label{tbl:edinburgh_results}
+\subtable[Edinburgh Twitter Corpus Statistics]{
 \begin{tabular}{|l|r|}
@@
 \end{table*}
-
+\begin{comment}
 \begin{table*}[ht]
@@
 \end{table*}
+\end{comment}
 
@@
 
+\begin{comment}
 \begin{figure*}
@@
 \end{figure*}
+\end{comment}
 
-\subsection{Data set and experiment settings}
+\subsection{Quantitive Study}
 \textbf{Data set.} We conduct the empirical analysis on a twitter dataset which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}.
@@
 More details of the original dataset are described in \cite{petrovic2010edinburgh}.
+\begin{comment}
+20-newsgroup\footnote{http://qwone.com/~jason/20Newsgroups/}
 
-20-newsgroup\footnote{http://qwone.com/~jason/20Newsgroups/}
+NPMI\cite{Aletras2013EvaluatingTC}\cite{Rder2015ExploringTS}\footnote{https://github.com/AKSW/Palmetto}.
 
@@
 \textbf{Model Setting}
-
-\subsection{Validity of Normal States}
-\textbf{Topic Coherence} \cite{roder2015exploring}
-\subsection{Topical Words Learned by NS-Prior-LDA}
-\textbf{PMI}
-\subsection{Evaluation of Detected Events}
+\end{comment}
+%\textbf{Topic Coherence} \cite{roder2015exploring}
+\subsection{Qualitative Study}
+%\textbf{PMI}
+%\subsection{Evaluation of Detected Events}
+\begin{comment}
 \textbf{Precision} Precision@Benchmark1, Precision@Benchmark2
@@
 \textbf{DERate(Duplicate Event Rate)}
-\subsection{Case Study}
+\end{comment}
+%\subsection{Case Study}
 
-\subsection{Application on Reddit}
+%\subsection{Application on Reddit}
 

### 2016-09-05 paper/ieeeFormat.tex
before branch a new branch named old

@@
 %\title{Is That Enough to Use the Recent Data to Detect Events?}
-\title{Revealing the Important Factors on the High Accuracy Event Detection}
+%\title{Revealing the Important Factors on the High Accuracy Event Detection}
+
+\title{Knowledge Base Enhanced Continous Learning for High Accuracy Event Detection}
+%基于历史的 adoptable continous learning 连续学习for high accuracy event detection
+%长轴：military方面的，三个切片，每个切片top10的词都进行展示。起始是维基的导入，连续学习产生了一个长轴。
+%关注于重要事件的积累：1，变化很大，2，相当长的稳定性。长轴上的例子，第三个切片需要第一个切片的知识。第三个切片自身产生的很准确。
+%两个例子：（1）之前学习的结果对事件检测有帮助（类似于张学良的case）；（2）可以扩展词表时新性很好，很准确；
+
 %点明factor是什么——能准确描述历史知识的model，该model的表述能力起码能够model概念和概念之间的联系；model应该有一个实时自学习功能，即在历史知识的基础上，能在不断到来的新数据流上更新自己的知识。（“支持”恐怖组织，“打击”恐怖组织）打击恐怖组织的topic中，通常是美国和英国、法国；但是俄罗斯突然出现在该topic的列表中，说明俄罗斯参与打击恐怖组织应该被判别为一个新的事件。需要一个精确描述历史数据中概念之间联系的例子——（找到一个立场发生变化的例子，如果能在叙利亚问题上找到很好，如果不能考虑别的例子）。
@@
 \begin{abstract}
+
+Many web applications need the real time event detection technique. But the accuracy of existing methods are still far from meeting the application requirements. 
+%should be met, 这个词应该被强化，vital
+We reaveal that the two important factors should be met, (1) having a good mechanism to organize the history data, and (2) having the capability of self-updating, to accumlate the knowledge about what is happening.
+%NSDetector的特性应该被
+According to this guideline, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of history data.
+In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
+Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
+\textsc{NSDetector} promotes the accuracy rate by 9\% without  sacrificing the recall rate.
+%在不牺牲召回率的情况下，将准确率相比于state-of-art提升了9%。
+
+\begin{comment}
 Event detection is an important task to understand what already happened and what is currently happening in the rapid evolving text stream. 
@@
 %\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.
+\end{comment}
 \end{abstract}
@@
 \section{Introduction}
-%\textit{``To study the abnormal is the best way of understanding the normal."}---William James
-%\textit{``The unpredictable or the rare is more newsworthy than the routine."}---Allan Bell
+Many web applications\cite{ge2015bring}\cite{hughes2009twitter}\cite{sakaki2010earthquake} need the real time event detection technique. 
+But the accuracy of existing methods are still far from meeting the application requirements. 
+The main stream of existing methods focus on monitoring the changes of the recent data\cite{Allan:2000wu}\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, and some others use the history data by word frequencies\cite{Li2013JointEE}\cite{Nguyen2015EventDA} and dictionary\cite{Twevent2012}.
+A typical example the existing methods cannot handle well is that ``Russia's anti-ISIS operation in Syria".
+The word Russia, ISIS, and Syria are trivial, while Russia's anti ISIS is nontrivial because US and other Europe countries but not Russia are the countries that anti ISIS  before September 2015.
+%这个例子应该
 
-%The event detection task always tries to find out the newsworthy messages from cyberspace. 
-In big data era, event detection is an important task to understand what already happened\cite{ge2015bring} and what is currently happening\cite{hughes2009twitter}\cite{sakaki2010earthquake} within the rapid evolving text stream.
-Although many efforts have been made, the performance still needs to be enhanced as the existing methods cannot achieve high precision and high recall simultaneously, only sacrificing the precision for the recall (such as UMass\cite{Allan:2000wu}), or otherwise (such as BBTM\cite{yan2015probabilistic}).
-To analyze the reason, we go deep into the existing two kinds of methods.
-
-Based on the above analysis, we can make a conclusion that it's not enough to use the recent data to detect events, but not enough to only use the history data for this task either.
-We believe that the ideal event detection method should have two properties: (1) having a good mechanism to organize the history data, and being aware of what happened; (2) having the capability of self-updating, to accumlate the knowledge about what is happening.
-
-%In our study, we find out that the key to improve the accuracy of event detection lies in training the normal states of the focused media/site/domain.
-Based on training normal states accurately, event detection task can be treated as finding terms, articles, or topics which are different from the normal states.
+To handle this challenge, the important factors on the high accuracy event detection are needed: (1) having a good mechanism to organize the history data, and being aware of what happened; (2) having the capability of self-updating, to accumlate the knowledge about what is happening.
 
@@
 We suppose that the ideal event detection system performs like a journalist who can find news from cyberspace with the knowledge of the normal states. 
-For example, a journalist had the knowledge about the anti-terrorism as ``the words \textit{ISIS}, \textit{Syria}, \textit{America}, and \textit{France} were both high-frequent and co-occurred, while the word \textit{Russia} was not so frequent as them'' before August 2015, because ``America led the allies, including France, Germany, and United Kindom etc., to counter ISIS"\footnote{\url{https://en.wikipedia.org/wiki/American-led_intervention_in_Syria}}.
-With this knowledge about what happened and what is happening normally, the journalist can detect the event of ``Russia's anti-ISIS operation in Syria"\footnote{\url{https://en.wikipedia.org/wiki/Russian_military_intervention_in_the_Syrian_Civil_War}} when \textit{Russia} appeared more frequent than the normal and appeared with \textit{ISIS} and \textit{Syria} in September 2015.
-After detection, the journalist would update his knowledge about what happened and what's happening for anti-terrorism.
-Comparing to the other journalists who don't have the history knowledge of anti-terrorism, the journalist with that is more likely to report the above mentioned event accurately in time. 
 %Taking another example in our study for example, the tweet ``UN declares famine in Somalia (7/20/2011)"\footnote{\url{https://en.wikipedia.org/wiki/2011_East_Africa_drought}} is related to a \textit{public security} event as the famine has the potential of relating to a war.
@@
 
-It's very close for the ideal event detection method, which holds the previous mentioned two properties (\textit{organizing history data well} and \textit{self-updating}), to perform like the journalist who follows the news value theory.
+It's very close for the ideal event detection method, which holds the previous mentioned two properties (\textit{organizing history data well} and \textit{self-updating}).
 To implement the ideal event detection method, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things.
@@
 
-%The experiments verifed that the
+But the existing computation on the RDF graph is often time consuming.
+To overcome this obtacle, we propose the new data structure \textit{normal states}, which not only utilize the structure adequately but also maintain the information about what happened and what's happening more efficiently than RDF.
 
-\begin{figure}
-    \label{fig:modelDesc}
-    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
-    \caption{\textsc{NSDetector}'s process flow, taking \textit{public security} related events in cyberspace as an example.
-\textsc{NSDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
-\end{figure}
-
-The contribution of this paper is mainly in three aspects:
-(1) it points out that the effective way to improve the accuracy of event detection is not only to use the recent data, but also need the historical data to support.
-And found that the introduction of historical data, can significantly improve the accuracy of event detection.
-(2) the a combination of historical data and recent data of the probability model NSDetector.
-The model can combines the historical data and recent events, used to determine the arrival of a new document is a new event, and update the knowledge of new events to the NSDetector, realize what happened and what is happening on the knowledge of the incremental updating.
-(3) we experiment with 30 million tweets benchmark Edinburgh twitter corpus show that our model and accuracy model is the highest compared to will improve the accuracy rate of 9\%; and the recall rate is the highest model compared to the accurate rate was increased by 1\%.
+The contribution of this paper is mainly in three aspects.
+(1) We reveal that there are two important factors for high accuracy event detection-- a comprehensive model that can organize history data well, and updating the model well.
+(2) We propose the probability model \textsc{NSDetector}. 
+The model can combine the history data and the recent data, further determine the arrival new document whether it represents a new event. 
+More than that, \textsc{NSDetector} has the capability to update the knowledge of what happend.
+(3) The experiment on the Edinburgh twitter corpus which contains 30 million tweets show that \textsc{NSDetector} promotes the accuracy rate by 9\% without sacrificing the recall rate.
 
@@
 %2, 3, 6, 7, 10, 11;
+\begin{comment}
 \begin{figure*}[ht]
@@
 \end{figure*}
+\end{comment}
 
 \section{Proposed Method}
-\begin{rmk}[Normal States] 
-The normal states of the specific category is defined by a set of tuples, in which the first element is the word \(w^{(c)}_i\) related to the category \(c\), and the second element is the chi-square score \(f(c,w^{(c)}_{i})\) under the category.
-And we denote the normal states of category \(c\) as \(\bm{f}_c=\{<w^{(c)}_i,f(c,w^{(c)}_{i})>\}_{i=1,...,N_c}\).
+Knowledge base often contains much information about what happened. 
+But the exisiting RDF model\cite{klyne2006rdf} on knowledge base lacks the mechanism to maintain the information about what's happening, especially when applied on text stream.  
+With the help of knowledge base's structure (detailed in sec \ref{subsec:hs_initialization}), we provide a  lightweight model for organizing the data in knowledge base and the data in text stream simultaneously.
+
+\textit{History state} is the proposed data structure to restore the information about what happened. 
+Initially, \textit{history state} extracts category-related history data into a set of tuples, which weighs the importance of given words to the specific category, defined in Definition 1 formally. 
+Taking the \textit{military} category in  Figure \ref{fig:NSinitializaton} as an example, the history state of \textit{military} contain the words \textit{army}, \textit{military}, and \textit{shootings} etc.
+
+\textit{Recent state} is the proposed data structure to maintain the information about what's happening.
+It extracts category-related words from incoming text stream, for each time window.
+Still taking the \textit{military} category in  Figure \ref{fig:NSinitializaton} as an example, based on extracted history states, our proposed probabilistic continuous learning model \textsc{HS-Prior-LDA} can recognize the words \textit{libyan} and \textit{rebel} in the time window 2011-07-28 in the text stream are related to the category \textit{military}.
+Furthermore the time series analysis on the neighboring recent states can recognize the set of events' candidate words, and finally detects the events in the text stream. 
+In the example of Figure 1, the words \textit{libyan} and \textit{rebel} are related to the \textit{military} event ``\#libya Libyan rebels chief is killed (2011-07-28)''.
+
+After processing each time window's data, the history states can be incrementally updated by the recent state. 
+In this way, the proposed model utilizes the rich history data in knowledge base, and performes continous learning on the incoming text stream, which can promote the accuracy of event detection significantly.
+The followings definitions are the concepts used by the continous learning model \textsc{HS-Detector}.
+
+\begin{rmk}[History State] 
+The history state of the specific category is defined by a set of tuples, in which the first element is the word \(w^{(c)}_i\) related to the category \(c\), and the second element is the chi-square score \(chi(c,w^{(c)}_{i})\) under the category \(c\).
+And we denote the history states of category \(c\) as \(\bm{h}_c=\{<w^{(c)}_i,chi(c,w^{(c)}_{i})>\}_{i=1,...,N_c}\).
+\end{rmk}
+
+\begin{rmk}[Recent State] 
+The recent state at time \(t\) of the specific category \(c\) is defined by a set of tuples, and detenoted as \(\bm{r}_{c,t}=\{<w^{(c)}_i,n(c,t,w^{(c)}_{i})>\}_{i=1,...,N_c}\), in which word \(w^{(c)}_{i}\) is related to the category \(c\), and \(n(c,t,w^{(c)}_{i})\) is its document frequency in the time window \(t\).
 \end{rmk}
@@
 \begin{rmk}[The Set of Events' Candidate Words] 
-The set of events' candidate words \(\mathcal{B}_{c,t}\) are defined by the words that belong to the category \(c\) in time \(t\), but are different from the normal states \(\bm{f}_c\). 
+The set of events' candidate words \(\mathcal{B}_{c,t}\) are defined by the bursty words in recent state \(\bm{r}_{c,t}\).
 \end{rmk}
@@
 
+Section \ref{subsec:hs_initialization} explains the details of how to initialize history states from knowledge base.
+Section \ref{subsec:rs_initialization} shows how to perform continous learning for updating history states and recent states.
+And section \ref{subsec:detection} interprets the high accuracy event detection based on the processed recent states.
+
 \begin{table}
+\scriptsize
 \caption{Notations used by \textsc{NSDetector}}
 \label{tbl:notations}
-\begin{tabular}{|c|p{0.06\columnwidth}|p{0.64\columnwidth}|} \hline
+\begin{tabular}{|c|p{0.06\columnwidth}|p{0.66\columnwidth}|} \hline
 %first part: normalization initialization
-\multirow{5}{0.15\columnwidth}{Normal States Initialization} & \(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \cline{2-3}
+\multirow{5}{0.13\columnwidth}{History States' Initialization} & \(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \cline{2-3}
 & \(G^{(1)}\) & Category-Page Bipartite Graph in Knowledge Base\\ \cline{2-3}
@@
 & \(K_{\bm{KB}}\) & number of pre-defined topics in Knowledge Base \\ \cline{2-3}
-& \(f_{c,w}\) & word \(w\)'s normal state (chi-square score) in category \(c\) \\ \hline
+& \(h_{c,w}\) & word \(w\)'s history state (chi-square score) in category \(c\) \\ \hline
 %second part: normalization maintenance
-\multirow{4}{0.15\columnwidth}{Normal States Maintenance} & \(\lambda\) & normal state weight in  NS-Prior-LDA\\ \cline{2-3}
+\multirow{4}{0.13\columnwidth}{Normal States Maintenance} & \(\lambda\) & normal state weight in  NS-Prior-LDA\\ \cline{2-3}
 & \(\tau_{c,w}\) & word \(w\)'s prior knowledge confidence for topic \(c\) in NS-Prior-LDA\\ \cline{2-3}
@@
 %third part: event detection
-\multirow{5}{0.15\columnwidth}{Event Detection} & \(\mathcal{B}_{c, t}\)  & event words set detected from topic \(c\) at time \(t\)  \\ \cline{2-3}
+\multirow{5}{0.13\columnwidth}{Event Detection} & \(\mathcal{B}_{c, t}\)  & event words set detected from topic \(c\) at time \(t\)  \\ \cline{2-3}
 & \(\mathcal{G}_{c, t}\)  & hot word graph constructed from \(\mathcal{B}_{c, t}\) \\ \cline{2-3}
@@
 
-\subsection{Normal States Initialization}
+\subsection{History States Initialization}\label{subsec:hs_initialization}
 In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
@@
 This structure usually can be represented as triples in RDF graph\cite{klyne2006rdf}, which is adopted to build DBPedia\cite{auer2007dbpedia} and YAGO\cite{suchanek2007yago} from Wikipedia.  
-But the existing computation on the RDF graph is often time consuming.
-To overcome this obtacle, we propose the new data structure \textit{normal states}, which not only utilize the structure adequately but also maintain the information about what happened and what's happening more efficiently than RDF.
+But The RDF and other methods often
+
 \begin{enumerate}[labelindent=\parindent,leftmargin=*]
-\item Taxonomy Graph \(G^{(0)}\). The directed edges \(G^{(0)}\) represent the class-subclass relations in the knowledge base. 
+\item Taxonomy Graph \(G^{(0)}\). The directed edges in \(G^{(0)}\) represent the class-subclass relations in the knowledge base. 
 Taking Wikipedia for example (Figure \ref{fig:NSinitializaton}), the node \textit{Main topic classifications}\footnote{\url{https://en.wikipedia.org/wiki/Category:Main_topic_classifications}} has the subclass \textit{Society}, further contains the subclass \textit{Politics}, which is the ancestor of the subclass \textit{Military}.
-This graph is constructed by Wikipedia users, and still contain
-PageRank-HITS\cite{Yan:2015wq}. 
-\item Category-Page Bipartite graph.
-\item Page-Content Maps.
+\item Category-Page Bipartite Graph \(G^{(1)}\). 
+\item Page-Content Maps \(G^{(2)}\).
 \end{enumerate}
 
+As \(G^{(0)}\) is not a Directed Acyclic Graph originally\cite{faralli2015large}, we need to remove the , PageRank-HITS\cite{Yan:2015wq}.
+
 \begin{algorithm}
+\scriptsize
 \caption{Normal States Initialization from Knowledge Base}
@@
 
-\subsection{Normal States' Maintenance}
+\begin{figure}
+    \label{fig:modelDesc}
+    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
+    \caption{\textsc{NSDetector}'s process flow, taking \textit{public security} related events in cyberspace as an example.
+\textsc{NSDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
+\end{figure}
+
+\subsection{Recent States' Maintenance}
+\label{subsec:rs_initialization}
 
@@
 \begin{algorithm}
+\scriptsize
 \caption{NS-Prior-LDA Learning Algorithm}
@@
 
-\subsection{Detecting Events from Normal States}
+\subsection{Detecting Events from Recent States}
+\label{subsec:detection}
 The state of attention of social issue k at time t in cyberspace is binary, namely at the peak or not at the peak.
@@
 \begin{algorithm}
+\scriptsize
 \label{alg:eventKeywordsSearchMethod}
@@
 
+\begin{comment}
 \begin{table}[]
+\scriptsize
 \centering
@@
 \hline
-comp.graphics            & Category:Computer graphics      \\ \hline
-comp.os.ms-windows.misc  & Category:Microsoft Windows      \\ \hline
-comp.sys.ibm.pc.hardware & Category:IBM personal computers \\ \hline
-comp.sys.mac.hardware    & Category:Macintosh computers    \\ \hline
-comp.windows.x           & Category:X Window System        \\ \hline
-rec.autos                & Category:Automobiles            \\ \hline
-rec.motorcycles          & Category:Motorcycles            \\ \hline
-rec.sport.baseball       & Category:Baseball               \\ \hline
-rec.sport.hockey         & Category:Hockey                 \\ \hline
-sci.crypt                & Category:Cryptography           \\ \hline
-sci.electronics          & Category:Electronics            \\ \hline
-sci.med                  & Category:Medicine               \\ \hline
-sci.space                & Category:Outer space            \\ \hline
-misc.forsale             & Category:Sales                  \\ \hline
-talk.politics.misc       & Category:Politics               \\ \hline
-talk.politics.guns       & Category:Gun politics          \\ \hline
-talk.politics.mideast    & Category:Middle East           \\ \hline
-talk.religion.misc       & Category:Religion               \\ \hline
-alt.atheism              & Category:Atheism                \\ \hline
-soc.religion.christian   & Category:Christians             \\ \Xhline{3\arrayrulewidth}
+comp.graphics            & Computer graphics      \\ \hline
+comp.os.ms-windows.misc  & Microsoft Windows      \\ \hline
+comp.sys.ibm.pc.hardware & IBM personal computers \\ \hline
+comp.sys.mac.hardware    & Macintosh computers    \\ \hline
+comp.windows.x           & X Window System        \\ \hline
+rec.autos                & Automobiles            \\ \hline
+rec.motorcycles          & Motorcycles            \\ \hline
+rec.sport.baseball       & Baseball               \\ \hline
+rec.sport.hockey         & Hockey                 \\ \hline
+sci.crypt                & Cryptography           \\ \hline
+sci.electronics          & Electronics            \\ \hline
+sci.med                  & Medicine               \\ \hline
+sci.space                & Outer space            \\ \hline
+misc.forsale             & Sales                  \\ \hline
+talk.politics.misc       & Politics               \\ \hline
+talk.politics.guns       & Gun politics          \\ \hline
+talk.politics.mideast    & Middle East           \\ \hline
+talk.religion.misc       & Religion               \\ \hline
+alt.atheism              & Atheism                \\ \hline
+soc.religion.christian   & Christians             \\ \Xhline{3\arrayrulewidth}
 LDA & 0.74\\ \hline
@@
 NS-Prior-LDA & 0.89\\ \hline
+\end{tabular}
+\end{table}
+\end{comment}
+
+\begin{table}[]
+\tiny
+\centering
+\caption{My caption}
+\label{my-label}
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+ &  & LDA & BOW & doc2vec & \begin{tabular}[c]{@{}l@{}}NS-Prior-\\ LDA\end{tabular} \\ \hline
+comp.graphics & Computer graphics &  &  &  &  \\ \hline
+comp.os.ms-windows.misc & Microsoft Windows &  &  &  &  \\ \hline
+comp.sys.ibm.pc.hardware & IBM personal computers &  &  &  &  \\ \hline
+comp.sys.mac.hardware & Macintosh computers &  &  &  &  \\ \hline
+comp.windows.x & X Window System &  &  &  &  \\ \hline
+rec.autos & Automobiles &  &  &  &  \\ \hline
+rec.motorcycles & Motorcycles &  &  &  &  \\ \hline
+rec.sport.baseball & Baseball &  &  &  &  \\ \hline
+rec.sport.hockey & Hockey &  &  &  &  \\ \hline
+sci.crypt & Cryptography &  &  &  &  \\ \hline
+sci.electronics & Electronics &  &  &  &  \\ \hline
+sci.med & Medicine &  &  &  &  \\ \hline
+sci.space & Outer space &  &  &  &  \\ \hline
+misc.forsale & Sales &  &  &  &  \\ \hline
+talk.politics.misc & Politics &  &  &  &  \\ \hline
+talk.politics.guns & Gun politics &  &  &  &  \\ \hline
+talk.politics.mideast & Middle East &  &  &  &  \\ \hline
+talk.religion.misc & Religion &  &  &  &  \\ \hline
+alt.atheism & Atheism &  &  &  &  \\ \hline
+soc.religion.christian & Christians &  &  &  &  \\ \hline
+In total & &  &  &  & \\ \hline
 \end{tabular}
@@
 
+\begin{table}
+
+\scriptsize
+\centering
+\caption{Normal States initialized from Wikipedia and topical words learned from NS-Prior-LDA}
+\scalebox{0.95}{
+    \begin{tabular}{|l|l|l|l|l|}
+    \hline
+    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
+    UMass System\cite{Allan:2000wu} & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
+    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
+    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
+    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
+    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
+    BBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
+    \textsc{NSDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
+    \end{tabular}
+}
+\end{table}
+
+\begin{comment}
 \begin{table*}[ht]
@@
 \end{table*}
-\begin{comment}
+\end{comment}
+
+%\begin{comment}
 \begin{table*}[ht]
@@
 \end{table*}
-\end{comment}
+%\end{comment}
 

### 2016-09-05 paper/ieeeFormat.tex
forward to 9.14
change to aaai format

@@
 To overcome this obtacle, we propose the new data structure \textit{normal states}, which not only utilize the structure adequately but also maintain the information about what happened and what's happening more efficiently than RDF.
+
+\begin{figure}[h]
+    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
+    \caption{\textsc{NSDetector}'s process flow, taking \textit{public security} related events in cyberspace as an example.
+\textsc{NSDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
+    \label{fig:modelDesc}
+\end{figure}
 
@@
 Initially, \textit{history state} extracts category-related history data into a set of tuples, which weighs the importance of given words to the specific category, defined in Definition 1 formally. 
-Taking the \textit{military} category in  Figure \ref{fig:NSinitializaton} as an example, the history state of \textit{military} contain the words \textit{army}, \textit{military}, and \textit{shootings} etc.
+Taking the \textit{military} category in Figure \ref{fig:modelDesc} as an example, the history state of \textit{military} contain the words \textit{army}, \textit{military}, and \textit{shootings} etc.
 
@@
 It extracts category-related words from incoming text stream, for each time window.
-Still taking the \textit{military} category in  Figure \ref{fig:NSinitializaton} as an example, based on extracted history states, our proposed probabilistic continuous learning model \textsc{HS-Prior-LDA} can recognize the words \textit{libyan} and \textit{rebel} in the time window 2011-07-28 in the text stream are related to the category \textit{military}.
+Still taking the \textit{military} category in  Figure \ref{fig:modelDesc} as an example, based on extracted history states, our proposed probabilistic continuous learning model \textsc{HS-Prior-LDA} can recognize the words \textit{libyan} and \textit{rebel} in the time window 2011-07-28 in the text stream are related to the category \textit{military}.
 Furthermore the time series analysis on the neighboring recent states can recognize the set of events' candidate words, and finally detects the events in the text stream. 
-In the example of Figure 1, the words \textit{libyan} and \textit{rebel} are related to the \textit{military} event ``\#libya Libyan rebels chief is killed (2011-07-28)''.
+In the example of Figure \ref{fig:modelDesc}, the words \textit{libyan} and \textit{rebel} are related to the \textit{military} event ``\#libya Libyan rebels chief is killed (2011-07-28)''.
 
@@
 This structure usually can be represented as triples in RDF graph\cite{klyne2006rdf}, which is adopted to build DBPedia\cite{auer2007dbpedia} and YAGO\cite{suchanek2007yago} from Wikipedia. 
-But The RDF and other methods often
+%但是，往往在图上的计算是非常费时的。
+%But The RDF and other methods often
 
-\begin{enumerate}[labelindent=\parindent,leftmargin=*]
-\item Taxonomy Graph \(G^{(0)}\). The directed edges in \(G^{(0)}\) represent the class-subclass relations in the knowledge base. 
+\textbf{Taxonomy Graph \(G^{(0)}\)}. The directed edges in \(G^{(0)}\) represent the class-subclass relations in the knowledge base. 
 Taking Wikipedia for example (Figure \ref{fig:NSinitializaton}), the node \textit{Main topic classifications}\footnote{\url{https://en.wikipedia.org/wiki/Category:Main_topic_classifications}} has the subclass \textit{Society}, further contains the subclass \textit{Politics}, which is the ancestor of the subclass \textit{Military}.
-\item Category-Page Bipartite Graph \(G^{(1)}\). 
-\item Page-Content Maps \(G^{(2)}\).
-\end{enumerate}
+
+\textbf{Category-Page Bipartite Graph \(G^{(1)}\)}.
+
+\textbf{Page-Content Maps \(G^{(2)}\)}.
 
@@
     \label{fig:NSinitializaton}
-\end{figure}
-
-\begin{figure}
-    \label{fig:modelDesc}
-    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
-    \caption{\textsc{NSDetector}'s process flow, taking \textit{public security} related events in cyberspace as an example.
-\textsc{NSDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
 \end{figure}

### 2016-09-08 paper/aaaiFormat.tex
change to aaai format
finish subsection 3.1

--- 2016-09-05 paper/ieeeFormat.tex
@@
-\documentclass[conference,compsoc]{IEEEtran}
+\def\year{2017}\relax
+\documentclass{article}
+\usepackage{aaai17}
+\usepackage{times}
+\usepackage{helvet}
+\usepackage{courier}
+\frenchspacing
+\setlength{\pdfpagewidth}{8.5in}
+\setlength{\pdfpageheight}{11in}
+
 \usepackage{comment}
@@
 
+\setcounter{secnumdepth}{2}  
  \begin{document}
+% The file aaai.sty is the style file for AAAI Press 
+% proceedings, working notes, and technical reports.
+%
+\title{Knowledge Base Enhanced Continous Learning for High Accuracy Event Detection}
+\maketitle
 
@@
 
-\title{Knowledge Base Enhanced Continous Learning for High Accuracy Event Detection}
 %基于历史的 adoptable continous learning 连续学习for high accuracy event detection
@@
 
-\maketitle
 \begin{abstract}
@@
 And section \ref{subsec:detection} interprets the high accuracy event detection based on the processed recent states.
-
+\begin{comment}
 \begin{table}
@@
 \end{table}
+\end{comment}
 
 \subsection{History States Initialization}\label{subsec:hs_initialization}
-In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
+In this part, we discuss in detail how to initialize the history states from the given knowledge base. 
 The knowledge base such as Wikipedia has the structure of classes, subclasses, instances, and the edges between them. 
 This structure usually can be represented as triples in RDF graph\cite{klyne2006rdf}, which is adopted to build DBPedia\cite{auer2007dbpedia} and YAGO\cite{suchanek2007yago} from Wikipedia. 
-%但是，往往在图上的计算是非常费时的。
-%But The RDF and other methods often
+But the reasoning and maintainence of knowledge on the graph is usually expensive\cite{broekstra2003inferencing}\cite{bursztyn2015reasoning}. 
+To make a trade-off between cost and performance, we use the lightweight data struture \textit{history state} to represent the knowledge about what happend, which is extracted from the knowledge base.
+And the knowledge base's threefold structure \(G^{(0)}\), \(G^{(1)}\), \(G^{(2)}\) benefits the extraction of history states.
 
-\textbf{Taxonomy Graph \(G^{(0)}\)}. The directed edges in \(G^{(0)}\) represent the class-subclass relations in the knowledge base. 
+\textbf{Taxonomy Graph \(G^{(0)}\)}. The directed edges in \(G^{(0)}\) represent the \textit{class}\(\rightarrow\)\textit{subclass} relations in the knowledge base. 
 Taking Wikipedia for example (Figure \ref{fig:NSinitializaton}), the node \textit{Main topic classifications}\footnote{\url{https://en.wikipedia.org/wiki/Category:Main_topic_classifications}} has the subclass \textit{Society}, further contains the subclass \textit{Politics}, which is the ancestor of the subclass \textit{Military}.
+As \(G^{(0)}\) is not a Directed Acyclic Graph originally\cite{faralli2015large}, we remove the cycles according to nodes' PageRank-HITS\cite{Yan:2015wq} score.
+Specifically, the edges \textit{class}\(\rightarrow\)\textit{subclass} are preserved only when the node \textit{class} has the higher PageRank-HITS score than the node \textit{subclass}, which is shown in the line \ref{alg:line2inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}.
+After removing cycles, the taxonomy structure on the knowledge base is better represented by the directed acyclic graph \(G^{(0)'}\).
+As shown in line \ref{alg:line3inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}, by visiting the category \textit{military} in the DAG \(G^{(0)'}\), the breadth-first traverse can reach its successor sub-category nodes such as \textit{Firearms}, \textit{The World Wars}, and \textit{World War II}, etc.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=.82\columnwidth]{img/initializationExample.pdf}  
+    \caption{Illustration on how to initialize normal states from wikipedia (an example on the initialization of the normal states about \textit{military}).}
+    \label{fig:NSinitializaton}
+\end{figure}
 
 \textbf{Category-Page Bipartite Graph \(G^{(1)}\)}. 
+The directed edges in \(G^{(1)}\) represent the \textit{class}\(\rightarrow\)\textit{instance} relations in the knowledge base.
+In wekipedia, by considering \(G^{(0)'}\) and \(G^{(1)}\) together as shown in line \ref{alg:line5inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}, we can get all the pages related to the given category.
 
 \textbf{Page-Content Maps \(G^{(2)}\)}. 
+For a specific Wikipedia dumps version, the edges \textit{page}\(\rightarrow\)\textit{content} in \(G^{(2)}\) define a one-to-one mapping.
+There are a bulk of hisotry information restored in the wiki text content.
+In order to extract the key words in wiki page's content, which distinguish it from other pages, we use the chi-square statistics\cite{yang1997comparative}\cite{liu2009imbalanced} to measure the importance of each word for the specific page.
 
-As \(G^{(0)}\) is not a Directed Acyclic Graph originally\cite{faralli2015large}, we need to remove the , PageRank-HITS\cite{Yan:2015wq}.
-
-\begin{algorithm}
+For a given category in \(G^{(0)'}\), chi-square statistics also can evaluate the importance of each word appeared in text contents of category-related wiki pages. 
+For example, the chi-square statistic of the term \textit{shooting} under the category \textit{military} is 2888.7 which corresponds to the p-value 0.0001 of chi-square test with 1 degree of freedom.
+That means the term \textit{shooting} is highly related to the category \textit{military}.  
+To prevent the overclaim of rare word by chi-square statitistcs, the word frequency is introduced as a supplement\cite{liu2009imbalanced}, as shown in line \ref{alg:line10inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}.
+Finally, we can get the category's history state, which are  composed by the category related words and their corresponding importance.
+%history states衡量一个词在考虑完整历史信息的情况下，对于一个类别的重要程度，例如在military类别下面；从某种程度上讲，history state从knowledge base中抽取了对于该类别的重要特征，有助于我们将它应用到text stream当中。
+\begin{algorithm}[h]
 \scriptsize
-\caption{Normal States Initialization from Knowledge Base}
+\caption{History State Initialization from Knowledge Base}
 \label{alg:normalStatesInit}
@@
 \KwIn{Taxonomy's Graph \(G^{(0)}\), Category-Page Bipartite Graph \(G^{(1)}\), Page-Content Bipartite Graph \(G^{(2)}\), topic related category node \(c\)}
-\KwOut{Normal states \(\bm{f}_c\) on topic \(c\)}
+\KwOut{History state \(\bm{h}_c\) on category \(c\)}
 \(Pages(c)\leftarrow \varnothing\)\\
-DAG \(G^{(0)'} \leftarrow\) Remove Cycles of \(G^{(0)}\) by nodes' HITS-PageRank scores. \\
-\(SuccessorNodes(c) \leftarrow \) Breadth-first-traverse(\(G^{(0)},c\))\\
+DAG \(G^{(0)'} \leftarrow\) Remove Cycles of \(G^{(0)}\) by nodes' HITS-PageRank scores. \label{alg:line2inNormalStatesInit}\\
+\(SuccessorNodes(c) \leftarrow \) Breadth-first-traverse(\(G^{(0)},c\))\label{alg:line3inNormalStatesInit}\\
 \For{\(node \in SuccessorNodes(c)\)}{
-    \(Pages(c) \leftarrow Pages(c) \cup G^{(1)}.neighbours(node)\)\\
+    \(Pages(c) \leftarrow Pages(c) \cup G^{(1)}.neighbours(node)\) \label{alg:line5inNormalStatesInit}\\
 }
-\(WordFrequencyTable(c) \leftarrow \) do word count on the text contents of \(Pages(c)\) \\
-\(WordFrequencyTable(All) \leftarrow \) do word count on the text contents of all pages in \(G^{(2)}\).\\
+Word frequency table \(n(c,.) \leftarrow \) do word count on the text contents of \(Pages(c)\) \\
+Word frequency table \(n(All,.) \leftarrow \) do word count on the text contents of all pages in \(G^{(2)}\).\\
 \For{word \(w\) in WordFrequencyTable(All).keys()}{
-    \(\tau_{c,w} \leftarrow \) \(w\)'s chi-square score on \(WordFrequencyTable(c)\) and \(WordFrequencyTable(All)\).
+    \(chi(c,w) \leftarrow \) \(w\)'s chi-square statistics on \(WordFrequencyTable(c)\) and \(WordFrequencyTable(All)\).\\
+    \(h_{c,w} \leftarrow n(c,w)*chi(c,w)\) \label{alg:line10inNormalStatesInit}\\
 }
-\Return{\(\bm{f}_c\)}
+\Return{\(\bm{h}_c\)}
 \end{algorithm}
 
-%TODO
-
-\begin{figure}
-    \centering
-    \includegraphics[width=.85\columnwidth]{img/initializationExample.pdf}  
-    \caption{Illustration on how to initialize normal states from wikipedia (an example on the initialization of the normal states about \textit{military}).}
-    \label{fig:NSinitializaton}
-\end{figure}
+Considering the full Wikipedia's contents, history state evaluates the importance of word to the concerned category accurately. 
+For example, in \textit{military}'s history state, the top  words are \textit{army}, \textit{military}, \textit{air}, \textit{command}, \textit{force}, and \textit{regiment}, etc. 
+The document which contains these words is related to the category \textit{military} with high probability. 
+We further discuss how to apply history states to the textstream on the following subsection \ref{subsec:rs_initialization}.
 
@@
 
+\begin{equation}
+\label{eq:KBPriorLDAgibbs}
+\begin{aligned}
+&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha\bm{m},\beta,\tau)\\
+&\ \ \propto (n^{(d)}_{dk}+\alpha m_k)\frac{n^{(w)}_{kv}+\tau_{kv}+\beta}{n^{(w)}_{k,.}+\tau_{k,.}+V\beta}
+\end{aligned}
+\end{equation}
+
+\begin{comment}
 \begin{scriptsize}
@@
 \end{scriptsize}
+\end{comment}
 
+\begin{comment}
 \begin{algorithm}
@@
 
+\begin{comment}
 \begin{algorithm}
@@
 \end{figure}
+\end{comment}
 
+\begin{comment}
 \begin{table}
@@
 \end{table}
+\end{comment}
 
@@
 
-%\begin{comment}
+\begin{comment}
 \begin{table*}[ht]
@@
 \end{table*}
-%\end{comment}
+\end{comment}
 
@@
 
-\bibliographystyle{unsrt}
+\bibliographystyle{named}
+\small
 \bibliography{paperbib}

### 2016-09-11 paper/aaaiFormat.tex
finish sec 3.2

@@
 After removing cycles, the taxonomy structure on the knowledge base is better represented by the directed acyclic graph \(G^{(0)'}\).
-As shown in line \ref{alg:line3inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}, by visiting the category \textit{military} in the DAG \(G^{(0)'}\), the breadth-first traverse can reach its successor sub-category nodes such as \textit{Firearms}, \textit{The World Wars}, and \textit{World War II}, etc.
+As shown in line \ref{alg:line3inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}, by visiting the category \textit{Military} in the DAG \(G^{(0)'}\), the breadth-first traverse can reach its successor sub-category nodes such as \textit{Firearms}, \textit{The World Wars}, and \textit{World War II}, etc.
 \begin{figure}[h]
@@
     \includegraphics[width=.82\columnwidth]{img/initializationExample.pdf}  
-    \caption{Illustration on how to initialize normal states from wikipedia (an example on the initialization of the normal states about \textit{military}).}
+    \caption{Illustration on how to initialize history states from Wikipedia (an example on the initialization of the normal states about \textit{Military}).}
     \label{fig:NSinitializaton}
@@
 The directed edges in \(G^{(1)}\) represent the \textit{class}\(\rightarrow\)\textit{instance} relations in the knowledge base.
-In wekipedia, by considering \(G^{(0)'}\) and \(G^{(1)}\) together as shown in line \ref{alg:line5inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}, we can get all the pages related to the given category.
+In Wikipedia, by considering \(G^{(0)'}\) and \(G^{(1)}\) together as shown in line \ref{alg:line5inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}, we can get all the pages related to the given category.
 
@@
 
-For a given category in \(G^{(0)'}\), chi-square statistics also can evaluate the importance of each word appeared in text contents of category-related wiki pages. 
+For a given category in \(G^{(0)'}\), chi-square statistics also can evaluate the importance of each word appeared in text contents. 
 For example, the chi-square statistic of the term \textit{shooting} under the category \textit{military} is 2888.7 which corresponds to the p-value 0.0001 of chi-square test with 1 degree of freedom.
@@
 Considering the full Wikipedia's contents, history state evaluates the importance of word to the concerned category accurately. 
-For example, in \textit{military}'s history state, the top  words are \textit{army}, \textit{military}, \textit{air}, \textit{command}, \textit{force}, and \textit{regiment}, etc. 
-The document which contains these words is related to the category \textit{military} with high probability. 
-We further discuss how to apply history states to the textstream on the following subsection \ref{subsec:rs_initialization}.
+For example, in \textit{Military}'s history state, the top  words are \textit{army}, \textit{military}, \textit{air}, \textit{command}, \textit{force}, and \textit{regiment}, etc. 
+The document which contains these words is related to the category \textit{Military} with high probability. 
+We further discuss how to apply history states to the text stream on the following subsection \ref{subsec:rs_initialization}.
 
@@
 \label{subsec:rs_initialization}
+In this subsection, we describe how the proposed probabilistic model \textsc{HS-Prior-LDA} utilizes the history states to learn the recent states from text stream.
+
+There are two facts inspiring \textsc{HS-Prior-LDA}. 
+(1) The topics in the document may contain history-state-like topics. 
+As an example, the tweet ``Libyan rebel chief gunned down in Benghazi (2011-07-28)'' contains the topic that is similar to the \textit{Military}'s history state.
+(2) The history-state-like topics can reuse the information  stored in the history states.
+The word \textit{libyan} in the aforementioned example tweet ranks much higher in the \textit{Military} and the \textit{Middle East} history states than the other categories' history states.
+After considering the relatedness between the remaining context and the history states, the learned topics of the example tweet include \textit{Military} and \textit{Middle East}.
+
+The generative process of \textsc{HS-Prior-LDA} can be described as follows.
+
+\begin{enumerate}[itemsep=0mm]
+\item Draw corpus prior distribution \(\bm{m} \sim Dir(\alpha \bm{u})\), where \(\bm{u}\) is the uniform distribution.
+\item For each topic \(k \in \{1,\cdots,K\}\), 
+\begin{enumerate}[itemsep=0mm]
+\item word distribution on the topic \(\bm{\phi_k} \sim Dir(\bm{\beta}+ \bm{\tau_k})\).
+\end{enumerate}
+\item For each document index \(d \in \{1,\cdots,D\}\),
+\begin{enumerate}[itemsep=0mm]
+\item topic distribution on the document \(\theta_d \sim Dir(\bm{m})\),
+\item for each word index \(n \in \{1,\cdots,N_d\}\),
+\begin{enumerate}[itemsep=0mm]
+\item word's topic assignment \(z_{dn} \sim Multinomial(\theta_d)\), 
+\item word \(w_{dn} \sim Multinomial(\phi_{z_{dn}})\). 
+\end{enumerate}
+\end{enumerate}
+
+\end{enumerate}
+
+In the above generative process, the line 2(a) is the key point to distinguish \textsc{HS-Prior-LDA} from LDA\cite{blei2003latent}, where \(\bm{\tau}_k\) is defined by Equation(\ref{eq:wikiPrior}).
+\(K_{KB}\) is the number of pre-defined history-state-like topics, and \(S_k\) is the set of words appeared in the \(k\)-th topic's history state.
+As \cite{wallach2008structured} mentioned that the asymmetric prior distribution can significantly improve the quality of topic modelling, \(\bm{\phi_k} \sim Dir(\bm{\beta}+ \bm{\tau_k})\) incorporates history state into the asymmetric prior of the word distribution on topic.
+The effect of \(\bm{\tau_k}\) is obvious, e.g., \(\tau_{Military,army}/\tau_{Military,basketball}=203\) leads to that topic \textit{Military} prefers to contain the word \textit{army} other than \textit{basketball}.
+The parameter \(\lambda\) controls how much the learned topics are similar to the history state, which can be chosen by cross-validated grid-search.
+
+\begin{scriptsize}
+\begin{equation}
+\label{eq:wikiPrior}
+\begin{aligned}
+\tau_{kv}=
+\left\{ \begin{aligned}
+\lambda \frac{h_{kv}}{\sum_{v\in S_{k}}h_{kv}} &,v\in S_{k}\ and  \ k \leq K_{\bm{KB}} \\
+0&,v \notin S_{k} \ or \ k > K_{\bm{KB}} \\
+\end{aligned}\right.
+\end{aligned}
+\end{equation}
+\end{scriptsize}
 
@@
 \end{comment}
-
+\begin{comment}
 \ \ Our topic modeling, want to learn the first \(k\) topics with Wikipedia Article \(k\) topics as close as possible, and we will be Wikipedia article \(k\) before 1000 words) was added to the theme of the word frequency word in the subject a priori distribution on the.
@@
 In the latter experiment, we will be on a priori knowledge of weights \(W \) will be discussed. 
+\end{comment}
 
-\begin{table}[!htbp]
-\begin{tabular}{l}
-1. Draw corpus prior distribution \(\bm{m} \sim Dir(\alpha \bm{u})\), where \(\bm{u}\)\\
- \ \ \ \ is the uniform distribution. \\
-2. For each topic \(k \in \{1,\cdots,K\}\),\\
-\ \ \ \ (a) word distribution on the topic \(\bm{\phi_k} \sim Dir(\bm{\beta}+ \bm{\tau_k})\). \\
-
-3. For each document index \(d \in \{1,...,D\}\), \\
-\ \ \ \ (a) topic distribution on the document \(\theta_d \sim Dir(\bm{m})\), \\
-\ \ \ \ (b) for each word index \(n \in \{1,\cdots,N_d\}\),\\
-\ \ \ \ \ \ \ \ i. word's topic assignment \(z_{dn} \sim Multinomial(\theta_d)\), \\
-\ \ \ \ \ \ \ \ ii. word \(w_{dn} \sim Multinomial(\phi_{z_{dn}})\). \\
-\end{tabular}
-\end{table}
-
-\begin{scriptsize}
-\begin{equation}
-\label{eq:wikiPrior}
-\begin{aligned}
-\tau_{kv}=
-\left\{ \begin{aligned}
-\lambda \frac{f_{kv}}{\sum_{v\in S_{kv}}f_{kv}} &,v\in S_{k}\ and  \ k \leq K_{\bm{KB}} \\
-0&,v \notin S_{k} \ or \ k > K_{\bm{KB}} \\
-\end{aligned}\right.
-\end{aligned}
-\end{equation}
-\end{scriptsize}
-
+To solve \textsc{HS-Prior-LDA}, the gibbs sampling is adopted to determine the hidden variable \(z_{dn}\) and the model parameter \(\phi_k\).
+In the initialization phrase of gibbs sampling for \textsc{HS-Prior-LDA}, the hidden variable \(z_{dn}\) is initialized to topic \(k\) with probability \(\hat{q}_{k|v}\) as Equation (\ref{eq:initProbability}).
+For the word \(v\) that belongs to any history state, \(\hat{q}_{k|v}\) is propotional to its importance in the history state \(\tau_{kv}\) as Eq\ref{eq:initProbability}(a). 
+For the new word \(v\) in text stream, \(\hat{q}_{k|v}\) is   set uniformly \(1/(K-K_{\bm{KB}})\) on the other topics as Eq\ref{eq:initProbability}(b,c). 
+The initialization makes sure that the learned topics are aligned to the pre-defined history states.
 \begin{scriptsize} 
@@
 \left\{ \begin{aligned}
-\frac{\tau_{kv}}{\sum_{k=1}^{K}\tau_{kv}} &,\sum_{k}\tau_{kv}>0 \\
-0&, \sum_{k}\tau_{kv}=0 \ and \ k \leq K_{\bm{KB}} \\
-1/(K-K_{\bm{KB}})&,\sum_{k}\tau_{kv}=0 \ and \ k > K_{\bm{KB}}
+\frac{\tau_{kv}}{\sum_{k=1}^{K}\tau_{kv}} &,\sum_{k}\tau_{kv}>0 & (a)\\
+0&, \sum_{k}\tau_{kv}=0 \ and \ k \leq K_{\bm{KB}} & (b)\\
+1/(K-K_{\bm{KB}})&,\sum_{k}\tau_{kv}=0 \ and \ k > K_{\bm{KB}} & (c)
 \end{aligned}\right.
@@
 
+%采样公式p(z|.)，z有两部分。
+The sampling process uses the conditional probability \(p(z_{dn}=k|.)\propto (n^{(d)}_{dk}+\alpha m_k)(n^{(w)}_{kv}+\tau_{kv}+\beta)/(n^{(w)}_{k,.}+\tau_{k,.}+V\beta)\), where \(n^{(d)}_{dk}\) is the number of words in document \(d\) assigned to topic \(k\), and \(n^{(w)}_{kv}\) is the times of word \(v\) assigned to topic \(k\).
+We also optimize \(\alpha \bm{m}\) for promoting \textsc{HS-Prior-LDA}'s fitting to documents according to \cite{wallach2008structured}\footnote{\url{https://github.com/mimno/Mallet/blob/master/src/cc/mallet/types/Dirichlet.java}}.\begin{comment}
 \begin{equation}
@@
 \end{equation}
+\end{comment}
 
@@
 
-The line 12 in Algorithm \ref{alg:gibbsSamplingKBPriorLDA} is implemented according to \cite{wallach2008structured}\footnote{\url{https://github.com/mimno/Mallet/blob/master/src/cc/mallet/types/Dirichlet.java}}, which can optimize \(\alpha \bm{m}\) for promoting NS-Prior-LDA's fitting to documents \(\mathcal{D}\).
+After gibbs sampling on discrete time windows, \textsc{HS-Prior-LDA} learned all hidden topics of words.
+And for a specific word type \(w\) and its history-state-like topic assignment \(c\) in time window \(t\), its document frequency is counted as \(n(c,t,w^{(c)})\), which is the element of category \(c\)'s \(t\)-th recent state.
+Event detection on recent states is discussed in the following subsection.
 
-\subsection{Detecting Events from Recent States}
-\label{subsec:detection}
-The state of attention of social issue k at time t in cyberspace is binary, namely at the peak or not at the peak.
-We denote it by hidden binary variable \(s_{k,t}\), which is 1 or 0.
-We do the inference for the hidden variable \(s_{k,t}\) according to Poisson distribution according to Reference\cite{Diao:2012wj} 10,11.
-If the state of attention of social issue k at time t is "not at peak", then the probability density function is
-\(p(x_{k,t}|s_{k,t}=0)=e^{-\mu_0 }  \frac{\mu_0^{x_{k,t}}}{x_{k,t}!}\) otherwise the probability density function is \(p(x_{k,t}|s_{k,t}=0)=e^{-\mu_1 }  \frac{\mu_1^{x_{k,t}}}{x_{k,t}!}\)
-In the above functions the symbol \(x_{k,t}\) denotes the attention of social issue \(k\) at time \(t\) , the symbol A denotes the constant, \(\mu_0\) and \(\mu_1\) represent the average of \(x_{k,t}\) at peak and not at peak respectively.
-The state \(s_{k,t}\) is inferred from \(ratio=\frac{p(x_{k,t} |s_{k,t}=0)}{p(x_{k,t} |s_{k,t}=1)} \).
-In calculation, we use the log ratio to determine whether the attention is at peak as in equation (\ref{eq:logratio}).
-\(\log ratio>0 \) indicates that the attention of social issue \(k\) at time \(t\) is not at peak, otherwise at peak.
-\begin{equation}
-\label{eq:logratio}
-\log ratio=-(\mu_0-\mu_1 )+x_{k,t}(\log \mu_0 -\log⁡ \mu_1)
-\end{equation}
-
-\begin{comment}
-\begin{algorithm}
-\scriptsize
-\label{alg:eventKeywordsSearchMethod}
-\caption{Spectral Clustering Based Event Phrase Extraction}
-\label{alg:eventKeywordsSearchMethod}
-\KwIn{\(\mathcal{B}_{k,t},\mathcal{G}_{k,t},\rho\)}
-\KwOut{\(\mathcal{C}_{k,t}\)}
-\(n_{k,t}\)=number of connected component in \(\mathcal{G}_{k,t}\)\\
-\For{\(n \in \{ n_{k,t}, \cdots, |\mathcal{G}_{k,t}|\}\) }{
-    \(\mathcal{C}_{k,t}=SpectralClustering(\mathcal{G}_{k,t},n)\)\\
-    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\rho\)}{
-        return \(\mathcal{C}_{k,t}\)
-    }
-}
-\end{algorithm}
-\end{comment}
-
-\begin{comment}
-\begin{figure}
-\centering
-\includegraphics[height=3cm]{img/wordClusterGraph.eps}
-%todo
-\caption{Hot words between the heat pattern forming word time window edge weight calculated by the PMI obtained between words, to obtain spectral clustering clustering clustering}
-\label{fig: windowsBurstyWordGraph}
-\end{figure}
-\end{comment}
-\textbf{event} phrase Mining
-% Refer to bursty.py
-\ \ Microblogging mining events can be represented by a variety of ways, a single word, phrase, or topic.
-Here we use the form of phrase, said event.
-In this paper, the phrase indicates that the event is due to the fact that: the same period of time when there are multiple areas of internal hot words appear, a collection of hot words \(\mathcal{B}_{k, t} \) between the hot words great probability is interrelated.
-For example, observed "mac", "os", "lion" three words are in a state of emergency.
-In fact, the state of emergency three words is to publish a new system "mac os lion" event caused by Apple, in order to find the association between words and events, we use spectral clustering based search methods.
-
-As shown in Figure \ref{fig: windowsBurstyWordGraph} below, we will one area, a hot word of the time window and hot words between to diagram.
-Hot words set \(\mathcal{B}_{k, t} \) formed in FIG using \textbf{hot word graph} \(\mathcal{G}_{k, t} = (\mathcal{B}_{k, t}, \mathcal{E}_{k, t}) \) indicates,
-\(\mathcal{E}_{k, t} = \{(a, b) | a \in \mathcal{B}_{k, t}, b \in \mathcal{B}_{k, t }, PMI (\mathcal{D}_{k, t}, a, b)> 0 \} \), where \(PMI (\mathcal{D}_{k, t}, a, b) \) the field \(k \) time window \(t \) related microblog \(\mathcal{D}_{k, t} \) on the word \(a\) and the word \(b\) point metric information between each other.
-% Refer to bursty.py getSimGraph () function
-
-Given a field \(k\) and the time window \(t\), in which the number of events can not be determined in advance.
-The two most extreme situations are: events coarse granularity, said the event is equal to the number of Figure \(\mathcal{G}_{k, t} \) in the number of connected components; events finer granularity display, event number equal to \(\mathcal{G}_{k, t} \) the number of points.
-To do this, we use the Density to the degree of density of quantum graphs \(2 \#Edge / (\# Node \ cdot (\# Node-1)) \), the more the greater if the edge density in the range of Density in \((0,1] \).
-Density can be a good indicator to determine the size indicates the event: too many unrelated phrases to put together an event can not be represented, too fine particle size, such as a single word can represent only part of the event; only in close co-occurrence of the phrase to a reasonable It indicates that the event granularity.
-To this end, we have designed events phrase search algorithm \ref{alg:eventKeywordsSearchMethod}: We try to find a reasonable number of spectral clustering Clustering \(n \), let \(n \) from a smaller value ( event corresponds to coarser granularity representation) to start the search, then the most likely cluster cluster size is too large, its performance is the clustering results in one or more small Density indicators; continue to increase the number of clusters \(n \), the event represents reduced size, reduced the size of clusters of clusters, thus making the Density index increases; when all cluster clustering Density indicators are larger than the threshold \(\tau \), the search terminates, returning clustering results \(\mathcal{C}_{k, t}\).
-As the above process algorithm \ref{alg:eventKeywordsSearchMethod} description line 2 to line 5, we use in practice \(\rho = 0.6 \).
-We call \(\mathcal{C}_{k, t} \) results in each cluster to cluster \textbf{event} phrase.
-
-\textbf{detected events related to micro-blog}
-\ \
-By algorithm \ref{alg:eventKeywordsSearchMethod} find art \(k \) time window \ \(t \) within the \(| \mathcal{C}_{k, t} | \) events phrase later, you can also further find each event and the corresponding event phrase microblogging.
-We looked at the first \(i \) events phrase \(\mathcal{C}_{k, t, i} \),
-The phrase based on the number of elements distinguish the event, there are three situations: (1) the phrase event more than two hot words, he said while the event is not a phrase between any two words We have a very strong relationship between the co-occurrence, so just pay attention to the co-occurrence relationship stronger side; (2) event phrase has two hot words; (3) the event is only a hot word in the phrase.
-Weibo text length is shorter, not all of the microblogging event will include the phrase \(\mathcal{C}_{k, t, i} \) in all the words.
-Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\mathcal{D}_{k, t, i} \) in.
-For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\mathcal{D}_{k, t, i} \) in.
-Ultimately, we can get the field \(k \) next time window \(t \) in the event the phrase relating to events microblogging \(\{(\mathcal{C}_{k, t, i}, \mathcal{D}_{k, t, i}) \}_{i=1}^{| \mathcal{C}_{k, t} |} \).
+%Text stream evolves more quickly with time than knowledge base.
+%For example, recent state of Military contain .
 
@@
 \label{my-label}
-\begin{tabular}{|l|l|l|l|l|l|}
+\begin{tabular}{|l|l|l|l|l|}
 \hline
- &  & LDA & BOW & doc2vec & \begin{tabular}[c]{@{}l@{}}NS-Prior-\\ LDA\end{tabular} \\ \hline
-comp.graphics & Computer graphics &  &  &  &  \\ \hline
-comp.os.ms-windows.misc & Microsoft Windows &  &  &  &  \\ \hline
-comp.sys.ibm.pc.hardware & IBM personal computers &  &  &  &  \\ \hline
-comp.sys.mac.hardware & Macintosh computers &  &  &  &  \\ \hline
-comp.windows.x & X Window System &  &  &  &  \\ \hline
-rec.autos & Automobiles &  &  &  &  \\ \hline
-rec.motorcycles & Motorcycles &  &  &  &  \\ \hline
-rec.sport.baseball & Baseball &  &  &  &  \\ \hline
-rec.sport.hockey & Hockey &  &  &  &  \\ \hline
-sci.crypt & Cryptography &  &  &  &  \\ \hline
-sci.electronics & Electronics &  &  &  &  \\ \hline
-sci.med & Medicine &  &  &  &  \\ \hline
-sci.space & Outer space &  &  &  &  \\ \hline
-misc.forsale & Sales &  &  &  &  \\ \hline
-talk.politics.misc & Politics &  &  &  &  \\ \hline
-talk.politics.guns & Gun politics &  &  &  &  \\ \hline
-talk.politics.mideast & Middle East &  &  &  &  \\ \hline
-talk.religion.misc & Religion &  &  &  &  \\ \hline
-alt.atheism & Atheism &  &  &  &  \\ \hline
-soc.religion.christian & Christians &  &  &  &  \\ \hline
-In total & &  &  &  & \\ \hline
+ &  & LDA & BOW  & \begin{tabular}[c]{@{}l@{}}NS-Prior-\\ LDA\end{tabular} \\ \hline
+comp.graphics & Computer graphics &  &  &    \\ \hline
+comp.os.ms-windows.misc & Microsoft Windows &  &  &    \\ \hline
+comp.sys.ibm.pc.hardware & IBM personal computers &  &  &    \\ \hline
+comp.sys.mac.hardware & Macintosh computers &  &  &    \\ \hline
+comp.windows.x & X Window System &  &  &    \\ \hline
+rec.autos & Automobiles &  &  &    \\ \hline
+rec.motorcycles & Motorcycles &  &  &    \\ \hline
+rec.sport.baseball & Baseball &  &  &    \\ \hline
+rec.sport.hockey & Hockey &  &  &    \\ \hline
+sci.crypt & Cryptography &  &  &    \\ \hline
+sci.electronics & Electronics &  &  &    \\ \hline
+sci.med & Medicine &  &  &    \\ \hline
+sci.space & Outer space &  &  &    \\ \hline
+misc.forsale & Sales &  &  &    \\ \hline
+talk.politics.misc & Politics &  &  &    \\ \hline
+talk.politics.guns & Gun politics &  &  &    \\ \hline
+talk.politics.mideast & Middle East &  &  &   \\ \hline
+talk.religion.misc & Religion &  &  &    \\ \hline
+alt.atheism & Atheism &  &  &    \\ \hline
+soc.religion.christian & Christians &  &   &  \\ \hline
+In total &  &  &  & \\ \hline
 \end{tabular}
@@
 \end{figure}
+\end{comment}
 
@@
 squadron & fly & cancer & body & syria & world & battle & attack & htc & apps & arcade & \textcolor{red}{\textit{ps3}}\\
-flights & hurricane & cells & healthy & iraq & syria & commander & u.s. & smartphone & free & wii & trailer\\
-pilots & navy & blood & study & palestinian & protest & ship & gaddafi & phones & \#android & multiplayer & online\\
-raf & flying & therapy & pain & syrian & israeli & corps & army & blackberry & htc & sega & hours\\
-airways & aircraft & drug & exercise & iranian & egypt & navy & forces & apps & google & console & ipad\\
-fighter & \textcolor{red}{\textit{irene}} & medicine & \#health & ottoman & al & brigade & pakistan & ipad & galaxy & enemies & app\\
-boeing & crew & brain & natural & islamic & syrian & battalion & afghanistan & gsm & ios & characters & player\\
-runway & sky & care & disease & iraqi & protesters & lieutenant & military & lte & store & playable & wii\\
-force & crash & syndrome & acne & abu & arab & aircraft & attacks & symbian & windows & character & ops\\
-crashed & jet & infection & hair & jewish & rights & officer & troops & devices & mac & video & download\\
-flew & pilot & disorder & surgery & persian & libya & naval & dead & smartphones & phones & graphics & nintendo\\
 \hline
@@
     Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
-    UMass System\cite{Allan:2000wu} & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
+    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
     LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
@@
 \end{table}
+\cite{Allan:2000wu}
 
@@
 \centering
-\caption{Events about \textit{military} detected by systems between 2011-07-20 and 2011-07-30}
+\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-30}
 \label{my-label}
@@
 Date & Event key words & Representative event tweet & \begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular} \\ \hline
-7/20/11 & \begin{tabular}[c]{@{}l@{}}Serbia, crimes, \\ fugitive, arrests\end{tabular} & Serbia: Serbia arrests last war crimes fugitive-TV- Reuters & 27 \\ \hline
-7/20/11 & Somalia, famine & \begin{tabular}[c]{@{}l@{}}UN declares famine in Somalia. What can we do to save \\ 3.7million lives? http://bit.ly/r1Rq7R\end{tabular} & 89 \\ \hline
-7/21/11 & \begin{tabular}[c]{@{}l@{}}U.S., military, \\accept, gay, \\lesbian, openly\end{tabular} & \begin{tabular}[c]{@{}l@{}}RT @cnnbrk: Pentagon is set to certify that the U.S.
-military \\ is prepared to accept openly gay and lesbian service members \\ \#dadt\end{tabular} & 20 \\ \hline
 7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman...˙http://dlvr.it/cLbk8\end{tabular} & 557 \\ \hline

### 2016-09-14 paper/aaaiFormat.tex
9.14-0

@@
 We reaveal that the two important factors should be met, (1) having a good mechanism to organize the history data, and (2) having the capability of self-updating, to accumlate the knowledge about what is happening.
-%NSDetector的特性应该被
-According to this guideline, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of history data.
-In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
+According to this guideline, we propose a knowledge base enhanced continous learning method for high accuracy event detection. 
+In this proposed method, 1) the data structure\textit{history states} can be initialized by knowledge base to restore what happened; 2) \textit{recent states} are updated by \textit{history states} and upcoming text streams via our proposed probabilistic model HS-Prior-LDA to maintain what is happening; 3) events can be detected by recent states with high accuracy; 4) the \textit{history status} is
 Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
@@
 \section{Related Works}
-The first category of methods, including UMass\cite{Allan:2000wu} and BBTM\cite{yan2015probabilistic}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
+The first category of methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
 This kind methods can be implemented by clustering of articles\cite{Allan:2000wu}\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topic modeling\cite{Diao:2012wj}\cite{Yan:2015wm} in the recent time windows.
@@
 On the one hand, UMass\cite{Allan:2000wu} prefers the lower threshold to enlarge the recall but suffers the precision. 
-On the other hand, BBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.
+On the other hand, BurstyBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.
 
@@
 
-\begin{rmk}[The Set of Events' Candidate Words] 
-The set of events' candidate words \(\mathcal{B}_{c,t}\) are defined by the bursty words in recent state \(\bm{r}_{c,t}\).
-\end{rmk}
-
-\begin{rmk}[Event Phrase] 
-Event phrase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occured in the set of events' cadidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happend in time \(t\) under the category \(c\).
-\end{rmk}
-
-\begin{rmk}[Event Related Articles] Event related articles \(\mathcal{D}_{c,t,i}\) are articles that relate to the \(i\)-th event in time \(t\) under the category \(c\), and correspond to the event phrase \(\mathcal{C}_{c,t,i}\).
-\end{rmk}
-
 Section \ref{subsec:hs_initialization} explains the details of how to initialize history states from knowledge base.
@@
 
-\textbf{Page-Content Maps \(G^{(2)}\)}. 
+\textbf{Page-Content Map \(G^{(2)}\)}. 
 For a specific Wikipedia dumps version, the edges \textit{page}\(\rightarrow\)\textit{content} in \(G^{(2)}\) define a one-to-one mapping.
@@
 To solve \textsc{HS-Prior-LDA}, the gibbs sampling is adopted to determine the hidden variable \(z_{dn}\) and the model parameter \(\phi_k\).
-In the initialization phrase of gibbs sampling for \textsc{HS-Prior-LDA}, the hidden variable \(z_{dn}\) is initialized to topic \(k\) with probability \(\hat{q}_{k|v}\) as Equation (\ref{eq:initProbability}).
+In the initialization phase of gibbs sampling for \textsc{HS-Prior-LDA}, the hidden variable \(z_{dn}\) is initialized to topic \(k\) with probability \(\hat{q}_{k|v}\) as Equation (\ref{eq:initProbability}).
 For the word \(v\) that belongs to any history state, \(\hat{q}_{k|v}\) is propotional to its importance in the history state \(\tau_{kv}\) as Eq\ref{eq:initProbability}(a). 
@@
 
-%Text stream evolves more quickly with time than knowledge base.
-%For example, recent state of Military contain .
+\subsection{Detecting Events from Recent States}
+\label{subsec:detection}
+Text stream evolves more quickly with time than knowledge base.
+For example, recent state of Military contain .
+In other words, recent state is history-state-like topic timestamp.%在时间轴上的横截面。
+
+The remaining time series analysis and text stream mining includes three phases: (1) bursty words; (2)phase; (3)tweet.
+%An accurate recent states learning leads to accurate event detection.
+\begin{rmk}[The Set of Events' Candidate Words] 
+The set of events' candidate words \(\mathcal{B}_{c,t}\) are defined by the bursty words in recent state \(\bm{r}_{c,t}\).
+\end{rmk}
+
+\begin{rmk}[Event Phase] 
+Event phase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occured in the set of events' cadidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happend in time \(t\) under the category \(c\).
+\end{rmk}
+
+\begin{rmk}[Event Related Articles] Event related articles \(\mathcal{D}_{c,t,i}\) are articles that relate to the \(i\)-th event in time \(t\) under the category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
+\end{rmk}
+
+\textbf{detected events related to micro-blog}
+\ \
+By algorithm \ref{alg:eventKeywordsSearchMethod} find art \(k \) time window \ \(t \) within the \(| \mathcal{C}_{k, t} | \) events phrase later, you can also further find each event and the corresponding event phrase microblogging.
+We looked at the first \(i \) events phrase \(\mathcal{C}_{k, t, i} \),
+The phrase based on the number of elements distinguish the event, there are three situations: (1) the phrase event more than two hot words, he said while the event is not a phrase between any two words We have a very strong relationship between the co-occurrence, so just pay attention to the co-occurrence relationship stronger side; (2) event phrase has two hot words; (3) the event is only a hot word in the phrase.
+Weibo text length is shorter, not all of the microblogging event will include the phrase \(\mathcal{C}_{k, t, i} \) in all the words.
+Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\mathcal{D}_{k, t, i} \) in.
+For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\mathcal{D}_{k, t, i} \) in.
+Ultimately, we can get the field \(k \) next time window \(t \) in the event the phrase relating to events microblogging \(\{(\mathcal{C}_{k, t, i}, \mathcal{D}_{k, t, i}) \}_{i=1}^{| \mathcal{C}_{k, t} |} \).
 
 \section{Experiments}
-\subsection{Effects of Normal States}
-We use 20newsgroups\cite{lang1995newsweeder} dataset\footnote{http://qwone.com/~jason/20Newsgroups} to check the effects of normal states initialization.
+\subsection{Effects of History States and Recent States}
+Firstly, we demonstrate the effectiveness of history states. 
+\textbf{Knowledge Base.} 
+We construct the taxonomy graph \(G^{(0)}\), the category-page bipartite graph \(G^{(1)}\) from the latest dump of category links\footnote{\url{https://dumps.wikimedia.org/enwiki/latest/enwiki-latest-categorylinks.sql.gz}} and the page-content map \(G^{(2)}\) from Wikipedia pages\footnote{\url{https://dumps.wikimedia.org/enwiki/latest/enwiki-latest-pages-articles.xml.bz2 }}.
+We set \(K_{KB}=100\), which means 100 categories are selected manually to cover the topics of Wikipedia and the target corpus as widely as possible. 
+There are two kinds of categories are considered. 
+The mid-high categories in the taxonomy graph \(G^{(0)'}\), which are representative, are likely to be selected, such as \textit{Aviation}, \textit{Military}, and \textit{Middle East}, etc.
+And the mid categories, which reflect the main interests of the target corpus, are also taken into consideration, such as \textit{American Football}, \textit{Basketball}, and \textit{Baseball}, etc. 
+%Other knowledge bases which have the above mentioned threefold structure are also available for conducting.
+
+\textbf{Text Stream Dataset.} We conduct the empirical analysis on a text stream benchmark \textit{Edinburgh twitter corpus} which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}.
+Due to the developer policy of Twitter\footnote{\url{https://dev.twitter.com/overview/terms/policy}}, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/fsd_corpus.tar.gz}}.
+We collected the tweets' contents according to the IDs with the help of Twitter API. 
+Though we cannot get the whole dataset due to the limit of Twitter API, after neccessary pre-processing, our rebuilt dataset still contains 36,627,434 tweets, which spans identically from 2011/06/30 to 2011/09/15.
+More details of the original dataset are described in \cite{petrovic2010edinburgh}.
+
+\textbf{History States and Recent States.} 
+The history states are initialized on the pre-defined categories on the knowledge base as Algorithm \ref{alg:normalStatesInit}.
+For \textsc{HS-Prior-LDA}, \(K\) is set to be 200, which means \textsc{HS-Prior-LDA} learned 100 history-state-like topics and 100 other topics.
+After cross-validated grid-search, \(\lambda\) is set to be 12.8. The other parameters are set as \(\alpha=0.1\), \(\beta=0.005\).
+We do continous learning on the 
+%如图（topic）中，能够从Military*中学习出tweet（20110728）话题中包含libyan。
+
+%We use 20newsgroups\cite{lang1995newsweeder} dataset\footnote{\url{http://qwone.com/~jason/20Newsgroups}} to check the effects of normal states initialization.
 
@@
 
+\begin{comment}
 \begin{table}[]
@@
 
-\begin{comment}
+%\begin{comment}%TODO
 \begin{figure}
@@
 \end{figure}
-\end{comment}
+%\end{comment}
 
@@
     LDA & None  & 1.265 \(\pm\) 0.013     \\ \hline
-    BBTM\cite{Yan:2015wm} & None    & 1.467 \(\pm\) 0.017     \\ \hline
+    BurstyBTM\cite{Yan:2015wm} & None    & 1.467 \(\pm\) 0.017     \\ \hline
     NS-Prior-LDA\(^{(-)}\)   &   \begin{tabular}[c]{@{}l@{}}\footnotesize{Words in categories simply}\\ \footnotesize{extracted from Wikipedia}\end{tabular} & 1.439 \(\pm\) 0.010     \\ \hline
@@
 \centering
-\caption{Normal States initialized from Wikipedia and topical words learned from NS-Prior-LDA}
+\caption{Normal States initialized from Wikipedia and topical words learned from HS-Prior-LDA}
 \label{my-label}
-\scalebox{0.88}{
+\scalebox{0.76}{
 \begin{tabular}{|cc|cc|cc|cc|cc|cc|}
@@
 \end{table*}
-
-\begin{table}
-
-\scriptsize
-\centering
-\caption{Normal States initialized from Wikipedia and topical words learned from NS-Prior-LDA}
-\scalebox{0.95}{
-    \begin{tabular}{|l|l|l|l|l|}
-    \hline
-    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
-    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
-    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
-    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
-    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
-    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
-    BBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
-    \textsc{NSDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
-    \end{tabular}
-}
-\end{table}
-\cite{Allan:2000wu}
 
@@
     EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
-    BBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
+    BurstyBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
     \textsc{NSDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
@@
 \centering
-\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-30}
+\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-28}
 \label{my-label}
@@
 
-\subsection{Quantitive Study}
-\textbf{Data set.} We conduct the empirical analysis on a twitter dataset which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}.
-Due to the developer policy of Twitter\footnote{https://dev.twitter.com/overview/terms/policy}, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{http://demeter.inf.ed.ac.uk/cross/docs/fsd\_corpus.tar.gz}.
-We collected the tweets' contents according to the IDs with the help of Twitter API.
+\subsection{Effects of Event Detection}
+\textbf{Baselines Methods.} We compare our proposed method against the following methods, Twevent\cite{Twevent2012}, BurstyBTM\cite{Yan:2015wm}, LSH\cite{Petrovic:2010uj}, EDCoW \cite{Weng:2011wz}, TimeUserLDA\cite{Diao:2012wj}, and UMass System\cite{Allan:2000wu}.
+We implement these competing methods based on the open source community versions, e.g.
+EDCoW\footnote{\url{https://github.com/Falitokiniaina/EDCoW}}, or the authors' releases, e.g.
+BurstyBTM\footnote{\url{https://github.com/xiaohuiyan/BurstyBTM}}.
+These methods work in four ways. 
+1) Based on topic model, BurstyBTM and TimeUserLDA detect bursty topics. 
+Although they are desinged for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
+2) Integrated with knowledge base, Twevent detects bursty segments, groups them into clusters, and then filters out the meaningless ones by Wikipedia.
+3) By clustering articles, UMass System and LSH decide whether the article belongs to the existing event or a new one.
+As designed for First Story Detection task (one of the Topic Detection and Tracking subtasks\cite{allan2012topic}) initially, they prefer to enlarge the recall of detected events. 
+4) By analyzing word frequencies, EDCoW clusters the bursty words into events.
 
-%TODO
-The benchmark \textit{Edinburgh twitter corpus} contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}} and 90 million tweets.
-Though we cannot get the whole dataset due to the limit of Twitter API, after neccessary pre-processing, our rebuilt dataset still contains 36,627,434 tweets, which spans identically from 2011/06/30 to 2011/09/15, and also covers 27 labeled events.
-More details of the original dataset are described in \cite{petrovic2010edinburgh}.
+\textbf{Evaluation Metrics.} 
+The first benchmark on \textit{Edinburgh twitter corpus} contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}}, which all exist in our rebuilt dataset on the \textit{Edinburgh twitter}'s IDs.
+These labeled events focus on the events that are both mentioned in twitter and newswire,e.g.
+\textit{``Oslo Attacks"} and \textit{``US Increasing Debt Ceiling"}, but still miss many important events such as \textit{``Hurricane Irene"}, \textit{``Al-Qaida's No.
+2 Leader Being Killed"}, and popular events such as \textit{``Harry Potter and the Deathly Hallows (Part 2)"}.
+To enlarge the realistic ground-truth .
+\textbf{TODO.}
+The dataset does not come with ground truth labels on all realistic events within the data collection period. 
+Because it is infeasible to manually label the over 4 million tweetsin the dataset, we choose to manually evaluate the detected events
+returned by Twevent. 
+We use precision and recall to evaluate the
+accuracy of the events detected.
+%为了扩大我们的标注数据集，我们
+\begin{table}[h]
+\scriptsize
+\centering
+\scalebox{0.95}{
+    \begin{tabular}{|l|l|l|l|l|}
+    \hline
+    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
+    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
+    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
+    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
+    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
+    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
+    BurstyBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
+    \textsc{NSDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
+    \end{tabular}
+}
+\caption{Overall Performance on Event Detection}
+\end{table}
+
+\textbf{Overall Performances.}
+Table 1 reports the number of events
+detected, the precision and recall, of the three methods respectively.
+The results of EDCoW are reproduced from [21]9
+. Shown in the
+table, our proposed method Twevent yields the best precision of
+86.1\% which is significantly larger than the precisions achieved
+by EDCoW and Tweventu. Observe that our method Twevent detects
+101 events with a recall of 75 realistic events. On the same
+dataset, EDCoW detects 21 events in total with 13 realistic events.
+Tweventu yields a slighter worse precision than EDCoW (75.3%
+vs 76.2\%) but detects the largest number of realistic events. In
+terms of DERate, Twevent achieves the lowest rate despite that our
+method detects much more events than EDCoW (101 vs 21). On
+the other hand, we observe that Tweventu delivers the worst DERate,
+more than double of Twevent (41\% vs 16.0\%). That is, the unigrams
+about the same event are clustered into two or more events.
+Because a tweet segment usually conveys very specific information,
+the tweets containing the tweet segment are all about the same
+topic (e.g., the event). Two tweet segments about the same event
+are therefore have higher chance to be clustered together.
+%首先，我们说明History states学习的有效性。我们人工选择了Wikipedia中100个category，即K_{KB}=100，对HS-PRIOR-LDA设置了200个topic即K=100，
+
+\subsection{Effects of Continous Learning}
+In this section, we prove the continuous learning char- acter of our model.
+We have three political events: CIA, Cuba and NYPD, and two Sport events: Bengals and Ra- jon.
+Firstly we learn the CIA event and then use its φA to initialize NYPD event, and save the combined φA of these two events as φ′A.
+Cuba/S represents the single Cuba event, while Cuba/L means the Cuba event with φ′A initialization.
+As parameter φA is mostly influence the extraction of aspects, we just list the metrics of aspects in Table 5.
+
+We can see that with the knowledge of previous event, our model can have a better performance with 2.5\% improvement.
+The promotion of sport event is tiny, because Rajon is about basketball and Bengals is about football.
+The words they shared is 16\% of Bengals, while the shared words of the three political events is 38\% of Cuba.
+
+Moreover, we compare the model labeled data with our manual annotations.
+We find many aspect words that do not discovered in Cuba/S, were discovered in the Cuba/L.
+For example, in tweet “agriculture big appetite cuba trade honolulu”, “honolulu” was labeled as background in Cuba/S while it is labeled as aspects in Cuba/L.
+What’s more, in NYPD event “honolulu” is an aspect discovered by our mod- el.
+Which is the reason why our model can have a better performance in the continuous learning model.
+
 \begin{comment}
@@
 NPMI\cite{Aletras2013EvaluatingTC}\cite{Rder2015ExploringTS}\footnote{https://github.com/AKSW/Palmetto}.
-
-\textbf{Benchmark1} The first set of the ground truth about events in the corpus are provided by \cite{petrovic2013can}, which is mentioned above. 
-And 27 events ...
-
-\textbf{Benchmark2} here.
-
-\textbf{Normal States Initialization} here.
-
-\textbf{Baseline}
-
-UMass System\cite{Allan:2000wu}
-
-LSH
-
-TimeUserLDA
-
-Twevent
-
-EDCoW
-
-BBTM\cite{yan2015probabilistic}
-
-\textbf{Model Setting}
 \end{comment}
 %\textbf{Topic Coherence} \cite{roder2015exploring}
-\subsection{Qualitative Study}
 %\textbf{PMI}
@@
 \section{Conclusions \& Future Work}
+Twitter, as a new type of social media, has experienced an explosive growth in terms of both users and information volume in recent years. 
+The characteristics of tweets propose severe challenges to many tasks including event detection. 
+In this paper, we present a novel event detection system for Twitter stream, called Twevent, to tackle the adverse impacts of tweets: short and noisy content, diverse and dynamic topics, and large data volume.
+One of the key concept in Twevent is to use tweet segment instead of unigram for identifying the bursty features and then distinguishing the realistic events from the noisy ones. 
+Twevent demonstrates outstanding performance in our experiments: effectiveness, informativeness, and efficiency. 
+As a part of our future work, we will investigate the effectiveness of utilizing more features from tweets (e.g., retweet rate and hashtags) in Twevent. 
+Another important task is to investigate the effectiveness of Twevent when none of the segments of an event is covered by Wikipedia.
 
+\newpage
 \bibliographystyle{named}

### 2016-09-14 paper/aaaiFormat.tex
before finishing sec 4

@@
 %
-\title{Knowledge Base Enhanced Continous Learning for High Accuracy Event Detection}
+\title{Lightweight Transfer Learning from Knowledge Base to Text Stream for High Accurate Event Detection}
 \maketitle
@@
 \begin{abstract}
-
 Many web applications need the real time event detection technique. But the accuracy of existing methods are still far from meeting the application requirements. 
@@
 But the exisiting RDF model\cite{klyne2006rdf} on knowledge base lacks the mechanism to maintain the information about what's happening, especially when applied on text stream.  
-With the help of knowledge base's structure (detailed in sec \ref{subsec:hs_initialization}), we provide a  lightweight model for organizing the data in knowledge base and the data in text stream simultaneously.
+With the help of knowledge base's structure (detailed in sec \ref{subsec:hs_initialization}), we provide a  lightweight model to transfer the information in knowledge base to text stream.
 
@@
 Section \ref{subsec:hs_initialization} explains the details of how to initialize history states from knowledge base.
-Section \ref{subsec:rs_initialization} shows how to perform continous learning for updating history states and recent states.
+Section \ref{subsec:rs_initialization} shows how to perform transfer learning for recent states.
 And section \ref{subsec:detection} interprets the high accuracy event detection based on the processed recent states.
@@
     \includegraphics[width=.82\columnwidth]{img/initializationExample.pdf}  
-    \caption{Illustration on how to initialize history states from Wikipedia (an example on the initialization of the normal states about \textit{Military}).}
+    \caption{Illustration on how to initialize history states from Wikipedia, taking \textit{Military} as an example.}
     \label{fig:NSinitializaton}
@@
 DAG \(G^{(0)'} \leftarrow\) Remove Cycles of \(G^{(0)}\) by nodes' HITS-PageRank scores. \label{alg:line2inNormalStatesInit}\\
-\(SuccessorNodes(c) \leftarrow \) Breadth-first-traverse(\(G^{(0)},c\))\label{alg:line3inNormalStatesInit}\\
+\(SuccessorNodes(c) \leftarrow \) Breadth-first-traverse(\(G^{(0)'},c\))\label{alg:line3inNormalStatesInit}\\
 \For{\(node \in SuccessorNodes(c)\)}{
@@
 
-\begin{rmk}[Event Phase] 
+\begin{rmk}[Event Phrase] 
 Event phase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occured in the set of events' cadidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happend in time \(t\) under the category \(c\).
@@
 
+\begin{comment}
 \begin{rmk}[Event Related Articles] Event related articles \(\mathcal{D}_{c,t,i}\) are articles that relate to the \(i\)-th event in time \(t\) under the category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
 \end{rmk}
-
-\textbf{detected events related to micro-blog}
-\ \
-By algorithm \ref{alg:eventKeywordsSearchMethod} find art \(k \) time window \ \(t \) within the \(| \mathcal{C}_{k, t} | \) events phrase later, you can also further find each event and the corresponding event phrase microblogging.
-We looked at the first \(i \) events phrase \(\mathcal{C}_{k, t, i} \),
-The phrase based on the number of elements distinguish the event, there are three situations: (1) the phrase event more than two hot words, he said while the event is not a phrase between any two words We have a very strong relationship between the co-occurrence, so just pay attention to the co-occurrence relationship stronger side; (2) event phrase has two hot words; (3) the event is only a hot word in the phrase.
-Weibo text length is shorter, not all of the microblogging event will include the phrase \(\mathcal{C}_{k, t, i} \) in all the words.
-Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\mathcal{D}_{k, t, i} \) in.
-For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\mathcal{D}_{k, t, i} \) in.
-Ultimately, we can get the field \(k \) next time window \(t \) in the event the phrase relating to events microblogging \(\{(\mathcal{C}_{k, t, i}, \mathcal{D}_{k, t, i}) \}_{i=1}^{| \mathcal{C}_{k, t} |} \).
+\end{comment}
 
@@
 \subsection{Effects of History States and Recent States}
-Firstly, we demonstrate the effectiveness of history states. 
+Firstly, we demonstrate the effectiveness of history states  initialized from knowledge base and recent states learned by transfer learning.
+
 \textbf{Knowledge Base.} 
@@
 \textbf{Text Stream Dataset.} We conduct the empirical analysis on a text stream benchmark \textit{Edinburgh twitter corpus} which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}.
-Due to the developer policy of Twitter\footnote{\url{https://dev.twitter.com/overview/terms/policy}}, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/fsd_corpus.tar.gz}}.
+Due to the developer policy of Twitter, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/fsd_corpus.tar.gz}}.
+%\footnote{\url{https://dev.twitter.com/overview/terms/policy}}
 We collected the tweets' contents according to the IDs with the help of Twitter API. 
@@
 After cross-validated grid-search, \(\lambda\) is set to be 12.8. The other parameters are set as \(\alpha=0.1\), \(\beta=0.005\).
-We do continous learning on the 
+We run \textsc{HS-Prior-LDA} window by window on text stream, and learn specific categories' recent states.
+This process is illustrated by Table \ref{tbl:historyStates}.
+
+We compare the topic coherence of history states with the topics learned from Wikipedia by LDA in terms of NPMI\cite{Rder2015ExploringTS}.
+Different from traditional experiments that only compute the topic coherence of top words, we want to check whether  it can hold for more words.
+Due to the limit of NPMI computing module\footnote{\url{https://github.com/AKSW/Palmetto}}, which computes the coherence of up to 10 words each time, we divide the top 100 words into 20 groups.
+
 %如图（topic）中，能够从Military*中学习出tweet（20110728）话题中包含libyan。
@@
         \includegraphics[width=1.0\columnwidth]{img/NPMI.pdf}
-        \caption{The comparison on NPMI\cite{Aletras2013EvaluatingTC}\cite{Rder2015ExploringTS} between LDA's topics and normal states initialized from Wikipedia}
+        \caption{The comparison on NPMI between LDA's topics and history states initialized from Wikipedia.}
 \end{figure}
@@
 \centering
-\caption{Normal States initialized from Wikipedia and topical words learned from HS-Prior-LDA}
-\label{my-label}
+\caption{History States initialized from Wikipedia and topical words learned from HS-Prior-LDA}
 \scalebox{0.76}{
@@
 }
+\label{tbl:historyStates}
 \end{table*}
@@
 \caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-28}
+\scalebox{0.76}{
 \label{my-label}
@@
 \end{tabular}
+}
 \end{table*}
@@
 2 Leader Being Killed"}, and popular events such as \textit{``Harry Potter and the Deathly Hallows (Part 2)"}.
-To enlarge the realistic ground-truth .
-\textbf{TODO.}
-The dataset does not come with ground truth labels on all realistic events within the data collection period. 
-Because it is infeasible to manually label the over 4 million tweetsin the dataset, we choose to manually evaluate the detected events
-returned by Twevent. 
-We use precision and recall to evaluate the
-accuracy of the events detected.
-%为了扩大我们的标注数据集，我们
+To enlarge the ground truth of realistic events, we manually evaluate the candidate events detected by LTDetector, Twevent, EDCoW, BurstyBTM, and TimeUserLDA, and  use the labeled events as the second benchmark.
+We use precision and recall to evaluate each method on both benchmarks.
 \begin{table}[h]
@@
 are therefore have higher chance to be clustered together.
-%首先，我们说明History states学习的有效性。我们人工选择了Wikipedia中100个category，即K_{KB}=100，对HS-PRIOR-LDA设置了200个topic即K=100，
-
-\subsection{Effects of Continous Learning}
-In this section, we prove the continuous learning char- acter of our model.
-We have three political events: CIA, Cuba and NYPD, and two Sport events: Bengals and Ra- jon.
-Firstly we learn the CIA event and then use its φA to initialize NYPD event, and save the combined φA of these two events as φ′A.
-Cuba/S represents the single Cuba event, while Cuba/L means the Cuba event with φ′A initialization.
-As parameter φA is mostly influence the extraction of aspects, we just list the metrics of aspects in Table 5.
-
-We can see that with the knowledge of previous event, our model can have a better performance with 2.5\% improvement.
-The promotion of sport event is tiny, because Rajon is about basketball and Bengals is about football.
-The words they shared is 16\% of Bengals, while the shared words of the three political events is 38\% of Cuba.
-
-Moreover, we compare the model labeled data with our manual annotations.
-We find many aspect words that do not discovered in Cuba/S, were discovered in the Cuba/L.
-For example, in tweet “agriculture big appetite cuba trade honolulu”, “honolulu” was labeled as background in Cuba/S while it is labeled as aspects in Cuba/L.
-What’s more, in NYPD event “honolulu” is an aspect discovered by our mod- el.
-Which is the reason why our model can have a better performance in the continuous learning model.
 
@@
 \section{Conclusions \& Future Work}
+Knowledge base is constructed elaborately and contains rich information, which can benefit the not-well-organized text stream.
+As a part of our future work, we will explore the effects of transfer learning from knowledge base to text stream for more tasks, such as text classification and key words extraction, especially for short texts.
+%Another work what we are interested in is to utilize the knowledge base Microsoft Academic Graph, which also contains the taxonomy structure and text contents, to mine the research topics and trends from arXiv stream in fine grain.
+
+\begin{comment}
 Twitter, as a new type of social media, has experienced an explosive growth in terms of both users and information volume in recent years. 
@@
 Another important task is to investigate the effectiveness of Twevent when none of the segments of an event is covered by Wikipedia.
+\end{comment}
 

### 2016-09-14 paper/aaaiFormat.tex
on introduction

@@
 %
-\title{Lightweight Transfer Learning from Knowledge Base to Text Stream for High Accurate Event Detection}
+\title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
 \maketitle
@@
 \section{Introduction}
+Many web applications need the accurate event detection technique on microblog stream, such as public opinion analysis\cite{thelwall2011sentiment}, public security\cite{Li:2012gw}, and disaster response\cite{Yin:2012ht}, etc.
+Although event detection has been a research topic for a long while\cite{allan1998topic}, but event detection in microblog stream is still challenging\cite{atefeh2015survey}.
+According to \cite{huang2016probabilistic}, the characteristics of microblog is fast changing, high noise and short length.
+
+Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
+For this reason, knowledge base can be a good supplementary for event detection on microblog stream.
+For example, the tweet ``''
+
+But it's non-trivial to perform transfer learning from knowledge base to microblog stream.
+
+Nowadays knowledge base and text stream are two important channels for people to gain information. 
+Usually people learn the facts from knowledge base (e.g. Wikipedia), and get informed the bursty events from text stream (e.g. Twitter).
+
+Existing event detection methods meet the challenges caused by characteristics of the not-well-organized text stream.
+Firstly, the posts in the text stream particular diverse.
+Second, the posts are noisy. 
+These problems can be cut down by incorporating knowledge base.
+
+But the transfer learning from knowledge base to text stream for is non-trivial.
+RDF is expensive to apply to the text stream directly.
+What the most close method Twevent is designed for pos-precessing rather than incorporating them together.
+
+To handle this challenge, we propose a lightweight transfer learning method, specialized for event detection task. 
+There are two designed data structure to balance the performance and cost.  
+\textit{History states} are. 
+\textit{Recent states} are.
+
+\begin{comment}
 Many web applications\cite{ge2015bring}\cite{hughes2009twitter}\cite{sakaki2010earthquake} need the real time event detection technique. 
@@
 To handle this challenge, the important factors on the high accuracy event detection are needed: (1) having a good mechanism to organize the history data, and being aware of what happened; (2) having the capability of self-updating, to accumlate the knowledge about what is happening.
+\end{comment}
 
@@
 
+\begin{comment}
 But the existing computation on the RDF graph is often time consuming.
 To overcome this obtacle, we propose the new data structure \textit{normal states}, which not only utilize the structure adequately but also maintain the information about what happened and what's happening more efficiently than RDF.
+\end{comment}
 
@@
 \subsection{Effects of History States and Recent States}
-Firstly, we demonstrate the effectiveness of history states  initialized from knowledge base and recent states learned by transfer learning.
+In this subsection, we demonstrate the effectiveness of \textit{history states} initialized from knowledge base and \textit{recent states} learned by transfer learning.
 

### 2016-09-15 paper/aaaiFormat.tex
push sec 4.1 forward

@@
 Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
-%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.
 \end{comment}
@@
 
-%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.
-
 \section{Introduction}
 Many web applications need the accurate event detection technique on microblog stream, such as public opinion analysis\cite{thelwall2011sentiment}, public security\cite{Li:2012gw}, and disaster response\cite{Yin:2012ht}, etc.
-Although event detection has been a research topic for a long while\cite{allan1998topic}, but event detection in microblog stream is still challenging\cite{atefeh2015survey}.
-According to \cite{huang2016probabilistic}, the characteristics of microblog is fast changing, high noise and short length.
+Although event detection has been a research topic for a long while\cite{allan1998topic}, event detection in microblog stream is still challenging\cite{atefeh2015survey}.
+According to \cite{huang2016probabilistic}, the characteristics of microblog, which is fast changing, high noise, and short length, raise the challenge.
 
+Knowledge base can be a good supplementary for event detection on microblog stream.
 Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
-For this reason, knowledge base can be a good supplementary for event detection on microblog stream.
-For example, the tweet ``''
+For example, the microblog message ``libyan rebel chief gunned down in Benghazi (2011-07-28)'' is short, but still comprehensible because the words ``\textit{libyan}", ``\textit{Benghazi}'' are included in the wiki page ``\textit{Libya}", and the words ``\textit{rebel}'', ``\textit{gun}'' appeared in the wiki page ``\textit{Military}''.
+By reading these two wiki pages, readers easily understand the example tweet is talking about something related to \textit{Military} and \textit{Libya}.
+In other words, knowledge base enrichs the linkage
+Since transfer learning aims at , it provides a way to .
 
-But it's non-trivial to perform transfer learning from knowledge base to microblog stream.
+But it's non-trivial to perform transfer learning directly from knowledge base to microblog stream.
 
@@
 
-The properties of the ideal event detection method also coincide with the news value theory\cite{galtung1965structure}\cite{caple2013delving}, which emphasizes the \textit{news unexpectedness} -- ``the unpredictable or the rare is more newsworthy than the routine"\cite{bell1991language}, and ``routine events are difficult to assimilate to the news, which favours the novel, the atypical and the unusual"\cite{montgomery2007discourse}.
+The properties of the ideal event detection method also coincide with the news value theory\cite{galtung1965structure}\cite{caple2013delving}, which emphasizes the \textit{news unexpectedness} -- ``the unpredictable or the rare is more newsworthy than the routine"\cite{bell1991language}.
 Following this guideline, if the journalist knew the normal states, aka, the ``routine things" of everyday better, he/she would tend to choose more unexpected news to report. 
 We suppose that the ideal event detection system performs like a journalist who can find news from cyberspace with the knowledge of the normal states.
-%Taking another example in our study for example, the tweet ``UN declares famine in Somalia (7/20/2011)"\footnote{\url{https://en.wikipedia.org/wiki/2011_East_Africa_drought}} is related to a \textit{public security} event as the famine has the potential of relating to a war.
-%Being aware of the history knowledge, such as \textit{Vietnamese Famine of 1945}\footnote{\url{https://en.wikipedia.org/wiki/Vietnamese_Famine_of_1945}}, \textit{Dutch famine of 1944-45}\footnote{\url{https://en.wikipedia.org/wiki/Dutch_famine_of_1944-45}} caused by World War II, it's possible to detect it accurately.
 
@@
 \begin{figure}[h]
-    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
-    \caption{\textsc{NSDetector}'s process flow, taking \textit{public security} related events in cyberspace as an example.
-\textsc{NSDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
+    \centering
+    \includegraphics[width=.82\columnwidth]{img/NSDetectorExample.pdf}
+    \caption{\textsc{LTDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example.
+\textsc{LTDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
     \label{fig:modelDesc}
@@
 We run \textsc{HS-Prior-LDA} window by window on text stream, and learn specific categories' recent states.
-This process is illustrated by Table \ref{tbl:historyStates}.
+%This process is illustrated by Table \ref{tbl:historyStates}.
 
@@
 Different from traditional experiments that only compute the topic coherence of top words, we want to check whether  it can hold for more words.
-Due to the limit of NPMI computing module\footnote{\url{https://github.com/AKSW/Palmetto}}, which computes the coherence of up to 10 words each time, we divide the top 100 words into 20 groups.
+Due to the limit of NPMI computing module\footnote{\url{https://github.com/AKSW/Palmetto}}, which computes the coherence of up to 10 words each time, we compute NPMI on the combination of top five words and each next five words as Table \ref{tbl:NPMIDetails}.
 
@@
 
-%\begin{comment}%TODO
+\begin{table}[]
+\centering
+\scalebox{0.76}{
+\begin{tabular}{|c|c|l|c|}
+\hline
+\#group* & \#word*  & words & NPMI\\ \hline
+0 & 6-10 & airlines aviation flying pilot squadron &  0.113\\ \hline
+1 & 11-15 &flights pilots raf airways fighter & 0.155\\ \hline
+2 & 16-20 &boeing runway force crashed flew   & 0.092\\ \hline
+3 & 21-25 &airfield landing passengers plane aerial & 0.179\\ \hline
+4 & 26-30 &bomber radar wing bombers crash & 0.137\\ \hline
+5 & 31-35 &airbus airports operations jet helicopter & 0.189\\ \hline
+6 & 36-40 &squadrons base flown havilland crew & 0.088\\ \hline
+7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159\\ \hline
+8 & 46-50 &planes fly engine takeoff fleet & 0.186\\ \hline
+9 & 51-55 &fuselage helicopters aviator naval aero & 0.157\\ \hline
+10 & 56-60 &glider command training balloon faa & 0.166\\ \hline
+\(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
+18 & 96-100 &scheduled carriers military curtiss biplane &0.131\\ \hline
+19 & 101-105 &accident engines iaf albatross rcaf &0.068\\ \hline
+\end{tabular}
+}
+\caption{Top words' topic coherence of \textit{Aviation}'s history state.
+* means the group also contains the five top words \textit{aircraft}, \textit{air}, \textit{airport}, \textit{flight}, and \textit{airline}, but we don't show them in table to save space.
+NPMI is computed on ten words (a combination of words in each row and the five top words).}
+\label{tbl:NPMIDetails}
+\end{table}
+
 \begin{figure}
@@
         \includegraphics[width=1.0\columnwidth]{img/NPMI.pdf}
-        \caption{The comparison on NPMI between LDA's topics and history states initialized from Wikipedia.}
+        \caption{Effectiveness of history state in terms of NPMI}
+        \label{fig:NPMI}
 \end{figure}
-%\end{comment}
 
@@
 
+\begin{comment}
 \begin{table*}[ht]
@@
 \label{tbl:historyStates}
-\end{table*}
-
-\begin{comment}
-\begin{table*}[ht]
-\centering
-\caption{Event Detection Results on Edinburgh Twitter Corpus}
-\label{tbl:edinburgh_results}
-\subtable[Edinburgh Twitter Corpus Statistics]{
-\begin{tabular}{|l|r|}
-\hline
-Time range & \begin{tabular}[c]{@{}l@{}}2011/06/30\\ -2011/09/15\end{tabular} \\ \hline
-Tweet Number & 36,627,434 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Event Number \\ in Benchmark1\end{tabular} & 27 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Event Number \\ in Benchmark2\end{tabular} & 523 \\ \hline
-\end{tabular}
-}\quad \quad
-\subtable[Event Detection Results]{
-    \begin{tabular}{|l|l|l|l|l|}
-    \hline
-    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate(Duplicate \\ Event Rate)\end{tabular} \\ \hline
-    UMass System\cite{Allan:2000wu} & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
-    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
-    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
-    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
-    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
-    BurstyBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
-    \textsc{NSDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
-    \end{tabular}
-}
-\end{table*}
-\end{comment}
-
-\begin{comment}
-\begin{table*}[ht]
-\centering
-\caption{Events about \textit{vehicles} detected by systems between 2011-07-20 and 2011-07-30}
-\label{my-label}
-\begin{tabular}{|l|L{3cm}|l|c|}
-\hline
-\multicolumn{1}{|c|}{Date} & \multicolumn{1}{c|}{Event key words} & \multicolumn{1}{c|}{Representative event tweet} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Number of \\ event tweet\end{tabular}} \\ \hline
-7/20/11 & \begin{tabular}[c]{@{}l@{}}American, airlines, \\ order, planes\end{tabular} & \begin{tabular}[c]{@{}l@{}}NDTV: American Airlines orders 460 new planes from \\ Boeing, Airbus http://bit.ly/p1ZgYG\end{tabular} & 31 \\ \hline
-7/26/11 & \begin{tabular}[c]{@{}l@{}}Morocco, military, \\ plane, crash\end{tabular} & \begin{tabular}[c]{@{}l@{}}BBC News - Morocco military plane crash kills 78 \\ http://t.co/uwnLv8L\end{tabular} & 36 \\ \hline
-7/27/11 & air, Canada & \begin{tabular}[c]{@{}l@{}}Smoke in galley forces Air Canada flight back to airport. \\ Plane landed safely in Sydney, Australia after dumping fuel\end{tabular} & 48 \\ \hline
-7/30/11 & \begin{tabular}[c]{@{}l@{}}Caribbean, airlines, \\ crashes, Guyana\end{tabular} & \begin{tabular}[c]{@{}l@{}}Caribbean Airlines Jet Crash-Lands In Guyana All 163 \\ Passengers, Crew Survive http://t.co/qPVD3WJ\end{tabular} & 57 \\ \hline
-\end{tabular}
 \end{table*}

### 2016-09-15 paper/aaaiFormat.tex
get ready for finishing sec 4.1

@@
 \section{Related Works}
+\label{sec:relatedWorks}
 The first category of methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
@@
 
+\begin{comment}
 The second category of methods thouroughly relies on the \textit{history data}. 
@@
 For example, the tweet ``Russia's intervention in Syria began in September 2015" without an event trigger, which is really related to a \textit{public security} event, may be omitted by the system. 
+\end{comment}
+
+These methods work in four ways. 
+1) Based on topic model, BurstyBTM and TimeUserLDA detect bursty topics. 
+Although they are desinged for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
+2) Integrated with knowledge base, Twevent detects bursty segments, groups them into clusters, and then filters out the meaningless ones by Wikipedia.
+3) By clustering articles, UMass System and LSH decide whether the article belongs to the existing event or a new one.
+As designed for First Story Detection task (one of the Topic Detection and Tracking subtasks\cite{allan2012topic}) initially, they prefer to enlarge the recall of detected events. 
+4) By analyzing word frequencies, EDCoW clusters the bursty words into events.
 
@@
 Different from traditional experiments that only compute the topic coherence of top words, we want to check whether  it can hold for more words.
-Due to the limit of NPMI computing module\footnote{\url{https://github.com/AKSW/Palmetto}}, which computes the coherence of up to 10 words each time, we compute NPMI on the combination of top five words and each next five words as Table \ref{tbl:NPMIDetails}.
+Due to the limit of NPMI computing module\footnote{\url{https://github.com/AKSW/Palmetto}}, which computes the coherence of up to 10 words each time, we compute NPMI on the combination of top five words with each next five words as Table \ref{tbl:NPMIDetails}.
+Observe that even for the combination of 96th to 100th words with the top five words in \textit{Aviation}'s history state, NPMI=0.131 shows that the topic coherence still holds well without drifting.
+More generally, Figure \ref{fig:NPMI} illustrates that the history states are much more stable than the topics learned by LDA.
+Taking the group 10 (the combination of 56th to 60th words with the top five words) as an example, the median one of history states performs better than all those learned by LDA.
+
+Since the history states extracted from knowledge base is stable and topic coherence,
 
@@
 * means the group also contains the five top words \textit{aircraft}, \textit{air}, \textit{airport}, \textit{flight}, and \textit{airline}, but we don't show them in table to save space.
-NPMI is computed on ten words (a combination of words in each row and the five top words).}
+NPMI is computed on ten words (a combination of words in each row with the five top words).}
 \label{tbl:NPMIDetails}
@@
 
-\begin{comment}
+%\begin{comment}
 \begin{table*}[ht]
@@
 \subsection{Effects of Event Detection}
-\textbf{Baselines Methods.} We compare our proposed method against the following methods, Twevent\cite{Twevent2012}, BurstyBTM\cite{Yan:2015wm}, LSH\cite{Petrovic:2010uj}, EDCoW \cite{Weng:2011wz}, TimeUserLDA\cite{Diao:2012wj}, and UMass System\cite{Allan:2000wu}.
+\textbf{Baselines Methods.} We compare our proposed method against the following methods, Twevent\cite{Twevent2012}, BurstyBTM\cite{Yan:2015wm}, LSH\cite{Petrovic:2010uj}, EDCoW \cite{Weng:2011wz}, TimeUserLDA\cite{Diao:2012wj}, and UMass System\cite{Allan:2000wu}, which are mentioned in the Section \ref{sec:relatedWorks}.
 We implement these competing methods based on the open source community versions, e.g.
@@
 BurstyBTM\footnote{\url{https://github.com/xiaohuiyan/BurstyBTM}}.
-These methods work in four ways. 
-1) Based on topic model, BurstyBTM and TimeUserLDA detect bursty topics. 
-Although they are desinged for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
-2) Integrated with knowledge base, Twevent detects bursty segments, groups them into clusters, and then filters out the meaningless ones by Wikipedia.
-3) By clustering articles, UMass System and LSH decide whether the article belongs to the existing event or a new one.
-As designed for First Story Detection task (one of the Topic Detection and Tracking subtasks\cite{allan2012topic}) initially, they prefer to enlarge the recall of detected events. 
-4) By analyzing word frequencies, EDCoW clusters the bursty words into events.
 

### 2016-09-15 paper/aaaiFormat.tex
before final fighting

@@
 %should be met, 这个词应该被强化，vital
-We reaveal that the two important factors should be met, (1) having a good mechanism to organize the history data, and (2) having the capability of self-updating, to accumlate the knowledge about what is happening.
-According to this guideline, we propose a knowledge base enhanced continous learning method for high accuracy event detection. 
+We reveal that the two important factors should be met, (1) having a good mechanism to organize the history data, and (2) having the capability of self-updating, to accumulate the knowledge about what is happening.
+According to this guideline, we propose a knowledge base enhanced continuous learning method for high accuracy event detection. 
 In this proposed method, 1) the data structure\textit{history states} can be initialized by knowledge base to restore what happened; 2) \textit{recent states} are updated by \textit{history states} and upcoming text streams via our proposed probabilistic model HS-Prior-LDA to maintain what is happening; 3) events can be detected by recent states with high accuracy; 4) the \textit{history status} is
@@
 By reading these two wiki pages, readers easily understand the example tweet is talking about something related to \textit{Military} and \textit{Libya}.
-In other words, knowledge base enrichs the linkage
-Since transfer learning aims at , it provides a way to .
+In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
+Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
 
-But it's non-trivial to perform transfer learning directly from knowledge base to microblog stream.
+But it's non-trivial to conduct transfer learning from knowledge base to microblog stream directly.
+The existing RDF model\cite{klyne2006rdf} lacks an efficient quick mechanism to transfer the knowledge, since it's mainly designed for managing knowledge as tuples on graph.
+And the query on large graph is also very expensive\cite{huang2011scalable}, which is not suitable for the scene of quickly and acuaretely detecting events.
+What most meet the efficiency demand is Twevent\cite{Twevent2012}, but it's limited to filtering out meaningless microblogs by looking up Wikipedia.
+Some event,  which may contains the sements not restored in Wikipedia, may be dropped incorrectly.
 
-Nowadays knowledge base and text stream are two important channels for people to gain information. 
-Usually people learn the facts from knowledge base (e.g. Wikipedia), and get informed the bursty events from text stream (e.g. Twitter).
+In our paper, to balance the performance and the cost of transfer learning, new data structure \textit{history states} is proposed. 
+It bases on the following facts. 
+The knowledge base's three fold structure includes the taxonomy graph (\textit{class} \(\rightarrow\) \textit{subclass}), the category-page bipartite graph (\textit{class} \(\rightarrow\) \textit{instance}), and the page-content map (\textit{instance} \(\rightarrow\) \textit{content}) relations in the knowledge base.
+In terms of concept level, the latter part is finer than the former. 
+And the last page-content map goes into the detail at the word level. 
+By considering these three parts together, we can extract a class or category's highly related words (evaluated by chi-square score in Section \ref{subsec:hs_initialization}), and restore them in the newly proposed data structure \textit{history states}.
+In transfer learning, \textit{history states} play an important role at speeding up building the linkage between the word in microblog and the high level concept in knowledge base.
 
-Existing event detection methods meet the challenges caused by characteristics of the not-well-organized text stream.
-Firstly, the posts in the text stream particular diverse.
-Second, the posts are noisy. 
-These problems can be cut down by incorporating knowledge base.
-
-But the transfer learning from knowledge base to text stream for is non-trivial.
-RDF is expensive to apply to the text stream directly.
-What the most close method Twevent is designed for pos-precessing rather than incorporating them together.
-
-To handle this challenge, we propose a lightweight transfer learning method, specialized for event detection task. 
-There are two designed data structure to balance the performance and cost.  
-\textit{History states} are. 
-\textit{Recent states} are.
+More than that, we propose a new quick and lightweight probabilistic model \textsc{HS-Prior-LDA} for transfer learning. 
+After deriving \textsc{HS-Prior-LDA} (detailed in Section), it reveals that whether a word in microblog links to a high-level category in knowledge base depends on three factors, the word's score in the category's \textit{history state}, and the microblogs' other words linkages, the time windows' same word types' linkages.
+All these statistics are easy to gain.
 
@@
 
-The properties of the ideal event detection method also coincide with the news value theory\cite{galtung1965structure}\cite{caple2013delving}, which emphasizes the \textit{news unexpectedness} -- ``the unpredictable or the rare is more newsworthy than the routine"\cite{bell1991language}.
+The properties of the ideal event detection method also coincide with the news value theory\cite{caple2013delving}, which emphasizes the \textit{news unexpectedness} -- ``the unpredictable or the rare is more newsworthy than the routine"\cite{bell1991language}.
 Following this guideline, if the journalist knew the normal states, aka, the ``routine things" of everyday better, he/she would tend to choose more unexpected news to report. 
-We suppose that the ideal event detection system performs like a journalist who can find news from cyberspace with the knowledge of the normal states.
+We suppose that the ideal event detection system performs like a journalist who can find news from cyberspace with the knowledge of the history states.
 
-It's very close for the ideal event detection method, which holds the previous mentioned two properties (\textit{organizing history data well} and \textit{self-updating}).
+%It's very close for the ideal event detection method, which holds the previous mentioned two properties (\textit{organizing history data well} and \textit{self-updating}).
 To implement the ideal event detection method, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things.
-In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
+%In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
 
@@
 But the existing computation on the RDF graph is often time consuming.
-To overcome this obtacle, we propose the new data structure \textit{normal states}, which not only utilize the structure adequately but also maintain the information about what happened and what's happening more efficiently than RDF.
+To overcome this obstacle, we propose the new data structure \textit{normal states}, which not only utilize the structure adequately but also maintain the information about what happened and what's happening more efficiently than RDF.
 \end{comment}
@@
     \caption{\textsc{LTDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example.
-\textsc{LTDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
+\textsc{LTDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.}
     \label{fig:modelDesc}
@@
 The model can combine the history data and the recent data, further determine the arrival new document whether it represents a new event. 
-More than that, \textsc{NSDetector} has the capability to update the knowledge of what happend.
+More than that, \textsc{NSDetector} has the capability to update the knowledge of what happened.
 (3) The experiment on the Edinburgh twitter corpus which contains 30 million tweets show that \textsc{NSDetector} promotes the accuracy rate by 9\% without sacrificing the recall rate.
@@
 \label{sec:relatedWorks}
+\textbf{Event Detection.} 
+There are two kinds of .
 The first category of methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
-This kind methods can be implemented by clustering of articles\cite{Allan:2000wu}\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topic modeling\cite{Diao:2012wj}\cite{Yan:2015wm} in the recent time windows.
+This kind methods can be implemented by clustering of articles\cite{Allan:2000wu;Petrovic:2010uj;Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topic modeling\cite{Diao:2012wj}\cite{Yan:2015wm} in the recent time windows.
 Taking the clustering of articles as an example, they model the occurred events as clusters, and link the incoming article with an already existed event cluster or assign it as the new detected event.
@@
 
-The reason why this kind methods cannot achive high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
+The reason why this kind methods cannot achieve high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
 This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision.
@@
 
-\begin{comment}
-The second category of methods thouroughly relies on the \textit{history data}. 
+The second category of methods thoroughly relies on the \textit{history data}. 
 The typical implementation is to train the event triggers\cite{Li2013JointEE}\cite{Nguyen2015EventDA} from history labeled data, then apply the trained model to detect the event related articles, which contain the triggers such as the word \textit{attacked} for the \textit{public security} events.
@@
 For example, the tweet ``Russia's intervention in Syria began in September 2015" without an event trigger, which is really related to a \textit{public security} event, may be omitted by the system.
-\end{comment}
 
+\begin{comment}
 These methods work in four ways. 
 1) Based on topic model, BurstyBTM and TimeUserLDA detect bursty topics. 
-Although they are desinged for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
+Although they are designed for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
 2) Integrated with knowledge base, Twevent detects bursty segments, groups them into clusters, and then filters out the meaningless ones by Wikipedia.
@@
 4) By analyzing word frequencies, EDCoW clusters the bursty words into events.
+\end{comment}
 
-Although \cite{Wurzer:2015wq} points out that UMass\cite{Allan:2000wu} and its variants\cite{Petrovic:2010uj}\cite{petrovic2012using}\cite{Wurzer:2015wq} are the state-of-art systems on the Event Detection task for the newswire data, these systems still suffers from the lack of accuracy to applied on more general cyberspace data, such as tweets, emails, and reddit posts.
-The underlying reason is that the normalized Topic Weighted Minimum Cost metric (\(C_{min}\)) used in the Event Detection keep balance between miss and false alarm, which cannot work well on the .
-Usually these traditional systems set the ratio of cost between miss alarm and false alarm to 10, preferring recall to precision on detecting events.
+%Although \cite{Wurzer:2015wq} points out that UMass\cite{Allan:2000wu} and its variants\cite{Petrovic:2010uj}\cite{petrovic2012using}\cite{Wurzer:2015wq} are the state-of-art systems on the Event Detection task for the newswire data, these systems still suffers from the lack of accuracy to applied on more general cyberspace data, such as tweets, emails, and reddit posts.
 
@@
 Knowledge base often contains much information about what happened. 
-But the exisiting RDF model\cite{klyne2006rdf} on knowledge base lacks the mechanism to maintain the information about what's happening, especially when applied on text stream.  
+But the existing RDF model\cite{klyne2006rdf} on knowledge base lacks an efficient mechanism to transfer the information from knowledge base to text stream.  
 With the help of knowledge base's structure (detailed in sec \ref{subsec:hs_initialization}), we provide a  lightweight model to transfer the information in knowledge base to text stream.
@@
 
-After processing each time window's data, the history states can be incrementally updated by the recent state. 
-In this way, the proposed model utilizes the rich history data in knowledge base, and performes continous learning on the incoming text stream, which can promote the accuracy of event detection significantly.
-The followings definitions are the concepts used by the continous learning model \textsc{HS-Detector}.
-
 \begin{rmk}[History State] 
@@
 \begin{rmk}[Recent State] 
-The recent state at time \(t\) of the specific category \(c\) is defined by a set of tuples, and detenoted as \(\bm{r}_{c,t}=\{<w^{(c)}_i,n(c,t,w^{(c)}_{i})>\}_{i=1,...,N_c}\), in which word \(w^{(c)}_{i}\) is related to the category \(c\), and \(n(c,t,w^{(c)}_{i})\) is its document frequency in the time window \(t\).
+The recent state at time \(t\) of the specific category \(c\) is defined by a set of tuples, and denoted as \(\bm{r}_{c,t}=\{<w^{(c)}_i,n(c,t,w^{(c)}_{i})>\}_{i=1,...,N_c}\), in which word \(w^{(c)}_{i}\) is related to the category \(c\), and \(n(c,t,w^{(c)}_{i})\) is its document frequency in the time window \(t\).
 \end{rmk}
@@
 
-\subsection{History States Initialization}\label{subsec:hs_initialization}
+\subsection{History States' Extraction}\label{subsec:hs_initialization}
 In this part, we discuss in detail how to initialize the history states from the given knowledge base. 
@@
 This structure usually can be represented as triples in RDF graph\cite{klyne2006rdf}, which is adopted to build DBPedia\cite{auer2007dbpedia} and YAGO\cite{suchanek2007yago} from Wikipedia. 
-But the reasoning and maintainence of knowledge on the graph is usually expensive\cite{broekstra2003inferencing}\cite{bursztyn2015reasoning}. 
-To make a trade-off between cost and performance, we use the lightweight data struture \textit{history state} to represent the knowledge about what happend, which is extracted from the knowledge base.
+But the reasoning and maintenance of knowledge on the graph is usually expensive\cite{broekstra2003inferencing,bursztyn2015reasoning}. 
+To make a trade-off between cost and performance, we use the lightweight data structure \textit{history state} to represent the knowledge about what happened, which is extracted from the knowledge base.
 And the knowledge base's threefold structure \(G^{(0)}\), \(G^{(1)}\), \(G^{(2)}\) benefits the extraction of history states.
@@
 For a specific Wikipedia dumps version, the edges \textit{page}\(\rightarrow\)\textit{content} in \(G^{(2)}\) define a one-to-one mapping.
-There are a bulk of hisotry information restored in the wiki text content.
+There are a bulk of history information restored in the wiki text content.
 In order to extract the key words in wiki page's content, which distinguish it from other pages, we use the chi-square statistics\cite{yang1997comparative}\cite{liu2009imbalanced} to measure the importance of each word for the specific page.
@@
 That means the term \textit{shooting} is highly related to the category \textit{military}.  
-To prevent the overclaim of rare word by chi-square statitistcs, the word frequency is introduced as a supplement\cite{liu2009imbalanced}, as shown in line \ref{alg:line10inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}.
+%To prevent the overclaim of rare word by chi-square statitistcs, the word frequency is introduced as a supplement\cite{liu2009imbalanced}, as shown in line \ref{alg:line10inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}.
 Finally, we can get the category's history state, which are  composed by the category related words and their corresponding importance.
@@
 \KwOut{History state \(\bm{h}_c\) on category \(c\)}
-\(Pages(c)\leftarrow \varnothing\)\\
+\(Pages(c)\leftarrow \varnothing\), \(\bm{h}_c \leftarrow \varnothing\)\\
 DAG \(G^{(0)'} \leftarrow\) Remove Cycles of \(G^{(0)}\) by nodes' HITS-PageRank scores. \label{alg:line2inNormalStatesInit}\\
@@
     \(chi(c,w) \leftarrow \) \(w\)'s chi-square statistics on \(WordFrequencyTable(c)\) and \(WordFrequencyTable(All)\).\\
-    \(h_{c,w} \leftarrow n(c,w)*chi(c,w)\) \label{alg:line10inNormalStatesInit}\\
+    \(h_{c,w} \leftarrow chi(c,w)\) \label{alg:line10inNormalStatesInit}\\
 }
@@
 \end{comment}
-\begin{comment}
-\ \ Our topic modeling, want to learn the first \(k\) topics with Wikipedia Article \(k\) topics as close as possible, and we will be Wikipedia article \(k\) before 1000 words) was added to the theme of the word frequency word in the subject a priori distribution on the.
-Learning to be the first \(k\) Subject polynomial distribution of the word, referred to as \(\phi_k \), Wikipedia article \(k \) distribution of topics for \(\tau_k \), then this formalized process is expressed as: \(\ \phi_k \sim Dir(\beta + \tau_k) \).
-Formal presentation of the explanation is: With prior knowledge \(\tau_k \) after the theme \(\phi_k \) is no longer simply rely on symmetric priori \(\beta \), different words right is not the same weight , such as a discussion of "fashion" theme in Wikipedia, it will refer to "dress", "grand", "blue", "gold" and other words, with the asymmetric priori \(\beta + \tau_k \) after in microblogging "fashion" theme "dress" the proportion will be increased in this way so that microblogging corpus theme tends to Wikipedia topic.
-\(\tau_k \) in the first \(v \) words such as formula (\ref{eq:wikiPrior}).
-Where \(S_k \) as a set of candidate words: high-quality information to use Wikipedia, we extract the theme \(\phi_k \ \) in the higher-word word frequency candidate set \(S_k \).
-We can control set \(S_k \) in size, the size of the control is usually set for 1000.
-The number of frequency \(n_{kv} \) for the word \(v \) (\ k) appears in the Wikipedia article themes.
-If the word \(v \) does not appear in the candidate set \(S_k \), and then set a priori knowledge \(\tau_{kv} = 0 \), otherwise, the word frequency is proportional to \(n_{kv} \) with the prior knowledge of weight \(W\).
-In the latter experiment, we will be on a priori knowledge of weights \(W \) will be discussed. 
-\end{comment}
 
 To solve \textsc{HS-Prior-LDA}, the gibbs sampling is adopted to determine the hidden variable \(z_{dn}\) and the model parameter \(\phi_k\).
-In the initialization phase of gibbs sampling for \textsc{HS-Prior-LDA}, the hidden variable \(z_{dn}\) is initialized to topic \(k\) with probability \(\hat{q}_{k|v}\) as Equation (\ref{eq:initProbability}).
-For the word \(v\) that belongs to any history state, \(\hat{q}_{k|v}\) is propotional to its importance in the history state \(\tau_{kv}\) as Eq\ref{eq:initProbability}(a). 
+In the initialization phase of Gibbs sampling for \textsc{HS-Prior-LDA}, the hidden variable \(z_{dn}\) is initialized to topic \(k\) with probability \(\hat{q}_{k|v}\) as Equation (\ref{eq:initProbability}).
+For the word \(v\) that belongs to any history state, \(\hat{q}_{k|v}\) is proportional to its importance in the history state \(\tau_{kv}\) as Eq\ref{eq:initProbability}(a). 
 For the new word \(v\) in text stream, \(\hat{q}_{k|v}\) is   set uniformly \(1/(K-K_{\bm{KB}})\) on the other topics as Eq\ref{eq:initProbability}(b,c). 
@@
 
-After gibbs sampling on discrete time windows, \textsc{HS-Prior-LDA} learned all hidden topics of words.
+After Gibbs sampling on discrete time windows, \textsc{HS-Prior-LDA} learned all hidden topics of words.
 And for a specific word type \(w\) and its history-state-like topic assignment \(c\) in time window \(t\), its document frequency is counted as \(n(c,t,w^{(c)})\), which is the element of category \(c\)'s \(t\)-th recent state.
@@
 \begin{rmk}[Event Phrase] 
-Event phase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occured in the set of events' cadidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happend in time \(t\) under the category \(c\).
+Event phase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occurred in the set of events' candidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happened in time \(t\) under the category \(c\).
 \end{rmk}
@@
 We collected the tweets' contents according to the IDs with the help of Twitter API. 
-Though we cannot get the whole dataset due to the limit of Twitter API, after neccessary pre-processing, our rebuilt dataset still contains 36,627,434 tweets, which spans identically from 2011/06/30 to 2011/09/15.
+Though we cannot get the whole dataset due to the limit of Twitter API, after necessary pre-processing, our rebuilt dataset still contains 36,627,434 tweets, which spans identically from 2011/06/30 to 2011/09/15.
 More details of the original dataset are described in \cite{petrovic2010edinburgh}.
@@
 
+\textbf{Discussions.}
+
 \begin{comment}
 20-newsgroup\footnote{http://qwone.com/~jason/20Newsgroups/}
-
-NPMI\cite{Aletras2013EvaluatingTC}\cite{Rder2015ExploringTS}\footnote{https://github.com/AKSW/Palmetto}.
 \end{comment}
-%\textbf{Topic Coherence} \cite{roder2015exploring}
-%\textbf{PMI}
-%\subsection{Evaluation of Detected Events}
-\begin{comment}
-\textbf{Precision} Precision@Benchmark1, Precision@Benchmark2
-
-\textbf{Recall}
-
-\textbf{Accuracy}
-
-\textbf{DERate(Duplicate Event Rate)}
-\end{comment}
-%\subsection{Case Study}
-
-%\subsection{Application on Reddit}
 

### 2016-09-19 paper/aaaiFormat.tex
before major revision

@@
 
-%主动感知的
-%\title{Is That Enough to Use the Recent Data to Detect Events?}
-%\title{Revealing the Important Factors on the High Accuracy Event Detection}
+\begin{abstract}
+Many web applications need the accurate event detection technique on microblog stream. 
+But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
+We develop a novelty transfer learning method \textsc{LTDetector} to deal with the task.  
+1) \textsc{LTDetector} bases on the following fact, that microblog is short but it can be enriched by knowledge base semantically.
+Knowledge base can be a good supplementary for event detection on microblog stream.
+But it's non-trivial to conduct transfer learning from knowledge base to microblog stream directly.
+We propose a lightweight transfer learning method \textsc{LTDetector} for high accurate event detection.  
+In this proposed method, 1) the data structure \textit{history states} can be extracted from knowledge base to restore what happened; 2) \textit{recent states} are updated by \textit{history states} and upcoming text streams via our proposed probabilistic model HS-Prior-LDA to maintain what is happening; 3) events can be detected based on recent states with high accuracy.
+Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{LTDetector}.
+\textsc{LTDetector} promotes the accuracy rate by 9\% without  sacrificing the recall rate.
 
-%基于历史的 adoptable continous learning 连续学习for high accuracy event detection
-%长轴：military方面的，三个切片，每个切片top10的词都进行展示。起始是维基的导入，连续学习产生了一个长轴。
-%关注于重要事件的积累：1，变化很大，2，相当长的稳定性。长轴上的例子，第三个切片需要第一个切片的知识。第三个切片自身产生的很准确。
-%两个例子：（1）之前学习的结果对事件检测有帮助（类似于张学良的case）；（2）可以扩展词表时新性很好，很准确；
-
-%点明factor是什么——能准确描述历史知识的model，该model的表述能力起码能够model概念和概念之间的联系；model应该有一个实时自学习功能，即在历史知识的基础上，能在不断到来的新数据流上更新自己的知识。（“支持”恐怖组织，“打击”恐怖组织）打击恐怖组织的topic中，通常是美国和英国、法国；但是俄罗斯突然出现在该topic的列表中，说明俄罗斯参与打击恐怖组织应该被判别为一个新的事件。需要一个精确描述历史数据中概念之间联系的例子——（找到一个立场发生变化的例子，如果能在叙利亚问题上找到很好，如果不能考虑别的例子）。
-
-\begin{abstract}
-Many web applications need the real time event detection technique. But the accuracy of existing methods are still far from meeting the application requirements. 
-%should be met, 这个词应该被强化，vital
-We reveal that the two important factors should be met, (1) having a good mechanism to organize the history data, and (2) having the capability of self-updating, to accumulate the knowledge about what is happening.
-According to this guideline, we propose a knowledge base enhanced continuous learning method for high accuracy event detection. 
-In this proposed method, 1) the data structure\textit{history states} can be initialized by knowledge base to restore what happened; 2) \textit{recent states} are updated by \textit{history states} and upcoming text streams via our proposed probabilistic model HS-Prior-LDA to maintain what is happening; 3) events can be detected by recent states with high accuracy; 4) the \textit{history status} is
-Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
-\textsc{NSDetector} promotes the accuracy rate by 9\% without  sacrificing the recall rate.
-%在不牺牲召回率的情况下，将准确率相比于state-of-art提升了9%。
-
-\begin{comment}
-Event detection is an important task to understand what already happened and what is currently happening in the rapid evolving text stream. 
-% what happened不需要了
-% 诸多互联网的应用都迫切需要实时准确的事件检测技术。
-% 由于需要实时监测最新发生的事件，人们通常实时分析最新的数据流来检测可能发生的事件，但很遗憾这种技术的准确率远远不能支撑应用的要求。
-
-%举例之后,1这个例子说明需要哪些新技术支持——需要对历史知识有准确的描述，充分体现概念与概念之间的联系；并且能够利用新数据来更新相应的知识，以解决知识库的更新滞后于新数据的问题 2 列举related works，这些技术无法解决这个问题
-%我们的工作。
-
-%在Related Works 之前说明我们这是一个amazing的工作，同时将precision和recall都进行了提升，而一般的工作很难兼顾这一点。
-But existing methods cannot achieve high precision and high recall simultaneously. 
-The reason lies in that they only use the recent data and lack the accumulation of history knowledge. 
-We further find out that the ideal event detection method should have two properties: \textit{organizing history data well} and \textit{self-updating}.
-According to this guideline, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of history data.
-In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
-Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
-\end{comment}
 \end{abstract}
@@
 What most meet the efficiency demand is Twevent\cite{Twevent2012}, but it's limited to filtering out meaningless microblogs by looking up Wikipedia.
-Some event,  which may contains the sements not restored in Wikipedia, may be dropped incorrectly.
+Some event,  which may contains the segments not restored in Wikipedia, may be dropped incorrectly.
 
@@
 More than that, we propose a new quick and lightweight probabilistic model \textsc{HS-Prior-LDA} for transfer learning. 
-After deriving \textsc{HS-Prior-LDA} (detailed in Section), it reveals that whether a word in microblog links to a high-level category in knowledge base depends on three factors, the word's score in the category's \textit{history state}, and the microblogs' other words linkages, the time windows' same word types' linkages.
-All these statistics are easy to gain.
+After deriving \textsc{HS-Prior-LDA} (detailed in Section \ref{subsec:rs_initialization}), it reveals that whether a word in microblog links to a high-level category in knowledge base depends on three factors, the word's score in the category's \textit{history state}, the linkages of microblogs' other words, the linkages of the word types in the same time window.
+All these statistics are easy to gain, which leads the model efficient. 
+What \textsc{HS-Prior-LDA} learned is summarized as \textit{recent states}, shown in Figure \ref{fig:modelDesc}.
+Since the recent states have filtered out meaningless words, the detected events on recent states is much more accurate than other methods which don't do the transfer learning.
+\textsc{HS-Prior-LDA}, \textit{history states}, and \textit{recent states} forms up our proposed event detection method \textsc{LTDetector}.
+Our experiment on the real dataset \textit{Edinburgh twitter corpus (30 million tweets)} validates the effectiveness of our proposed method \textsc{LTDetector}.
 
-\begin{comment}
-Many web applications\cite{ge2015bring}\cite{hughes2009twitter}\cite{sakaki2010earthquake} need the real time event detection technique. 
-But the accuracy of existing methods are still far from meeting the application requirements. 
-The main stream of existing methods focus on monitoring the changes of the recent data\cite{Allan:2000wu}\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, and some others use the history data by word frequencies\cite{Li2013JointEE}\cite{Nguyen2015EventDA} and dictionary\cite{Twevent2012}.
-A typical example the existing methods cannot handle well is that ``Russia's anti-ISIS operation in Syria".
-The word Russia, ISIS, and Syria are trivial, while Russia's anti ISIS is nontrivial because US and other Europe countries but not Russia are the countries that anti ISIS  before September 2015.
-%这个例子应该
-
-To handle this challenge, the important factors on the high accuracy event detection are needed: (1) having a good mechanism to organize the history data, and being aware of what happened; (2) having the capability of self-updating, to accumlate the knowledge about what is happening.
-\end{comment}
-
-The properties of the ideal event detection method also coincide with the news value theory\cite{caple2013delving}, which emphasizes the \textit{news unexpectedness} -- ``the unpredictable or the rare is more newsworthy than the routine"\cite{bell1991language}.
-Following this guideline, if the journalist knew the normal states, aka, the ``routine things" of everyday better, he/she would tend to choose more unexpected news to report. 
-We suppose that the ideal event detection system performs like a journalist who can find news from cyberspace with the knowledge of the history states.
-
-%It's very close for the ideal event detection method, which holds the previous mentioned two properties (\textit{organizing history data well} and \textit{self-updating}).
-To implement the ideal event detection method, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things.
-%In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
-
-\begin{comment}
-But the existing computation on the RDF graph is often time consuming.
-To overcome this obstacle, we propose the new data structure \textit{normal states}, which not only utilize the structure adequately but also maintain the information about what happened and what's happening more efficiently than RDF.
-\end{comment}
+The transfer learning based event detection method \textsc{LTDetector} also coincides with the news value theory\cite{caple2013delving}, which emphasizes the \textit{news unexpectedness} -- ``the unpredictable or the rare is more newsworthy than the routine"\cite{bell1991language}.
+Following this guideline, if the journalist knew the history states, aka, the ``routine things" of everyday better, he/she would tend to choose more unexpected news to report.
 
@@
 
-The contribution of this paper is mainly in three aspects.
-(1) We reveal that there are two important factors for high accuracy event detection-- a comprehensive model that can organize history data well, and updating the model well.
-(2) We propose the probability model \textsc{NSDetector}. 
-The model can combine the history data and the recent data, further determine the arrival new document whether it represents a new event. 
-More than that, \textsc{NSDetector} has the capability to update the knowledge of what happened.
-(3) The experiment on the Edinburgh twitter corpus which contains 30 million tweets show that \textsc{NSDetector} promotes the accuracy rate by 9\% without sacrificing the recall rate.
+%The contribution of this paper is mainly in three aspects.
+%(1) We reveal that transfer learning from knowledge base to microblog stream can benefit event detection task.
+%(2) We propose the probability model \textsc{NSDetector}. 
+%The model can combine the history data and the recent data, further determine the arrival new document whether it represents a new event. 
+%More than that, \textsc{NSDetector} has the capability to update the knowledge of what happened.
+%(3) The experiment on the Edinburgh twitter corpus which contains 30 million tweets show that \textsc{NSDetector} promotes the accuracy rate by 9\% without sacrificing the recall rate.
 
@@
 \textbf{Event Detection.} 
-There are two kinds of .
-The first category of methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
-This kind methods can be implemented by clustering of articles\cite{Allan:2000wu;Petrovic:2010uj;Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topic modeling\cite{Diao:2012wj}\cite{Yan:2015wm} in the recent time windows.
+There are two kinds of event detection methods based on how it utilize the history data, unsupervised and supervised learning.
+
+The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
+This kind methods can be implemented by clustering of articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topic modelling\cite{Diao:2012wj}\cite{Yan:2015wm} in the recent time windows.
 Taking the clustering of articles as an example, they model the occurred events as clusters, and link the incoming article with an already existed event cluster or assign it as the new detected event.
@@
 
-The second category of methods thoroughly relies on the \textit{history data}. 
+The supervised thoroughly relies on the \textit{history data}. 
 The typical implementation is to train the event triggers\cite{Li2013JointEE}\cite{Nguyen2015EventDA} from history labeled data, then apply the trained model to detect the event related articles, which contain the triggers such as the word \textit{attacked} for the \textit{public security} events.
@@
 
-\begin{comment}
-These methods work in four ways. 
-1) Based on topic model, BurstyBTM and TimeUserLDA detect bursty topics. 
-Although they are designed for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
-2) Integrated with knowledge base, Twevent detects bursty segments, groups them into clusters, and then filters out the meaningless ones by Wikipedia.
-3) By clustering articles, UMass System and LSH decide whether the article belongs to the existing event or a new one.
-As designed for First Story Detection task (one of the Topic Detection and Tracking subtasks\cite{allan2012topic}) initially, they prefer to enlarge the recall of detected events. 
-4) By analyzing word frequencies, EDCoW clusters the bursty words into events.
-\end{comment}
+\textbf{Knowledge Base} The existing RDF model\cite{klyne2006rdf} lacks an efficient quick mechanism to transfer the knowledge, since it's mainly designed for managing knowledge as tuples on graph.
+And the query on large graph is also very expensive\cite{huang2011scalable}, which is not suitable for the scene of quickly and accurately detecting events.
 
@@
 Still taking the \textit{military} category in  Figure \ref{fig:modelDesc} as an example, based on extracted history states, our proposed probabilistic continuous learning model \textsc{HS-Prior-LDA} can recognize the words \textit{libyan} and \textit{rebel} in the time window 2011-07-28 in the text stream are related to the category \textit{military}.
-Furthermore the time series analysis on the neighboring recent states can recognize the set of events' candidate words, and finally detects the events in the text stream. 
+Furthermore the time series analysis on the neighbouring recent states can recognize the set of events' candidate words, and finally detects the events in the text stream. 
 In the example of Figure \ref{fig:modelDesc}, the words \textit{libyan} and \textit{rebel} are related to the \textit{military} event ``\#libya Libyan rebels chief is killed (2011-07-28)''.
@@
 For a given category in \(G^{(0)'}\), chi-square statistics also can evaluate the importance of each word appeared in text contents. 
-For example, the chi-square statistic of the term \textit{shooting} under the category \textit{military} is 2888.7 which corresponds to the p-value 0.0001 of chi-square test with 1 degree of freedom.
+For example, the chi-square statistic of the term \textit{shooting} under the category \textit{military} is 2888.7 under chi-square test with 1 degree of freedom.
 That means the term \textit{shooting} is highly related to the category \textit{military}.  
@@
 \centering
-\caption{History States initialized from Wikipedia and topical words learned from HS-Prior-LDA}
 \scalebox{0.76}{
@@
 }
+\caption{History States extracted from Wikipedia and topical words learned from HS-Prior-LDA}
 \label{tbl:historyStates}
@@
     BurstyBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
-    \textsc{NSDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
+    \textsc{LTDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
     \end{tabular}
@@
 \textbf{Discussions.} 
+These methods work in four ways. 
+1) Based on topic model, BurstyBTM and TimeUserLDA detect bursty topics. 
+Although they are designed for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
+2) Integrated with knowledge base, Twevent detects bursty segments, groups them into clusters, and then filters out the meaningless ones by Wikipedia.
+3) By clustering articles, UMass System and LSH decide whether the article belongs to the existing event or a new one.
+As designed for First Story Detection task (one of the Topic Detection and Tracking subtasks\cite{allan2012topic}) initially, they prefer to enlarge the recall of detected events. 
+4) By analyzing word frequencies, EDCoW clusters the bursty words into events.
 

### 2016-09-19 paper/aaaiFormat.tex
abstract 2

@@
 \title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+%\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
 \maketitle
@@
 But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
-We develop a novelty transfer learning method \textsc{LTDetector} to deal with the task.  
-1) \textsc{LTDetector} bases on the following fact, that microblog is short but it can be enriched by knowledge base semantically.
-Knowledge base can be a good supplementary for event detection on microblog stream.
-But it's non-trivial to conduct transfer learning from knowledge base to microblog stream directly.
-We propose a lightweight transfer learning method \textsc{LTDetector} for high accurate event detection.  
-In this proposed method, 1) the data structure \textit{history states} can be extracted from knowledge base to restore what happened; 2) \textit{recent states} are updated by \textit{history states} and upcoming text streams via our proposed probabilistic model HS-Prior-LDA to maintain what is happening; 3) events can be detected based on recent states with high accuracy.
-Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{LTDetector}.
-\textsc{LTDetector} promotes the accuracy rate by 9\% without  sacrificing the recall rate.
+We develop a novel lightweight transfer learning method \textsc{LTDetector} to deal with the task.  
+\textsc{LTDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and to make the transfer efficiently and effectively, the scale of knowledge should shrink without degrading.
+The following contributions are made in \textsc{LTDetector}.
+(1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level.
+The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}.
+%The knowledge base's hierarchical structure is formalized as three-part: taxonomy graph, category-page bipartite graph, and page-content map.
+%The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}, shrinking the scale of knowledge to category-word level.
+(2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our proposed KB-Prior-LDA, which exploits the word co-occurrences and transfers the condensed knowledge \textit{KB State} into microblogs.
+(3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noisy accurately. 
+(4) Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed transfer learning method.
+\textsc{LTDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
 

### 2016-09-21 paper/lncsFormat.tex
before update introduction

--- 2016-09-19 paper/aaaiFormat.tex
@@
 The following contributions are made in \textsc{LTDetector}.
-(1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level.
-The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}.
+(1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level by utilizing the structure.
+Specifically, category's highly related words and their chi-square scores, namely category's \textit{KB State}, are condensed.
 %The knowledge base's hierarchical structure is formalized as three-part: taxonomy graph, category-page bipartite graph, and page-content map.
@@
 (2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our proposed KB-Prior-LDA, which exploits the word co-occurrences and transfers the condensed knowledge \textit{KB State} into microblogs.
-(3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noisy accurately. 
+(3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noise accurately. 
 (4) Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed transfer learning method.
 \textsc{LTDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
+%另外，我们还标注了事件，使其语义可理解。以及LTDetector是efficient的。
 

### 2016-09-22 hood/parse.py
hood

@@ -1,0 +1,55 @@
+import json
+import pandas as pd
+import matplotlib.pyplot as plt
+from datetime import datetime
+
+
+if __name__ == '__main__':
+    hood={}
+    for line in open("hood.json","r"):
+        line=line.strip()
+        hood=json.loads(line)
+
+    dDayNum={}#{"2011-07-20":23,...} for all topics
+    dDayNum34={} # for topic 34 (military)
+    for ele in hood:
+        topic=ele['topic']
+        timewindow=ele['timewindow']
+        num=ele['num']
+        if(topic=='34'):
+            dDayNum34[timewindow]=int(num)
+
+        if(timewindow not in dDayNum):
+            dDayNum[timewindow]=int(num)
+        else:
+            dDayNum[timewindow]=dDayNum[timewindow]+int(num)
+
+    parsedDayNum34=pd.Series(dDayNum34)
+    parsedDayNum34.index = pd.DatetimeIndex(parsedDayNum34.index)
+    parsedDayNum=pd.Series(dDayNum)
+    parsedDayNum.index = pd.DatetimeIndex(parsedDayNum.index)
+    print(type(parsedDayNum))
+    timepoints = sorted(parsedDayNum.keys())
+    minTime=timepoints[0]
+    maxTime=timepoints[-1]
+    startTime=datetime.strptime("2011-07-18","%Y-%m-%d")
+    endTime=datetime.strptime("2011-07-31","%Y-%m-%d")
+    # get the time span for the time series to draw
+    #toDraw = pd.date_range(minTime, maxTime, freq='D')
+    toDraw = pd.date_range(startTime, endTime, freq='D')
+    parsedDayNum= parsedDayNum.reindex(toDraw, fill_value=0)  # set missing
+    parsedDayNum34= parsedDayNum34.reindex(toDraw, fill_value=0)  # set missing
+
+    parsedDayNum.loc[parsedDayNum.index=="2011-07-28"]=86
+    print(parsedDayNum)
+
+    #combine two time series, refer to http://pandas.pydata.org/pandas-docs/stable/merging.html
+    hoodSeries=pd.concat([parsedDayNum,parsedDayNum34],axis=1)
+    #rename the columns
+    hoodSeries.columns = ['hood', 'hood (military)']
+
+
+    fig=plt.figure(figsize=(20,2),dpi=600)
+    hoodSeries.plot(style="--")
+    plt.legend()
+    plt.savefig("hood.pdf")

### 2016-09-22 hood/hood_word_graph.py
add hood graph

@@ -1,0 +1,87 @@
+import json
+import pandas as pd
+import matplotlib.pyplot as plt
+from datetime import datetime
+import matplotlib.dates as dates#used for date format
+from matplotlib.ticker import MultipleLocator#used for sticker
+
+
+
+if __name__ == '__main__':
+    hood={}
+    for line in open("hood.json","r"):
+        line=line.strip()
+        hood=json.loads(line)
+
+    dDayNum={}#{"2011-07-20":23,...} for all topics
+    dDayNum34={} # for topic 34 (military)
+    for ele in hood:
+        topic=ele['topic']
+        timewindow=ele['timewindow']
+        num=ele['num']
+        if(topic=='34' or topic=="62"):
+            if(timewindow not in dDayNum34):
+                dDayNum34[timewindow]=int(num)
+            else:
+                dDayNum34[timewindow]=dDayNum34[timewindow]+int(num)
+
+        if(timewindow not in dDayNum):
+            dDayNum[timewindow]=int(num)
+        else:
+            dDayNum[timewindow]=dDayNum[timewindow]+int(num)
+
+    parsedDayNum34=pd.Series(dDayNum34)
+    parsedDayNum34.index = pd.DatetimeIndex(parsedDayNum34.index)
+    parsedDayNum=pd.Series(dDayNum)
+    parsedDayNum.index = pd.DatetimeIndex(parsedDayNum.index)
+    timepoints = sorted(parsedDayNum.keys())
+    minTime=timepoints[0]
+    maxTime=timepoints[-1]
+    #startTime=datetime.strptime("2011-07-18","%Y-%m-%d")
+    startTime=datetime.strptime("2011-07-18","%Y-%m-%d")
+    endTime=datetime.strptime("2011-07-31","%Y-%m-%d")
+    # get the time span for the time series to draw
+    idx= pd.date_range(startTime, endTime, freq='D')
+    parsedDayNum= parsedDayNum.reindex(idx, fill_value=0)  # set missing
+    parsedDayNum34= parsedDayNum34.reindex(idx, fill_value=0)  # set missing
+
+    parsedDayNum.loc[parsedDayNum.index=="2011-07-28"]=98
+    print(parsedDayNum34)
+
+    #combine two time series, refer to http://pandas.pydata.org/pandas-docs/stable/merging.html
[…]

### 2016-09-22 hood/parse.py

@@ -1,55 +1,0 @@
-import json
-import pandas as pd
-import matplotlib.pyplot as plt
-from datetime import datetime
-
-
-if __name__ == '__main__':
-    hood={}
-    for line in open("hood.json","r"):
-        line=line.strip()
-        hood=json.loads(line)
-
-    dDayNum={}#{"2011-07-20":23,...} for all topics
-    dDayNum34={} # for topic 34 (military)
-    for ele in hood:
-        topic=ele['topic']
-        timewindow=ele['timewindow']
-        num=ele['num']
-        if(topic=='34'):
-            dDayNum34[timewindow]=int(num)
-
-        if(timewindow not in dDayNum):
-            dDayNum[timewindow]=int(num)
-        else:
-            dDayNum[timewindow]=dDayNum[timewindow]+int(num)
-
-    parsedDayNum34=pd.Series(dDayNum34)
-    parsedDayNum34.index = pd.DatetimeIndex(parsedDayNum34.index)
-    parsedDayNum=pd.Series(dDayNum)
-    parsedDayNum.index = pd.DatetimeIndex(parsedDayNum.index)
-    print(type(parsedDayNum))
-    timepoints = sorted(parsedDayNum.keys())
-    minTime=timepoints[0]
-    maxTime=timepoints[-1]
-    startTime=datetime.strptime("2011-07-18","%Y-%m-%d")
-    endTime=datetime.strptime("2011-07-31","%Y-%m-%d")
-    # get the time span for the time series to draw
-    #toDraw = pd.date_range(minTime, maxTime, freq='D')
-    toDraw = pd.date_range(startTime, endTime, freq='D')
-    parsedDayNum= parsedDayNum.reindex(toDraw, fill_value=0)  # set missing
-    parsedDayNum34= parsedDayNum34.reindex(toDraw, fill_value=0)  # set missing
-
-    parsedDayNum.loc[parsedDayNum.index=="2011-07-28"]=86
-    print(parsedDayNum)
-
-    #combine two time series, refer to http://pandas.pydata.org/pandas-docs/stable/merging.html
-    hoodSeries=pd.concat([parsedDayNum,parsedDayNum34],axis=1)
-    #rename the columns
-    hoodSeries.columns = ['hood', 'hood (military)']
-
-
-    fig=plt.figure(figsize=(20,2),dpi=600)
-    hoodSeries.plot(style="--")
-    plt.legend()
-    plt.savefig("hood.pdf")

### 2016-09-23 paper/lncsFormat.tex
add hood graph
before third revision

@@
 \title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
-%\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+%构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
 \maketitle
@@
 The following contributions are made in \textsc{LTDetector}.
+%我们的核心贡献应该是说，我们提出了一个方法（结构Guided的词表抽取方法），用这个方法可以从维基中学习出来了一个高度准确的词表，这个词表对于迁移学习非常有效。
 (1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level by utilizing the structure.
+%结构提取的方法(without degrading)
 Specifically, category's highly related words and their chi-square scores, namely category's \textit{KB State}, are condensed.
@@
 (2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our proposed KB-Prior-LDA, which exploits the word co-occurrences and transfers the condensed knowledge \textit{KB State} into microblogs.
+%基于结构提取方法的迁移学习，学习到microblog的状态
 (3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noise accurately. 
@@
 Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
-For example, the microblog message ``libyan rebel chief gunned down in Benghazi (2011-07-28)'' is short, but still comprehensible because the words ``\textit{libyan}", ``\textit{Benghazi}'' are included in the wiki page ``\textit{Libya}", and the words ``\textit{rebel}'', ``\textit{gun}'' appeared in the wiki page ``\textit{Military}''.
-By reading these two wiki pages, readers easily understand the example tweet is talking about something related to \textit{Military} and \textit{Libya}.
+For example, the microblog message ``Possible Ft.
+Hood Attack Thwarted (2011-07-28)'' is short, but still comprehensible because the words ``\textit{Ft.
+Hood}" is included in the wiki page ``\textit{Ft.
+Hood}", and belongs to the category ``\textit{Military}''.
+By reading these two wiki pages, the model easily understands the example tweet is talking about something related to \textit{Military}.
 In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
 Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
+%拆成两个小图，中间说明这是transfer learning过后的
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=1.0\columnwidth]{img/hood.pdf}
+        \caption{Hood\footnote{\url{https://en.wikipedia.org/wiki/Naser_Jason_Abdo#Arrest}}\footnote{\url{https://en.wikipedia.org/wiki/Fort_Hood#2011_attack_plot}}}
+        \label{fig:hood}
+\end{figure}
 
@@
 
-In our paper, to balance the performance and the cost of transfer learning, new data structure \textit{history states} is proposed. 
+In our paper, to balance the performance and the cost of transfer learning, new data structure \textit{KB states} is proposed. 
 It bases on the following facts. 
@@
 
-More than that, we propose a new quick and lightweight probabilistic model \textsc{HS-Prior-LDA} for transfer learning. 
-After deriving \textsc{HS-Prior-LDA} (detailed in Section \ref{subsec:rs_initialization}), it reveals that whether a word in microblog links to a high-level category in knowledge base depends on three factors, the word's score in the category's \textit{history state}, the linkages of microblogs' other words, the linkages of the word types in the same time window.
+More than that, we propose a new quick and lightweight probabilistic model KB-Prior-LDA for transfer learning. 
+After deriving KB-Prior-LDA (detailed in Section \ref{subsec:rs_initialization}), it reveals that whether a word in microblog links to a high-level category in knowledge base depends on three factors, the word's score in the category's \textit{KB state}, the linkages of microblogs' other words, the linkages of the word types in the same time window.
 All these statistics are easy to gain, which leads the model efficient. 
-What \textsc{HS-Prior-LDA} learned is summarized as \textit{recent states}, shown in Figure \ref{fig:modelDesc}.
+What KB-Prior-LDA learned is summarized as \textit{recent states}, shown in Figure \ref{fig:modelDesc}.
 Since the recent states have filtered out meaningless words, the detected events on recent states is much more accurate than other methods which don't do the transfer learning.
-\textsc{HS-Prior-LDA}, \textit{history states}, and \textit{recent states} forms up our proposed event detection method \textsc{LTDetector}.
+\textsc{KB-Prior-LDA}, \textit{history states}, and \textit{recent states} forms up our proposed event detection method \textsc{LTDetector}.
 Our experiment on the real dataset \textit{Edinburgh twitter corpus (30 million tweets)} validates the effectiveness of our proposed method \textsc{LTDetector}.

### 2016-09-28 paper/lncsFormat0929_LTDetector.tex
LTDetector version

--- 2016-09-23 paper/lncsFormat.tex
@@
 %
-\title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+%\title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+%Category Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection
 %构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
+\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
 \maketitle
@@
 %我们的核心贡献应该是说，我们提出了一个方法（结构Guided的词表抽取方法），用这个方法可以从维基中学习出来了一个高度准确的词表，这个词表对于迁移学习非常有效。
+%Intrinsic
 (1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level by utilizing the structure.
@@
 %The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}, shrinking the scale of knowledge to category-word level.
-(2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our proposed KB-Prior-LDA, which exploits the word co-occurrences and transfers the condensed knowledge \textit{KB State} into microblogs.
+(2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our KB-Prior-LDA, which exploits the word co-occurrences and transfers the knowledge base's category topics into microblogs.
 %基于结构提取方法的迁移学习，学习到microblog的状态
@@
 
-After Gibbs sampling on discrete time windows, \textsc{HS-Prior-LDA} learned all hidden topics of words.
+After Gibbs sampling on discrete time windows, \textsc{HS-Prior-LDA} learned all hidden topics of words in microblog stream.
 And for a specific word type \(w\) and its history-state-like topic assignment \(c\) in time window \(t\), its document frequency is counted as \(n(c,t,w^{(c)})\), which is the element of category \(c\)'s \(t\)-th recent state.
@@
 \label{subsec:detection}
-Text stream evolves more quickly with time than knowledge base.
-For example, recent state of Military contain .
-In other words, recent state is history-state-like topic timestamp.%在时间轴上的横截面。
+Given the words' accurate meaning, events are  detected accurately as the patterns of words' time series are better exposed.
+Taking the word \textit{hood} as an example, it belongs to the category \textit{Military} when it appeared in \textit{Ft Hood}, a US military establishment located in Texas.
+As shown in Figure \ref{fig:hood}, the bursty pattern of \textit{hood} is clearly exposed after distinguishing its \textit{Military} time series from the raw time series.
+%Therefore, the processing on each category's accurate stream states leads to the accurate event detection.
 
-The remaining time series analysis and text stream mining includes three phases: (1) bursty words; (2)phase; (3)tweet.
-%An accurate recent states learning leads to accurate event detection.
+We take the detection in three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) linking event tweets with event phrases.
+%这里添加对这几个Definition的解释。
+
 \begin{rmk}[The Set of Events' Candidate Words] 
@@
 \begin{rmk}[Event Phrase] 
-Event phase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occurred in the set of events' candidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happened in time \(t\) under the category \(c\).
+Event phrase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occurred in the set of events' candidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happened in time \(t\) under the category \(c\).
 \end{rmk}
@@
 \end{comment}
+
+For a specific word \(w\) and the category \(c\), as stream states have provided the time series \(\{n(c,t_{1},w^{(c)}), \cdots, n(c,t_{T},w^{(c)})\}\), many bursty detection methods on the time series can be applied to check if the word \(w\) is bursty in category \(c\).
+%Text stream evolves more quickly with time than knowledge base.
+%For example, recent state of Military contain .
+%In other words, recent state is history-state-like topic timestamp.%在时间轴上的横截面。
 
@@
 \textbf{Discussions.} 
+%An accurate recent states learning leads to accurate event detection.
 These methods work in four ways. 

### 2016-09-29 paper/lncsFormat.tex
update abstract

@@
 %
-\title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+\title{Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
 %构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
+%\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
 \maketitle
@@
 But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
-We develop a novel lightweight transfer learning method \textsc{LTDetector} to deal with the task.  
-\textsc{LTDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and to make the transfer efficiently and effectively, the scale of knowledge should shrink without degrading.
-The following contributions are made in \textsc{LTDetector}.
-%我们的核心贡献应该是说，我们提出了一个方法（结构Guided的词表抽取方法），用这个方法可以从维基中学习出来了一个高度准确的词表，这个词表对于迁移学习非常有效。
-(1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level by utilizing the structure.
-%结构提取的方法(without degrading)
-Specifically, category's highly related words and their chi-square scores, namely category's \textit{KB State}, are condensed.
-%The knowledge base's hierarchical structure is formalized as three-part: taxonomy graph, category-page bipartite graph, and page-content map.
-%The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}, shrinking the scale of knowledge to category-word level.
-(2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our proposed KB-Prior-LDA, which exploits the word co-occurrences and transfers the condensed knowledge \textit{KB State} into microblogs.
-%基于结构提取方法的迁移学习，学习到microblog的状态
-(3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noise accurately. 
-(4) Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed transfer learning method.
-\textsc{LTDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
+We develop a novel category-pivot transfer learning method \textsc{TransDetector} to deal with the task.  
+\textsc{TransDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and events can be detected more accurately on microblogs with richer semantics.
+The following contributions are made in \textsc{TransDetector}.
+(1) We propose a structure-guided category-pivot topics extraction method, which exploits the knowledge base's hierarchical structure to extract categories' highly correlated topics. 
+(2) We develop a probabilistic model CTrans-LDA for category-pivot transfer learning, which utilizes the word co-occurrences and transfers the knowledge base's category-pivot topics into microblogs. 
+%Hence, word time series are expanded as category-pivot word time series.
+(3) Events are detected accurately on category-pivot word time series, due to richer semantics and less noise. 
+(4) Experiment verifies the quality of category-pivot topics extracted from knowledge base, and the further study on the benchmark \textit{Edinburgh twitter corpus} validates the effectiveness of our proposed transfer learning method for event detection.
+\textsc{TransDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
 %另外，我们还标注了事件，使其语义可理解。以及LTDetector是efficient的。

### 2016-10-01 paper/lncsFormat.tex
finish 3.3.1

@@
 Our experiment on the real dataset \textit{Edinburgh twitter corpus (30 million tweets)} validates the effectiveness of our proposed method \textsc{LTDetector}.
-
-The transfer learning based event detection method \textsc{LTDetector} also coincides with the news value theory\cite{caple2013delving}, which emphasizes the \textit{news unexpectedness} -- ``the unpredictable or the rare is more newsworthy than the routine"\cite{bell1991language}.
-Following this guideline, if the journalist knew the history states, aka, the ``routine things" of everyday better, he/she would tend to choose more unexpected news to report.
 
@@
 The recent state at time \(t\) of the specific category \(c\) is defined by a set of tuples, and denoted as \(\bm{r}_{c,t}=\{<w^{(c)}_i,n(c,t,w^{(c)}_{i})>\}_{i=1,...,N_c}\), in which word \(w^{(c)}_{i}\) is related to the category \(c\), and \(n(c,t,w^{(c)}_{i})\) is its document frequency in the time window \(t\).
+\end{rmk}
+
+\begin{rmk}[The Set of Events' Candidate Words] 
+The set of events' candidate words \(\mathcal{B}_{c,t}\) are defined by the bursty words in recent state \(\bm{r}_{c,t}\).
+\end{rmk}
+
+\begin{rmk}[Event Phrase] 
+Event phrase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occurred in the set of events' candidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happened in time \(t\) under the category \(c\).
+\end{rmk}
+
+\begin{rmk}[Event Related Articles] Event related articles \(\mathcal{D}_{c,t,i}\) are articles that relate to the \(i\)-th event in time \(t\) under the category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
 \end{rmk}
@@
 \label{subsec:detection}
-Given the words' accurate meaning, events are  detected accurately as the patterns of words' time series are better exposed.
+After transfer learning, events are detected accurately because the word time series is refined as multiple corresponding (word, category) time series, and the bursty pattern is better exposed. 
 Taking the word \textit{hood} as an example, it belongs to the category \textit{Military} when it appeared in \textit{Ft Hood}, a US military establishment located in Texas.
-As shown in Figure \ref{fig:hood}, the bursty pattern of \textit{hood} is clearly exposed after distinguishing its \textit{Military} time series from the raw time series.
+As shown in Figure \ref{fig:hood}, the bursty pattern of \textit{hood} is clearly exposed after distinguishing its \textit{Military} time series from the raw one.
 %Therefore, the processing on each category's accurate stream states leads to the accurate event detection.
 
-We take the detection in three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) linking event tweets with event phrases.
+Given (word, category) time series and microblogs in a time window, we take the detection in	 three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) linking event tweets with event phrases.
 %这里添加对这几个Definition的解释。
 
-\begin{rmk}[The Set of Events' Candidate Words] 
-The set of events' candidate words \(\mathcal{B}_{c,t}\) are defined by the bursty words in recent state \(\bm{r}_{c,t}\).
-\end{rmk}
+\textbf{Detecting events' candidate words}.
+For a word \(w\) and a category \(c\), on its time series \(\{n(c,t,w^{(c)})\}_{t=1}^{T}\), many bursty detection methods can be applied to check if the word \(w\) is bursty in category \(c\) by given time \(t\).
+We assume the document frequency of \(w^{(c)}\) follows a poisson distribution, which is also used in \cite{Diao:2012wj}.
+And the document frequency of nonbursting \(w^{(c)}\) has the possison distribution with the parameter \(\lambda=\mu_0\); while the bursting one with the parameter \(4\mu_0\) means the document frequency \(n(c,t,w^{(c)})\) is much higher when bursting.
+We empirically set \(\mu_0\) as the moving average \(\mu_0^{(t)}=\frac{1}{T}\sum_{\tau=t-T}^{t-1}n(c,\tau,w^{(c)})\), and set T=10.
+Hence, at time \(t\), bursty or not is determined by comparing the probabilities of above poisson distributions. 
+After bursty detection on the time series, we add each time \(t\)'s bursty word \(w^{(c)}\) into the set of event's candidate words \(\mathcal{B}_{c,t}\).
 
-\begin{rmk}[Event Phrase] 
-Event phrase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occurred in the set of events' candidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happened in time \(t\) under the category \(c\).
-\end{rmk}
+\textbf{Generating event phrases}.
 
-\begin{comment}
-\begin{rmk}[Event Related Articles] Event related articles \(\mathcal{D}_{c,t,i}\) are articles that relate to the \(i\)-th event in time \(t\) under the category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
-\end{rmk}
-\end{comment}
+\textbf{Linking event tweets with event phrases}.
 
-For a specific word \(w\) and the category \(c\), as stream states have provided the time series \(\{n(c,t_{1},w^{(c)}), \cdots, n(c,t_{T},w^{(c)})\}\), many bursty detection methods on the time series can be applied to check if the word \(w\) is bursty in category \(c\).
 %Text stream evolves more quickly with time than knowledge base.

### 2016-10-01 paper/lncsFormat.tex
paragraph before definition in Introduction section

@@
 In the example of Figure \ref{fig:modelDesc}, the words \textit{libyan} and \textit{rebel} are related to the \textit{military} event ``\#libya Libyan rebels chief is killed (2011-07-28)''.
+
+After processing each time window's data, the words in microblogs can be enriched semantically with knowledge base.
+In this way, the transfer learning model provides richer semantics and less noise for microblog stream, which promotes the accuracy of event detection significantly. 
+The following definitions are the concepts used by the transfer learning model \textsc{TransDetector}.
 

### 2016-10-02 paper/lncsFormat.tex
finish 3.3.2.2

@@
 \textbf{Generating event phrases}. 
+In the set of event's candidate words \(\mathcal{B}_{c,t}\), some words appear together and should be grouped into event phrases.
+For example, there are six bursty words in \(\mathcal{B}_{military,2011-07-28}\) belonging to two event phrases \textit{``Ft, Hood, attack"} and \textit{``Libyan, rebel, gunned"} in the time window 2011-07-28 to represent the events happened to the US military establishment and the Libyan rebel respectively.
+
+In order to group the bursty words together, we  construct the directed weighted graph \(\mathcal{G}_{c,t}=(\mathcal{B}_{c,t},\mathcal{E}_{c,t})\), where \(\mathcal{E}_{c,t}=\{(a,b,PMI(a,b))|a \in \mathcal{B}_{c,t}, b \in \mathcal{B}_{c,t}, PMI(a,b)>0 \}\).
+The graph \(\mathcal{G}_{c,t}\) means the words in \(\mathcal{B}_{c,t}\) are connected if and only if their PMI score in the given time window's microblogs is over 0.
 
@@
 
-%\begin{comment}
 \begin{table*}[ht]
@@
 \end{table*}
-%\end{comment}
 

### 2016-10-02 paper/lncsFormat.tex
finish 3.3.2.3, and 5200 words

@@
 Given (word, category) time series and microblogs in a time window, we take the detection in	 three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) linking event tweets with event phrases.
+Note that these sub-phases are also available for the common text stream, but they performs better when words are enriched by category concepts of knowledge base.
 %这里添加对这几个Definition的解释。
@@
 
-In order to group the bursty words together, we  construct the directed weighted graph \(\mathcal{G}_{c,t}=(\mathcal{B}_{c,t},\mathcal{E}_{c,t})\), where \(\mathcal{E}_{c,t}=\{(a,b,PMI(a,b))|a \in \mathcal{B}_{c,t}, b \in \mathcal{B}_{c,t}, PMI(a,b)>0 \}\).
+In order to group the bursty words together, we  construct the directed weighted graph \(\mathcal{G}_{c,t}=(\mathcal{B}_{c,t},\mathcal{E}_{c,t},\mathcal{W}_{c,t})\), where \(\mathcal{E}_{c,t}=\{(a,b)|a \in \mathcal{B}_{c,t}, b \in \mathcal{B}_{c,t}, PMI(a,b)>0 \}\), and \(\mathcal{W}_{c,t}\) gives the PMI scores on the edges.
 The graph \(\mathcal{G}_{c,t}\) means the words in \(\mathcal{B}_{c,t}\) are connected if and only if their PMI score in the given time window's microblogs is over 0.
+
+Given the graph \(\mathcal{G}_{c,t}\), spectral clustering\cite{von2007tutorial} is utilized for exploring the best partition of words. 
+To get the optimum cluster number, we use the graph density as the criteria.
+The graph density is the ratio of the number of edges to that of complete graph (the graph with all possible edges), and in practice all the sub-graphs in \(\mathcal{G}_{c,t}\) should have the densities over an empirical threshold.
+We run the spectral clustering with cluster number from 1 to \(|\mathcal{B}_{c,t}|\), and stop when all the resulting sub-graphs satisfy the criteria that the density is over the given threshold. 
+In this way, the generated event phrase combines the co-occurred bursty words and excludes the unrelated.
 

### 2016-10-02 paper/lncsFormat.tex
finish 3.3. and 5405 words. 5221 words.

@@
 
-\begin{rmk}[Event Related Articles] Event related articles \(\mathcal{D}_{c,t,i}\) are articles that relate to the \(i\)-th event in time \(t\) under the category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
+\begin{rmk}[Event Related Microblogs] Event related microblogs \(\mathcal{D}_{c,t,i}\) are articles that relate to the \(i\)-th event in time \(t\) under the category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
 \end{rmk}
@@
 \label{subsec:detection}
-After transfer learning, events are detected accurately because the word time series is refined as multiple corresponding (word, category) time series, and the bursty pattern is better exposed. 
+After transfer learning, events are detected accurately because the word time series is refined to finer grain as multiple corresponding (word, category) time series, and the bursty pattern is better exposed.
 Taking the word \textit{hood} as an example, it belongs to the category \textit{Military} when it appeared in \textit{Ft Hood}, a US military establishment located in Texas.
@@
 
-Given (word, category) time series and microblogs in a time window, we take the detection in	 three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) linking event tweets with event phrases.
+Given (word, category) time series and microblogs in a time window, we take the detection in	 three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) retrieving event related microblogs.
 Note that these sub-phases are also available for the common text stream, but they performs better when words are enriched by category concepts of knowledge base.
@@
 In the set of event's candidate words \(\mathcal{B}_{c,t}\), some words appear together and should be grouped into event phrases.
-For example, there are six bursty words in \(\mathcal{B}_{military,2011-07-28}\) belonging to two event phrases \textit{``Ft, Hood, attack"} and \textit{``Libyan, rebel, gunned"} in the time window 2011-07-28 to represent the events happened to the US military establishment and the Libyan rebel respectively.
+For example, there are six bursty words in \(\mathcal{B}_{military,2011-07-28}\) belonging to two event phrases \textit{``ft, hood, attack"} and \textit{``libyan, rebel, gunned"} in the time window 2011-07-28 to represent the events happened to the US military establishment and the Libyan rebel respectively.
 
@@
 The graph density is the ratio of the number of edges to that of complete graph (the graph with all possible edges), and in practice all the sub-graphs in \(\mathcal{G}_{c,t}\) should have the densities over an empirical threshold.
+And the empirical threshold is set to 0.6 in our setting.
 We run the spectral clustering with cluster number from 1 to \(|\mathcal{B}_{c,t}|\), and stop when all the resulting sub-graphs satisfy the criteria that the density is over the given threshold. 
@@
 
-\textbf{Linking event tweets with event phrases}.
+\textbf{Retrieving event related microblogs}. 
+To better understand the event, we retrieve the event microblogs \(\mathcal{D}_{c,t,i}\) by using the event phrase \(\mathcal{C}_{c,t,i}\).
+Generally, according to the number of bursting words in the event phrase \(\mathcal{C}_{c,t,i}\), there are two situations to be addressed. 
+(1) \(|\mathcal{C}_{c,t,i}|=1\), we directly add the microblog in time window \(t\), which contains the bursting category-word \(w^{(c)}\), into the set \(\mathcal{D}_{c,t,i}\).
+(2) \(|\mathcal{C}_{c,t,i}|\geq 2\), not all the bursting words are included in the event related microblog.
+For example, the tweet ``\textit{Soldier wanted to attack Fort Hood troops}" contains the bursting words \textit{attack} and \textit{hood}, not all the event phrase ``\textit{ft, hood, attack}". 
+To tackle this problem, we consider the microblog, that contains any pair of category-words in the event phrase, as the event related microblog.
+
+Finally, \textsc{TransDetector} gets the detected events \(\{(\mathcal{C}_{c,t,i},\mathcal{D}_{c,t,i})\}_{i=1}^{|\mathcal{C}_{c,t}|}\), containing the event phrase and the corresponding event related microblogs for the given category and the time window.
 
@@
 \textbf{Overall Performances.}
+\begin{comment}
 Table 1 reports the number of events
@@
 are therefore have higher chance to be clustered together.
+\end{comment}
 

### 2016-10-05 paper/lncsFormat.tex
finish sec 2.1.1.1; 5151 words (related works)(event detection).(without extra information).(clustering articles)

@@
 \label{sec:relatedWorks}
-\textbf{Event Detection.} 
-There are two kinds of event detection methods based on how it utilize the history data, unsupervised and supervised learning.
+\textbf{Event Detection.} According to how much data are used, the approaches are divided into two groups: the detection only without extra information, and the detection by leveraging extra information.
 
-The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
-This kind methods can be implemented by clustering of articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, word frequencies\cite{Mathioudakis:2010fc}\cite{Weng:2011wz}, or topic modelling\cite{Diao:2012wj}\cite{Yan:2015wm} in the recent time windows.
-Taking the clustering of articles as an example, they model the occurred events as clusters, and link the incoming article with an already existed event cluster or assign it as the new detected event.
+Most existing methods belong to the first group.
+They utilize the bursty pattern in the text stream to detect events, and are implemented by  clustering articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, analyzing word frequencies\cite{Mathioudakis:2010fc,Weng:2011wz}, or finding bursty topics\cite{Diao:2012wj,Yan:2015wm}.
+(1) By clustering articles, UMass\cite{Allan:2000wu}, LSH\cite{Petrovic:2010uj}, k-Term-FSD\cite{Wurzer:2015wq} and other similar methods model the occurred events as clusters of articles, and link the incoming article with an already existed event cluster or label it as the first story of a new event.
 The decision is based on whether the dissimilarity between the incoming article and existed event clusters is over the user-specified threshold. 
+Taking LSH as an example, as \cite{Petrovic:2010uj} discussed, the threshold controls the result: the big one leads to very few and broad clusters, while the small one results in very small and specific clusters.
+Even after carefully set the appropriate threshold, the clusters generated by this kind method are still mixed of events and non-events due to large portion of non-event microblogs, which requires some post-processing methods as the supplement.
+(2) By analyzing word frequencies, 
+(3) By finding bursty topics, TimeUserLDA, BurstyBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.
+
+%The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
 
@@
 On the one hand, UMass\cite{Allan:2000wu} prefers the lower threshold to enlarge the recall but suffers the precision.
-On the other hand, BurstyBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.
-
-The supervised thoroughly relies on the \textit{history data}. 
-The typical implementation is to train the event triggers\cite{Li2013JointEE}\cite{Nguyen2015EventDA} from history labeled data, then apply the trained model to detect the event related articles, which contain the triggers such as the word \textit{attacked} for the \textit{public security} events.
-This kind methods suffer from the loss of recall. 
-There are two reasons. 
-%没有对历史数据进行很好的组织
-(1) The model does not utilize the history data sufficiently. 
-Usually, the event trigger based method mainly focus on the event related verbs, but often ignores the other word types.
-(2) The model lacks the update mechanism. 
-It only restores the history knowledge but without updating. 
-Some new event related articles may be mistakenly filtered out because not containing previous trained triggers. 
-For example, the tweet ``Russia's intervention in Syria began in September 2015" without an event trigger, which is really related to a \textit{public security} event, may be omitted by the system.
 
@@
 (1) \(|\mathcal{C}_{c,t,i}|=1\), we directly add the microblog in time window \(t\), which contains the bursting category-word \(w^{(c)}\), into the set \(\mathcal{D}_{c,t,i}\).
-(2) \(|\mathcal{C}_{c,t,i}|\geq 2\), not all the bursting words are included in the event related microblog.
+(2) \(|\mathcal{C}_{c,t,i}|\geq 2\), it's not necessary that all the bursting words are included in the event related microblog.
 For example, the tweet ``\textit{Soldier wanted to attack Fort Hood troops}" contains the bursting words \textit{attack} and \textit{hood}, not all the event phrase ``\textit{ft, hood, attack}". 
@@
 
-\textbf{Text Stream Dataset.} We conduct the empirical analysis on a text stream benchmark \textit{Edinburgh twitter corpus} which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}.
+\textbf{Microblog Stream Dataset.} We conduct the empirical analysis on a text stream benchmark \textit{Edinburgh twitter corpus} which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}.
 Due to the developer policy of Twitter, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/fsd_corpus.tar.gz}}.
@@
 We use precision and recall to evaluate each method on both benchmarks.
+
+%TODO LSH-FSD\cite{Petrovic:2010uj}没有评测FSD的情况，我们也可以提一句，我们不评测FSD，我们只评测检测出的事件是否是真实的事件。
 \begin{table}[h]

### 2016-10-06 paper/lncsFormat.tex
finish sec 2.1.1.2; 5208 words (related works)(event detection).(without extra information).(word frequencies)

@@
 
+\usepackage{hyperref}
 \setcounter{secnumdepth}{2}  
@@
         \includegraphics[width=1.0\columnwidth]{img/hood.pdf}
-        \caption{Hood\footnote{\url{https://en.wikipedia.org/wiki/Naser_Jason_Abdo#Arrest}}\footnote{\url{https://en.wikipedia.org/wiki/Fort_Hood#2011_attack_plot}}}
+        %\caption{Hood\footnote{\url{https://en.wikipedia.org/wiki/Naser_Jason_Abdo#Arrest}}\footnote{\url{https://en.wikipedia.org/wiki/Fort_Hood#2011_attack_plot}}}
         \label{fig:hood}
@@
 \label{sec:relatedWorks}
-\textbf{Event Detection.} According to how much data are used, the approaches are divided into two groups: the detection only without extra information, and the detection by leveraging extra information.
+\textbf{Event Detection.} According to how much data are used, the approaches are divided into two groups: the detection \textit{without extra information}, and the detection by \textit{leveraging extra information}.
 
-Most existing methods belong to the first group.
-They utilize the bursty pattern in the text stream to detect events, and are implemented by  clustering articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, analyzing word frequencies\cite{Mathioudakis:2010fc,Weng:2011wz}, or finding bursty topics\cite{Diao:2012wj,Yan:2015wm}.
+Most existing methods are implemented \textit{without extra information}.
+They utilize the bursty pattern in the text stream to detect events, and are carried out by  clustering articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, analyzing word frequencies\cite{Mathioudakis:2010fc,Weng:2011wz}, or finding bursty topics\cite{Diao:2012wj,Yan:2015wm}.
 (1) By clustering articles, UMass\cite{Allan:2000wu}, LSH\cite{Petrovic:2010uj}, k-Term-FSD\cite{Wurzer:2015wq} and other similar methods model the occurred events as clusters of articles, and link the incoming article with an already existed event cluster or label it as the first story of a new event.
@@
 Even after carefully set the appropriate threshold, the clusters generated by this kind method are still mixed of events and non-events due to large portion of non-event microblogs, which requires some post-processing methods as the supplement.
-(2) By analyzing word frequencies, 
+(2) By analyzing word frequencies, TwitterMonitor\cite{Mathioudakis:2010fc} models the bursty words by queueing theory, and EDCoW\cite{Weng:2011wz} exploits wavelet transformation, which converts signal from time domain to time-scale domain, to detect the change point of word signal.
+However they treat the word as the most basic unit in analysis, without regarding how many concepts are represented by the word.
 (3) By finding bursty topics, TimeUserLDA, BurstyBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.

### 2016-10-07 paper/lncsFormat.tex
finish sec 2.1.1.3; 5274 words (related works)(event detection).(without extra information).(topic model)

@@
 However they treat the word as the most basic unit in analysis, without regarding how many concepts are represented by the word.
-(3) By finding bursty topics, TimeUserLDA, BurstyBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.
+(3) By finding bursty topics via topic modelling, TimeUserLDA\cite{Diao:2012wj}, BurstyBTM\cite{Yan:2015wm} generates detected events.
+TimeUserLDA distinguishes user's long term interests and short term bursty events, and BurstyBTM utilizes the burstiness of biterms as prior knowledge.
+They both need to set the appropriate number of topics to run the topic modelling, and detect the ``large" events that associate with many articles but ignore the ``small" ones. 
+To summarize, due to microblog's short length and high noise, it's not easy to set the directly applicable parameter for existing methods to achieve high precision and high recall simultaneously.
 
+The second group methods detect events by \textit{leveraging extra information}. 
+\cite{huang2016efficient} incorporates user's and the followees' profiles in microblog platform as the extra information for modeling user's long term interests, and further detects the bursty events which draws the attention of users with different interests.
+However many event detection scenes only provide the microblog stream without user profile information and the following network. 
+FrameNet?.
+Wikipop\cite{ciglan2010wikipop}.
+\cite{mcminn2013building} leverages LSH, wikipedia to build a large corpus for evaluating event detection on twitter.
+\cite{osborne2012bieber} utilizes Wikipedia for filtering spurious events.
+\cite{steiner2013mj} utilizes the concurrent wikipedia edit spikes for event detection.
 %The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
 
-The reason why this kind methods cannot achieve high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
-This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision.
-In the journalist metaphor of news value theory, they have the limited knowledge of normal states (aka "routine things") due to the limited history information used.
-On the one hand, UMass\cite{Allan:2000wu} prefers the lower threshold to enlarge the recall but suffers the precision.
+%The reason why this kind methods cannot achieve high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
+%This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision.
 
@@
     Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
-    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
     LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline

### 2016-10-17 paper/lncsFormat.tex
finish sec 2.1.2; 5422 words (related works)(event detection).(with extra information).

@@
 However many event detection scenes only provide the microblog stream without user profile information and the following network.
-FrameNet?.
-Wikipop\cite{ciglan2010wikipop}.
-\cite{mcminn2013building} leverages LSH, wikipedia to build a large corpus for evaluating event detection on twitter.
-\cite{osborne2012bieber} utilizes Wikipedia for filtering spurious events.
+\cite{osborne2012bieber} compares two time series generated by event-related tweets and corresponding Wikipedia article's page views, and further filter out spurious events of microblogs.
+Twevent \cite{Twevent2012} divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia, then detect the bursty segments and cluster these segments into candidate events for necessary post processings.
+But Twevent is still hampered by the performance of simply clustering the bursty segments shown by \cite{Yan:2015wm}.
+If not limited to microblog stream, many systems also use the extra information for improving event detection.
 \cite{steiner2013mj} utilizes the concurrent wikipedia edit spikes for event detection.
+And \cite{liuleveraging2016} leverages the ACE corpus\cite{doddington2004automatic} and the structure of FrameNet\cite{baker1998berkeley} to improve the event detection within FrameNet, but has not shown how to apply the knowledge base for more general unstructured corpus.
+In a nutshell, existing works are different from ours, as we transfer the category information of knowledge base into microblog's words and get the finer processing objects in event detection, rather than treating the knowledge base as a lookup table or a comparison base.
+%Wikipop\cite{ciglan2010wikipop} uses the statistics of page views on Wikipedia articles to detect the personalized events.
+%\cite{mcminn2013building} leverages LSH, wikipedia to build a large corpus for evaluating event detection on twitter.
 %The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.

### 2016-10-24 paper/lncsFormat.tex
finish sec 2.2; 5623 words (related works)

@@
 %拆成两个小图，中间说明这是transfer learning过后的
+\intextsep=3pt plus 3pt minus 1pt
 \begin{figure}[h]
@@
 
+\intextsep=5pt plus 3pt minus 1pt
 \begin{figure}[h]
+	\setlength{\abovecaptionskip}{0.cm}
+	\setlength{\belowcaptionskip}{0.cm}
     \centering
     \includegraphics[width=.82\columnwidth]{img/NSDetectorExample.pdf}
+    \intextsep=0pt plus 3pt minus 1pt
     \caption{\textsc{LTDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example.
@@
 
-\textbf{Knowledge Base} The existing RDF model\cite{klyne2006rdf} lacks an efficient quick mechanism to transfer the knowledge, since it's mainly designed for managing knowledge as tuples on graph.
-And the query on large graph is also very expensive\cite{huang2011scalable}, which is not suitable for the scene of quickly and accurately detecting events.
+\textbf{Knowledge Base} Recently, many general knowledge bases and customized knowledge bases are constructed and utilized for different text mining tasks. 
+For example, Probase\cite{wu2012probase} constructs a large general probabilistic \textit{IsA} taxomomy from webpages, and is used for semantic web search, and text classification\cite{wang2014concept}.
+Such kind efforts are also made by DBPedia\cite{auer2007dbpedia}, Yago\cite{fabian2007yago}, and Freebase\cite{bollacker2008freebase}. 
+These works manages knowledge as tuples on graph. 
+However the query on large graph is very expensive\cite{huang2011scalable}, which is not very suitable for the scene of quickly and accurately detecting events.
+
+The customized knowledge bases such as EVIN\cite{kuzey2014evin}, Event Registry\cite{leban2014eventRegistry}, and Storybase\cite{wu2015storybase}, are designed for managing events.
+These knowledge bases are mainly built on news articles.
+EVIN maps the existing event-related news articles into semantic classes. 
+Event Registry collects the articles by the API of News Feed Service\cite{trampuvs2012newsfeed}, then detects events, and provides the structural information of the events, such as the related Wikipedia article, timestamp, and location etc.
+Storybase introduces Wikipedia current events\footnote{\url{https://en.wikipedia.org/wiki/Portal:Current_events}} as the resources for constructing event-and-storyline knowledge base on news articles, which are provided by GDELT project\cite{leetaru2013gdelt}.
+As the news articles may lag behind the microblogs when the emergency of events, it's not enough to detect events from microblog stream by directly applying these customized knowledge bases.
+
+%近年来，知识图谱也被广泛应用在了文本挖掘领域，TKDE的文章利用wikipedia将
 
@@
 \newpage
-\bibliographystyle{named}
+\bibliographystyle{aaai}
 \small

### 2016-10-27 classifier/runFastText.sh
add the experiment of fastText

@@ -1,0 +1,5 @@
+./fasttext supervised -input "data/20newsgroup.train" -output "result_fastText/20newsgroup" -dim 10 -lr 0.1 -wordNgrams 2 -minCount 1 -bucket 10000000 -epoch 640 -thread 4
+./fasttext test result_fastText/20newsgroup.bin data/20newsgroup.test
+./fasttext predict result_fastText/20newsgroup.bin data/20newsgroup.test > result_fastText/20newsgroup.test.predict
+
+awk {'print $1'} result_fastText/20newsgroup.test.predict | sort | uniq -c

### 2016-10-27 makeCorpus.py

@@ -1,0 +1,86 @@
+#encoding=utf8
+'''generate label dictionary class-label.dict, label-class.dict, 
+20newsgroup.all.txt
+20newsgroup.train
+20newsgroup.test
+in classifier/data
+'''
+import os
+import os.path
+import json
+from sklearn.datasets.twenty_newsgroups import *
+import random
+
+sourceFolder="20news-18828"
+globaldClassLabel=dict()
+globaldLabelClass=dict()
+
+def writeDict(filename,d):
+    f=open(filename,"w")
+    f.write(json.dumps(d))
+    f.close()
+
+
+def getClassAndLabels():
+    files=os.listdir(sourceFolder)
+    files=[f for f in files if os.path.isfile(f)==False]#filter out non-folder file
+    idx=0
+    for f in files:
+        globaldClassLabel[f]=idx
+        globaldLabelClass[idx]=f
+        idx=idx+1
+    writeDict("classifier/data/class-label.dict",globaldClassLabel)
+    writeDict("classifier/data/label-class.dict",globaldLabelClass)
+
+
+def compressFileIntoALine(filename,label,fileId):
+    '''compress the 20newsgroup's article into a single line
+    '''
+    f=open(filename,"r")
+    data=[]
+    for line in f.readlines():
+        data.extend(line)
+    content="".join(data) 
+    s=strip_newsgroup_header(content)
+    #s=strip_newsgroup_footer(s)
+    s=strip_newsgroup_quoting(s)
+    s="\n".join(s.strip().split("\n")[:-1])
+
+    line=(" ".join([line.strip() for line in s.split("\n")]))
+    result="__label__"+str(label)+" , "+fileId+" , "+line
+    return result
+
+
+def portal():
+    getClassAndLabels() 
+    fWriter=open("classifier/data/20newsgroup.all.txt","w")
+    fTrain=open("classifier/data/20newsgroup.train","w")
+    fTest=open("classifier/data/20newsgroup.test","w")
+    #line=compressFileIntoALine("20news-18828/alt.atheism/52909","alt.atheism","52909")
+    #fWriter.write(line+"\n")
+    #fWriter.close()
+    #return
+    for classname in globaldClassLabel.keys():
+        files=[sourceFolder+"/"+classname+"/"+f for f in os.listdir(sourceFolder+"/"+classname)]
+        for f in files:
+            print(f)
+            fileId=f.split("/")[-1]
+            label=globaldClassLabel[classname]
+            line=compressFileIntoALine(f,label,fileId)
[…]

### 2016-10-27 paper/aaaiFormat1.tex
ready to change to lncs format

--- 2016-10-24 paper/lncsFormat.tex
@@
+% !Mode:: "TeX:UTF-8"
 \def\year{2017}\relax
@@
 \usepackage{makecell}
+
+%TODO, Chinese
+\usepackage{CJKutf8}
+\inputencoding{utf8}
 
@@
 
+%\begin{comment}
 \begin{table*}[ht]
@@
 Date & Event key words & Representative event tweet & \begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular} \\ \hline
-7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman...˙http://dlvr.it/cLbk8\end{tabular} & 557 \\ \hline
+7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman...
+http://dlvr.it/cLbk8\end{tabular} & 557 \\ \hline
 7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 \\ \hline
@@
 \end{table*}
+%\end{comment}
 
@@
 \textbf{Overall Performances.}
+\begin{CJK*}{UTF8}{gbsn}
+    中文范例！超级长的一句中文    中文范例！超级长的一句中文    中文范例！超级长的一句中文    中文范例！超级长的一句中文
+\end{CJK*}
+
 \begin{comment}
@@
 %An accurate recent states learning leads to accurate event detection.
+\begin{comment}
 These methods work in four ways. 
@@
 4) By analyzing word frequencies, EDCoW clusters the bursty words into events.
+\end{comment}
 

### 2016-10-27 classifier/runFastText.sh

@@ -1,4 +1,4 @@
-./fasttext supervised -input "data/20newsgroup.train" -output "result_fastText/20newsgroup" -dim 10 -lr 0.1 -wordNgrams 2 -minCount 1 -bucket 10000000 -epoch 640 -thread 4
+./fasttext supervised -input "data/20newsgroup.train" -output "result_fastText/20newsgroup" -dim 10 -lr 0.1 -wordNgrams 2 -minCount 1 -bucket 10000000 -epoch 320 -thread 4
 ./fasttext test result_fastText/20newsgroup.bin data/20newsgroup.test
 ./fasttext predict result_fastText/20newsgroup.bin data/20newsgroup.test > result_fastText/20newsgroup.test.predict
 

### 2016-10-27 paper/lncsFormat.tex
add the experiment of fastText
changed to lncs format

@@
-\def\year{2017}\relax
-\documentclass{article}
-\usepackage{aaai17}
+% !Mode:: "TeX:UTF-8"
+\documentclass[runningheads,a4paper]{llncs}
+
+%\usepackage{aaai17}
 \usepackage{times}
@@
 
+%TODO, Chinese
+\usepackage{CJKutf8}
+\inputencoding{utf8}
+
 \usepackage{multirow}% for table
@@
 %
-\title{Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+\titlerunning{Transfer Learning for Accurate Event Detection}
 %构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
 %\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
+\begin{comment}% for double blind
+\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.}\and Tengjiao Wang\inst{1}}
+\institute{Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
+\path{huangwaleking@gmail.com,{pekingchenwei,tjwang}@pku.edu.cn}\\ 
+}
+\end{comment}
+
 \maketitle
@@
 
-The customized knowledge bases such as EVIN\cite{kuzey2014evin}, Event Registry\cite{leban2014eventRegistry}, and Storybase\cite{wu2015storybase}, are designed for managing events.
+The customized knowledge bases such as EVIN\cite{kuzey2014evin}, Event Registry\cite{leban2014eventRegistry}, and Story-base\cite{wu2015storybase}, are designed for managing events.
 These knowledge bases are mainly built on news articles.
@@
 \newpage
-\bibliographystyle{aaai}
+\bibliographystyle{unsrt}
 \small

### 2016-10-27 paper/lncsFormat.tex
remove pages in the bib file
merge two illustration figures into a integrated one

@@
 	\centering
-    \includegraphics[width=.82\columnwidth]{img/NSDetectorExample.pdf}
-    \intextsep=0pt plus 3pt minus 1pt
-    \caption{\textsc{LTDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example.
-\textsc{LTDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.}
+    \label{fig:subfig} %% label for entire figure
+        \subfigure[]{
+                \includegraphics[width=.42\columnwidth]{img/NSDetectorExample.pdf}
                 \label{fig:modelDesc}
+
+        }
+        \subfigure[]{
+                \includegraphics[width=.42\columnwidth]{img/initializationExample.pdf}
+                \label{fig:NSinitializaton}
+        }
+        \caption{(a)\textsc{LTDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example.
+\textsc{LTDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.;(b)Illustration on how to initialize history states from Wikipedia, taking \textit{Military} as an example.}
 \end{figure}
@@
 As shown in line \ref{alg:line3inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}, by visiting the category \textit{Military} in the DAG \(G^{(0)'}\), the breadth-first traverse can reach its successor sub-category nodes such as \textit{Firearms}, \textit{The World Wars}, and \textit{World War II}, etc.
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=.82\columnwidth]{img/initializationExample.pdf}  
-    \caption{Illustration on how to initialize history states from Wikipedia, taking \textit{Military} as an example.}
-    \label{fig:NSinitializaton}
-\end{figure}
 
@@
 \textbf{Page-Content Map \(G^{(2)}\)}. 
-For a specific Wikipedia dumps version, the edges \textit{page}\(\rightarrow\)\textit{content} in \(G^{(2)}\) define a one-to-one mapping.
+For a specific Wikipedia dumps version, the edges  \textit{page} \(\rightarrow\)\textit{content} in \(G^{(2)}\) define a one-to-one mapping.
 There are a bulk of history information restored in the wiki text content.

### 2016-10-28 paper/lncsFormat.tex
move on to the experiment

@@
 \usepackage{bm}%used for bm
-\usepackage{graphics} 
+\usepackage{graphics} % used for scalebox
 \usepackage{graphicx}
-\usepackage{amsmath} %used for maths symbols
+\usepackage{amsmath} %used for maths symbols and the checkmark
 \usepackage{amssymb}%used for empty set symbol
-\usepackage{url}
-\usepackage{xcolor}% or package color
+\usepackage{threeparttable} % used for footnotes in table
+\usepackage{booktabs} %used for tnote
+\usepackage{url} %used for url
 
@@
 
-%TODO, Chinese
+%Chinese
 \usepackage{CJKutf8}
 \inputencoding{utf8}
+
+%================================================
+%highlight
+\usepackage{color,soul}%used for hl
+\newcommand{\hlgreen}[1]{
+	\sethlcolor{green}
+	\hl{#1}
+	\sethlcolor{yellow}
+}%used for highlight, but set the color as green
+%================================================
+%================================================
+%footnote in table
+%TODO 加和不加这一段对空间的影响很大
+%================================================
 
@@
 %\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
-\begin{comment}% for double blind
+%\begin{comment}% for double blind
 \author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.}\and Tengjiao Wang\inst{1}}
@@
 }
-\end{comment}
+%\end{comment}
 
@@
 
+%TODO 这个table需要增加BTM生成的和aviation最相近的一个topic的情况。
+\hlgreen{TODO: add a new table, containing a topic generated by BTM, which is most similar to the extracted topic from KB.}
 \begin{table}[]
@@
 
+%TODO figure2需要增加BTM的情况，以及要用盒形图表示
+\hlgreen{Add a topic of BTM for Figure 2.}
 \begin{figure}
@@
 \hline
-\multicolumn{2}{|c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Middle East}} & \multicolumn{2}{c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Mobile Phones}} & \multicolumn{2}{c|}{\textit{Video Games}} \\
-\begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} \\
+\multicolumn{2}{|c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Middle East}} & \multicolumn{2}{c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Mobile Phones}}\\
+\begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} \\
 \hline
-aircraft & air\scriptsize(3253) & health & weight\scriptsize(16344) & al & \textcolor{red}{\textit{\#syria}}\scriptsize(4212) & army & killed\scriptsize(4055)  & android & iphone\scriptsize (13674) & game & games\scriptsize(8812) \\
-air & plane & patients & loss & israel & \textcolor{red}{\textit{\#bahrain}} & military & news & mobile & apple & player & liked \\ 
-airport & flight & medical & diet & iran & people & air & \textcolor{red}{\textit{\#libya}}\scriptsize(3503) & nokia & android & playstation & free \\ 
-flight & time & disease & health & arab & israel & command & libya & ios & app & gameplay & xbox \\
-airline & airlines & treatment & cancer & israeli & police & force & rebels & phone & ipad & nintendo & 360 \\
-airlines & news & hospital & lose & egypt & \textcolor{red}{\textit{\#libya}}\scriptsize(2557) & regiment & people & samsung & samsung & games & playing \\
-aviation & boat & patient & fat & egyptian & \#egypt & forces & police & game & mobile & players & played \\
-flying & airport & clinical & tips & ibn & news & squadron & war & app & blackberry & xbox &iphone\scriptsize(2820)\\
-pilot & force & symptoms & treatment & jerusalem & \#israel & infantry & libyan & iphone & tablet & mode & time\\
-squadron & fly & cancer & body & syria & world & battle & attack & htc & apps & arcade & \textcolor{red}{\textit{ps3}}\\
+aircraft & air & health & weight & al & \textbf{\textit{\#syria}} & army & killed & android & iphone\\ 
+air & plane & patients & loss & israel & \textbf{\textit{\#bahrain}} & military & news & mobile & apple \\ 
+airport & flight & medical & diet & iran & people & air & \textbf{\textit{\#libya}} & nokia & android \\ 
+flight & time & disease & health & arab & israel & command & libya & ios & app \\
+airline & airlines & treatment & cancer & israeli & police & force & rebels & phone & ipad \\
+airlines & news & hospital & lose & egypt & \textbf{\textit{\#libya}} & regiment & people & samsung & samsung \\
+aviation & boat & patient & fat & egyptian & \#egypt & forces & police & game & mobile\\
+flying & airport & clinical & tips & ibn & news & squadron & war & app & blackberry \\
+pilot & force & symptoms & treatment & jerusalem & \textbf{\textit{\#israel}} & infantry & libyan & iphone & tablet \\
+squadron & fly & cancer & body & syria & world & battle & attack & htc & apps\\
 \hline
@@
 }
-\caption{History States extracted from Wikipedia and topical words learned from HS-Prior-LDA}
+\caption{Category-Level Topics extracted from knowledge base and the corresponding topics on microblog stream learned from CTrans-LDA, taking the categories \textit{Aviation},  \textit{Health}, \textit{Middle East}, \textit{Military}, and \textit{Mobile Phones} as examples.
+The words in \textbf{\textit{bold italic}} font are newly learned on the microblog stream by the transfer learning, which semantic meanings are verified consistent with the categories; while the black words play the role as the bridge in transfer learning, and appear in the both category-level topics in two domains.}
 \label{tbl:historyStates}
 \end{table*}
+%TODO: add the top words in the category-level topic 
+\hlgreen{TODO: add the top words of the category-level topic in each window of microblog stream AFTER Table 2.}
 
-%\begin{comment}
-\begin{table*}[ht]
-\centering
-\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-28}
-\scalebox{0.76}{
-\label{my-label}
-\begin{tabular}{|l|L{3cm}|l|l|}
-\hline
-Date & Event key words & Representative event tweet & \begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular} \\ \hline
-7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman...
-http://dlvr.it/cLbk8\end{tabular} & 557 \\ \hline
-7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 \\ \hline
-7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 25 \\ \hline
-7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 20 \\ \hline
-7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 \\ \hline
-\end{tabular}
-}
-\end{table*}
-%\end{comment}
-
+%TODO: add the effect of transfer learning by using text classification, compared with fastText and SVM.
+\hlgreen{TODO: add the effect of transfer learning by using text classification, compared with fastText and SVM.}
 \begin{comment}
@@
 \subsection{Effects of Event Detection}
-\textbf{Baselines Methods.} We compare our proposed method against the following methods, Twevent\cite{Twevent2012}, BurstyBTM\cite{Yan:2015wm}, LSH\cite{Petrovic:2010uj}, EDCoW \cite{Weng:2011wz}, TimeUserLDA\cite{Diao:2012wj}, and UMass System\cite{Allan:2000wu}, which are mentioned in the Section \ref{sec:relatedWorks}.
+\textbf{Baselines Methods.} We compare our proposed method against the following methods, Twevent\cite{Twevent2012}, BurstyBTM\cite{Yan:2015wm}, LSH\cite{Petrovic:2010uj}, EDCoW\cite{Weng:2011wz}, TimeUserLDA\cite{Diao:2012wj}, and UMass System\cite{Allan:2000wu}, which are mentioned in the Section \ref{sec:relatedWorks}.
 We implement these competing methods based on the open source community versions, e.g.
@@
 %TODO LSH-FSD\cite{Petrovic:2010uj}没有评测FSD的情况，我们也可以提一句，我们不评测FSD，我们只评测检测出的事件是否是真实的事件。
+\hlgreen{TODO: check the number of detected events.}
 \begin{table}[h]
@@
 \scalebox{0.95}{
-    \begin{tabular}{|l|l|l|l|l|}
+    \begin{tabular}{|l|l|l|l|l|l|}
     \hline
-    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
-    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
-    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
-    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
-    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
-    BurstyBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
-    \textsc{LTDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
+    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}F@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
+    LSH & 0.824 & 0.095 & 0.803 & - & 0.302 \\ \hline
+    TimeUserLDA & 0.353 & 0.536 & 0.071 & - & 0.054 \\ \hline
+    Twevent & 0.824 & 0.697 & 0.641 & - & 0.113 \\ \hline
+    EDCoW & 0.412 & 0.756 & 0.119 & - & 0.290 \\ \hline
+    BurstyBTM & 0.647 & 0.809 & 0.170 & - & 0.045 \\ \hline
+    \textsc{TransDetector} & 1.000 & 0.894 & 0.950 & - & 0.042 \\ \hline
     \end{tabular}
@@
 \caption{Overall Performance on Event Detection}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-28}
+\label{my-label}
+\scalebox{0.77}{
+\begin{threeparttable}  
+\begin{tabular}{|c|l|l|c|l|l|l|l|l|l|}
+\hline
+\multirow{2}{*}{Date} & \multirow{2}{*}{Event key words} & \multirow{2}{*}{Representative event tweet} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular}} & \multicolumn{6}{c|}{Methods\tnote{a}} \\ \cline{5-10}
+ &  &  &  & L & TU & TW & E & B & TD \\ \hline
+7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman...
+http://dlvr.it/cLbk8\end{tabular} & 557 & \checkmark &  &  &  &  &  \\ \hline
+7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 & \checkmark &  &  &  &  &  \\ \hline
+7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 47 & \checkmark &  &  &  &  &  \\ \hline
+7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 52 & \checkmark &  &  &  &  &  \\ \hline
+7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 & \checkmark &  &  &  &  &  \\ \hline
+\end{tabular}
+
+\begin{tablenotes}  
+\item[a] L=LSH\cite{Petrovic:2010uj}, TU=TimeUserLDA\cite{Diao:2012wj}, TW=Twevent\cite{Twevent2012}, E=EDCoW\cite{Weng:2011wz}, B=BurstyBTM\cite{Yan:2015wm}, TD=\textsc{TransDetector}.
+\end{tablenotes}  
+\end{threeparttable}  
+}
 \end{table}

### 2016-11-01 paper/lncsFormat.tex
before modifying

@@
 \begin{table}[]
+\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
+\setlength{\belowcaptionskip}{0.cm}
 \centering
-\scalebox{0.76}{
-\begin{tabular}{|c|c|l|c|}
-\hline
-\#group* & \#word*  & words & NPMI\\ \hline
-0 & 6-10 & airlines aviation flying pilot squadron &  0.113\\ \hline
-1 & 11-15 &flights pilots raf airways fighter & 0.155\\ \hline
-2 & 16-20 &boeing runway force crashed flew   & 0.092\\ \hline
-3 & 21-25 &airfield landing passengers plane aerial & 0.179\\ \hline
-4 & 26-30 &bomber radar wing bombers crash & 0.137\\ \hline
-5 & 31-35 &airbus airports operations jet helicopter & 0.189\\ \hline
-6 & 36-40 &squadrons base flown havilland crew & 0.088\\ \hline
-7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159\\ \hline
-8 & 46-50 &planes fly engine takeoff fleet & 0.186\\ \hline
-9 & 51-55 &fuselage helicopters aviator naval aero & 0.157\\ \hline
-10 & 56-60 &glider command training balloon faa & 0.166\\ \hline
-\(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
-18 & 96-100 &scheduled carriers military curtiss biplane &0.131\\ \hline
-19 & 101-105 &accident engines iaf albatross rcaf &0.068\\ \hline
-\end{tabular}
-}
 \caption{Top words' topic coherence of \textit{Aviation}'s history state.
@@
 NPMI is computed on ten words (a combination of words in each row with the five top words).}
+\scalebox{0.76}{
+\begin{tabular}{|c|l|l|l !{\vrule width 1pt} c|l|l|l|}
+\hline
+\multicolumn{4}{|c!{\vrule width 1pt}}{TransDetector} & \multicolumn{4}{c|}{LightLDA}    \\ \hline
+\#group*  & \#words*  & words  & NPMI & \#group* & \#words* & words & NPMI \\ \hline
+0 & 6-10 & airlines aviation flying pilot squadron &  0.113 & 0 & 6-10 & & \\ \hline
+1 & 11-15 &flights pilots raf airways fighter & 0.155 & 1 & 11-15 & & \\ \hline
+2 & 16-20 &boeing runway force crashed flew   & 0.092 & 2 & 16-20 & & \\ \hline
+3 & 21-25 &airfield landing passengers plane aerial & 0.179 & 3 & 21-25 & & \\ \hline
+4 & 26-30 &bomber radar wing bombers crash & 0.137 & 4 & 26-30 & & \\ \hline
+5 & 31-35 &airbus airports operations jet helicopter & 0.189 & 5 & 31-35 & & \\ \hline
+6 & 36-40 &squadrons base flown havilland crew & 0.088 & 6 & 36-40 & & \\ \hline
+7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159 & 7 & 41-45 & & \\ \hline
+8 & 46-50 &planes fly engine takeoff fleet & 0.186 & 8 & 46-50 & & \\ \hline
+9 & 51-55 &fuselage helicopters aviator naval aero & 0.157 & 9 & 51-55 & & \\ \hline
+10 & 56-60 &glider command training balloon faa & 0.166 & 10 & 56-60 & & \\ \hline
+\(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\) & \(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
+18 & 96-100 &scheduled carriers military curtiss biplane &0.131 & 11 & 96-100 & & \\ \hline
+19 & 101-105 &accident engines iaf albatross rcaf &0.068 & 12 & 101-105 & & \\ \hline
+\end{tabular}
+}
 \label{tbl:NPMIDetails}
@@
 \begin{table*}[ht]
+\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
+\setlength{\belowcaptionskip}{0.cm}
 \centering
-\scalebox{0.76}{
+\caption{Category-Level Topics extracted from knowledge base and the corresponding topics on microblog stream learned from CTrans-LDA, taking the categories \textit{Aviation},  \textit{Health}, \textit{Middle East}, \textit{Military}, and \textit{Mobile Phones} as examples.
+The words in \textbf{\textit{bold italic}} font are newly learned on the microblog stream by the transfer learning, which semantic meanings are verified consistent with the categories; while the words in normal font play the role as the bridge in transfer learning, and appear in the both category-level topics in two domains.}
+\scalebox{0.8}{
 \begin{tabular}{|cc|cc|cc|cc|cc|cc|}
@@
 }
-\caption{Category-Level Topics extracted from knowledge base and the corresponding topics on microblog stream learned from CTrans-LDA, taking the categories \textit{Aviation},  \textit{Health}, \textit{Middle East}, \textit{Military}, and \textit{Mobile Phones} as examples.
-The words in \textbf{\textit{bold italic}} font are newly learned on the microblog stream by the transfer learning, which semantic meanings are verified consistent with the categories; while the black words play the role as the bridge in transfer learning, and appear in the both category-level topics in two domains.}
 \label{tbl:historyStates}
@@
 \begin{table}[h]
+\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
+\setlength{\belowcaptionskip}{0.cm}
+\centering
+\caption{Overall Performance on Event Detection}
 \scriptsize
-\centering
 \scalebox{0.95}{
@@
 }
-\caption{Overall Performance on Event Detection}
 \end{table}
@@
 \begin{table}
+\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
+\setlength{\belowcaptionskip}{0.cm}
 \centering

### 2016-11-01 paper/lncsFormat.tex
the table about extraction effects is done

@@
 %TODO 这个table需要增加BTM生成的和aviation最相近的一个topic的情况。
-\hlgreen{TODO: add a new table, containing a topic generated by BTM, which is most similar to the extracted topic from KB.}
+%\hlgreen{TODO: add a new table, containing a topic generated by BTM, which is most similar to the extracted topic from KB.}
 \begin{table}[]
@@
 NPMI is computed on ten words (a combination of words in each row with the five top words).}
-\scalebox{0.76}{
+\scalebox{0.67}{
 \begin{tabular}{|c|l|l|l !{\vrule width 1pt} c|l|l|l|}
@@
 \#group*  & \#words*  & words  & NPMI & \#group* & \#words* & words & NPMI \\ \hline
-0 & 6-10 & airlines aviation flying pilot squadron &  0.113 & 0 & 6-10 & & \\ \hline
-1 & 11-15 &flights pilots raf airways fighter & 0.155 & 1 & 11-15 & & \\ \hline
-2 & 16-20 &boeing runway force crashed flew   & 0.092 & 2 & 16-20 & & \\ \hline
-3 & 21-25 &airfield landing passengers plane aerial & 0.179 & 3 & 21-25 & & \\ \hline
-4 & 26-30 &bomber radar wing bombers crash & 0.137 & 4 & 26-30 & & \\ \hline
-5 & 31-35 &airbus airports operations jet helicopter & 0.189 & 5 & 31-35 & & \\ \hline
-6 & 36-40 &squadrons base flown havilland crew & 0.088 & 6 & 36-40 & & \\ \hline
-7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159 & 7 & 41-45 & & \\ \hline
-8 & 46-50 &planes fly engine takeoff fleet & 0.186 & 8 & 46-50 & & \\ \hline
-9 & 51-55 &fuselage helicopters aviator naval aero & 0.157 & 9 & 51-55 & & \\ \hline
-10 & 56-60 &glider command training balloon faa & 0.166 & 10 & 56-60 & & \\ \hline
+-1 & 1-5 & aircraft air airport flight airline &  & -1 & 1-5 & engine aircraft car air power & \\ \hline
+0 & 6-10 & airlines aviation flying pilot squadron &  0.113 & 0 & 6-10 & design flight model production speed & 0.112\\ \hline
+1 & 11-15 &flights pilots raf airways fighter & 0.155 & 1 & 11-15 &system vehicle cars engines mm & 0.062\\ \hline
+2 & 16-20 &boeing runway force crashed flew   & 0.092 & 2 & 16-20 & fuel vehicles designed models type & 0.072\\ \hline
+3 & 21-25 &airfield landing passengers plane aerial & 0.179 & 3 & 21-25 & version front produced rear electric & 0.035\\ \hline
+4 & 26-30 &bomber radar wing bombers crash & 0.137 & 4 & 26-30 & space control motor standard development & 0.085\\ \hline
+5 & 31-35 &airbus airports operations jet helicopter & 0.189 & 5 & 31-35 & film range light using available & -0.002\\ \hline
+6 & 36-40 &squadrons base flown havilland crew & 0.088 & 6 & 36-40 & wing powered wheel weight launch & 0.087\\ \hline
+7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159 & 7 & 41-45 & developed low test ford cylinder & 0.007\\ \hline
+8 & 46-50 &planes fly engine takeoff fleet & 0.186 & 8 & 46-50 & equipment side pilot hp aviation & 0.091\\ \hline
+9 & 51-55 &fuselage helicopters aviator naval aero & 0.157 & 9 & 51-55 & systems us sold body drive & -0.051\\ \hline
+10 & 56-60 &glider command training balloon faa & 0.166 & 10 & 56-60 & gear introduced class safety seat & 0.069\\ \hline
 \(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\) & \(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
-18 & 96-100 &scheduled carriers military curtiss biplane &0.131 & 11 & 96-100 & & \\ \hline
-19 & 101-105 &accident engines iaf albatross rcaf &0.068 & 12 & 101-105 & & \\ \hline
+18 & 96-100 &scheduled carriers military curtiss biplane &0.131 & 18 & 96-100 & transmission special replaced limited different & 0.059\\ \hline
+19 & 101-105 &accident engines iaf albatross rcaf &0.068 & 19 & 101-105 & features machine nuclear even unit & 0.011\\ \hline
 \end{tabular}

### 2016-11-02 paper/lncsFormat.tex
update the npmi figure

@@
 
+%\usepackage{ulem}%used for uwave
 \usepackage{comment}
@@
 %\begin{comment}% for double blind
-\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.}\and Tengjiao Wang\inst{1}}
+\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Yazhou Wang\inst{1} \and Tengjiao Wang\inst{1}}
 \institute{Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
@@
 NPMI is computed on ten words (a combination of words in each row with the five top words).}
-\scalebox{0.67}{
+\scalebox{0.65}{
 \begin{tabular}{|c|l|l|l !{\vrule width 1pt} c|l|l|l|}
 \hline
-\multicolumn{4}{|c!{\vrule width 1pt}}{TransDetector} & \multicolumn{4}{c|}{LightLDA}    \\ \hline
-\#group*  & \#words*  & words  & NPMI & \#group* & \#words* & words & NPMI \\ \hline
+\multicolumn{4}{|c!{\vrule width 1pt}}{Category-Level Topics extracted from Wikipedia by \textsc{TransDetector}} & \multicolumn{4}{c|}{Topics Learned from Wikipedia by LightLDA}    \\ \hline
+Group ID& \#words*  & words  & NPMI & \#group* & Group ID& words & NPMI \\ \hline
 -1 & 1-5 & aircraft air airport flight airline &  & -1 & 1-5 & engine aircraft car air power & \\ \hline
@@
 %TODO figure2需要增加BTM的情况，以及要用盒形图表示
-\hlgreen{Add a topic of BTM for Figure 2.}
 \begin{figure}
+	\setlength{\abovecaptionskip}{0.cm}
+	\setlength{\belowcaptionskip}{0.cm}
         \centering

### 2016-11-02 boxplot.R

@@ -1,0 +1,13 @@
+library("ggplot2")
+
+df<-read.csv(file="/Users/huangwaleking/git/detector/npmi.csv",header=TRUE)
+npmis<-df %>% filter(group<=50)
+
+npmis$model<-factor(npmis$model,levels=c("Category-Level Topics","Topics learned by LightLDA"))
+npmis$group<-factor(npmis$group)
+
+p <- ggplot(data = npmis, aes(x=group, y=npmiscore)) + 
+  geom_boxplot(aes(fill = model))
+  #geom_jitter(aes(colour = model))
+
+print(p)

### 2016-11-02 npmi.R

@@ -1,0 +1,26 @@
+library("dplyr")
+library("ggplot2")
+library("splines")
+library("gridExtra")
+
+npmis<-read.csv(file="/Users/huangwaleking/git/detector/npmi.csv",header=TRUE)
+
+scores<-npmis %>% filter(group<=50)
+
+scores$model<-factor(scores$model,levels=c("Category-Level Topics","Topics learned by LightLDA"))
+
+p<-ggplot(data=scores,aes(x=group, y=npmiscore,fill=model,color=model)) +
+  geom_point(alpha = 0.7,size=1,aes(shape = model)) +
+  stat_smooth(method = "lm", alpha=0.5,formula= y ~ ns(x,49))+ 
+  labs(y="NPMI",x="Group ID",size=9)+ #set y and x labels
+  coord_cartesian(xlim=c(2, 48))+ #hardcode, don't why these values, but they work
+  theme_bw()+ #remove the grid
+  theme(legend.position=c(0.73,0.59), legend.justification=c(0,0),legend.text=element_text(size=8))+
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.title=element_blank())
+  
+
+
+#print(p)
+pdf("npmi.pdf",height=2.5, width=8)
+grid.arrange(p, nrow=1)
+dev.off()

### 2016-11-02 npmiDf.py

@@ -1,0 +1,55 @@
+import matplotlib.pyplot as plt
+import pandas
+import os
+
+
+def getSeries(filename,topicName,modelName,df):
+    '''
+    :param filename: "/Users/huangwaleking/Downloads/baseline_lda/97_npmi.txt"
+    :param modelName: "LightLDA" or "TransDetector"
+    :param topicName: "46" or "Aviation"
+    :param df: the dataframe to be updated
+    :return: df
+    '''
+    idx = 0
+    for line in open(filename, "r").readlines()[1:]:
+        if line != "\n":
+            splitted = line.split("\t")
+            npmi = float(splitted[1])
+            if(idx<=100):
+                df.loc[len(df)]=[topicName, modelName, idx, npmi]
+            idx += 1
+    return df
+
+
+
+def getDataframe():
+    # dataframe: topic, model, group, score
+    df = pandas.DataFrame(columns=('topic', 'model', 'group', 'npmiscore'))
+
+    #part 1, read in the npmi scores of baseline LDA
+
+    baselineTopicNames=[str(e) for e in [58,86,16,7,46,
+                                         71,31,81,38,29,
+                                         98,21,5,44,28,
+                                         79,97,1,19,22]]
+    for bTopicName in baselineTopicNames:
+        baselineTopicNPMIfile="/Users/huangwaleking/Downloads/baseline_lda/"+bTopicName+"_npmi.txt"
+        df=getSeries(baselineTopicNPMIfile,bTopicName,"Topics learned by LightLDA",df)
+
+    #part 2, read in the npmi scores of topics extracted by TransDetector
+    transDetectorTopicNames = ["Film", "Tennis", "Chemistry", "Golf","Aviation",
+                               "Medicine","Animals","Mobile","Military","Taxation",
+                               "Christians","Harry","Beverages","Foods","Law",
+                               "Mathematics","Photography","Middle","Video","Basketball"]
+    #transDetectorTopicNames = [e.split("_")[0] for e in os.listdir("/Users/huangwaleking/Downloads/nt/")]
+    for transDetectorTopicName in transDetectorTopicNames:
+        transDetectorNPMIfile = "/Users/huangwaleking/Downloads/nt/" + transDetectorTopicName + "_npmi.txt"
+        df = getSeries(transDetectorNPMIfile, transDetectorTopicName, "Category-Level Topics", df)
+
+    return df
+
+
+df=getDataframe()
+print(df)
+df.to_csv("/Users/huangwaleking/git/detector/npmi.csv",header=True,index=True)

### 2016-11-07 paper/lncsFormat.tex
6063 words

--- 2016-11-01 paper/lncsFormat.tex
@@
 
+\usepackage{showframe}%show the margin
+%\usepackage{ulem}%used for uwave
 \usepackage{comment}
@@
 %================================================
-%footnote in table
-%TODO 加和不加这一段对空间的影响很大
-%================================================
+
+%================================
+%中文
+\inputencoding{utf8}
+\newcommand{\chinese}[1]{
+	\begin{CJK*}{UTF8}{gbsn}
+	#1	
+	\end{CJK*}
+}
+%================================
 
@@
 %
-\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+%\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+\title{Leveraging Knowledge Base for Accurate Event Detection on Microblog Stream}
 \titlerunning{Transfer Learning for Accurate Event Detection}
@@
 %\begin{comment}% for double blind
-\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.}\and Tengjiao Wang\inst{1}}
+\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Tengjiao Wang\inst{1} \and Yazhou Wang\inst{1} }
 \institute{Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
 \path{huangwaleking@gmail.com,{pekingchenwei,tjwang}@pku.edu.cn}\\ 
+\path{pkuwangyz@gmail.com}
 }
@@
 But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
-We develop a novel category-pivot transfer learning method \textsc{TransDetector} to deal with the task.  
+We develop a novel category-level transfer learning method \textsc{TransDetector} to deal with the task.  
 \textsc{TransDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and events can be detected more accurately on microblogs with richer semantics.
+%文本短，建模很困难；直接做迁移学习困难，两者的组织结构不同，如何从精心构造的知识库迁移到微博是一个很大的挑战。
+%所以我们提出了Category-Level Transfer Learning ...
 The following contributions are made in \textsc{TransDetector}.
-(1) We propose a structure-guided category-pivot topics extraction method, which exploits the knowledge base's hierarchical structure to extract categories' highly correlated topics. 
-(2) We develop a probabilistic model CTrans-LDA for category-pivot transfer learning, which utilizes the word co-occurrences and transfers the knowledge base's category-pivot topics into microblogs. 
+(1) We propose a structure-guided category-level topics extraction method, which exploits the knowledge base's hierarchical structure to extract categories' highly correlated topics. 
+(2) We develop a probabilistic model CTrans-LDA for category-level transfer learning, which utilizes the word co-occurrences and transfers the knowledge base's category-level topics into microblogs. 
 %Hence, word time series are expanded as category-pivot word time series.
-(3) Events are detected accurately on category-pivot word time series, due to richer semantics and less noise. 
-(4) Experiment verifies the quality of category-pivot topics extracted from knowledge base, and the further study on the benchmark \textit{Edinburgh twitter corpus} validates the effectiveness of our proposed transfer learning method for event detection.
+(3) Events are detected accurately on category-level word time series, due to richer semantics and less noise. 
+(4) Experiment verifies the quality of category-level topics extracted from knowledge base, and the further study on the benchmark \textit{Edinburgh twitter corpus} validates the effectiveness of our proposed transfer learning method for event detection.
 \textsc{TransDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
@@
         }
-        \caption{(a)\textsc{LTDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example.
-\textsc{LTDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.;(b)Illustration on how to initialize history states from Wikipedia, taking \textit{Military} as an example.}
+        \caption{(a)\textsc{TransDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example.
+\textsc{TransDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.;(b)Illustration on how to initialize history states from Wikipedia, taking \textit{Military} as an example.}
 \end{figure}
@@
 %history states衡量一个词在考虑完整历史信息的情况下，对于一个类别的重要程度，例如在military类别下面；从某种程度上讲，history state从knowledge base中抽取了对于该类别的重要特征，有助于我们将它应用到text stream当中。
+\setlength{\textfloatsep}{3pt}% Remove \textfloatsep
 \begin{algorithm}[h]
@@
 \section{Experiments}
-\subsection{Effects of History States and Recent States}
+\subsection{Data Sets}
 In this subsection, we demonstrate the effectiveness of \textit{history states} initialized from knowledge base and \textit{recent states} learned by transfer learning.
@@
 
-\textbf{History States and Recent States.} 
-The history states are initialized on the pre-defined categories on the knowledge base as Algorithm \ref{alg:normalStatesInit}.
-For \textsc{HS-Prior-LDA}, \(K\) is set to be 200, which means \textsc{HS-Prior-LDA} learned 100 history-state-like topics and 100 other topics.
-After cross-validated grid-search, \(\lambda\) is set to be 12.8. The other parameters are set as \(\alpha=0.1\), \(\beta=0.005\).
-We run \textsc{HS-Prior-LDA} window by window on text stream, and learn specific categories' recent states.
+\subsection{Effects of Categroy-Level Topics}
+The category-level topics are initialized on the pre-defined categories from the knowledge base as Algorithm \ref{alg:normalStatesInit}.
 %This process is illustrated by Table \ref{tbl:historyStates}.
 
+\textbf{Evaluation Metrics.}
 We compare the topic coherence of history states with the topics learned from Wikipedia by LDA in terms of NPMI\cite{Rder2015ExploringTS}.
@@
 Due to the limit of NPMI computing module\footnote{\url{https://github.com/AKSW/Palmetto}}, which computes the coherence of up to 10 words each time, we compute NPMI on the combination of top five words with each next five words as Table \ref{tbl:NPMIDetails}.
+
+\textbf{Results.}
 Observe that even for the combination of 96th to 100th words with the top five words in \textit{Aviation}'s history state, NPMI=0.131 shows that the topic coherence still holds well without drifting.
@@
 Since the history states extracted from knowledge base is stable and topic coherence,
+
+%\hlgreen{TODO: add a new table, containing a topic generated by BTM, which is most similar to the extracted topic from KB.}
+\begin{table}[h]
+\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
+\setlength{\belowcaptionskip}{0.cm}
+\centering
+\caption{Top words' topic coherence of \textit{Aviation}'s history state.
+* means the group also contains the five top words \textit{aircraft}, \textit{air}, \textit{airport}, \textit{flight}, and \textit{airline}, but we don't show them in table to save space.
+NPMI is computed on ten words (a combination of words in each row with the five top words).}
+\scalebox{0.65}{
+\begin{tabular}{|c|l|l|l !{\vrule width 1pt} c|l|l|l|}
+\hline
+\multicolumn{4}{|c!{\vrule width 1pt}}{Category-Level Topics extracted from Wikipedia by \textsc{TransDetector}} & \multicolumn{4}{c|}{Topics Learned from Wikipedia by LightLDA}    \\ \hline
+Group ID& \#words*  & words  & NPMI & Group ID& \#words*& words & NPMI \\ \hline
+-1 & 1-5 & aircraft air airport flight airline &  & -1 & 1-5 & engine aircraft car air power & \\ \hline
+0 & 6-10 & airlines aviation flying pilot squadron &  0.113 & 0 & 6-10 & design flight model production speed & 0.112\\ \hline
+1 & 11-15 &flights pilots raf airways fighter & 0.155 & 1 & 11-15 &system vehicle cars engines mm & 0.062\\ \hline
+2 & 16-20 &boeing runway force crashed flew   & 0.092 & 2 & 16-20 & fuel vehicles designed models type & 0.072\\ \hline
+3 & 21-25 &airfield landing passengers plane aerial & 0.179 & 3 & 21-25 & version front produced rear electric & 0.035\\ \hline
+4 & 26-30 &bomber radar wing bombers crash & 0.137 & 4 & 26-30 & space control motor standard development & 0.085\\ \hline
+5 & 31-35 &airbus airports operations jet helicopter & 0.189 & 5 & 31-35 & film range light using available & -0.002\\ \hline
+6 & 36-40 &squadrons base flown havilland crew & 0.088 & 6 & 36-40 & wing powered wheel weight launch & 0.087\\ \hline
+7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159 & 7 & 41-45 & developed low test ford cylinder & 0.007\\ \hline
+8 & 46-50 &planes fly engine takeoff fleet & 0.186 & 8 & 46-50 & equipment side pilot hp aviation & 0.091\\ \hline
+9 & 51-55 &fuselage helicopters aviator naval aero & 0.157 & 9 & 51-55 & systems us sold body drive & -0.051\\ \hline
+10 & 56-60 &glider command training balloon faa & 0.166 & 10 & 56-60 & gear introduced class safety seat & 0.069\\ \hline
+\(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\) & \(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
+18 & 96-100 &scheduled carriers military curtiss biplane &0.131 & 18 & 96-100 & transmission special replaced limited different & 0.059\\ \hline
+19 & 101-105 &accident engines iaf albatross rcaf &0.068 & 19 & 101-105 & features machine nuclear even unit & 0.011\\ \hline
+\end{tabular}
+}
+\label{tbl:NPMIDetails}
+\end{table}
+
+\begin{figure}[h]
+	\setlength{\abovecaptionskip}{0.cm}
+	\setlength{\belowcaptionskip}{0.cm}
+        \centering
+        \includegraphics[width=1.0\columnwidth]{img/NPMI.pdf}
+        \caption{The variable that has the greatest impact on the outcome is its newsworthiness.}
+        \label{fig:NPMI}
+\end{figure}
+
+\textbf{Category-Level Topics Learned from Microblog Stream.}
+For Trans-LDA, \(K\) is set to be 200, which means Trans-LDA learned 100 history-state-like topics and 100 other topics.
+After cross-validated grid-search, \(\lambda\) is set to be 12.8. The other parameters are set as \(\alpha=0.1\), \(\beta=0.005\).
+We run \textsc{Trans-LDA} window by window on text stream, and learn specific categories' topics.
 
@@
 \begin{table}[]
-\scriptsize
+\tiny
 \centering
 \caption{Normal State's cateogries corresponding to the 20-newsgroups corpus, and the F1 score on the classification task}
-\label{my-label}
-\begin{tabular}{|l|l|}
-\hline
-comp.graphics            & Computer graphics      \\ \hline
-comp.os.ms-windows.misc  & Microsoft Windows      \\ \hline
-comp.sys.ibm.pc.hardware & IBM personal computers \\ \hline
-comp.sys.mac.hardware    & Macintosh computers    \\ \hline
-comp.windows.x           & X Window System        \\ \hline
-rec.autos                & Automobiles            \\ \hline
-rec.motorcycles          & Motorcycles            \\ \hline
-rec.sport.baseball       & Baseball               \\ \hline
-rec.sport.hockey         & Hockey                 \\ \hline
-sci.crypt                & Cryptography           \\ \hline
-sci.electronics          & Electronics            \\ \hline
-sci.med                  & Medicine               \\ \hline
-sci.space                & Outer space            \\ \hline
-misc.forsale             & Sales                  \\ \hline
-talk.politics.misc       & Politics               \\ \hline
-talk.politics.guns       & Gun politics          \\ \hline
-talk.politics.mideast    & Middle East           \\ \hline
-talk.religion.misc       & Religion               \\ \hline
-alt.atheism              & Atheism                \\ \hline
-soc.religion.christian   & Christians             \\ \Xhline{3\arrayrulewidth}
-LDA & 0.74\\ \hline
-BOW & 0.84\\ \hline
-doc2vec & 0.73\\ \hline
-NS-Prior-LDA & 0.89\\ \hline
-\end{tabular}
-\end{table}
-\end{comment}
-
-\begin{comment}
-\begin{table}[]
-\tiny
-\centering
-\caption{My caption}
 \label{my-label}
@@
 
-%TODO 这个table需要增加BTM生成的和aviation最相近的一个topic的情况。
-%\hlgreen{TODO: add a new table, containing a topic generated by BTM, which is most similar to the extracted topic from KB.}
-\begin{table}[]
-\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
-\setlength{\belowcaptionskip}{0.cm}
-\centering
-\caption{Top words' topic coherence of \textit{Aviation}'s history state.
-* means the group also contains the five top words \textit{aircraft}, \textit{air}, \textit{airport}, \textit{flight}, and \textit{airline}, but we don't show them in table to save space.
-NPMI is computed on ten words (a combination of words in each row with the five top words).}
-\scalebox{0.67}{
-\begin{tabular}{|c|l|l|l !{\vrule width 1pt} c|l|l|l|}
-\hline
-\multicolumn{4}{|c!{\vrule width 1pt}}{TransDetector} & \multicolumn{4}{c|}{LightLDA}    \\ \hline
-\#group*  & \#words*  & words  & NPMI & \#group* & \#words* & words & NPMI \\ \hline
--1 & 1-5 & aircraft air airport flight airline &  & -1 & 1-5 & engine aircraft car air power & \\ \hline
-0 & 6-10 & airlines aviation flying pilot squadron &  0.113 & 0 & 6-10 & design flight model production speed & 0.112\\ \hline
-1 & 11-15 &flights pilots raf airways fighter & 0.155 & 1 & 11-15 &system vehicle cars engines mm & 0.062\\ \hline
-2 & 16-20 &boeing runway force crashed flew   & 0.092 & 2 & 16-20 & fuel vehicles designed models type & 0.072\\ \hline
-3 & 21-25 &airfield landing passengers plane aerial & 0.179 & 3 & 21-25 & version front produced rear electric & 0.035\\ \hline
-4 & 26-30 &bomber radar wing bombers crash & 0.137 & 4 & 26-30 & space control motor standard development & 0.085\\ \hline
-5 & 31-35 &airbus airports operations jet helicopter & 0.189 & 5 & 31-35 & film range light using available & -0.002\\ \hline
-6 & 36-40 &squadrons base flown havilland crew & 0.088 & 6 & 36-40 & wing powered wheel weight launch & 0.087\\ \hline
-7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159 & 7 & 41-45 & developed low test ford cylinder & 0.007\\ \hline
-8 & 46-50 &planes fly engine takeoff fleet & 0.186 & 8 & 46-50 & equipment side pilot hp aviation & 0.091\\ \hline
-9 & 51-55 &fuselage helicopters aviator naval aero & 0.157 & 9 & 51-55 & systems us sold body drive & -0.051\\ \hline
-10 & 56-60 &glider command training balloon faa & 0.166 & 10 & 56-60 & gear introduced class safety seat & 0.069\\ \hline
-\(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\) & \(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
-18 & 96-100 &scheduled carriers military curtiss biplane &0.131 & 18 & 96-100 & transmission special replaced limited different & 0.059\\ \hline
-19 & 101-105 &accident engines iaf albatross rcaf &0.068 & 19 & 101-105 & features machine nuclear even unit & 0.011\\ \hline
-\end{tabular}
-}
-\label{tbl:NPMIDetails}
-\end{table}
-
-%TODO figure2需要增加BTM的情况，以及要用盒形图表示
-\hlgreen{Add a topic of BTM for Figure 2.}
-\begin{figure}
-        \centering
-        \includegraphics[width=1.0\columnwidth]{img/NPMI.pdf}
-        \caption{Effectiveness of history state in terms of NPMI}
-        \label{fig:NPMI}
-\end{figure}
-
 \begin{comment}
@@
 \centering
-\caption{Category-Level Topics extracted from knowledge base and the corresponding topics on microblog stream learned from CTrans-LDA, taking the categories \textit{Aviation},  \textit{Health}, \textit{Middle East}, \textit{Military}, and \textit{Mobile Phones} as examples.
+\caption{Category-Level Topics extracted from knowledge base and the corresponding topics on microblog stream learned from Trans-LDA, taking the categories \textit{Aviation},  \textit{Health}, \textit{Middle East}, \textit{Military}, and \textit{Mobile Phones} as examples.
 The words in \textbf{\textit{bold italic}} font are newly learned on the microblog stream by the transfer learning, which semantic meanings are verified consistent with the categories; while the words in normal font play the role as the bridge in transfer learning, and appear in the both category-level topics in two domains.}
@@
 %TODO: add the top words in the category-level topic 
-\hlgreen{TODO: add the top words of the category-level topic in each window of microblog stream AFTER Table 2.}
+%\hlgreen{TODO: add the top words of the category-level topic in each window of microblog stream AFTER Table 2.}
 
 %TODO: add the effect of transfer learning by using text classification, compared with fastText and SVM.
-\hlgreen{TODO: add the effect of transfer learning by using text classification, compared with fastText and SVM.}
+%\hlgreen{TODO: add the effect of transfer learning by using text classification, compared with fastText and SVM.}
 \begin{comment}
@@
 \subsection{Effects of Event Detection}
-\textbf{Baselines Methods.} We compare our proposed method against the following methods, Twevent\cite{Twevent2012}, BurstyBTM\cite{Yan:2015wm}, LSH\cite{Petrovic:2010uj}, EDCoW\cite{Weng:2011wz}, TimeUserLDA\cite{Diao:2012wj}, and UMass System\cite{Allan:2000wu}, which are mentioned in the Section \ref{sec:relatedWorks}.
+\textbf{Baselines Methods.} We compare our proposed method against the following methods, Twevent\cite{Twevent2012}, BurstyBTM\cite{Yan:2015wm}, LSH\cite{Petrovic:2010uj}, EDCoW\cite{Weng:2011wz}, and TimeUserLDA\cite{Diao:2012wj}, which are mentioned in the Section \ref{sec:relatedWorks}.
 We implement these competing methods based on the open source community versions, e.g.
@@
 BurstyBTM\footnote{\url{https://github.com/xiaohuiyan/BurstyBTM}}.
+The above methods are set carefully according to the descriptions in the papers.
+More precisely, (1) for LSH, 13 bits per hash table, 20 hash tables are set, and top 500 clusters with high entropy are selected as the event candidates; (2) for Twevent, the number of candidate bursty segments is set to be the square root of the window size, the newsworthiness threshold is set to be 4, and 375 candidate events are detected; (3) for EDCoW, the tunable parameter \(\gamma\) value is set to be 40, and 192 bursty ``phrases" are found for evaluation; (4) for TimeUserLDA, the topic number is set to be 500, and the most 100 bursty topics are selected as candidate events; (5) for BurstyBTM, the topic number is set to be 200, which is also the number of bursty topics in the model.
+The information about the number of events to be evaluated is listed in Table \ref{tbl:overall}, where TransDetector detects 457 events after filtering out too niche events that contain less than 20 tweets.
 
-\textbf{Evaluation Metrics.} 
+\textbf{Benchmarks and Evaluation Metrics.} 
+The evaluation is conducted on two benchmarks.
 The first benchmark on \textit{Edinburgh twitter corpus} contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}}, which all exist in our rebuilt dataset on the \textit{Edinburgh twitter}'s IDs.
@@
 2 Leader Being Killed"}, and popular events such as \textit{``Harry Potter and the Deathly Hallows (Part 2)"}.
-To enlarge the ground truth of realistic events, we manually evaluate the candidate events detected by LTDetector, Twevent, EDCoW, BurstyBTM, and TimeUserLDA, and  use the labeled events as the second benchmark.
-We use precision and recall to evaluate each method on both benchmarks.
+To include these important events and enlarge the ground truth of realistic events pool, we build the second benchmark carefully.
+We manually evaluate the candidate events detected by LSH,  \textsc{TransDetector}, Twevent, EDCoW, BurstyBTM, and TimeUserLDA, with the help of the Wikipedia Current Event Portal\footnote{\url{https://en.wikipedia.org/wiki/Portal:Current_events}} and a local search engine built on Lucene.
+The labeling process generates the Benchmark2, and contains 395 events.
+We use precision and recall to evaluate each method on both benchmarks, and utilize the DERate(Duplicate Event Rate) metric\cite{Twevent2012} to measure the readability of detected events.
+The smaller the metric DERate, the less duplicate events to be filtered out in the application.
 
-%TODO LSH-FSD\cite{Petrovic:2010uj}没有评测FSD的情况，我们也可以提一句，我们不评测FSD，我们只评测检测出的事件是否是真实的事件。
-\hlgreen{TODO: check the number of detected events.}
+%LSH-FSD\cite{Petrovic:2010uj}没有评测FSD的情况，我们也可以提一句，我们不评测FSD，我们只评测检测出的事件是否是真实的事件。
+
+\textbf{Results.}
+%\chinese{我们需要说明几个问题。1，在Benchmark2上，事件有395个；LSH能够检测到3337个聚类簇，判断它是否命中我们采用比较聚类簇中心的方法，}
+In general, our method is better than the existing methods in terms of precision and recall, only sacrificing in the DERate slightly, as shown in Table \ref{tbl:overall}. 
+This is because an event could be grouped into multiple categories (e.g.
+the event ``S\&P downgrade US credit rating", related to the politics category and the financial category simultaneously), but is not a problem as the method \textsc{TrasnDetector} has already achieved the high precision and recall.
+
+Comparing to \textsc{TrasnDetector}, the existing methods are suffered from having to choose between precision and recall, but not both. 
+Taking the method Twevent as an example, which also utilizes the knowledge base for promoting the event detection performance, it has three parameters to trade off.
+The variable that has the greatest impact on the outcome is its newsworthiness.
+
 \begin{table}[h]
@@
 \caption{Overall Performance on Event Detection}
+
 \scriptsize
-\scalebox{0.95}{
-    \begin{tabular}{|l|l|l|l|l|l|}
+\scalebox{1}{
+\begin{threeparttable}
+
+\begin{tabular}{|c|c|c|c|c|c|c|}
     \hline
-    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}F@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate\\(Duplicate \\ Event Rate)\end{tabular} \\ \hline
-    LSH & 0.824 & 0.095 & 0.803 & - & 0.302 \\ \hline
-    TimeUserLDA & 0.353 & 0.536 & 0.071 & - & 0.054 \\ \hline
-    Twevent & 0.824 & 0.697 & 0.641 & - & 0.113 \\ \hline
-    EDCoW & 0.412 & 0.756 & 0.119 & - & 0.290 \\ \hline
-    BurstyBTM & 0.647 & 0.809 & 0.170 & - & 0.045 \\ \hline
-    \textsc{TransDetector} & 1.000 & 0.894 & 0.950 & - & 0.042 \\ \hline
+    Method & \begin{tabular}[c]{@{}c@{}}Number of\\Events to \\ be Evaluated \end{tabular} & \begin{tabular}[c]{@{}c@{}}Recall@ \\ Benchmark1\end{tabular}& \begin{tabular}[c]{@{}c@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}c@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}c@{}}F@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}c@{}}DERate\tnote{a}\ \ (Duplicate\\ Event Rate)@\\ Benchmark2\end{tabular} \\ \hline
+    LSH & 500 & 0.704 & 0.788 & 0.651 & 0.713 & 0.348 \\ \hline
+    TimeUserLDA & 100 & 0.370 & 0.790 & 0.177 & 0.289 & 0.114 \\ \hline
+    Twevent & 375 &  0.741 & 0.808 & 0.658 & 0.725 & 0.142 \\ \hline
+    EDCoW & 192 & 0.556 & 0.714 & 0.258 & 0.379 & 0.255 \\ \hline
+    BurstyBTM & 200 & 0.667 & 0.825 & 0.384 & 0.497 & \textbf{0.079} \\ \hline
+    \textsc{TransDetector} & 457 & \textbf{0.889} & \textbf{0.912} & \textbf{0.876} & \textbf{0.894} & 0.170 \\ \hline
     \end{tabular}
+
+\begin{tablenotes}  
+\item[a] DERate = (the number of duplicate events) / (the total number of detected realistic events)\cite{Twevent2012}
+\end{tablenotes}  
+\end{threeparttable}  
 }
+\label{tbl:overall}
 \end{table}
+
+\begin{figure}[h]
+	\setlength{\abovecaptionskip}{0.cm}
+	\setlength{\belowcaptionskip}{0.cm}
+        \centering
+        \includegraphics[width=1.0\columnwidth]{img/barchartOnBenchmark1.pdf}
+        \caption{The relation between the recall and the event size}
+        \label{fig:Benchmark1}
+\end{figure}
 
@@
 \begin{threeparttable}  
-\begin{tabular}{|c|l|l|c|l|l|l|l|l|l|}
+\begin{tabular}{|c|l|l|c|c|c|c|c|c|c|}
 \hline
@@
 7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman...
-http://dlvr.it/cLbk8\end{tabular} & 557 & \checkmark &  &  &  &  &  \\ \hline
-7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 & \checkmark &  &  &  &  &  \\ \hline
-7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 47 & \checkmark &  &  &  &  &  \\ \hline
-7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 52 & \checkmark &  &  &  &  &  \\ \hline
-7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 & \checkmark &  &  &  &  &  \\ \hline
+http://dlvr.it/cLbk8\end{tabular} & 557 & \checkmark & \checkmark & \checkmark &  &  &  \\ \hline
+7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 & \checkmark & - &  &  &  &  \\ \hline
+7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 47 & \checkmark & - &  &  &  &  \\ \hline
+7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 52 & \checkmark & - &  &  &  &  \\ \hline
+7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 & \checkmark & - &  &  &  &  \\ \hline
 \end{tabular}
@@
 \end{table}
-
-\textbf{Overall Performances.}
-\begin{CJK*}{UTF8}{gbsn}
-    中文范例！超级长的一句中文    中文范例！超级长的一句中文    中文范例！超级长的一句中文    中文范例！超级长的一句中文
-\end{CJK*}
 
@@
 
-\textbf{Discussions.} 
 %An accurate recent states learning leads to accurate event detection.

### 2016-11-07 barplot.R

@@ -1,0 +1,24 @@
+library("ggplot2")
+library("dplyr")
+library("gridExtra")
+
+df<-read.csv(file="/Users/huangwaleking/git/detector/OnBenchmark1.csv",header=TRUE)
+
+df2 <- df %>% group_by(group,method) %>% 
+            summarise(n_detect=sum(detected),n_total=n(),recall=n_detect/n_total)
+
+#order the method
+df2$group<-factor(df2$group,levels=c(">200","(100,200]","(50,100]","[0,50]"))
+df2$method<-factor(df2$method,levels=c("TimeUserLDA","BurstyBTM","EDCoW","LSH","Twevent","TransDetector"))
+
+p <- ggplot(df2, aes(fill=method, y=recall, x=group))+
+      geom_bar(position="dodge",stat = "identity") +
+      scale_fill_manual(values=c("#E5E5E5", "#F1EEF6","#BDC9E1","#74A9CF","#2B8CBE","#045A8D"))+
+      theme_bw()+
+      labs(y="Recall@Benchmark1",x="Group with different event size (number of tweets)",size=9)+ #set y and x labels
+      theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), legend.title=element_blank())
+
+#print(p)  
+pdf("barchartOnBenchmark1.pdf",height=2, width=8)
+grid.arrange(p, nrow=1)
+dev.off()

### 2016-11-07 benchmark1.py

@@ -1,0 +1,26 @@
+import pandas
+
+#old dataframe
+df=pandas.read_csv("/Users/huangwaleking/git/detector/TransDetecotrResult_CSV.csv")
+
+methodColIdx=df.columns.tolist().index("LSH") #the pivot to look for columns that before methods
+
+columnsName=df.columns.tolist()#the column names
+methodsName=columnsName[methodColIdx:]#LSH, TimeUserLDA, ...
+
+columnsNum=len(df.columns)
+rowsNum=len(df)
+
+#new dataframe
+df2=pandas.DataFrame(columns=('eventName', 'date', '#tweets', 'group','detected','method'))
+for row in range(0,rowsNum):
+    for methodName in methodsName:
+        r=df.ix[row, 0:methodColIdx].tolist()
+        r.append(df.ix[row][methodName]) #be careful
+        r.append(methodName)  # be careful
+        df2.loc[len(df2)]=r
+
+print(df2)
+df2.to_csv("/Users/huangwaleking/git/detector/OnBenchmark1.csv",header=True)
+#save csv
+

### 2016-11-07 paper/lncsFormat.tex
6341 words, finish table 4

@@
 
-\usepackage{showframe}%show the margin
+%\usepackage{showframe}%show the margin
 %\usepackage{ulem}%used for uwave
@@
 The graph \(\mathcal{G}_{c,t}\) means the words in \(\mathcal{B}_{c,t}\) are connected if and only if their PMI score in the given time window's microblogs is over 0. 
-
 Given the graph \(\mathcal{G}_{c,t}\), spectral clustering\cite{von2007tutorial} is utilized for exploring the best partition of words. 
@@
 To tackle this problem, we consider the microblog, that contains any pair of category-words in the event phrase, as the event related microblog.
-
 Finally, \textsc{TransDetector} gets the detected events \(\{(\mathcal{C}_{c,t,i},\mathcal{D}_{c,t,i})\}_{i=1}^{|\mathcal{C}_{c,t}|}\), containing the event phrase and the corresponding event related microblogs for the given category and the time window.
@@
 We collected the tweets' contents according to the IDs with the help of Twitter API. 
-Though we cannot get the whole dataset due to the limit of Twitter API, after necessary pre-processing, our rebuilt dataset still contains 36,627,434 tweets, which spans identically from 2011/06/30 to 2011/09/15.
+Though we cannot get the whole dataset due to the limit of Twitter API, after necessary pre-processing, our rebuilt dataset still contains 36,627,434 tweets, which also spans from 2011/06/30 to 2011/09/15.
 More details of the original dataset are described in \cite{petrovic2010edinburgh}.
@@
 The above methods are set carefully according to the descriptions in the papers.
-More precisely, (1) for LSH, 13 bits per hash table, 20 hash tables are set, and top 500 clusters with high entropy are selected as the event candidates; (2) for Twevent, the number of candidate bursty segments is set to be the square root of the window size, the newsworthiness threshold is set to be 4, and 375 candidate events are detected; (3) for EDCoW, the tunable parameter \(\gamma\) value is set to be 40, and 192 bursty ``phrases" are found for evaluation; (4) for TimeUserLDA, the topic number is set to be 500, and the most 100 bursty topics are selected as candidate events; (5) for BurstyBTM, the topic number is set to be 200, which is also the number of bursty topics in the model.
+More precisely, (1) for LSH, 13 bits per hash table, 20 hash tables are set, and top 500 clusters with high entropy are selected as the event candidates; (2) for Twevent, the number of candidate bursty segments is set to be the square root of the window size, the newsworthiness threshold is set to be 4, and 375 candidate events are detected; (3) for EDCoW, the tunable parameter \(\gamma\) value is set to be 40, and 349 bursty ``phrases" are found for evaluation; (4) for TimeUserLDA, the topic number is set to be 500, and the most 100 bursty topics are selected as candidate events; (5) for BurstyBTM, the topic number is set to be 200, which is also the number of bursty topics in the model.
 The information about the number of events to be evaluated is listed in Table \ref{tbl:overall}, where TransDetector detects 457 events after filtering out too niche events that contain less than 20 tweets.
@@
 %\chinese{我们需要说明几个问题。1，在Benchmark2上，事件有395个；LSH能够检测到3337个聚类簇，判断它是否命中我们采用比较聚类簇中心的方法，}
-In general, our method is better than the existing methods in terms of precision and recall, only sacrificing in the DERate slightly, as shown in Table \ref{tbl:overall}. 
+In general, our method is better than the existing methods in terms of the precision and the recall, only sacrificing in the DERate slightly, as shown in Table \ref{tbl:overall}. 
 This is because an event could be grouped into multiple categories (e.g.
-the event ``S\&P downgrade US credit rating", related to the politics category and the financial category simultaneously), but is not a problem as the method \textsc{TrasnDetector} has already achieved the high precision and recall.
+the event \textit{``S\&P downgrade US credit rating"}, related to the politics category and the financial category simultaneously), but is not a problem as the method \textsc{TrasnDetector} has already achieved the high precision and recall.
 
 Comparing to \textsc{TrasnDetector}, the existing methods are suffered from having to choose between precision and recall, but not both. 
-Taking the method Twevent as an example, which also utilizes the knowledge base for promoting the event detection performance, it has three parameters to trade off.
-The variable that has the greatest impact on the outcome is its newsworthiness.
+Taking the method Twevent as an example, which also utilizes the knowledge base for promoting the event detection performance, it has three parameters to trade off, in which the newsworthiness is the most impact one.
+In our experiment, when setting newsworthiness to be 4, Twevent achieves its best performance in terms of F value; lower or higher of value sacrifices the recall or precision. 
+The other methods also meet the same problem of tuning parameters, such as the topic number for TimeUserLDA and BurstyBTM, and the distance threshold for LSH.
 
@@
     Twevent & 375 &  0.741 & 0.808 & 0.658 & 0.725 & 0.142 \\ \hline
-    EDCoW & 192 & 0.556 & 0.714 & 0.258 & 0.379 & 0.255 \\ \hline
+    EDCoW & 349 & 0.556 & 0.748 & 0.511 & 0.607 & 0.226 \\ \hline
     BurstyBTM & 200 & 0.667 & 0.825 & 0.384 & 0.497 & \textbf{0.079} \\ \hline
@@
 
+In order to understand why the existing methods cannot perform well, we dive into the results on the Benchmark1, and show the relation between the recall and the event size (number of microblogs related to the events) in Figure \ref{fig:Benchmark1}.
+The 27 events are divided into 4 groups according to its size. 
+The first group contains 5 very popular events, having more than 200 microblogs, such as \textit{``S\&P downgrade US credit rating''} with 656 microblogs, \textit{``Atlantis shuttle lands''} with 595 microblogs, etc.
+The remaining groups' sizes are listed in the x-axis of Figure \ref{fig:Benchmark1}.
+The fourth group contains 11 not-so-popular events, each containing less than 50 microblogs, such as \textit{``War criminal Goran hadzic arrested"} with only 27 microblogs reported.
+In our experimental settings, the methods all perform well on the very popular events, but perform worse on the not-so-popular events.
+For the not-so-popular events, the underlying bursty pattern is not so obvious that leads many methods to fail to catch the pattern.
+We further find out that the number of microblogs in an event follows a power-law distribution, which similar phenomenon is also reported in \cite{Twevent2012}.
+The widespread existence of such not-so-popular events challenge almost all the existing event detection methods.
+
 \begin{figure}[h]
@@
 \end{figure}
+
+Illustrated in Table \ref{tbl:overall} and Figure \ref{fig:Benchmark1}, \textsc{TransDetector} achieves very good results even on the not-so-popular events.
 
@@
 7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman...
-http://dlvr.it/cLbk8\end{tabular} & 557 & \checkmark & \checkmark & \checkmark &  &  &  \\ \hline
-7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 & \checkmark & - &  &  &  &  \\ \hline
-7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 47 & \checkmark & - &  &  &  &  \\ \hline
-7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 52 & \checkmark & - &  &  &  &  \\ \hline
-7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 & \checkmark & - &  &  &  &  \\ \hline
+http://dlvr.it/cLbk8\end{tabular} & 557 & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\ \hline
+7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 & - & - & \checkmark &  \checkmark & - & \checkmark \\ \hline
+7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 47 & \checkmark & - & \checkmark & \checkmark & - & \checkmark \\ \hline
+7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 52 & - & - & - & - & - & \checkmark \\ \hline
+7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 & - & - & - & - & - & \checkmark \\ \hline
 \end{tabular}

### 2016-11-08 paper/lncsFormat.tex
before remove \begin{comment}

@@
 
-%\usepackage{showframe}%show the margin
+\usepackage{showframe}%show the margin
 %\usepackage{ulem}%used for uwave
@@
 %
-%\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
-\title{Leveraging Knowledge Base for Accurate Event Detection on Microblog Stream}
+\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+%\title{Leveraging Knowledge Base for Accurate Event Detection on Microblog Stream}
 \titlerunning{Transfer Learning for Accurate Event Detection}
@@
 
-Knowledge base can be a good supplementary for event detection on microblog stream.
+Knowledge base can be a good supplementary for event detection on microblog stream to address these challenges.
 Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
@@
 Hood}" is included in the wiki page ``\textit{Ft.
-Hood}", and belongs to the category ``\textit{Military}''.
-By reading these two wiki pages, the model easily understands the example tweet is talking about something related to \textit{Military}.
+Hood}", and belongs to the category ``\textit{Military}'' at a higher conceptual level.
+By regarding these two wiki pages and the word \textit{attack} (also highly related to \textit{Military}), the model easily understands the example tweet is about something related to \textit{Military}.
 In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
 Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
-%拆成两个小图，中间说明这是transfer learning过后的
-\intextsep=3pt plus 3pt minus 1pt
+Taking the below Figure \ref{fig:hood} as an example, the fluctuation of time series of raw word \textit{hood} is not so obvious to reflect the event happened to the military base \textit{Ft. Hood}.
+After referring to the knowledge base and extracting the time series of word \textit{``hood"} about \textit{``Military"}, it's more vivid to detect the event happened on July 28th, 2011.
+
+\intextsep=0pt plus 0pt minus 0pt
 \begin{figure}[h]
+		\setlength{\abovecaptionskip}{0.cm}
+        \setlength{\belowcaptionskip}{0.cm}
         \centering
         \includegraphics[width=1.0\columnwidth]{img/hood.pdf}
-        %\caption{Hood\footnote{\url{https://en.wikipedia.org/wiki/Naser_Jason_Abdo#Arrest}}\footnote{\url{https://en.wikipedia.org/wiki/Fort_Hood#2011_attack_plot}}}
+        \caption{The comparison of the time series between the raw word \textit{hood} and the \textit{Military} related word \textit{hood}, computed on the \textit{Edinburgh twitter corpus}\cite{petrovic2012using}.
+The rise on July 28th, 2011 is corresponding to the event mentioned in \url{https://en.wikipedia.org/wiki/Fort_Hood\#2011_attack_plot}.}
         \label{fig:hood}
@@
 
-But it's non-trivial to conduct transfer learning from knowledge base to microblog stream directly.
+The benefit of enriching the semantics for micorblogs is attractive, but it's non-trivial to transfer the knowledge restored in the knowledge base into microblog stream directly.
 The existing RDF model\cite{klyne2006rdf} lacks an efficient quick mechanism to transfer the knowledge, since it's mainly designed for managing knowledge as tuples on graph.
 And the query on large graph is also very expensive\cite{huang2011scalable}, which is not suitable for the scene of quickly and acuaretely detecting events.
-What most meet the efficiency demand is Twevent\cite{Twevent2012}, but it's limited to filtering out meaningless microblogs by looking up Wikipedia.
-Some event,  which may contains the segments not restored in Wikipedia, may be dropped incorrectly.
+What already most meets the efficiency demand is Twevent\cite{Twevent2012}, but it's limited in filtering out meaningless microblogs by looking up Wikipedia.
+Some event, which contains the segments not restored in Wikipedia, may be dropped by Twevent incorrectly.
 
@@
 In transfer learning, \textit{history states} play an important role at speeding up building the linkage between the word in microblog and the high level concept in knowledge base.
+
+\cite{dai2007transferring}.
 
@@
         \subfigure[]{
-                \includegraphics[width=.42\columnwidth]{img/NSDetectorExample.pdf}
+                \includegraphics[width=.50\columnwidth]{img/NSDetectorExample.pdf}
                 \label{fig:modelDesc}
@@
         \subfigure[]{
-                \includegraphics[width=.42\columnwidth]{img/initializationExample.pdf}
+                \includegraphics[width=.44\columnwidth]{img/initializationExample.pdf}
                 \label{fig:NSinitializaton}
@@
 
-%The reason why this kind methods cannot achieve high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
-%This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision.
-
 \textbf{Knowledge Base} Recently, many general knowledge bases and customized knowledge bases are constructed and utilized for different text mining tasks. 
@@
 
-%近年来，知识图谱也被广泛应用在了文本挖掘领域，TKDE的文章利用wikipedia将
-
-%Although \cite{Wurzer:2015wq} points out that UMass\cite{Allan:2000wu} and its variants\cite{Petrovic:2010uj}\cite{petrovic2012using}\cite{Wurzer:2015wq} are the state-of-art systems on the Event Detection task for the newswire data, these systems still suffers from the lack of accuracy to applied on more general cyberspace data, such as tweets, emails, and reddit posts.
-
-%\textbf{Knowledge Base}. \cite{faralli2015large} propose the Twixonomy Graph.
-
-%Twitter Trending Topic Classification
-%We use PageRank-HITS\cite{Yan:2015wq} algorithm to update score of categories in wikipedia.
-
-%3*4 figures, 0-11 is reorganized in the following order: 0, 1, 4, 5, 8, 9;
-%2, 3, 6, 7, 10, 11;
+\section{Proposed Method}
+In this section, we present a novel category-level transfer learning method for event detection, namely \textsc{TransDetector}. 
+Illustrated in Figure \ref{fig:modelDesc}, \textsc{TransDetector} consists of three parts: (1) extracting category-level topics in knowledge base, (2) transfer learning on category-level topics in microblog stream, (3) detecting events from category-level word time series.
 \begin{comment}
-\begin{figure*}[ht]
-        \centering
-        \label{fig:subfig} %% label for entire figure
-        \subfigure[\((0.25,0.25,0.25)\)]{
-                \label{fig:subfig:a} %% label for first subfigure a
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph0.pdf}
-        }
-        \subfigure[\((0.5,0.5,0.5)\)]{
-                \label{fig:subfig:b} %% label for second subfigure b
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph1.pdf}
-        } 
-        \subfigure[\((0.25,0.25,0.75)\)]{
-                \label{fig:subfig:c} %% label for third subfigure c
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph4.pdf}
-        }
-        \subfigure[\((0.5,0.5,1.5)\)]{
-                \label{fig:subfig:a} %% label for first subfigure d
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph5.pdf}
-        }
-        \subfigure[\((0.25,0.75,0.75)\)]{
-                \label{fig:subfig:d} %% label for third subfigure e
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph8.pdf}
-        }
-        \subfigure[\((0.5,1.5,1.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure f
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph9.pdf}
-        }\hspace{1in}
-        \subfigure[\((1.5,1.5,1.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure g
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph2.pdf}
-        }
-        \subfigure[\((2.5,2.5,2.5)\)]{
-                \label{fig:subfig:a} %% label for first subfigure h
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph3.pdf}
-        }
-        \subfigure[\((1.5,1.5,2.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure i
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph6.pdf}
-        }
-        \subfigure[\((2.5,2.5,3.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure j
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph7.pdf}
-        }
-        \subfigure[\((1.5,2.5,2.5)\)]{
-                \label{fig:subfig:d} %% label for third subfigure k
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph10.pdf}
-        }
-        \subfigure[\((2.5,3.5,3.5)\)]{
-                \label{fig:subfig:a} %% label for first subfigure l
-                \includegraphics[height=2.14cm]{img/croppedDirichletGraph11.pdf}
-        }\hspace{1in}
-        \caption{Illustration of Dirichlet distribution's probabilistic density on the 3-dimensional simplex when given different priors.
-(a,b,g,h) the left four subfigures illustrate the probabilistic density when given the symetric priors for Dirichlet distribution; (c,d,i,j) the central subfigures illustrate the probablistic density given ; (e,f,k,l) }
-\end{figure*}
-\end{comment}
-
-\section{Proposed Method}
 Knowledge base often contains much information about what happened. 
@@
 The following definitions are the concepts used by the transfer learning model \textsc{TransDetector}. 
+\end{comment}
 
@@
 \label{my-label}
-\scalebox{0.77}{
+\scalebox{0.76}{
 \begin{threeparttable}  

### 2016-11-10 paper/lncsFormat.tex
the Figure 4 is colorful

@@
 
-\usepackage{showframe}%show the margin
+\let\proof\relax
+\let\endproof\relax
+\usepackage{amsthm}%used for theorem and definition
+%\usepackage{showframe}%show the margin
 %\usepackage{ulem}%used for uwave
@@
 \inputencoding{utf8}
+
+%================================================
+%Definition
+\newtheorem{thm}{Theorem}
+
+\newtheoremstyle{exampstyle}
+  {0pt} % Space above
+  {0pt} % Space below
+  {} % Body font
+  {} % Indent amount
+  {\bfseries} % Theorem head font
+  {.} % Punctuation after theorem head
+  {.5em} % Space after theorem head
+  {} % Theorem head spec (can be left empty, meaning `normal')
+
+\theoremstyle{exampstyle}
+\newtheorem{rmkWithoutSpacing}[thm]{Definition}
+%================================================
 
@@
 %\title{Leveraging Knowledge Base for Accurate Event Detection on Microblog Stream}
-\titlerunning{Transfer Learning for Accurate Event Detection}
+\titlerunning{\ }
 %构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
 %\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
-%\begin{comment}% for double blind
+\begin{comment}% for double blind
 \author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Tengjiao Wang\inst{1} \and Yazhou Wang\inst{1} }
@@
 }
-%\end{comment}
+\end{comment}
 
@@
 Hood}", and belongs to the category ``\textit{Military}'' at a higher conceptual level.
-By regarding these two wiki pages and the word \textit{attack} (also highly related to \textit{Military}), the model easily understands the example tweet is about something related to \textit{Military}.
-In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
+By regarding these wiki information and the word \textit{attack} (also highly related to \textit{Military}), the model easily understands the example tweet is about something related to \textit{Military}.
+In other words, knowledge base enriches the linkages between words and concepts, and provides more comprehensive context for microblogs.
 Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
 Taking the below Figure \ref{fig:hood} as an example, the fluctuation of time series of raw word \textit{hood} is not so obvious to reflect the event happened to the military base \textit{Ft. Hood}.
-After referring to the knowledge base and extracting the time series of word \textit{``hood"} about \textit{``Military"}, it's more vivid to detect the event happened on July 28th, 2011.
+After transferring the knowledge about \textit{``Military"} into the microblog stream, the time series of word \textit{``hood"} related to \textit{``Military"} is extracted, which is more vivid to detect the event happened on July 28th, 2011.
 
@@
         \caption{The comparison of the time series between the raw word \textit{hood} and the \textit{Military} related word \textit{hood}, computed on the \textit{Edinburgh twitter corpus}\cite{petrovic2012using}.
-The rise on July 28th, 2011 is corresponding to the event mentioned in \url{https://en.wikipedia.org/wiki/Fort_Hood\#2011_attack_plot}.}
+The rise of document frequency on July 28th, 2011 is corresponding to the event mentioned in \url{https://en.wikipedia.org/wiki/Fort_Hood\#2011_attack_plot}.}
         \label{fig:hood}
@@
 The existing RDF model\cite{klyne2006rdf} lacks an efficient quick mechanism to transfer the knowledge, since it's mainly designed for managing knowledge as tuples on graph.
-And the query on large graph is also very expensive\cite{huang2011scalable}, which is not suitable for the scene of quickly and acuaretely detecting events.
-What already most meets the efficiency demand is Twevent\cite{Twevent2012}, but it's limited in filtering out meaningless microblogs by looking up Wikipedia.
-Some event, which contains the segments not restored in Wikipedia, may be dropped by Twevent incorrectly.
+And the query on large graph is also very expensive\cite{huang2011scalable}, which is not suitable for the scene of quickly and accurately detecting events.
+In existing methods, what meets the demand most is Twevent\cite{Twevent2012}, but it's limited in only treating Wikipedia as a looking-up table and may drop some events incorrectly.
 
-In our paper, to balance the performance and the cost of transfer learning, new data structure \textit{KB states} is proposed. 
+In our paper, to balance the performance and the cost of leveraging knowledge base for event detection, we develop a novel category-level transfer learning method, namely \textsc{TransDetector}.
+It consists of three phases: extracting of category-level topics in knowledge base, conducting transfer learning to get category-level topics in microblog stream, and detecting events from category-level word time series, as illustrated in Figure \ref{fig:modelDesc}.
+We explain the main idea of the three parts in \textsc{TransDetector}, and leave more technique details in Section \ref{sec:TransDetector}.
+(1) For the \textbf{extracting} phase, we propose a structural-guided category-level topics extraction method on the knowledge base, . 
 It bases on the following facts. 
-The knowledge base's three fold structure includes the taxonomy graph (\textit{class} \(\rightarrow\) \textit{subclass}), the category-page bipartite graph (\textit{class} \(\rightarrow\) \textit{instance}), and the page-content map (\textit{instance} \(\rightarrow\) \textit{content}) relations in the knowledge base.
+The knowledge base has the three fold hierarchical structure, consisting of the taxonomy graph (\textit{class} \(\rightarrow\) \textit{subclass}), the category-page bipartite graph (\textit{class} \(\rightarrow\) \textit{instance}), and the page-content map (\textit{instance} \(\rightarrow\) \textit{content}), as illustrated in Figure \ref{fig:NSinitializaton}.
 In terms of concept level, the latter part is finer than the former. 
 And the last page-content map goes into the detail at the word level. 
-By considering these three parts together, we can extract a class or category's highly related words (evaluated by chi-square score in Section \ref{subsec:hs_initialization}), and restore them in the newly proposed data structure \textit{history states}.
-In transfer learning, \textit{history states} play an important role at speeding up building the linkage between the word in microblog and the high level concept in knowledge base.
+By considering these three parts together, we can extract a class or category's highly related words, and restore them in \textit{category-level topics in knowledge base}.
+(2) For the \textbf{conducting transfer learning} phase, we propose a novel probabilistic model CTrans-LDA for transferring the knowledge.
+CTrans-LDA works in the bayesian transfer learning way like \cite{dai2007transferring}, by utilizing the extracted \textit{category-level topics in knowledge base} as the informative priors to bridge two data domains.
+After running CTrans-LDA, it labels whether a word in a microblog message should link to a category concept in knowledge base.
+Applying CTrans-LDA on more microblogs, it gets the \textit{category-level topics in microblog stream}.
+(3) For the \textbf{detecting} phase,
 
-\cite{dai2007transferring}.
-
-More than that, we propose a new quick and lightweight probabilistic model KB-Prior-LDA for transfer learning. 
-After deriving KB-Prior-LDA (detailed in Section \ref{subsec:rs_initialization}), it reveals that whether a word in microblog links to a high-level category in knowledge base depends on three factors, the word's score in the category's \textit{KB state}, the linkages of microblogs' other words, the linkages of the word types in the same time window.
-All these statistics are easy to gain, which leads the model efficient. 
-What KB-Prior-LDA learned is summarized as \textit{recent states}, shown in Figure \ref{fig:modelDesc}.
 Since the recent states have filtered out meaningless words, the detected events on recent states is much more accurate than other methods which don't do the transfer learning.
-\textsc{KB-Prior-LDA}, \textit{history states}, and \textit{recent states} forms up our proposed event detection method \textsc{LTDetector}.
+\textsc{CTrans-LDA}, \textit{history states}, and \textit{recent states} forms up our proposed event detection method \textsc{LTDetector}.
 Our experiment on the real dataset \textit{Edinburgh twitter corpus (30 million tweets)} validates the effectiveness of our proposed method \textsc{LTDetector}.
 
+%In transfer learning, \textit{history states} play an important role at speeding up building the linkage between the word in microblog and the high level concept in knowledge base.
+
 \intextsep=5pt plus 3pt minus 1pt
-\begin{figure}[h]
+\begin{figure}
 	\setlength{\abovecaptionskip}{0.cm}
@@
     \label{fig:subfig} %% label for entire figure
-        \subfigure[]{
-                \includegraphics[width=.50\columnwidth]{img/NSDetectorExample.pdf}
+        \subfigure[\textsc{TransDetector}'s Process Flow]{
+                \includegraphics[width=.44\columnwidth]{img/NSDetectorExample.pdf}
                 \label{fig:modelDesc}
@@
         }
-        \subfigure[]{
+        \subfigure[Extracting Category-Level Topics in Knowledge Base]{
                 \includegraphics[width=.44\columnwidth]{img/initializationExample.pdf}
@@
         }
-        \caption{(a)\textsc{TransDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example.
-\textsc{TransDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.;(b)Illustration on how to initialize history states from Wikipedia, taking \textit{Military} as an example.}
+        \caption{(a) \textsc{TransDetector}'s process flow, taking \textit{Military} related events in microblogs as an example.
+\textsc{TransDetector} includes three phases: extracting category-level topics in knowledge base, conducting transfer learning to get category-level topics in microblog stream, and detecting events from category-level word time series; (b) Illustration on how to extract category-level topics in knowledge base via its three fold hierarchical structure, taking \textit{Military} as an example.}
 \end{figure}
 
-%The contribution of this paper is mainly in three aspects.
+To sum up, the contribution of this paper is mainly in four aspects.
+(1) We propose a structure-guided category-level topics extraction method, which exploits the knowledge base's hierarchical structure to extract categories' highly correlated topics. 
+(2) We develop a probabilistic model CTrans-LDA for category-level transfer learning, which utilizes the word co-occurrences and transfers the knowledge base's category-level topics into microblogs. 
+(3) Events are detected accurately on category-level word time series, due to richer semantics and less noise. 
+(4) Experiment verifies the quality of category-level topics extracted from knowledge base, and the further study on the benchmark \textit{Edinburgh twitter corpus} validates the effectiveness of our proposed transfer learning method for event detection.
+
 %(1) We reveal that transfer learning from knowledge base to microblog stream can benefit event detection task.
@@
 \label{sec:relatedWorks}
-\textbf{Event Detection.} According to how much data are used, the approaches are divided into two groups: the detection \textit{without extra information}, and the detection by \textit{leveraging extra information}.
+\textbf{Event Detection.} Based on how much data used, the methods are mainly in two groups, the detection \textit{without extra information} and that by \textit{leveraging extra information}.
 
 Most existing methods are implemented \textit{without extra information}.
-They utilize the bursty pattern in the text stream to detect events, and are carried out by  clustering articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, analyzing word frequencies\cite{Mathioudakis:2010fc,Weng:2011wz}, or finding bursty topics\cite{Diao:2012wj,Yan:2015wm}.
-(1) By clustering articles, UMass\cite{Allan:2000wu}, LSH\cite{Petrovic:2010uj}, k-Term-FSD\cite{Wurzer:2015wq} and other similar methods model the occurred events as clusters of articles, and link the incoming article with an already existed event cluster or label it as the first story of a new event.
+They are mainly carried out by clustering articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, analyzing word frequencies\cite{Mathioudakis:2010fc,Weng:2011wz}, or finding bursty topics\cite{Diao:2012wj,Yan:2015wm} etc.
+(1) By clustering articles, UMass\cite{Allan:2000wu}, LSH\cite{Petrovic:2010uj}, k-Term-FSD\cite{Wurzer:2015wq} and other similar methods model the occurred events as clusters of articles.
 The decision is based on whether the dissimilarity between the incoming article and existed event clusters is over the user-specified threshold. 
-Taking LSH as an example, as \cite{Petrovic:2010uj} discussed, the threshold controls the result: the big one leads to very few and broad clusters, while the small one results in very small and specific clusters.
-Even after carefully set the appropriate threshold, the clusters generated by this kind method are still mixed of events and non-events due to large portion of non-event microblogs, which requires some post-processing methods as the supplement.
-(2) By analyzing word frequencies, TwitterMonitor\cite{Mathioudakis:2010fc} models the bursty words by queueing theory, and EDCoW\cite{Weng:2011wz} exploits wavelet transformation, which converts signal from time domain to time-scale domain, to detect the change point of word signal.
-However they treat the word as the most basic unit in analysis, without regarding how many concepts are represented by the word.
+(2) By analyzing word frequencies, EDCoW\cite{Weng:2011wz} exploits wavelet transformation, which converts signal from time domain to time-scale domain, to detect the change point of word signal. 
+However they treat the word as the most basic unit in analysis, without regarding polysemy words.
 (3) By finding bursty topics via topic modelling, TimeUserLDA\cite{Diao:2012wj}, BurstyBTM\cite{Yan:2015wm} generates detected events.
 TimeUserLDA distinguishes user's long term interests and short term bursty events, and BurstyBTM utilizes the burstiness of biterms as prior knowledge.
-They both need to set the appropriate number of topics to run the topic modelling, and detect the ``large" events that associate with many articles but ignore the ``small" ones. 
+This kind method needs to set the appropriate number of topics, and detects the ``large" events but ignore the ``small" ones. 
 To summarize, due to microblog's short length and high noise, it's not easy to set the directly applicable parameter for existing methods to achieve high precision and high recall simultaneously.
@@
 The second group methods detect events by \textit{leveraging extra information}. 
-\cite{huang2016efficient} incorporates user's and the followees' profiles in microblog platform as the extra information for modeling user's long term interests, and further detects the bursty events which draws the attention of users with different interests.
-However many event detection scenes only provide the microblog stream without user profile information and the following network.
-\cite{osborne2012bieber} compares two time series generated by event-related tweets and corresponding Wikipedia article's page views, and further filter out spurious events of microblogs.
+\cite{huang2016efficient} incorporates user's and the followees' profiles to help to detect the events of public concern. 
+However it's not easy to get this kind contextual information.
+\cite{osborne2012bieber} compares two time series generated by event-related tweets and the corresponding Wikipedia article's page views, and further filter out spurious events of microblogs.
 Twevent \cite{Twevent2012} divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia, then detect the bursty segments and cluster these segments into candidate events for necessary post processings.
-But Twevent is still hampered by the performance of simply clustering the bursty segments shown by \cite{Yan:2015wm}.
-If not limited to microblog stream, many systems also use the extra information for improving event detection.
-\cite{steiner2013mj} utilizes the concurrent wikipedia edit spikes for event detection.
+But as shown in \cite{Yan:2015wm}, Twevent is still hampered by the performance of simply clustering the bursty segments.
+Beyond the scope of microblog stream, \cite{steiner2013mj} utilizes the concurrent wikipedia edit spikes for event detection.
 And \cite{liuleveraging2016} leverages the ACE corpus\cite{doddington2004automatic} and the structure of FrameNet\cite{baker1998berkeley} to improve the event detection within FrameNet, but has not shown how to apply the knowledge base for more general unstructured corpus.
 In a nutshell, existing works are different from ours, as we transfer the category information of knowledge base into microblog's words and get the finer processing objects in event detection, rather than treating the knowledge base as a lookup table or a comparison base.
-%Wikipop\cite{ciglan2010wikipop} uses the statistics of page views on Wikipedia articles to detect the personalized events.
-%\cite{mcminn2013building} leverages LSH, wikipedia to build a large corpus for evaluating event detection on twitter.
-%The unsupervised methods, including UMass\cite{Allan:2000wu} and BurstyBTM\cite{Yan:2015wm}, use \textit{the data within the recent time windows} to help to decide whether the incoming article is related to a new event.
 
-\textbf{Knowledge Base} Recently, many general knowledge bases and customized knowledge bases are constructed and utilized for different text mining tasks. 
+\textbf{Knowledge Base.} Many general knowledge bases and customized knowledge bases are constructed and utilized for different text mining tasks. 
 For example, Probase\cite{wu2012probase} constructs a large general probabilistic \textit{IsA} taxomomy from webpages, and is used for semantic web search, and text classification\cite{wang2014concept}.
@@
 
-\section{Proposed Method}
+\section{\textsc{TransDetector}} 
+\label{sec:TransDetector}
 In this section, we present a novel category-level transfer learning method for event detection, namely \textsc{TransDetector}. 
 Illustrated in Figure \ref{fig:modelDesc}, \textsc{TransDetector} consists of three parts: (1) extracting category-level topics in knowledge base, (2) transfer learning on category-level topics in microblog stream, (3) detecting events from category-level word time series.
+
+\textit{Category-level Topics in Knowledge Base} is a set of tuples extracted from knowledge base, which weighs the importance of given words to the specific category, defined in Definition 1 formally.
+Taking the \textit{military} category in Figure \ref{fig:modelDesc} as an example, the history state of \textit{military} contain the words \textit{army}, \textit{military}, and \textit{shootings} etc.
+
 \begin{comment}
@@
 It extracts category-related words from incoming text stream, for each time window.
-Still taking the \textit{military} category in  Figure \ref{fig:modelDesc} as an example, based on extracted history states, our proposed probabilistic continuous learning model \textsc{HS-Prior-LDA} can recognize the words \textit{libyan} and \textit{rebel} in the time window 2011-07-28 in the text stream are related to the category \textit{military}.
+Still taking the \textit{military} category in  Figure \ref{fig:modelDesc} as an example, based on extracted history states, our proposed probabilistic continuous learning model CTrans-LDA can recognize the words \textit{libyan} and \textit{rebel} in the time window 2011-07-28 in the text stream are related to the category \textit{military}.
 Furthermore the time series analysis on the neighbouring recent states can recognize the set of events' candidate words, and finally detects the events in the text stream. 
@@
 
-After processing each time window's data, the words in microblogs can be enriched semantically with knowledge base.
-In this way, the transfer learning model provides richer semantics and less noise for microblog stream, which promotes the accuracy of event detection significantly. 
-The following definitions are the concepts used by the transfer learning model \textsc{TransDetector}. 
 \end{comment}
 
-\begin{rmk}[History State] 
-The history state of the specific category is defined by a set of tuples, in which the first element is the word \(w^{(c)}_i\) related to the category \(c\), and the second element is the chi-square score \(chi(c,w^{(c)}_{i})\) under the category \(c\).
-And we denote the history states of category \(c\) as \(\bm{h}_c=\{<w^{(c)}_i,chi(c,w^{(c)}_{i})>\}_{i=1,...,N_c}\).
-\end{rmk}
+\begin{rmkWithoutSpacing}[\textbf{Category-level Topics in Knowledge Base}] 
+Given category \(c\), the category level topic in knowledge base is defined by a set of tuples, in which the first element is the word \(w^{(c)}_i\) related to the category \(c\), and the second element is the chi-square score \(chi(c,w^{(c)}_{i})\) under the category \(c\).
+And we denote \(c\)'s category-level topic in knowledge base as \(\bm{h}_c=\{<w^{(c)}_i,chi(c,w^{(c)}_{i})>\}_{i=1,...,N_c}\).
+\end{rmkWithoutSpacing}
 
-\begin{rmk}[Recent State] 
-The recent state at time \(t\) of the specific category \(c\) is defined by a set of tuples, and denoted as \(\bm{r}_{c,t}=\{<w^{(c)}_i,n(c,t,w^{(c)}_{i})>\}_{i=1,...,N_c}\), in which word \(w^{(c)}_{i}\) is related to the category \(c\), and \(n(c,t,w^{(c)}_{i})\) is its document frequency in the time window \(t\).
-\end{rmk}
+\begin{rmkWithoutSpacing}[\textbf{Category-level Topics in Microblog Stream}] 
+Given category \(c\), the category level topic in microblog stream at time \(t\) is defined by a set of tuples, and denoted as \(\bm{r}_{c,t}=\{<w^{(c)}_i,n(c,t,w^{(c)}_{i})>\}_{i=1,...,N_c}\), in which word \(w^{(c)}_{i}\) is related to the category \(c\), and \(n(c,t,w^{(c)}_{i})\) is its document frequency in the time window \(t\).
+\end{rmkWithoutSpacing}
 
-\begin{rmk}[The Set of Events' Candidate Words] 
-The set of events' candidate words \(\mathcal{B}_{c,t}\) are defined by the bursty words in recent state \(\bm{r}_{c,t}\).
-\end{rmk}
+\begin{rmkWithoutSpacing}[\textbf{Category-level Word Time Series}] 
+Given category \(c\) and word \(w\), the category level word time series is a list extracted from \(\{\bm{r}_{c,t}\}_{t=1}^{T}\), and denoted as \(\{n(c,t,w^{(c)}_{i})\}_{t=1}^{T}\).
+\end{rmkWithoutSpacing}
 
-\begin{rmk}[Event Phrase] 
+\begin{rmkWithoutSpacing}[\textbf{The Set of Events' Candidate Words}] 
+The set of events' candidate words \(\mathcal{B}_{c,t}\) are groups of the bursty words in \(\bm{r}_{c,t}\).
+\end{rmkWithoutSpacing}
+
+\begin{rmkWithoutSpacing}[Event Phrase] 
 Event phrase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occurred in the set of events' candidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happened in time \(t\) under the category \(c\).
-\end{rmk}
+\end{rmkWithoutSpacing}
 
-\begin{rmk}[Event Related Microblogs] Event related microblogs \(\mathcal{D}_{c,t,i}\) are articles that relate to the \(i\)-th event in time \(t\) under the category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
-\end{rmk}
+\begin{rmkWithoutSpacing}[Event Related Microblogs] Event related microblogs \(\mathcal{D}_{c,t,i}\) are articles relating to the \(i\)-th event in time \(t\) of category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
+\end{rmkWithoutSpacing}
 
@@
 And section \ref{subsec:detection} interprets the high accuracy event detection based on the processed recent states.
-\begin{comment}
-\begin{table}
-\scriptsize
-\caption{Notations used by \textsc{NSDetector}}
-\label{tbl:notations}
-\begin{tabular}{|c|p{0.06\columnwidth}|p{0.66\columnwidth}|} \hline
-%first part: normalization initialization
-\multirow{5}{0.13\columnwidth}{History States' Initialization} & \(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \cline{2-3}
-& \(G^{(1)}\) & Category-Page Bipartite Graph in Knowledge Base\\ \cline{2-3}
-& \(G^{(2)}\) & Page-Content Map in Knowledge Base\\ \cline{2-3}
-& \(c\) & topic related category node in \(G^{(0)}\), \(G^{(1)}\) \\ \cline{2-3}
-& \(K_{\bm{KB}}\) & number of pre-defined topics in Knowledge Base \\ \cline{2-3}
-& \(h_{c,w}\) & word \(w\)'s history state (chi-square score) in category \(c\) \\ \hline
-%second part: normalization maintenance
-\multirow{4}{0.13\columnwidth}{Normal States Maintenance} & \(\lambda\) & normal state weight in  NS-Prior-LDA\\ \cline{2-3}
-& \(\tau_{c,w}\) & word \(w\)'s prior knowledge confidence for topic \(c\) in NS-Prior-LDA\\ \cline{2-3}
-& \(S_c\) & topic \(c\)'s all normal states related words \\ \cline{2-3}
-& \(K\) & number of topics in NS-Prior-LDA such as \(K>K_{\bm{KB}}\)\\ \hline
-%third part: event detection
-\multirow{5}{0.13\columnwidth}{Event Detection} & \(\mathcal{B}_{c, t}\)  & event words set detected from topic \(c\) at time \(t\)  \\ \cline{2-3}
-& \(\mathcal{G}_{c, t}\)  & hot word graph constructed from \(\mathcal{B}_{c, t}\) \\ \cline{2-3}
-& \(\mathcal{C}_{c,t,i}\) & event \(i\)-th related words in topic \(c\) at time \(t\) \\ \cline{2-3}
-& \(\mathcal{D}_{c,t,i}\) & event \(i\)-th related articles in topic \(c\) at time \(t\) \\ \cline{2-3}
-& \(\rho\) & density threshold for the sub-graph constructed by event words  \\ \hline
-
-\end{tabular}
-\label{symbolsInModel}
-\end{table}
-\end{comment}
 
@@
 \label{subsec:rs_initialization}
-In this subsection, we describe how the proposed probabilistic model \textsc{HS-Prior-LDA} utilizes the history states to learn the recent states from text stream.
+In this subsection, we describe how the proposed probabilistic model CTrans-LDA utilizes the history states to learn the recent states from text stream.
 
-There are two facts inspiring \textsc{HS-Prior-LDA}. 
+There are two facts inspiring CTrans-LDA. 
 (1) The topics in the document may contain history-state-like topics. 
@@
 
-The generative process of \textsc{HS-Prior-LDA} can be described as follows.
-
-\begin{enumerate}[itemsep=0mm]
+The generative process of CTrans-LDA can be described as follows.
+\begin{enumerate}[topsep=0pt,itemsep=0mm]
 \item Draw corpus prior distribution \(\bm{m} \sim Dir(\alpha \bm{u})\), where \(\bm{u}\) is the uniform distribution.
@@
 
-In the above generative process, the line 2(a) is the key point to distinguish \textsc{HS-Prior-LDA} from LDA\cite{blei2003latent}, where \(\bm{\tau}_k\) is defined by Equation(\ref{eq:wikiPrior}).
+In the above generative process, the line 2(a) is the key point to distinguish CTrans-LDA from LDA\cite{blei2003latent}, where \(\bm{\tau}_k\) is defined by Equation(\ref{eq:wikiPrior}).
 \(K_{KB}\) is the number of pre-defined history-state-like topics, and \(S_k\) is the set of words appeared in the \(k\)-th topic's history state.
@@
 
+\setlength{\abovedisplayskip}{0pt}
+\setlength{\belowdisplayskip}{0pt}
 \begin{scriptsize}
@@
 
-\begin{comment}
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.75\columnwidth]{model/lda_tikz.pdf}
-    \caption{Probabilistic model for training normal states by using history information.}
-    %The convolution neural network for extracting character-level representations of words. Dashed arrows indicate a dropout layer applied before character embeddings are input to CNN.}
-    \label{fig:NS-Prior-LDA}
-\end{figure}
-\end{comment}
-
-To solve \textsc{HS-Prior-LDA}, the gibbs sampling is adopted to determine the hidden variable \(z_{dn}\) and the model parameter \(\phi_k\).
-In the initialization phase of Gibbs sampling for \textsc{HS-Prior-LDA}, the hidden variable \(z_{dn}\) is initialized to topic \(k\) with probability \(\hat{q}_{k|v}\) as Equation (\ref{eq:initProbability}).
-For the word \(v\) that belongs to any history state, \(\hat{q}_{k|v}\) is proportional to its importance in the history state \(\tau_{kv}\) as Eq\ref{eq:initProbability}(a). 
-For the new word \(v\) in text stream, \(\hat{q}_{k|v}\) is   set uniformly \(1/(K-K_{\bm{KB}})\) on the other topics as Eq\ref{eq:initProbability}(b,c). 
+To solve CTrans-LDA, the gibbs sampling is adopted to determine the hidden variable \(z_{dn}\) and the model parameter \(\phi_k\).
+In the initialization phase of Gibbs sampling for CTrans-LDA, the hidden variable \(z_{dn}\) is initialized to topic \(k\) with probability \(\hat{q}_{k|v}\) as Equation (\ref{eq:initProbability}).
+For the word \(v\) that belongs to any history state, \(\hat{q}_{k|v}\) is proportional to its importance in the history state \(\tau_{kv}\) as Equation \ref{eq:initProbability}(a). 
+For the new word \(v\) in text stream, \(\hat{q}_{k|v}\) is   set uniformly \(1/(K-K_{\bm{KB}})\) on the other topics as Equation \ref{eq:initProbability}(b,c). 
 The initialization makes sure that the learned topics are aligned to the pre-defined history states.
+\setlength{\abovedisplayskip}{1pt}
+\setlength{\belowdisplayskip}{1pt}
 \begin{scriptsize} 
@@
 The sampling process uses the conditional probability \(p(z_{dn}=k|.)\propto (n^{(d)}_{dk}+\alpha m_k)(n^{(w)}_{kv}+\tau_{kv}+\beta)/(n^{(w)}_{k,.}+\tau_{k,.}+V\beta)\), where \(n^{(d)}_{dk}\) is the number of words in document \(d\) assigned to topic \(k\), and \(n^{(w)}_{kv}\) is the times of word \(v\) assigned to topic \(k\).
-We also optimize \(\alpha \bm{m}\) for promoting \textsc{HS-Prior-LDA}'s fitting to documents according to \cite{wallach2008structured}\footnote{\url{https://github.com/mimno/Mallet/blob/master/src/cc/mallet/types/Dirichlet.java}}.\begin{comment}
-\begin{equation}
-\label{eq:KBPriorLDAgibbs}
-\begin{aligned}
-&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha\bm{m},\beta,\tau)\\
-&\ \ \propto (n^{(d)}_{dk}+\alpha m_k)\frac{n^{(w)}_{kv}+\tau_{kv}+\beta}{n^{(w)}_{k,.}+\tau_{k,.}+V\beta}
-\end{aligned}
-\end{equation}
-\end{comment}
+We set \(\alpha=0.1\) and \(\beta=0.01\) according to the suggestion by \cite{tang2014understanding}.
 
-\begin{comment}
-\begin{scriptsize}
-\begin{equation}
-\label{eq:KBPriorLDAgibbs}
-\begin{aligned}
-&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha\bm{m},\beta,\tau)\\
-&\ \ \propto (n^{(d)}_{dk}+\alpha m_k)\frac{n^{(w)}_{kv}+\tau_{kv}+\beta}{n^{(w)}_{k,.}+\tau_{k,.}+V\beta}
-\end{aligned}
-\end{equation}
-\end{scriptsize}
-\end{comment}
-
-\begin{comment}
-\begin{algorithm}
-\scriptsize
-\caption{NS-Prior-LDA Learning Algorithm}
-\label{alg:gibbsSamplingKBPriorLDA}
-\KwIn{Documents \(\mathcal{D}\) (a.k.a., \(\bm{w_{1:D}}\)), and normal states \(\bm{f}_{1:K_{\bm{KB}}}\)}
-\KwOut{The sufficient statistics \(\bm{n^{(d)}}\), \(\bm{n^{(w)}}\)}
-\tcc{Initialization of NS-Prior-LDA}
-\For{\(d=1:D\)}{
-    \For{\(n=1:N_d\)}{
-        \(v=w_{dn}\), sample \(z_{dn}=k\) as Eq(\ref{eq:wikiPrior})(\ref{eq:initProbability}).\\
-        Update the sufficient statistics \(n^{(d)}_{d,k}\), \(n^{(w)}_{k,v}\).\\
-            }
-        }
-\For{\(i= 1:I\)}{
-    \tcc{E-Step of NS-Prior-LDA}
-    \For{\(i=1:I_E\)}{
-        \For{\(d=1:D\)}{
-            \For{\(n=1:N_d\)}{
-                Set \(v=w_{dn}\), and reset the sufficient statistics \(n^{(d)}_{d,z_{dn}}\), \(n^{(w)}_{z_{dn},v}\).\\
-                Resample \(z_{dn}=k\) as Eq(\ref{eq:wikiPrior})(\ref{eq:KBPriorLDAgibbs}).\\
-                Update the sufficient statistics \(n^{(d)}_{d,k}\), \(n^{(w)}_{k,v}\).\\
-            }
-        }
-    }
-    \tcc{M-Step of NS-Prior-LDA}
-    Optimize \(\alpha \bm{m}\) by the fixed-point iteration\cite{wallach2008structured}. 
-}
-\Return{\(\bm{n^{(w)}}\)}
-\end{algorithm}
-\end{comment}
-
-After Gibbs sampling on discrete time windows, \textsc{HS-Prior-LDA} learned all hidden topics of words in microblog stream.
+After Gibbs sampling on discrete time windows, CTrans-LDA learned all hidden topics of words in microblog stream.
 And for a specific word type \(w\) and its history-state-like topic assignment \(c\) in time window \(t\), its document frequency is counted as \(n(c,t,w^{(c)})\), which is the element of category \(c\)'s \(t\)-th recent state.
@@
 
-\subsection{Detecting Events from Recent States}
+\subsection{Detecting Events from Category-Level Word Time Series}
 \label{subsec:detection}
-After transfer learning, events are detected accurately because the word time series is refined to finer grain as multiple corresponding (word, category) time series, and the bursty pattern is better exposed.
-Taking the word \textit{hood} as an example, it belongs to the category \textit{Military} when it appeared in \textit{Ft Hood}, a US military establishment located in Texas.
-As shown in Figure \ref{fig:hood}, the bursty pattern of \textit{hood} is clearly exposed after distinguishing its \textit{Military} time series from the raw one.
-%Therefore, the processing on each category's accurate stream states leads to the accurate event detection.
-
-Given (word, category) time series and microblogs in a time window, we take the detection in	 three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) retrieving event related microblogs.
+After transfer learning, it's much easier to detect the event from category-level word time series, which is shown in Figure \ref{fig:hood}.
+We take the detection in three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; and (3) retrieving event related microblogs.
 Note that these sub-phases are also available for the common text stream, but they performs better when words are enriched by category concepts of knowledge base.
@@
 For a word \(w\) and a category \(c\), on its time series \(\{n(c,t,w^{(c)})\}_{t=1}^{T}\), many bursty detection methods can be applied to check if the word \(w\) is bursty in category \(c\) by given time \(t\).
-We assume the document frequency of \(w^{(c)}\) follows a poisson distribution, which is also used in \cite{Diao:2012wj}.
+In our paper, we assume the document frequency of \(w^{(c)}\) follows a poisson distribution, which is also used in \cite{Diao:2012wj}.
 And the document frequency of nonbursting \(w^{(c)}\) has the possison distribution with the parameter \(\lambda=\mu_0\); while the bursting one with the parameter \(4\mu_0\) means the document frequency \(n(c,t,w^{(c)})\) is much higher when bursting.
@@
 
-In order to group the bursty words together, we  construct the directed weighted graph \(\mathcal{G}_{c,t}=(\mathcal{B}_{c,t},\mathcal{E}_{c,t},\mathcal{W}_{c,t})\), where \(\mathcal{E}_{c,t}=\{(a,b)|a \in \mathcal{B}_{c,t}, b \in \mathcal{B}_{c,t}, PMI(a,b)>0 \}\), and \(\mathcal{W}_{c,t}\) gives the PMI scores on the edges.
+To group the bursty words together, we  construct the directed weighted graph \(\mathcal{G}_{c,t}=(\mathcal{B}_{c,t},\mathcal{E}_{c,t},\mathcal{W}_{c,t})\), where \(\mathcal{E}_{c,t}=\{(a,b)|a \in \mathcal{B}_{c,t}, b \in \mathcal{B}_{c,t}, PMI(a,b)>0 \}\), and \(\mathcal{W}_{c,t}\) gives the PMI scores on the edges.
 The graph \(\mathcal{G}_{c,t}\) means the words in \(\mathcal{B}_{c,t}\) are connected if and only if their PMI score in the given time window's microblogs is over 0. 
-Given the graph \(\mathcal{G}_{c,t}\), spectral clustering\cite{von2007tutorial} is utilized for exploring the best partition of words. 
+Given the graph \(\mathcal{G}_{c,t}\), the spectral clustering\cite{von2007tutorial} is utilized for exploring the best partition of words. 
 To get the optimum cluster number, we use the graph density as the criteria.
-The graph density is the ratio of the number of edges to that of complete graph (the graph with all possible edges), and in practice all the sub-graphs in \(\mathcal{G}_{c,t}\) should have the densities over an empirical threshold.
-And the empirical threshold is set to 0.6 in our setting.
-We run the spectral clustering with cluster number from 1 to \(|\mathcal{B}_{c,t}|\), and stop when all the resulting sub-graphs satisfy the criteria that the density is over the given threshold. 
+The graph density is the ratio of the number of edges to that of complete graph (the graph with all possible edges). 
+We search the best cluster number from 1 to \(|\mathcal{B}_{c,t}|\), and stop when all the resulting sub-graphs satisfy the criteria that the density is over the threshold, which is set to 0.6 empirically.
 In this way, the generated event phrase combines the co-occurred bursty words and excludes the unrelated.
@@
 \section{Experiments}
-\subsection{Data Sets}
+%\subsection{Data Sets}
 In this subsection, we demonstrate the effectiveness of \textit{history states} initialized from knowledge base and \textit{recent states} learned by transfer learning.
@@
 \scalebox{0.65}{
-\begin{tabular}{|c|l|l|l !{\vrule width 1pt} c|l|l|l|}
+\begin{tabular}{|c|l|l|c !{\vrule width 1pt} c|l|l|c|}
 \hline
@@
 Group ID& \#words*  & words  & NPMI & Group ID& \#words*& words & NPMI \\ \hline
--1 & 1-5 & aircraft air airport flight airline &  & -1 & 1-5 & engine aircraft car air power & \\ \hline
+- & 1-5 & aircraft air airport flight airline &-& - & 1-5 & engine aircraft car air power &-\\ \hline
 0 & 6-10 & airlines aviation flying pilot squadron &  0.113 & 0 & 6-10 & design flight model production speed & 0.112\\ \hline
@@
 Illustrated in Table \ref{tbl:overall} and Figure \ref{fig:Benchmark1}, \textsc{TransDetector} achieves very good results even on the not-so-popular events. 
+\hlgreen{To check} 
+After processing each time window's data, the words in microblogs can be enriched semantically with knowledge base.
+In this way, the transfer learning model provides richer semantics and less noise for microblog stream, which promotes the accuracy of event detection significantly. 
+The following definitions are the concepts used by the transfer learning model \textsc{TransDetector}. 
+\hlgreen{To Check}
+After transfer learning, events are detected accurately because the word time series is refined to finer grain as multiple corresponding (word, category) time series, and the bursty pattern is better exposed.
+Taking the word \textit{hood} as an example, it belongs to the category \textit{Military} when it appeared in \textit{Ft Hood}, a US military establishment located in Texas.
+\hlgreen{To Check}
+As shown in Figure \ref{fig:hood}, the bursty pattern of \textit{hood} is clearly exposed after distinguishing its \textit{Military} time series from the raw one.
+%Therefore, the processing on each category's accurate stream states leads to the accurate event detection.
 
@@
 \end{table}
-
-\begin{comment}
-Table 1 reports the number of events
-detected, the precision and recall, of the three methods respectively.
-The results of EDCoW are reproduced from [21]9
-. Shown in the
-table, our proposed method Twevent yields the best precision of
-86.1\% which is significantly larger than the precisions achieved
-by EDCoW and Tweventu. Observe that our method Twevent detects
-101 events with a recall of 75 realistic events. On the same
-dataset, EDCoW detects 21 events in total with 13 realistic events.
-Tweventu yields a slighter worse precision than EDCoW (75.3%
-vs 76.2\%) but detects the largest number of realistic events. In
-terms of DERate, Twevent achieves the lowest rate despite that our
-method detects much more events than EDCoW (101 vs 21). On
-the other hand, we observe that Tweventu delivers the worst DERate,
-more than double of Twevent (41\% vs 16.0\%). That is, the unigrams
-about the same event are clustered into two or more events.
-Because a tweet segment usually conveys very specific information,
-the tweets containing the tweet segment are all about the same
-topic (e.g., the event). Two tweet segments about the same event
-are therefore have higher chance to be clustered together.
-\end{comment}
 

### 2016-11-10 barplot.R

@@ -13,7 +13,8 @@ df2$method<-factor(df2$method,levels=c("TimeUserLDA","BurstyBTM","EDCoW","LSH","
 
 p <- ggplot(df2, aes(fill=method, y=recall, x=group))+
       geom_bar(position="dodge",stat = "identity") +
-      scale_fill_manual(values=c("#E5E5E5", "#F1EEF6","#BDC9E1","#74A9CF","#2B8CBE","#045A8D"))+
+      #scale_fill_manual(values=c("#E5E5E5", "#F1EEF6","#BDC9E1","#74A9CF","#2B8CBE","#045A8D"))+ #dark
+      scale_fill_manual(values=c("#EE9336", "#EED757","#D4EE3D","#B9EE91","#79DCD1","#4CB3EE"))+
       theme_bw()+
       labs(y="Recall@Benchmark1",x="Group with different event size (number of tweets)",size=9)+ #set y and x labels
       theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), legend.title=element_blank())

### 2016-11-10 hood/hood_word_graph.py

@@ -46,20 +46,22 @@ if __name__ == '__main__':
     parsedDayNum34= parsedDayNum34.reindex(idx, fill_value=0)  # set missing
 
     parsedDayNum.loc[parsedDayNum.index=="2011-07-28"]=98
-    print(parsedDayNum34)
 
     #combine two time series, refer to http://pandas.pydata.org/pandas-docs/stable/merging.html
     hoodSeries=pd.concat([parsedDayNum,parsedDayNum34],axis=1)
     #rename the columns
     hoodSeries.columns = ['hood', 'hood (military)']
 
-    #ac.plot_date(hoodSeries,'v-')
     fig,ax=plt.subplots()
     #set figure size
     fig.set_size_inches(8,2)
     #plot
     #ax.plot_date(idx.to_pydatetime(),hoodSeries,'v-')
-    ax.plot(hoodSeries,'v-')
+    #todo, set different lengeds
+    print(hoodSeries.ix[:,1])
+    #ax.plot(hoodSeries,'v-')
+    ax.plot(hoodSeries.ix[:,0],'v-')
+    ax.plot(hoodSeries.ix[:,1],'o--')
     #set x axis
     ax.xaxis.set_minor_locator(dates.DayLocator(interval=1))
     ax.xaxis.set_minor_formatter(dates.DateFormatter('%d'))

### 2016-11-10 paper/lncsFormat.tex
figures' colors done

@@
 \(K_{KB}\) is the number of pre-defined history-state-like topics, and \(S_k\) is the set of words appeared in the \(k\)-th topic's history state.
-As \cite{wallach2008structured} mentioned that the asymmetric prior distribution can significantly improve the quality of topic modelling, \(\bm{\phi_k} \sim Dir(\bm{\beta}+ \bm{\tau_k})\) incorporates history state into the asymmetric prior of the word distribution on topic.
+As \cite{wallach2008structured} mentioned that the asymmetric prior distribution can significantly improve the quality of topic modelling, \(\bm{\phi_k} \sim Dir(\bm{\beta}+ \bm{\tau_k})\) incorporates \textit{category-level topics in knowledge base} into the asymmetric prior of the word distribution on topic.
 The effect of \(\bm{\tau_k}\) is obvious, e.g., \(\tau_{Military,army}/\tau_{Military,basketball}=203\) leads to that topic \textit{Military} prefers to contain the word \textit{army} other than \textit{basketball}.

### 2016-11-10 barplot.R

@@ -14,7 +14,8 @@ df2$method<-factor(df2$method,levels=c("TimeUserLDA","BurstyBTM","EDCoW","LSH","
 p <- ggplot(df2, aes(fill=method, y=recall, x=group))+
       geom_bar(position="dodge",stat = "identity") +
       #scale_fill_manual(values=c("#E5E5E5", "#F1EEF6","#BDC9E1","#74A9CF","#2B8CBE","#045A8D"))+ #dark
-      scale_fill_manual(values=c("#EE9336", "#EED757","#D4EE3D","#B9EE91","#79DCD1","#4CB3EE"))+
+      #scale_fill_manual(values=c("#EE9336", "#EED757","#D4EE3D","#B9EE91","#79DCD1","#4CB3EE"))+ #colorful
+      scale_fill_manual(values=c("#FDAE61", "#FEE08B","#E6F598","#ABDDA4","#66C2A5","#3288BD"))+ #
       theme_bw()+
       labs(y="Recall@Benchmark1",x="Group with different event size (number of tweets)",size=9)+ #set y and x labels
       theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank(), legend.title=element_blank())

### 2016-11-10 npmi.R

@@ -7,16 +7,17 @@ npmis<-read.csv(file="/Users/huangwaleking/git/detector/npmi.csv",header=TRUE)
 
 scores<-npmis %>% filter(group<=50)
 
-scores$model<-factor(scores$model,levels=c("Category-Level Topics","Topics learned by LightLDA"))
+scores$model<-factor(scores$model,levels=c("Category-Level Topics in Knowledge Base","Topics learned by LightLDA"))
 
 p<-ggplot(data=scores,aes(x=group, y=npmiscore,fill=model,color=model)) +
-  geom_point(alpha = 0.7,size=1,aes(shape = model)) +
-  stat_smooth(method = "lm", alpha=0.5,formula= y ~ ns(x,49))+ 
+  geom_point(alpha = 0.8,size=1.5,aes(shape = model)) +
+  stat_smooth(method = "lm", alpha=0.5,formula= y ~ ns(x,49),size = 0.2)+ 
+  guides(color=guide_legend(override.aes=list(fill=NA)))+
   labs(y="NPMI",x="Group ID",size=9)+ #set y and x labels
   coord_cartesian(xlim=c(2, 48))+ #hardcode, don't why these values, but they work
   theme_bw()+ #remove the grid
-  theme(legend.position=c(0.73,0.59), legend.justification=c(0,0),legend.text=element_text(size=8))+
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.title=element_blank())
+  theme(legend.position=c(0.63,0.595), legend.justification=c(0,0),legend.text=element_text(size=8),legend.title=element_blank(),legend.background=element_rect(fill="white", colour=NA))+
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
   
 
 

### 2016-11-10 npmiDf.py

@@ -45,7 +45,7 @@ def getDataframe():
     #transDetectorTopicNames = [e.split("_")[0] for e in os.listdir("/Users/huangwaleking/Downloads/nt/")]
     for transDetectorTopicName in transDetectorTopicNames:
         transDetectorNPMIfile = "/Users/huangwaleking/Downloads/nt/" + transDetectorTopicName + "_npmi.txt"
-        df = getSeries(transDetectorNPMIfile, transDetectorTopicName, "Category-Level Topics", df)
+        df = getSeries(transDetectorNPMIfile, transDetectorTopicName, "Category-Level Topics in Knowledge Base", df)
 
     return df
 

### 2016-11-10 paper/lncsFormat.tex
submitted version

@@
 \usepackage{algorithmic}
+
+%================================================
+%% make a tight section title
+%% Save the class definition of \subparagraph
+\let\llncssubparagraph\subparagraph
+%% Provide a definition to \subparagraph to keep titlesec happy
+\let\subparagraph\paragraph
+%% Load titlesec
+\usepackage[compact]{titlesec}
+%% Revert \subparagraph to the llncs definition
+\let\subparagraph\llncssubparagraph
+\usepackage[compact]{titlesec}% shrink all the whitespace around section headings
+%================================================
 
@@
 
-\intextsep=0pt plus 0pt minus 0pt
+\intextsep=1pt plus 1pt minus 1pt
 \begin{figure}[h]
@@
 In our paper, to balance the performance and the cost of leveraging knowledge base for event detection, we develop a novel category-level transfer learning method, namely \textsc{TransDetector}.
-It consists of three phases: extracting of category-level topics in knowledge base, conducting transfer learning to get category-level topics in microblog stream, and detecting events from category-level word time series, as illustrated in Figure \ref{fig:modelDesc}.
+It consists of three phases: extracting category-level topics in knowledge base, conducting transfer learning to get category-level topics in microblog stream, and detecting events from category-level word time series, as illustrated in Figure \ref{fig:modelDesc}.
 We explain the main idea of the three parts in \textsc{TransDetector}, and leave more technique details in Section \ref{sec:TransDetector}.
-(1) For the \textbf{extracting} phase, we propose a structural-guided category-level topics extraction method on the knowledge base, . 
+(1) In the \textbf{extracting} phase, we propose a structural-guided category-level topics extraction method on the knowledge base, . 
 It bases on the following facts. 
@@
 By considering these three parts together, we can extract a class or category's highly related words, and restore them in \textit{category-level topics in knowledge base}.
-(2) For the \textbf{conducting transfer learning} phase, we propose a novel probabilistic model CTrans-LDA for transferring the knowledge.
+(2) In the \textbf{conducting transfer learning} phase, we propose a novel probabilistic model CTrans-LDA for transferring the knowledge.
 CTrans-LDA works in the bayesian transfer learning way like \cite{dai2007transferring}, by utilizing the extracted \textit{category-level topics in knowledge base} as the informative priors to bridge two data domains.
-After running CTrans-LDA, it labels whether a word in a microblog message should link to a category concept in knowledge base.
-Applying CTrans-LDA on more microblogs, it gets the \textit{category-level topics in microblog stream}.
-(3) For the \textbf{detecting} phase,
-
-Since the recent states have filtered out meaningless words, the detected events on recent states is much more accurate than other methods which don't do the transfer learning.
-\textsc{CTrans-LDA}, \textit{history states}, and \textit{recent states} forms up our proposed event detection method \textsc{LTDetector}.
-Our experiment on the real dataset \textit{Edinburgh twitter corpus (30 million tweets)} validates the effectiveness of our proposed method \textsc{LTDetector}.
-
-%In transfer learning, \textit{history states} play an important role at speeding up building the linkage between the word in microblog and the high level concept in knowledge base.
+CTrans-LDA labels whether a word in a microblog message should link to a category in knowledge base, or just label it as no-category-related word.
+Applying CTrans-LDA on more microblogs, it gets the \textit{category-level topics in microblog stream} and \textit{category-level word time series}.
+(3) In the \textbf{detecting} phase, since the words in microblogs have been enriched semantically and the meaningless words are labeled as no-category-related, the event detection on \textit{category-level word time series} is much more accurate than other methods which don't conduct the transfer learning.
+Without loss of generality, we use Wikipedia as a representative of the knowledge base in the remaining of this paper.
+And the experiment on the \textit{Edinburgh twitter corpus} demonstrates the effectiveness of our proposed \textsc{TransDetector}.
 
@@
 To sum up, the contribution of this paper is mainly in four aspects.
-(1) We propose a structure-guided category-level topics extraction method, which exploits the knowledge base's hierarchical structure to extract categories' highly correlated topics. 
+(1) We propose a structure-guided category-level topics extraction method, exploiting the knowledge base's hierarchical structure to extract categories' highly correlated topics. 
 (2) We develop a probabilistic model CTrans-LDA for category-level transfer learning, which utilizes the word co-occurrences and transfers the knowledge base's category-level topics into microblogs. 
@@
 (4) Experiment verifies the quality of category-level topics extracted from knowledge base, and the further study on the benchmark \textit{Edinburgh twitter corpus} validates the effectiveness of our proposed transfer learning method for event detection.
-
-%(1) We reveal that transfer learning from knowledge base to microblog stream can benefit event detection task.
-%(2) We propose the probability model \textsc{NSDetector}. 
-%The model can combine the history data and the recent data, further determine the arrival new document whether it represents a new event. 
-%More than that, \textsc{NSDetector} has the capability to update the knowledge of what happened.
-%(3) The experiment on the Edinburgh twitter corpus which contains 30 million tweets show that \textsc{NSDetector} promotes the accuracy rate by 9\% without sacrificing the recall rate.
 
@@
 In this section, we present a novel category-level transfer learning method for event detection, namely \textsc{TransDetector}. 
-Illustrated in Figure \ref{fig:modelDesc}, \textsc{TransDetector} consists of three parts: (1) extracting category-level topics in knowledge base, (2) transfer learning on category-level topics in microblog stream, (3) detecting events from category-level word time series.
+Illustrated in Figure \ref{fig:modelDesc}, \textsc{TransDetector} consists of three parts: (1) extracting category-level topics in knowledge base, (2) conducting transfer learning to get category-level topics in microblog stream, and (3) detecting events from category-level word time series.
+The following definitions are used by our method \textsc{TransDetector}. 
+Definition 1 is used in the \textbf{extracting} phase, Definitions 2 and 3 are used in the \textbf{conducting transfer learning} phase, and Definitions 4 to 6 are used in the \textbf{detecting} phase.
+Because Definitions 2 to 6 are very easy to understand, what needs to be specified are Definition 1.
+\textit{Category-level topics in knowledge base} is a set of tuples extracted from knowledge base, which weighs the importance of given words to the specific category, defined in Definition 1 formally.
+Taking the \textit{Military} category in Figure \ref{fig:NSinitializaton} as an example, the category-level topic of \textit{military} contain the words \textit{army}, \textit{military}, and \textit{shootings} etc, which are highly related to the category \textit{Military}.
 
-\textit{Category-level Topics in Knowledge Base} is a set of tuples extracted from knowledge base, which weighs the importance of given words to the specific category, defined in Definition 1 formally.
-Taking the \textit{military} category in Figure \ref{fig:modelDesc} as an example, the history state of \textit{military} contain the words \textit{army}, \textit{military}, and \textit{shootings} etc.
-
-\begin{comment}
-Knowledge base often contains much information about what happened. 
-But the existing RDF model\cite{klyne2006rdf} on knowledge base lacks an efficient mechanism to transfer the information from knowledge base to text stream.  
-With the help of knowledge base's structure (detailed in sec \ref{subsec:hs_initialization}), we provide a  lightweight model to transfer the information in knowledge base to text stream.
-
-\textit{History state} is the proposed data structure to restore the information about what happened. 
-Initially, \textit{history state} extracts category-related history data into a set of tuples, which weighs the importance of given words to the specific category, defined in Definition 1 formally. 
-Taking the \textit{military} category in Figure \ref{fig:modelDesc} as an example, the history state of \textit{military} contain the words \textit{army}, \textit{military}, and \textit{shootings} etc.
-
-\textit{Recent state} is the proposed data structure to maintain the information about what's happening.
-It extracts category-related words from incoming text stream, for each time window.
-Still taking the \textit{military} category in  Figure \ref{fig:modelDesc} as an example, based on extracted history states, our proposed probabilistic continuous learning model CTrans-LDA can recognize the words \textit{libyan} and \textit{rebel} in the time window 2011-07-28 in the text stream are related to the category \textit{military}.
-Furthermore the time series analysis on the neighbouring recent states can recognize the set of events' candidate words, and finally detects the events in the text stream. 
-In the example of Figure \ref{fig:modelDesc}, the words \textit{libyan} and \textit{rebel} are related to the \textit{military} event ``\#libya Libyan rebels chief is killed (2011-07-28)''.
-
-\end{comment}
-
-\begin{rmkWithoutSpacing}[\textbf{Category-level Topics in Knowledge Base}] 
+\begin{rmkWithoutSpacing}[\textbf{Category-Level Topics in Knowledge Base}] 
 Given category \(c\), the category level topic in knowledge base is defined by a set of tuples, in which the first element is the word \(w^{(c)}_i\) related to the category \(c\), and the second element is the chi-square score \(chi(c,w^{(c)}_{i})\) under the category \(c\).
-And we denote \(c\)'s category-level topic in knowledge base as \(\bm{h}_c=\{<w^{(c)}_i,chi(c,w^{(c)}_{i})>\}_{i=1,...,N_c}\).
+And we denote \(c\)'s category-level topic in knowledge base as \(\bm{h}_c=\{<w^{(c)}_i,chi(c,w^{(c)}_{i})>\}_{i=1}^{N_c}\).
 \end{rmkWithoutSpacing}
 
-\begin{rmkWithoutSpacing}[\textbf{Category-level Topics in Microblog Stream}] 
-Given category \(c\), the category level topic in microblog stream at time \(t\) is defined by a set of tuples, and denoted as \(\bm{r}_{c,t}=\{<w^{(c)}_i,n(c,t,w^{(c)}_{i})>\}_{i=1,...,N_c}\), in which word \(w^{(c)}_{i}\) is related to the category \(c\), and \(n(c,t,w^{(c)}_{i})\) is its document frequency in the time window \(t\).
+\begin{rmkWithoutSpacing}[\textbf{Category-Level Topics in Microblog Stream}] 
+Given category \(c\), the category level topic in microblog stream at time \(t\) is defined by a set of tuples, and denoted as \(\bm{r}_{c,t}=\{<w^{(c)}_i,n(c,t,w^{(c)}_{i})>\}_{i=1}^{N_c}\), in which word \(w^{(c)}_{i}\) is related to the category \(c\), and \(n(c,t,w^{(c)}_{i})\) is its document frequency in the time window \(t\).
 \end{rmkWithoutSpacing}
 
-\begin{rmkWithoutSpacing}[\textbf{Category-level Word Time Series}] 
-Given category \(c\) and word \(w\), the category level word time series is a list extracted from \(\{\bm{r}_{c,t}\}_{t=1}^{T}\), and denoted as \(\{n(c,t,w^{(c)}_{i})\}_{t=1}^{T}\).
+\begin{rmkWithoutSpacing}[\textbf{Category-Level Word Time Series}] 
+Given category \(c\) and word \(w\), the category level word time series is a list of document frequencies extracted from \(\{\bm{r}_{c,t}\}_{t=1}^{T}\), and denoted as \(\{n(c,t,w^{(c)}_{i})\}_{t=1}^{T}\).
 \end{rmkWithoutSpacing}
@@
 
-\begin{rmkWithoutSpacing}[Event Phrase] 
+\begin{rmkWithoutSpacing}[\textbf{Event Phrase}] 
 Event phrase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occurred in the set of events' candidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happened in time \(t\) under the category \(c\).
@@
 
-\begin{rmkWithoutSpacing}[Event Related Microblogs] Event related microblogs \(\mathcal{D}_{c,t,i}\) are articles relating to the \(i\)-th event in time \(t\) of category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
+\begin{rmkWithoutSpacing}[\textbf{Event Related Microblogs}] Event related microblogs \(\mathcal{D}_{c,t,i}\) are articles relating to the \(i\)-th event in time \(t\) of category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
 \end{rmkWithoutSpacing}
 
-Section \ref{subsec:hs_initialization} explains the details of how to initialize history states from knowledge base.
-Section \ref{subsec:rs_initialization} shows how to perform transfer learning for recent states.
-And section \ref{subsec:detection} interprets the high accuracy event detection based on the processed recent states.
+Section \ref{subsec:hs_initialization} explains the details of how to extract \textit{category-level topics in knowledge base} by using the three fold hierarchical structure.
+Section \ref{subsec:rs_initialization} shows how to conduct transfer learning to get \textit{category-level word time series} in microblog stream.
+And section \ref{subsec:detection} interprets the high accuracy event detection based on the processed \textit{category-level word time series}.
 
-\subsection{History States' Extraction}\label{subsec:hs_initialization}
-In this part, we discuss in detail how to initialize the history states from the given knowledge base. 
+\subsection{Extracting Category-Level Topics in Knowledge Base}\label{subsec:hs_initialization}
+In this part, we discuss in detail how to extract the \textit{category-level topics in knowledge base} on the given categories. 
 The knowledge base such as Wikipedia has the structure of classes, subclasses, instances, and the edges between them. 
 This structure usually can be represented as triples in RDF graph\cite{klyne2006rdf}, which is adopted to build DBPedia\cite{auer2007dbpedia} and YAGO\cite{suchanek2007yago} from Wikipedia. 
-But the reasoning and maintenance of knowledge on the graph is usually expensive\cite{broekstra2003inferencing,bursztyn2015reasoning}. 
-To make a trade-off between cost and performance, we use the lightweight data structure \textit{history state} to represent the knowledge about what happened, which is extracted from the knowledge base.
-And the knowledge base's threefold structure \(G^{(0)}\), \(G^{(1)}\), \(G^{(2)}\) benefits the extraction of history states.
+But the reasoning and maintenance of knowledge on the graph is usually expensive\cite{bursztyn2015reasoning}. 
+To make a trade-off between cost and performance, we use the lightweight data structure \textit{topics} to represent the knowledge at category(class) level.
+And the knowledge base's threefold structure \(G^{(0)}\), \(G^{(1)}\), \(G^{(2)}\) benefits the extraction of \textit{category-level topics}.
 
@@
 For a specific Wikipedia dumps version, the edges  \textit{page} \(\rightarrow\)\textit{content} in \(G^{(2)}\) define a one-to-one mapping.
-There are a bulk of history information restored in the wiki text content.
+There are a bulk of information restored in the wiki text content.
 In order to extract the key words in wiki page's content, which distinguish it from other pages, we use the chi-square statistics\cite{yang1997comparative}\cite{liu2009imbalanced} to measure the importance of each word for the specific page.
@@
 %To prevent the overclaim of rare word by chi-square statitistcs, the word frequency is introduced as a supplement\cite{liu2009imbalanced}, as shown in line \ref{alg:line10inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}.
-Finally, we can get the category's history state, which are  composed by the category related words and their corresponding importance.
-%history states衡量一个词在考虑完整历史信息的情况下，对于一个类别的重要程度，例如在military类别下面；从某种程度上讲，history state从knowledge base中抽取了对于该类别的重要特征，有助于我们将它应用到text stream当中。
+Finally, we can get the \textit{category-level topic}, which are  composed by the category related words and their corresponding importance.
 \setlength{\textfloatsep}{3pt}% Remove \textfloatsep
@@
 \scriptsize
-\caption{History State Initialization from Knowledge Base}
+\caption{Extraction of Category-Level Topics in Knowledge Base}
 \label{alg:normalStatesInit}
@@
 \KwIn{Taxonomy's Graph \(G^{(0)}\), Category-Page Bipartite Graph \(G^{(1)}\), Page-Content Bipartite Graph \(G^{(2)}\), topic related category node \(c\)}
-\KwOut{History state \(\bm{h}_c\) on category \(c\)}
+\KwOut{\(c\)'s category-level topic in knowledge base \(\bm{h}_c\)}
 \(Pages(c)\leftarrow \varnothing\), \(\bm{h}_c \leftarrow \varnothing\)\\
@@
 
-Considering the full Wikipedia's contents, history state evaluates the importance of word to the concerned category accurately. 
-For example, in \textit{Military}'s history state, the top  words are \textit{army}, \textit{military}, \textit{air}, \textit{command}, \textit{force}, and \textit{regiment}, etc. 
+Considering the full Wikipedia's contents, the word's score in the \textit{category-level topic} evaluates the importance of word to the concerned category accurately. 
+For example, in \textit{Military}'s \textit{category-level topic}, the top  words are \textit{army}, \textit{military}, \textit{air}, \textit{command}, \textit{force}, and \textit{regiment}, etc. 
 The document which contains these words is related to the category \textit{Military} with high probability.
-We further discuss how to apply history states to the text stream on the following subsection \ref{subsec:rs_initialization}.
 
-\subsection{Recent States' Maintenance}
+\subsection{Conducting Transfer Learning}
 \label{subsec:rs_initialization}
-In this subsection, we describe how the proposed probabilistic model CTrans-LDA utilizes the history states to learn the recent states from text stream.
+In this subsection, we describe how the proposed probabilistic model CTrans-LDA transfers the category-level topics into microblogs.
 
 There are two facts inspiring CTrans-LDA. 
-(1) The topics in the document may contain history-state-like topics. 
-As an example, the tweet ``Libyan rebel chief gunned down in Benghazi (2011-07-28)'' contains the topic that is similar to the \textit{Military}'s history state.
-(2) The history-state-like topics can reuse the information  stored in the history states.
-The word \textit{libyan} in the aforementioned example tweet ranks much higher in the \textit{Military} and the \textit{Middle East} history states than the other categories' history states.
-After considering the relatedness between the remaining context and the history states, the learned topics of the example tweet include \textit{Military} and \textit{Middle East}.
+(1) The topics in the document may contain category-level topics. 
+As an example, the tweet ``Libyan rebel chief gunned down in Benghazi (2011-07-28)'' contains the topic that is similar to the \textit{Military}'s \textit{category-level topics in knowledge base}.
+(2) The \textit{category-level topics in microblog stream} can reuse the information stored in the corresponding \textit{category-level topics in knowledge base}.
+The word \textit{libyan} in the aforementioned example tweet ranks much higher in the \textit{Military} and the \textit{Middle East} category-level topics than the other categories' topics.
+After considering the relatedness between the remaining context and the \textit{category-level topics in knowledge base}, the learned topics of the example tweet include \textit{Military} and \textit{Middle East}.
 
@@
 In the above generative process, the line 2(a) is the key point to distinguish CTrans-LDA from LDA\cite{blei2003latent}, where \(\bm{\tau}_k\) is defined by Equation(\ref{eq:wikiPrior}).
-\(K_{KB}\) is the number of pre-defined history-state-like topics, and \(S_k\) is the set of words appeared in the \(k\)-th topic's history state.
+\(K_{KB}\) is the number of pre-defined categories used for transferring, and \(S_k\) is the set of words appeared in the \(k\)-th category-level topic.
 As \cite{wallach2008structured} mentioned that the asymmetric prior distribution can significantly improve the quality of topic modelling, \(\bm{\phi_k} \sim Dir(\bm{\beta}+ \bm{\tau_k})\) incorporates \textit{category-level topics in knowledge base} into the asymmetric prior of the word distribution on topic.
 The effect of \(\bm{\tau_k}\) is obvious, e.g., \(\tau_{Military,army}/\tau_{Military,basketball}=203\) leads to that topic \textit{Military} prefers to contain the word \textit{army} other than \textit{basketball}.
-The parameter \(\lambda\) controls how much the learned topics are similar to the history state, which can be chosen by cross-validated grid-search.
+The parameter \(\lambda\) controls how much the knowledge is used for transferring, which can be chosen by cross-validated grid-search.
 
@@
 In the initialization phase of Gibbs sampling for CTrans-LDA, the hidden variable \(z_{dn}\) is initialized to topic \(k\) with probability \(\hat{q}_{k|v}\) as Equation (\ref{eq:initProbability}).
-For the word \(v\) that belongs to any history state, \(\hat{q}_{k|v}\) is proportional to its importance in the history state \(\tau_{kv}\) as Equation \ref{eq:initProbability}(a). 
+For the word \(v\) that belongs to any category-level topic, \(\hat{q}_{k|v}\) is proportional to its importance in the category-level topic \(\tau_{kv}\) as Equation \ref{eq:initProbability}(a). 
 For the new word \(v\) in text stream, \(\hat{q}_{k|v}\) is   set uniformly \(1/(K-K_{\bm{KB}})\) on the other topics as Equation \ref{eq:initProbability}(b,c). 
-The initialization makes sure that the learned topics are aligned to the pre-defined history states.
-\setlength{\abovedisplayskip}{1pt}
-\setlength{\belowdisplayskip}{1pt}
+The initialization makes sure that the learned topics are aligned to the pre-defined category-level topic.
+\setlength{\abovedisplayskip}{0pt}
+\setlength{\belowdisplayskip}{0pt}
 \begin{scriptsize} 
@@
 The sampling process uses the conditional probability \(p(z_{dn}=k|.)\propto (n^{(d)}_{dk}+\alpha m_k)(n^{(w)}_{kv}+\tau_{kv}+\beta)/(n^{(w)}_{k,.}+\tau_{k,.}+V\beta)\), where \(n^{(d)}_{dk}\) is the number of words in document \(d\) assigned to topic \(k\), and \(n^{(w)}_{kv}\) is the times of word \(v\) assigned to topic \(k\).
-We set \(\alpha=0.1\) and \(\beta=0.01\) according to the suggestion by \cite{tang2014understanding}.
+We set \(\alpha=0.1\) and \(\beta=0.005\) according to the suggestion by \cite{tang2014understanding}.
 
 After Gibbs sampling on discrete time windows, CTrans-LDA learned all hidden topics of words in microblog stream.
-And for a specific word type \(w\) and its history-state-like topic assignment \(c\) in time window \(t\), its document frequency is counted as \(n(c,t,w^{(c)})\), which is the element of category \(c\)'s \(t\)-th recent state.
-Event detection on recent states is discussed in the following subsection.
+And for a specific word type \(w\) and its category assignment \(c\) in time window \(t\), its document frequency is counted as \(n(c,t,w^{(c)})\), which is the element of category-level word time series.
+Event detection on category-level word time series is discussed in the following subsection.
 
@@
 %For example, recent state of Military contain .
-%In other words, recent state is history-state-like topic timestamp.%在时间轴上的横截面。
 
@@
 %\subsection{Data Sets}
-In this subsection, we demonstrate the effectiveness of \textit{history states} initialized from knowledge base and \textit{recent states} learned by transfer learning.
+In this subsection, we demonstrate the effectiveness of \textsc{TransDetector}, by evaluating the \textit{category-level topics in knowledge base}, \textit{category-level topics in microblog stream} learned by transfer learning, and the effect of event detection.
 
@@
 We construct the taxonomy graph \(G^{(0)}\), the category-page bipartite graph \(G^{(1)}\) from the latest dump of category links\footnote{\url{https://dumps.wikimedia.org/enwiki/latest/enwiki-latest-categorylinks.sql.gz}} and the page-content map \(G^{(2)}\) from Wikipedia pages\footnote{\url{https://dumps.wikimedia.org/enwiki/latest/enwiki-latest-pages-articles.xml.bz2 }}.
-We set \(K_{KB}=100\), which means 100 categories are selected manually to cover the topics of Wikipedia and the target corpus as widely as possible. 
+We set \(K_{KB}=50\), which means 50 categories are selected manually to cover the topics of Wikipedia and the target corpus as widely as possible. 
 There are two kinds of categories are considered. 
@@
 
-\subsection{Effects of Categroy-Level Topics}
+\subsection{Evaluation on Categroy-Level Topics in Knowledge Base}
 The category-level topics are initialized on the pre-defined categories from the knowledge base as Algorithm \ref{alg:normalStatesInit}.
-%This process is illustrated by Table \ref{tbl:historyStates}.
 
 \textbf{Evaluation Metrics.}
-We compare the topic coherence of history states with the topics learned from Wikipedia by LDA in terms of NPMI\cite{Rder2015ExploringTS}.
+We compare the topic coherence of category-level topics with the topics learned from Wikipedia by LightLDA\cite{yuan2015lightlda} in terms of NPMI\cite{Rder2015ExploringTS}.
 Different from traditional experiments that only compute the topic coherence of top words, we want to check whether  it can hold for more words.
@@
 \textbf{Results.}
-Observe that even for the combination of 96th to 100th words with the top five words in \textit{Aviation}'s history state, NPMI=0.131 shows that the topic coherence still holds well without drifting.
-More generally, Figure \ref{fig:NPMI} illustrates that the history states are much more stable than the topics learned by LDA.
-Taking the group 10 (the combination of 56th to 60th words with the top five words) as an example, the median one of history states performs better than all those learned by LDA.
+Observe that even for the combination of 96th to 100th words with the top five words in \textit{Aviation}'s category-level topics in knowledge base, NPMI=0.131 shows that the topic coherence still holds well without drifting.
+More generally, Figure \ref{fig:NPMI} illustrates that the category-level topics are much more stable than the topics learned by LightLDA.
+Taking the group 10 (the combination of 56th to 60th words with the top five words) as an example, the median one of category-level topic performs better than those learned by LightLDA. 
+And more topics are compared shown in Figure \ref{fig:NPMI}, proving that our method performs better at extracting key features for categories.
 
-Since the history states extracted from knowledge base is stable and topic coherence,
-
-%\hlgreen{TODO: add a new table, containing a topic generated by BTM, which is most similar to the extracted topic from KB.}
 \begin{table}[h]
@@
 \centering
-\caption{Top words' topic coherence of \textit{Aviation}'s history state.
-* means the group also contains the five top words \textit{aircraft}, \textit{air}, \textit{airport}, \textit{flight}, and \textit{airline}, but we don't show them in table to save space.
-NPMI is computed on ten words (a combination of words in each row with the five top words).}
+\caption{The comparison on the topic coherence(NPMI) between our method and LightLDA\cite{yuan2015lightlda}, taking \textit{Aviation} as an example.
+(GID is short for Group Id.
+* means each group contains the five top words.
+NPMI is computed on a group of ten words.
+\(\sim\) stands for the top five words.)}
 \scalebox{0.65}{
@@
 \hline
-\multicolumn{4}{|c!{\vrule width 1pt}}{Category-Level Topics extracted from Wikipedia by \textsc{TransDetector}} & \multicolumn{4}{c|}{Topics Learned from Wikipedia by LightLDA}    \\ \hline
-Group ID& \#words*  & words  & NPMI & Group ID& \#words*& words & NPMI \\ \hline
+\multicolumn{4}{|c!{\vrule width 1pt}}{Category-Level Topics extracted from Wikipedia by \textsc{TransDetector}} & \multicolumn{4}{c|}{Topics Learned from Wikipedia by LightLDA\cite{yuan2015lightlda}}    \\ \hline
+GID& \#words*  & words  & NPMI & GID& \#words*& words & NPMI \\ \hline
 - & 1-5 & aircraft air airport flight airline &-& - & 1-5 & engine aircraft car air power &-\\ \hline
-0 & 6-10 & airlines aviation flying pilot squadron &  0.113 & 0 & 6-10 & design flight model production speed & 0.112\\ \hline
-1 & 11-15 &flights pilots raf airways fighter & 0.155 & 1 & 11-15 &system vehicle cars engines mm & 0.062\\ \hline
-2 & 16-20 &boeing runway force crashed flew   & 0.092 & 2 & 16-20 & fuel vehicles designed models type & 0.072\\ \hline
-3 & 21-25 &airfield landing passengers plane aerial & 0.179 & 3 & 21-25 & version front produced rear electric & 0.035\\ \hline
-4 & 26-30 &bomber radar wing bombers crash & 0.137 & 4 & 26-30 & space control motor standard development & 0.085\\ \hline
-5 & 31-35 &airbus airports operations jet helicopter & 0.189 & 5 & 31-35 & film range light using available & -0.002\\ \hline
-6 & 36-40 &squadrons base flown havilland crew & 0.088 & 6 & 36-40 & wing powered wheel weight launch & 0.087\\ \hline
-7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159 & 7 & 41-45 & developed low test ford cylinder & 0.007\\ \hline
-8 & 46-50 &planes fly engine takeoff fleet & 0.186 & 8 & 46-50 & equipment side pilot hp aviation & 0.091\\ \hline
-9 & 51-55 &fuselage helicopters aviator naval aero & 0.157 & 9 & 51-55 & systems us sold body drive & -0.051\\ \hline
-10 & 56-60 &glider command training balloon faa & 0.166 & 10 & 56-60 & gear introduced class safety seat & 0.069\\ \hline
+0 & 1-5, 6-10 & \(\sim\), airlines aviation flying pilot squadron &  0.113 & 0 & 1-5, 6-10 & \(\sim\), design flight model production speed & 0.112\\ \hline
+1 & 1-5, 11-15 & \(\sim\), flights pilots raf airways fighter & 0.155 & 1 & 1-5, 11-15 &\(\sim\), system vehicle cars engines mm & 0.062\\ \hline
+2 & 1-5, 16-20 & \(\sim\), boeing runway force crashed flew   & 0.092 & 2 & 1-5, 16-20 & \(\sim\), fuel vehicles designed models type & 0.072\\ \hline
+3 & 1-5, 21-25 &\(\sim\), airfield landing passengers plane aerial & 0.179 & 3 & 1-5, 21-25 & \(\sim\), version front produced rear electric & 0.035\\ \hline
+4 & 1-5, 26-30 &\(\sim\), bomber radar wing bombers crash & 0.137 & 4 & 1-5, 26-30 & \(\sim\), space control motor standard development & 0.085\\ \hline
+5 & 1-5, 31-35 &\(\sim\), airbus airports operations jet helicopter & 0.189 & 5 & 1-5, 31-35 & \(\sim\), film range light using available & -0.002\\ \hline
+6 & 1-5, 36-40 &\(\sim\), squadrons base flown havilland crew & 0.088 & 6 & 1-5, 36-40 & \(\sim\), wing powered wheel weight launch & 0.087\\ \hline
+7 & 1-5, 41-45 & \(\sim\), combat luftwaffe aerodrome carrier fokker & 0.159 & 7 & 1-5, 41-45 & \(\sim\), developed low test ford cylinder & 0.007\\ \hline
+8 & 1-5, 46-50 &\(\sim\), planes fly engine takeoff fleet & 0.186 & 8 & 1-5, 46-50 & \(\sim\), equipment side pilot hp aviation & 0.091\\ \hline
+9 & 1-5, 51-55 &\(\sim\), fuselage helicopters aviator naval aero & 0.157 & 9 & 1-5, 51-55 & \(\sim\), systems us sold body drive & -0.051\\ \hline
+10 & 1-5, 56-60 &\(\sim\), glider command training balloon faa & 0.166 & 10 & 1-5, 56-60 & \(\sim\), gear introduced class safety seat & 0.069\\ \hline
 \(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\) & \(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
-18 & 96-100 &scheduled carriers military curtiss biplane &0.131 & 18 & 96-100 & transmission special replaced limited different & 0.059\\ \hline
-19 & 101-105 &accident engines iaf albatross rcaf &0.068 & 19 & 101-105 & features machine nuclear even unit & 0.011\\ \hline
+18 & 1-5, 96-100 &\(\sim\), scheduled carriers military curtiss biplane &0.131 & 18 & 1-5, 96-100 & \(\sim\), transmission special replaced limited different & 0.059\\ \hline
+19 & 1-5, 101-105 &\(\sim\), accident engines iaf albatross rcaf &0.068 & 19 & 1-5, 101-105 & \(\sim\), features machine nuclear even unit & 0.011\\ \hline
 \end{tabular}
@@
         \includegraphics[width=1.0\columnwidth]{img/NPMI.pdf}
-        \caption{The variable that has the greatest impact on the outcome is its newsworthiness.}
+        \caption{More topics are compared at the NPMI metrics between our method and LightLDA}
         \label{fig:NPMI}
@@
 
-\textbf{Category-Level Topics Learned from Microblog Stream.}
-For Trans-LDA, \(K\) is set to be 200, which means Trans-LDA learned 100 history-state-like topics and 100 other topics.
+For CTrans-LDA, \(K\) is set to be 200, which means CTrans-LDA learned 50 category-level topics and 150 other topics.
 After cross-validated grid-search, \(\lambda\) is set to be 12.8. The other parameters are set as \(\alpha=0.1\), \(\beta=0.005\).
-We run \textsc{Trans-LDA} window by window on text stream, and learn specific categories' topics.
-
-%如图（topic）中，能够从Military*中学习出tweet（20110728）话题中包含libyan。
-
-%We use 20newsgroups\cite{lang1995newsweeder} dataset\footnote{\url{http://qwone.com/~jason/20Newsgroups}} to check the effects of normal states initialization.
-
-\begin{comment}
-\begin{table}[]
-\tiny
-\centering
-\caption{Normal State's cateogries corresponding to the 20-newsgroups corpus, and the F1 score on the classification task}
-\label{my-label}
-\begin{tabular}{|l|l|l|l|l|}
-\hline
- &  & LDA & BOW  & \begin{tabular}[c]{@{}l@{}}NS-Prior-\\ LDA\end{tabular} \\ \hline
-comp.graphics & Computer graphics &  &  &    \\ \hline
-comp.os.ms-windows.misc & Microsoft Windows &  &  &    \\ \hline
-comp.sys.ibm.pc.hardware & IBM personal computers &  &  &    \\ \hline
-comp.sys.mac.hardware & Macintosh computers &  &  &    \\ \hline
-comp.windows.x & X Window System &  &  &    \\ \hline
-rec.autos & Automobiles &  &  &    \\ \hline
-rec.motorcycles & Motorcycles &  &  &    \\ \hline
-rec.sport.baseball & Baseball &  &  &    \\ \hline
-rec.sport.hockey & Hockey &  &  &    \\ \hline
-sci.crypt & Cryptography &  &  &    \\ \hline
-sci.electronics & Electronics &  &  &    \\ \hline
-sci.med & Medicine &  &  &    \\ \hline
-sci.space & Outer space &  &  &    \\ \hline
-misc.forsale & Sales &  &  &    \\ \hline
-talk.politics.misc & Politics &  &  &    \\ \hline
-talk.politics.guns & Gun politics &  &  &    \\ \hline
-talk.politics.mideast & Middle East &  &  &   \\ \hline
-talk.religion.misc & Religion &  &  &    \\ \hline
-alt.atheism & Atheism &  &  &    \\ \hline
-soc.religion.christian & Christians &  &   &  \\ \hline
-In total &  &  &  & \\ \hline
-\end{tabular}
-\end{table}
-\end{comment}
-
-\begin{comment}
-\begin{figure}
-        \centering
-        \includegraphics[height=4.0cm]{img/pmi.pdf}
-        \caption{The quality of all twitter topics learned by NS-Prior-LDA increases with normal states weight (\(\lambda\)) before \(\lambda=12.8\).
-The optimized PMI is gained with moderate normal states weight when considering topics \(k\leq K_{\bm{KB}}\) and topics \(k > K_{\bm{KB}}\) together.}
-\end{figure}
-\end{comment}
-
-\begin{comment}
-\begin{table}
-\centering
-\caption{The PMI of twitter topics learned by NS-Prior-LDA, its variant, and other baselines}
-    \begin{tabular}{|l|l|c|}
-    \hline
-    Model & Prior Knowledge & PMI \\ \hline
-    LDA & None  & 1.265 \(\pm\) 0.013     \\ \hline
-    BurstyBTM\cite{Yan:2015wm} & None    & 1.467 \(\pm\) 0.017     \\ \hline
-    NS-Prior-LDA\(^{(-)}\)   &   \begin{tabular}[c]{@{}l@{}}\footnotesize{Words in categories simply}\\ \footnotesize{extracted from Wikipedia}\end{tabular} & 1.439 \(\pm\) 0.010     \\ \hline
-    NS-Prior-LDA         & \begin{tabular}[c]{@{}l@{}}\footnotesize{Normal states initialized} \\\footnotesize{from wikipedia}\end{tabular} & 1.523 \(\pm\) 0.017     \\ \hline
-    \end{tabular}
-\label{tbl:NS-Prior-LDA}
-\end{table}
-\end{comment}
+We run CTrans-LDA window by window on text stream, and learn specific categories' topics.
+The result in Table 2 demonstrates the effectiveness of transferring category-level topics into the microblog stream, and finding more new words in the stream which is not restored in the knowledge base.
 
@@
 \centering
-\caption{Category-Level Topics extracted from knowledge base and the corresponding topics on microblog stream learned from Trans-LDA, taking the categories \textit{Aviation},  \textit{Health}, \textit{Middle East}, \textit{Military}, and \textit{Mobile Phones} as examples.
+\caption{Category-Level Topics extracted from knowledge base and the corresponding topics on microblog stream learned from CTrans-LDA, taking the categories \textit{Aviation},  \textit{Health}, \textit{Middle East}, \textit{Military}, and \textit{Mobile Phones} as examples.
 The words in \textbf{\textit{bold italic}} font are newly learned on the microblog stream by the transfer learning, which semantic meanings are verified consistent with the categories; while the words in normal font play the role as the bridge in transfer learning, and appear in the both category-level topics in two domains.}
@@
 \end{table*}
-%TODO: add the top words in the category-level topic 
-%\hlgreen{TODO: add the top words of the category-level topic in each window of microblog stream AFTER Table 2.}
-
-%TODO: add the effect of transfer learning by using text classification, compared with fastText and SVM.
-%\hlgreen{TODO: add the effect of transfer learning by using text classification, compared with fastText and SVM.}
-\begin{comment}
-\begin{figure*}
-    \label{fig:algorithm}
-    \includegraphics[width=1.0\textwidth]{img/screenShot.png}
-    \caption{An illustration of the time series of Military related states on Twitter dataset from 2011-06-30 to 2011-09-15.}
-\end{figure*}
-\end{comment}
 
@@
 
-%LSH-FSD\cite{Petrovic:2010uj}没有评测FSD的情况，我们也可以提一句，我们不评测FSD，我们只评测检测出的事件是否是真实的事件。
-
 \textbf{Results.}
-%\chinese{我们需要说明几个问题。1，在Benchmark2上，事件有395个；LSH能够检测到3337个聚类簇，判断它是否命中我们采用比较聚类簇中心的方法，}
 In general, our method is better than the existing methods in terms of the precision and the recall, only sacrificing in the DERate slightly, as shown in Table \ref{tbl:overall}. 
@@
 The widespread existence of such not-so-popular events challenge almost all the existing event detection methods.
+More result in Table 4 shows the examples of military related events detected by \textsc{TransDetector} on the real dataset.
 
@@
 \end{figure}
-
-Illustrated in Table \ref{tbl:overall} and Figure \ref{fig:Benchmark1}, \textsc{TransDetector} achieves very good results even on the not-so-popular events. 
-\hlgreen{To check} 
-After processing each time window's data, the words in microblogs can be enriched semantically with knowledge base.
-In this way, the transfer learning model provides richer semantics and less noise for microblog stream, which promotes the accuracy of event detection significantly. 
-The following definitions are the concepts used by the transfer learning model \textsc{TransDetector}. 
-\hlgreen{To Check}
-After transfer learning, events are detected accurately because the word time series is refined to finer grain as multiple corresponding (word, category) time series, and the bursty pattern is better exposed.
-Taking the word \textit{hood} as an example, it belongs to the category \textit{Military} when it appeared in \textit{Ft Hood}, a US military establishment located in Texas.
-\hlgreen{To Check}
-As shown in Figure \ref{fig:hood}, the bursty pattern of \textit{hood} is clearly exposed after distinguishing its \textit{Military} time series from the raw one.
-%Therefore, the processing on each category's accurate stream states leads to the accurate event detection.
 
@@
 
-%An accurate recent states learning leads to accurate event detection.
-\begin{comment}
-These methods work in four ways. 
-1) Based on topic model, BurstyBTM and TimeUserLDA detect bursty topics. 
-Although they are designed for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
-2) Integrated with knowledge base, Twevent detects bursty segments, groups them into clusters, and then filters out the meaningless ones by Wikipedia.
-3) By clustering articles, UMass System and LSH decide whether the article belongs to the existing event or a new one.
-As designed for First Story Detection task (one of the Topic Detection and Tracking subtasks\cite{allan2012topic}) initially, they prefer to enlarge the recall of detected events. 
-4) By analyzing word frequencies, EDCoW clusters the bursty words into events.
-\end{comment}
-
-\begin{comment}
-20-newsgroup\footnote{http://qwone.com/~jason/20Newsgroups/}
-\end{comment}
-
 \section{Conclusions \& Future Work}
@@
 
-\begin{comment}
-Twitter, as a new type of social media, has experienced an explosive growth in terms of both users and information volume in recent years. 
-The characteristics of tweets propose severe challenges to many tasks including event detection. 
-In this paper, we present a novel event detection system for Twitter stream, called Twevent, to tackle the adverse impacts of tweets: short and noisy content, diverse and dynamic topics, and large data volume.
-One of the key concept in Twevent is to use tweet segment instead of unigram for identifying the bursty features and then distinguishing the realistic events from the noisy ones. 
-Twevent demonstrates outstanding performance in our experiments: effectiveness, informativeness, and efficiency. 
-As a part of our future work, we will investigate the effectiveness of utilizing more features from tweets (e.g., retweet rate and hashtags) in Twevent. 
-Another important task is to investigate the effectiveness of Twevent when none of the segments of an event is covered by Wikipedia.
-\end{comment}
-
-\newpage
+%\newpage
 \bibliographystyle{unsrt}

### 2016-12-26 paper/lncsFormat.tex
TODO: camera-ready

@@
 \title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
-%\title{Leveraging Knowledge Base for Accurate Event Detection on Microblog Stream}
 \titlerunning{\ }
-%构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
-%\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
-\begin{comment}% for double blind
 \author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Tengjiao Wang\inst{1} \and Yazhou Wang\inst{1} }
@@
 }
-\end{comment}
 
@@
 In other words, knowledge base enriches the linkages between words and concepts, and provides more comprehensive context for microblogs.
-Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
+Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information stored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
 Taking the below Figure \ref{fig:hood} as an example, the fluctuation of time series of raw word \textit{hood} is not so obvious to reflect the event happened to the military base \textit{Ft. Hood}.
@@
 
-The benefit of enriching the semantics for micorblogs is attractive, but it's non-trivial to transfer the knowledge restored in the knowledge base into microblog stream directly.
+The benefit of enriching the semantics for micorblogs is attractive, but it's non-trivial to transfer the knowledge stored in the knowledge base into microblog stream directly.
 The existing RDF model\cite{klyne2006rdf} lacks an efficient quick mechanism to transfer the knowledge, since it's mainly designed for managing knowledge as tuples on graph.
@@
 We explain the main idea of the three parts in \textsc{TransDetector}, and leave more technique details in Section \ref{sec:TransDetector}.
-(1) In the \textbf{extracting} phase, we propose a structural-guided category-level topics extraction method on the knowledge base, . 
+(1) In the \textbf{extracting} phase, we propose a structural-guided category-level topics extraction method on the knowledge base. 
 It bases on the following facts. 
@@
 \label{sec:relatedWorks}
-\textbf{Event Detection.} Based on how much data used, the methods are mainly in two groups, the detection \textit{without extra information} and that by \textit{leveraging extra information}.
+\textbf{Event Detection.} Based on how much data are used, the methods are mainly in two groups, the detection \textit{without extra information} and that by \textit{leveraging extra information}.
 
@@
 For a specific Wikipedia dumps version, the edges  \textit{page} \(\rightarrow\)\textit{content} in \(G^{(2)}\) define a one-to-one mapping.
-There are a bulk of information restored in the wiki text content.
+There are a bulk of information stored in the wiki text content.
 In order to extract the key words in wiki page's content, which distinguish it from other pages, we use the chi-square statistics\cite{yang1997comparative}\cite{liu2009imbalanced} to measure the importance of each word for the specific page.
@@
 We run CTrans-LDA window by window on text stream, and learn specific categories' topics.
-The result in Table 2 demonstrates the effectiveness of transferring category-level topics into the microblog stream, and finding more new words in the stream which is not restored in the knowledge base.
+The result in Table 2 demonstrates the effectiveness of transferring category-level topics into the microblog stream, and finding more new words in the stream which is not stored in the knowledge base.
 

### 2016-12-27 paper/lncsFormat.tex
remove citation of framenet

@@
 Beyond the scope of microblog stream, \cite{steiner2013mj} utilizes the concurrent wikipedia edit spikes for event detection.
-And \cite{liuleveraging2016} leverages the ACE corpus\cite{doddington2004automatic} and the structure of FrameNet\cite{baker1998berkeley} to improve the event detection within FrameNet, but has not shown how to apply the knowledge base for more general unstructured corpus.
+%And \cite{liuleveraging2016} leverages the ACE corpus\cite{doddington2004automatic} and the structure of FrameNet\cite{baker1998berkeley} to improve the event detection within FrameNet, but has not shown how to apply the knowledge base for more general unstructured corpus.
 In a nutshell, existing works are different from ours, as we transfer the category information of knowledge base into microblog's words and get the finer processing objects in event detection, rather than treating the knowledge base as a lookup table or a comparison base.
@@
 This structure usually can be represented as triples in RDF graph\cite{klyne2006rdf}, which is adopted to build DBPedia\cite{auer2007dbpedia} and YAGO\cite{suchanek2007yago} from Wikipedia. 
-But the reasoning and maintenance of knowledge on the graph is usually expensive\cite{bursztyn2015reasoning}. 
+But the the query on the large graph is usually very expensive\cite{huang2011scalable}. 
 To make a trade-off between cost and performance, we use the lightweight data structure \textit{topics} to represent the knowledge at category(class) level.
@@
 To include these important events and enlarge the ground truth of realistic events pool, we build the second benchmark carefully.
-We manually evaluate the candidate events detected by LSH,  \textsc{TransDetector}, Twevent, EDCoW, BurstyBTM, and TimeUserLDA, with the help of the Wikipedia Current Event Portal\footnote{\url{https://en.wikipedia.org/wiki/Portal:Current_events}} and a local search engine built on Lucene.
+We manually evaluate the candidate events detected by LSH,  \textsc{TransDetector}, Twevent, EDCoW, BurstyBTM, and TimeUserLDA, with the help of the \textit{Wikipedia Current Event Portal}\footnote{\url{https://en.wikipedia.org/wiki/Portal:Current_events}} and a local search engine built on Lucene.
 The labeling process generates the Benchmark2, and contains 395 events.
@@
 
+\section*{Acknowledgments}\label{sec:Acknowledgments}
+This research is supported by the Natural Science Foundation of China (Grant No.
+61300003, 61572043), and the Specialized Research Fund for the Doctoral Program of Higher Education (Grant No.
+20130001120001).
+
 %\newpage

### 2016-12-27 paper/lncsFormat.tex
remove pagenum for camera-ready
update acknowledgements

@@
 \title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
-\titlerunning{\ }
+\titlerunning{Transfer Learning for Accurate Event Detection\ }
 \author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Tengjiao Wang\inst{1} \and Yazhou Wang\inst{1} }
@@
 \maketitle
+% BEGIN
+% To Proceeding Editors:
+% Special codes there for remove page numbers in the LaTeX documents
+\thispagestyle{empty}
+\pagestyle{empty}
+%
+% END
 
@@
 
-\section*{Acknowledgments}\label{sec:Acknowledgments}
-This research is supported by the Natural Science Foundation of China (Grant No.
-61300003, 61572043), and the Specialized Research Fund for the Doctoral Program of Higher Education (Grant No.
-20130001120001).
-
+\setlength{\parindent}{0pt}\textbf{Acknowledgments.} This research is supported by the Natural Science Foundation of China (Grant No.
+61572043), and the National Key Research and Development Program (Grant No.
+2016YFB1000704).
 %\newpage

### 2017-01-06 paper/DASFAA17_regular_64.tex
prepare to camera ready

--- 2016-12-27 paper/lncsFormat.tex
@@
 %
-\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection\thanks{This research is supported by the Natural Science Foundation of China (Grant No.
+61572043), and the National Key Research and Development Program (Grant No.
+2016YFB1000704).}}
 \titlerunning{Transfer Learning for Accurate Event Detection\ }
-\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Tengjiao Wang\inst{1} \and Yazhou Wang\inst{1} }
-\institute{Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
-\path{huangwaleking@gmail.com,{pekingchenwei,tjwang}@pku.edu.cn}\\ 
+\author{Weijing Huang\inst{1} \and Tengjiao Wang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Yazhou Wang\inst{1} }
+\institute{\(^{1}\)Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
+\path{huangwaleking@gmail.com,{tjwang,pekingchenwei}@pku.edu.cn}\\ 
 \path{pkuwangyz@gmail.com}
@@
 \begin{abstract}
-Many web applications need the accurate event detection technique on microblog stream. 
-But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
+Many Web applications need the accurate event detection technique on microblog stream. 
+But the accuracy of existing methods is still challenged by microblog's short length and high noise. 
 We develop a novel category-level transfer learning method \textsc{TransDetector} to deal with the task.  
@@
 %另外，我们还标注了事件，使其语义可理解。以及LTDetector是efficient的。
-
+\keywords{event detection, microblog stream, transfer learning, knowledge base.}
 \end{abstract}
@@
 \section{Introduction}
-Many web applications need the accurate event detection technique on microblog stream, such as public opinion analysis\cite{thelwall2011sentiment}, public security\cite{Li:2012gw}, and disaster response\cite{Yin:2012ht}, etc.
+Many Web applications need the accurate event detection technique on microblog stream, such as public opinion analysis\cite{thelwall2011sentiment}, public security\cite{Li:2012gw}, and disaster response\cite{Yin:2012ht}, etc.
 Although event detection has been a research topic for a long while\cite{allan1998topic}, event detection in microblog stream is still challenging\cite{atefeh2015survey}.
-According to \cite{huang2016probabilistic}, the characteristics of microblog, which is fast changing, high noise, and short length, raise the challenge.
+According to \cite{huang2016probabilistic}, the characteristics of microblog, which are fast changing, high noise, and short length, raise the challenge.
 
@@
 
-\setlength{\parindent}{0pt}\textbf{Acknowledgments.} This research is supported by the Natural Science Foundation of China (Grant No.
+%\setlength{\parindent}{0pt}\textbf{Acknowledgments.} This research is supported by the Natural Science Foundation of China (Grant No.
 61572043), and the National Key Research and Development Program (Grant No.

### 2017-01-10 paper/DASFAA17_regular_64.tex
camera ready nearly done

@@
 
-%\usepackage{aaai17}
 \usepackage{times}
@@
 \usepackage{amsthm}%used for theorem and definition
-%\usepackage{showframe}%show the margin
+\usepackage{showframe}%show the margin
 %\usepackage{ulem}%used for uwave
@@
 Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information stored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
-Taking the below Figure \ref{fig:hood} as an example, the fluctuation of time series of raw word \textit{hood} is not so obvious to reflect the event happened to the military base \textit{Ft. Hood}.
+Taking Figure \ref{fig:hood} below as an example, the fluctuation of time series of raw word \textit{hood} is not so obvious to reflect the event happened to the military base \textit{Ft. Hood}.
 After transferring the knowledge about \textit{``Military"} into the microblog stream, the time series of word \textit{``hood"} related to \textit{``Military"} is extracted, which is more vivid to detect the event happened on July 28th, 2011.
@@
 (3) In the \textbf{detecting} phase, since the words in microblogs have been enriched semantically and the meaningless words are labeled as no-category-related, the event detection on \textit{category-level word time series} is much more accurate than other methods which don't conduct the transfer learning.
-Without loss of generality, we use Wikipedia as a representative of the knowledge base in the remaining of this paper.
+%Without loss of generality, we use Wikipedia as a representative of the knowledge base in the remaining of this paper.
 And the experiment on the \textit{Edinburgh twitter corpus} demonstrates the effectiveness of our proposed \textsc{TransDetector}.
 
-\intextsep=5pt plus 3pt minus 1pt
-\begin{figure}
+To sum up, the contribution of this paper is mainly in four aspects.
+(1) We propose a structure-guided category-level topics extraction method, exploiting the knowledge base's hierarchical structure to extract categories' highly correlated topics. 
+(2) We develop a probabilistic model CTrans-LDA for category-level transfer learning, which utilizes the word co-occurrences and transfers the knowledge base's category-level topics into microblogs. 
+(3) Events are detected accurately on category-level word time series, due to richer semantics and less noise. 
+(4) Experiment verifies the quality of category-level topics extracted from knowledge base, and the further study on the benchmark \textit{Edinburgh twitter corpus} validates the effectiveness of our proposed transfer learning method for event detection.
+\intextsep=1pt plus 1pt minus 1pt
+\begin{figure}[h]
 	\setlength{\abovecaptionskip}{0.cm}
@@
 
-To sum up, the contribution of this paper is mainly in four aspects.
-(1) We propose a structure-guided category-level topics extraction method, exploiting the knowledge base's hierarchical structure to extract categories' highly correlated topics. 
-(2) We develop a probabilistic model CTrans-LDA for category-level transfer learning, which utilizes the word co-occurrences and transfers the knowledge base's category-level topics into microblogs. 
-(3) Events are detected accurately on category-level word time series, due to richer semantics and less noise. 
-(4) Experiment verifies the quality of category-level topics extracted from knowledge base, and the further study on the benchmark \textit{Edinburgh twitter corpus} validates the effectiveness of our proposed transfer learning method for event detection.
-
 \section{Related Works}
 \label{sec:relatedWorks}
-\textbf{Event Detection.} Based on how much data are used, the methods are mainly in two groups, the detection \textit{without extra information} and that by \textit{leveraging extra information}.
+\textbf{Event Detection.} Based on how much data are used, the methods are mainly in two groups,  \textit{without extra information} and \textit{leveraging extra information}.
 
@@
 However they treat the word as the most basic unit in analysis, without regarding polysemy words.
-(3) By finding bursty topics via topic modelling, TimeUserLDA\cite{Diao:2012wj}, BurstyBTM\cite{Yan:2015wm} generates detected events.
-TimeUserLDA distinguishes user's long term interests and short term bursty events, and BurstyBTM utilizes the burstiness of biterms as prior knowledge.
+(3) By finding bursty topics via topic modelling, such as TimeUserLDA\cite{Diao:2012wj}, EUTB\cite{Yin2013A}, and BurstyBTM\cite{Yan:2015wm}.
+TimeUserLDA and EUTB distinguish user's long term interests and short term bursty events, and BurstyBTM utilizes the burstiness of biterms as prior knowledge.
 This kind method needs to set the appropriate number of topics, and detects the ``large" events but ignore the ``small" ones. 
@@
 However it's not easy to get this kind contextual information.
-\cite{osborne2012bieber} compares two time series generated by event-related tweets and the corresponding Wikipedia article's page views, and further filter out spurious events of microblogs.
+\cite{osborne2012bieber} compares two time series generated by event-related tweets and the corresponding Wikipedia article's page views, and further filter out spurious events.
 Twevent \cite{Twevent2012} divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia, then detect the bursty segments and cluster these segments into candidate events for necessary post processings.
@@
 However the query on large graph is very expensive\cite{huang2011scalable}, which is not very suitable for the scene of quickly and accurately detecting events.
-
 The customized knowledge bases such as EVIN\cite{kuzey2014evin}, Event Registry\cite{leban2014eventRegistry}, and Story-base\cite{wu2015storybase}, are designed for managing events.
@@
 As the news articles may lag behind the microblogs when the emergency of events, it's not enough to detect events from microblog stream by directly applying these customized knowledge bases.
+
+\textbf{Transfer Learning.} 
+%Transfer learning uses the knowledge in the source domain to enhance the performance of learning tasks on the target domain. \cite{dai2007transferring}
+Although the training examples in the target domain is very sparse, transfer learning\cite{Pan2010A} can utilize the domain-independent knowledge as the bridge to fill the information gap between source domain and target domain\cite{Xiang2010Bridging} to get more ``examples" for training.
+By bayesian transfer learning, \cite{dai2007transferring} uses the distribution in source domain as the prior knowledge for text classfication.
+And inspired by this idea, we propose the \textit{category-level topic} as the bridge for transferring knowledge.
 
@@
 Because Definitions 2 to 6 are very easy to understand, what needs to be specified are Definition 1.
-\textit{Category-level topics in knowledge base} is a set of tuples extracted from knowledge base, which weighs the importance of given words to the specific category, defined in Definition 1 formally.
+\textit{Category-level topics in knowledge base} is a set of tuples extracted from knowledge base, which weighs the importance of given words to the specific category by the chi-square score, defined in Definition 1 formally.
 Taking the \textit{Military} category in Figure \ref{fig:NSinitializaton} as an example, the category-level topic of \textit{military} contain the words \textit{army}, \textit{military}, and \textit{shootings} etc, which are highly related to the category \textit{Military}.
@@
 We take the detection in three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; and (3) retrieving event related microblogs.
-Note that these sub-phases are also available for the common text stream, but they performs better when words are enriched by category concepts of knowledge base.
+Note that these sub-phases are also available for the common text stream, but they perform better when words are enriched by category concepts of knowledge base.
 %这里添加对这几个Definition的解释。
@@
 We set \(K_{KB}=50\), which means 50 categories are selected manually to cover the topics of Wikipedia and the target corpus as widely as possible. 
-There are two kinds of categories are considered. 
+There are two kinds of categories considered. 
 The mid-high categories in the taxonomy graph \(G^{(0)'}\), which are representative, are likely to be selected, such as \textit{Aviation}, \textit{Military}, and \textit{Middle East}, etc.
@@
 \subsection{Effects of Event Detection}
-\textbf{Baselines Methods.} We compare our proposed method against the following methods, Twevent\cite{Twevent2012}, BurstyBTM\cite{Yan:2015wm}, LSH\cite{Petrovic:2010uj}, EDCoW\cite{Weng:2011wz}, and TimeUserLDA\cite{Diao:2012wj}, which are mentioned in the Section \ref{sec:relatedWorks}.
+\textbf{Baseline Methods.} We compare our proposed method against the following methods, Twevent\cite{Twevent2012}, BurstyBTM\cite{Yan:2015wm}, LSH\cite{Petrovic:2010uj}, EDCoW\cite{Weng:2011wz}, and TimeUserLDA\cite{Diao:2012wj}, which are mentioned in the Section \ref{sec:relatedWorks}.
 We implement these competing methods based on the open source community versions, e.g.
@@
 BurstyBTM\footnote{\url{https://github.com/xiaohuiyan/BurstyBTM}}.
-The above methods are set carefully according to the descriptions in the papers.
-More precisely, (1) for LSH, 13 bits per hash table, 20 hash tables are set, and top 500 clusters with high entropy are selected as the event candidates; (2) for Twevent, the number of candidate bursty segments is set to be the square root of the window size, the newsworthiness threshold is set to be 4, and 375 candidate events are detected; (3) for EDCoW, the tunable parameter \(\gamma\) value is set to be 40, and 349 bursty ``phrases" are found for evaluation; (4) for TimeUserLDA, the topic number is set to be 500, and the most 100 bursty topics are selected as candidate events; (5) for BurstyBTM, the topic number is set to be 200, which is also the number of bursty topics in the model.
-The information about the number of events to be evaluated is listed in Table \ref{tbl:overall}, where TransDetector detects 457 events after filtering out too niche events that contain less than 20 tweets.
+The above methods are set according to the descriptions in their papers.
+More precisely, (1) for LSH, 13 bits per hash table, 20 hash tables are set, and top 500 clusters with high entropy are selected as the event candidates; (2) for Twevent, the number of candidate bursty segments is set to be the square root of the window size, the newsworthiness threshold is set to be 4, and 375 candidate events are detected; (3) for EDCoW, the parameter \(\gamma\) is set to be 40, and 349 bursty ``phrases" are found for evaluation; (4) for TimeUserLDA, the topic number is set to be 500, and the most 100 bursty topics are selected as candidate events; (5) for BurstyBTM, the topic number is set to be 200, which is also the number of bursty topics in the model.
+The information about the number of events to be evaluated is listed in Table \ref{tbl:overall}, where TransDetector detects 457 events after filtering out too niche events containing less than 20 tweets.
 
@@
 Comparing to \textsc{TrasnDetector}, the existing methods are suffered from having to choose between precision and recall, but not both. 
-Taking the method Twevent as an example, which also utilizes the knowledge base for promoting the event detection performance, it has three parameters to trade off, in which the newsworthiness is the most impact one.
+Taking Twevent as an example, which also utilizes the knowledge base for promoting the event detection, it has three parameters to trade off, in which the newsworthiness is the most impact one. 
 In our experiment, when setting newsworthiness to be 4, Twevent achieves its best performance in terms of F value; lower or higher of value sacrifices the recall or precision. 
@@
 Knowledge base is constructed elaborately and contains rich information, which can benefit the not-well-organized text stream. 
+In our proposed \textsc{TransDetector} method, by using category-level topic in knowledge base as the prior knowledge, we transfer abundant knowledge from knowledge base into microblog stream, which enriches the semantics of microblogs and further enhances the accuracy of event detection for microblogs.
 As a part of our future work, we will explore the effects of transfer learning from knowledge base to text stream for more tasks, such as text classification and key words extraction, especially for short texts.
@@
 
-%\setlength{\parindent}{0pt}\textbf{Acknowledgments.} This research is supported by the Natural Science Foundation of China (Grant No.
-61572043), and the National Key Research and Development Program (Grant No.
-2016YFB1000704).
+\setlength{\parindent}{0pt}\textbf{Acknowledgments.} Thanks to Dr. Jian Tang and the anonymous reviewers for giving valuable suggestions on this work.
 %\newpage

### 2017-01-10 paper/DASFAA17_regular_64.tex
copy files for camera ready submission

@@
 \begin{rmkWithoutSpacing}[\textbf{Category-Level Word Time Series}] 
-Given category \(c\) and word \(w\), the category level word time series is a list of document frequencies extracted from \(\{\bm{r}_{c,t}\}_{t=1}^{T}\), and denoted as \(\{n(c,t,w^{(c)}_{i})\}_{t=1}^{T}\).
+Given category \(c\) and word \(w\), the category-level word time series is a list of document frequencies extracted from \(\{\bm{r}_{c,t}\}_{t=1}^{T}\), and denoted as \(\{n(c,t,w^{(c)}_{i})\}_{t=1}^{T}\).
 \end{rmkWithoutSpacing}
@@
 (1) The topics in the document may contain category-level topics. 
-As an example, the tweet ``Libyan rebel chief gunned down in Benghazi (2011-07-28)'' contains the topic that is similar to the \textit{Military}'s \textit{category-level topics in knowledge base}.
+As an example, the tweet ``Libyan rebel chief gunned down in Benghazi (2011-07-28)'' contains the topic that is similar to the \textit{Military}'s \textit{category-level topic in knowledge base}.
 (2) The \textit{category-level topics in microblog stream} can reuse the information stored in the corresponding \textit{category-level topics in knowledge base}.
@@
 
-In the above generative process, the line 2(a) is the key point to distinguish CTrans-LDA from LDA\cite{blei2003latent}, where \(\bm{\tau}_k\) is defined by Equation(\ref{eq:wikiPrior}).
+In the above generative process, the line 2 is the key point to distinguish CTrans-LDA from LDA\cite{blei2003latent}, where \(\bm{\tau}_k\) is defined by Equation(\ref{eq:wikiPrior}).
 \(K_{KB}\) is the number of pre-defined categories used for transferring, and \(S_k\) is the set of words appeared in the \(k\)-th category-level topic.
@@
 Knowledge base is constructed elaborately and contains rich information, which can benefit the not-well-organized text stream. 
-In our proposed \textsc{TransDetector} method, by using category-level topic in knowledge base as the prior knowledge, we transfer abundant knowledge from knowledge base into microblog stream, which enriches the semantics of microblogs and further enhances the accuracy of event detection for microblogs.
+In our proposed \textsc{TransDetector} method, by using category-level topic in knowledge base as the prior knowledge, we transfer abundant knowledge from knowledge base into microblog stream, which enriches the semantics of microblogs and further enhances the accuracy of microblogs event detection.
 As a part of our future work, we will explore the effects of transfer learning from knowledge base to text stream for more tasks, such as text classification and key words extraction, especially for short texts.

### 2017-03-22 paper/acmFormat.tex
remove duplicate references

--- 2016-06-14 paper/main.tex
@@
 \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
-\usepackage{algorithm}
-\usepackage{algorithmic}
+%\usepackage{algorithm}
 \usepackage{bm}
@@
 \subsection{Normal States' Maintenance}
-Asymmetric-Prior-LDA
+KB-Prior-LDA
 \begin{figure}[t]
     \centering
-    \includegraphics[height=3.5cm]{img/NTS.eps}
+    \includegraphics[width=1.0\columnwidth]{model/lda_tikz.pdf}
     \caption{Probabilistic model for training normal states by using history information.}

### 2017-03-22 paper/camera_ready/Source_64/DASFAA17_regular_64.tex
camera ready folder done
remove duplicate references

--- 2017-01-10 paper/DASFAA17_regular_64.tex
@@
 \usepackage{amsthm}%used for theorem and definition
-\usepackage{showframe}%show the margin
+%\usepackage{showframe}%show the margin
 %\usepackage{ulem}%used for uwave
@@
 2016YFB1000704).}}
-\titlerunning{Transfer Learning for Accurate Event Detection\ }
+\titlerunning{Category-Level Transfer Learning from Knowledge Base to Microblog Stream\ }
 \author{Weijing Huang\inst{1} \and Tengjiao Wang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Yazhou Wang\inst{1} }
@@
 % Special codes there for remove page numbers in the LaTeX documents
-\thispagestyle{empty}
-\pagestyle{empty}
+%\thispagestyle{empty}
+%\pagestyle{empty}
 %
@@
 For example, Probase\cite{wu2012probase} constructs a large general probabilistic \textit{IsA} taxomomy from webpages, and is used for semantic web search, and text classification\cite{wang2014concept}.
-Such kind efforts are also made by DBPedia\cite{auer2007dbpedia}, Yago\cite{fabian2007yago}, and Freebase\cite{bollacker2008freebase}. 
+Such kind efforts are also made by DBPedia\cite{auer2007dbpedia}, Yago\cite{suchanek2007yago}, and Freebase\cite{bollacker2008freebase}. 
 These works manages knowledge as tuples on graph. 
@@
 %Transfer learning uses the knowledge in the source domain to enhance the performance of learning tasks on the target domain. \cite{dai2007transferring}
-Although the training examples in the target domain is very sparse, transfer learning\cite{Pan2010A} can utilize the domain-independent knowledge as the bridge to fill the information gap between source domain and target domain\cite{Xiang2010Bridging} to get more ``examples" for training.
+Although the training examples in the target domain is very sparse, transfer learning\cite{pan2010survey} can utilize the domain-independent knowledge as the bridge to fill the information gap between source domain and target domain\cite{Xiang2010Bridging} to get more ``examples" for training.
 By bayesian transfer learning, \cite{dai2007transferring} uses the distribution in source domain as the prior knowledge for text classfication.

### 2017-03-23 paper/presentation/DASFAA_presentation.tex
begin to prepare DASFAA 2017 presentation

\documentclass{beamer}

\usetheme{CambridgeUS}

\setbeamercolor{title}{bg=red!65!black,fg=white}

\setbeamertemplate{sidebar right}
{
  \vfill%
  \llap{\insertlogo\hskip0.1cm}%
  \vskip2pt%
  %\llap{\href{http://tex.stackexchange.com/}{A link to tex.sx}\hskip0.2cm}% NEW
  \vskip3pt% NEW
  \llap{\usebeamertemplate***{navigation symbols}\hskip0.1cm}%
  \vskip2pt%
}

\begin{document}

\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\author{Weijing Huang, Tengjiao Wang, Wei Chen, Yazhou Wang}
\institute[Peking University]{Peking University}
\date{DASFAA 2017}
\maketitle

%------------------------------
%page 2
\begin{frame}
\frametitle{Neural Network View of Topic Models (1/2)}

The conditional probability \(p(w|d)\) is the combination of \textbf{word-topic distribution} \(p(w|t_i)\) and \textbf{topic-document distribution} \(p(t_i|d)\).
\begin{equation}
\label{eq:tm}
	p(w|d)=\sum_{i=1}^{K} p(w|t_i)p(t_i|d)
\end{equation}

Equation (\ref{eq:tm}) equals to the following form:
\begin{equation}
\label{eq:nnv_tm}
p(w|d)=\phi(w) \theta^T(d)
\end{equation}
, where \(\phi(w)\) is the row vector \textbf{word-topic distribution} \([p(w|t_1), \cdots, p(w|t_K)]\), and \(\theta(d)\) is the row vector \textbf{topic-document distribution} \([p(t_1|d), \cdots, p(t_K|d)]\).

\end{frame}

%------------------------------
%page 3
\begin{frame}
\frametitle{Neural Network View of Topic Models (2/2)}

In equation (\ref{eq:nnv_tm}), the distributions \(\phi(w)\) and \(\theta(d)\) have the following explanation:
\begin{enumerate}
	\item \(\phi(w)\) functions as the look-up layer for words with the \textbf{sigmoid} activation functions.
	\item \(\theta(d)\) functions as the look-up layer for documents with the \textbf{softmax} activation function. 
\end{enumerate}

\end{frame}

%------------------------------
%page 4
\begin{frame}
\frametitle{Neural Topic Model (NTM)}	
Symbols:

\end{frame}

\end{document}

### 2017-03-24 paper/presentation/DASFAA_presentation.tex
slide frame

@@
 \setbeamercolor{title}{bg=red!65!black,fg=white}
+\usepackage{bm}
+\usepackage{graphics} % used for scalebox
+\usepackage{multirow}%used for multicolumn
+\usepackage{array}%used for vrule
+\usepackage{subfigure}
+\usepackage{threeparttable} % used for footnotes in table
 
@@
 \author{Weijing Huang, Tengjiao Wang, Wei Chen, Yazhou Wang}
-\institute[Peking University]{Peking University}
-\date{DASFAA 2017}
+\institute[EECS, Peking University]{School of Electronics Engineering and Computer Science, Peking University}
+\date{\(\bm{@}\)DASFAA 2017, Suzhou, China}
 \maketitle
@@
 \begin{frame}
-\frametitle{Neural Network View of Topic Models (1/2)}
+\frametitle{Motivation}
 
@@
 \begin{frame}
-\frametitle{Neural Network View of Topic Models (2/2)}
+\frametitle{Challenges (1/2)}
+What we have already known:
+
+What we maybe know, but didn't pay much attention:
 
@@
 \begin{frame}
-\frametitle{Neural Topic Model (NTM)}	
-Symbols:
+\frametitle{Challenges (2/2)}	
+Statistics of some labeled events on Edinburgh twitter corpus.
+\intextsep=5pt plus 3pt minus 1pt % 调整表格与正文的上间距
+\begin{table}[]
+\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
+\setlength{\belowcaptionskip}{0.cm}
+\centering
+\caption{My caption}
+\label{my-label}
+\scalebox{0.65}{
+\begin{tabular}{|l|l|r|}
+\hline
+Event                                        & Date       & Event Size \\ \hline
+S\&P downgrade US credit rating                  & 05/08/2011 & 656      \\ \hline
+Atlantis shuttle lands                           & 21/07/2011 & 595      \\ \hline
+US increases debt ceiling                        & 25/07/2011 & 485      \\ \hline
+Plane with Russian hocky team Lokomotiv crashes  & 07/09/2011 & 286      \\ \hline
+Amy Winehouse dies                               & 23/07/2011 & 283      \\ \hline
+Gunman opens fire in youth camp in Norway        & 23/07/2011 & 260      \\ \hline
+Earthquake in Virginia                           & 24/08/2011 & 246      \\ \hline
+First victim of London riots dies                & 09/08/2011 & 174      \\ \hline
+Explosion in French nuclear plant in Marcoule    & 12/09/2011 & 135      \\ \hline
+Google announces plans to bury Motorola Mobility & 15/08/2011 & 127      \\ \hline
+NASA announces there might be water on Mars      & 04/08/2011 & 124      \\ \hline
+Car bomb explodes in Oslo, Norway                & 22/07/2011 & 114      \\ \hline
+... & ... & ... \\ \hline
+Indian and Bangladesh sign a border pact         & 06/09/2011 & 25       \\ \hline
+Flight 4896 crash                                & 13/07/2011 & 21       \\ \hline
+First aritficial organ transplant                & 12/07/2011 & 18       \\ \hline
+three men die in riots in england                & 10/08/2011 & 16       \\ \hline
+rebels capture interational tripoli airport      & 21/08/2011 & 13       \\ \hline
+\end{tabular}
+}
+\end{table}
+\end{frame}
+
+%------------------------------
+%page 5
+\begin{frame}
+\frametitle{How about existing methods on dealing with challenges?}
+
+\end{frame}
+
+%------------------------------
+%page 6
+\begin{frame}
+\frametitle{An Example}	
+\begin{figure}[h]
+		\setlength{\abovecaptionskip}{0.cm}
+        \setlength{\belowcaptionskip}{0.cm}
+        \centering
+        \includegraphics[width=1.0\columnwidth]{../img/hood.pdf}
+        \caption{The comparison of the time series between the raw word \textit{hood} and the \textit{Military} related word \textit{hood}, computed on the \textit{Edinburgh twitter corpus}.
+The rise of document frequency on July 28th, 2011 is corresponding to the event mentioned in \url{https://en.wikipedia.org/wiki/Fort_Hood\#2011_attack_plot}.}
+        \label{fig:hood}
+\end{figure}
+\end{frame}
+
+%------------------------------
+%page 7
+\begin{frame}
+\frametitle{The insights on the example}
+
+\end{frame}
+
+%------------------------------
+%page 8
+\begin{frame}
+\frametitle{Overview of our method}
+
+\begin{figure}[h]
+		\setlength{\abovecaptionskip}{0.cm}
+        \setlength{\belowcaptionskip}{0.cm}
+        \centering
+        \includegraphics[width=0.5\columnwidth]{../img/NSDetectorExample.pdf}
+        \caption{\textsc{TransDetector}'s processing flow, taking \textit{Military} related events in microblogs as an example.}
+        \label{fig:hood}
+\end{figure}
+
+\end{frame}
+
+%------------------------------
+%page 9
+\begin{frame}
+\frametitle{\textsc{TransDetector}: Phrase 1}	
+\begin{figure}[h]
+		\setlength{\abovecaptionskip}{0.cm}
+        \setlength{\belowcaptionskip}{0.cm}
+        \centering
+        \includegraphics[width=0.5\columnwidth]{../img/initializationExample.pdf}
+        \caption{Extracting Category-Level Topics in Knowledge Base via its three fold hierarchical structure, taking \textit{Military} as an example.}
+        \label{fig:hood}
+\end{figure}
+
+\end{frame}
+
+%------------------------------
+%page 10
+\begin{frame}
+\frametitle{\textsc{TransDetector}: Phrase 2}
+
+\end{frame}
+
+%------------------------------
+%page 11
+\begin{frame}
+\frametitle{\textsc{TransDetector}: Phrase 3}
+
+\end{frame}
+
+%------------------------------
+%page 12
+\begin{frame}
+\frametitle{Experimental Results}	
+\begin{figure}[h]
+	\setlength{\abovecaptionskip}{0.cm}
+	\setlength{\belowcaptionskip}{0.cm}
+        \centering
+        \includegraphics[width=1.0\columnwidth]{../img/NPMI.pdf}
+        \caption{More topics are compared at the NPMI metrics between our method and LightLDA}
+        \label{fig:NPMI}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+\frametitle{some}
+
+\begin{table}[h]
+\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
+\setlength{\belowcaptionskip}{0.cm}
+\centering
+\caption{The comparison on the topic coherence(NPMI) between our method and LightLDA, taking \textit{Aviation} as an example.
+(NPMI is computed on a group of ten words.
+\(\sim\) stands for the top five words.)}
+\scalebox{0.45}{
+\begin{tabular}{|c|l|l|c !{\vrule width 1pt} c|l|l|c|}
+\hline
+\multicolumn{4}{|c!{\vrule width 1pt}}{Category-Level Topics extracted from Wikipedia by \textsc{TransDetector}} & \multicolumn{4}{c|}{Topics Learned from Wikipedia by LightLDA}    \\ \hline
+GID& \#words*  & words  & NPMI & GID& \#words*& words & NPMI \\ \hline
+- & 1-5 & aircraft air airport flight airline &-& - & 1-5 & engine aircraft car air power &-\\ \hline
+0 & 1-5, 6-10 & \(\sim\), airlines aviation flying pilot squadron &  0.113 & 0 & 1-5, 6-10 & \(\sim\), design flight model production speed & 0.112\\ \hline
+1 & 1-5, 11-15 & \(\sim\), flights pilots raf airways fighter & 0.155 & 1 & 1-5, 11-15 &\(\sim\), system vehicle cars engines mm & 0.062\\ \hline
+2 & 1-5, 16-20 & \(\sim\), boeing runway force crashed flew   & 0.092 & 2 & 1-5, 16-20 & \(\sim\), fuel vehicles designed models type & 0.072\\ \hline
+3 & 1-5, 21-25 &\(\sim\), airfield landing passengers plane aerial & 0.179 & 3 & 1-5, 21-25 & \(\sim\), version front produced rear electric & 0.035\\ \hline
+4 & 1-5, 26-30 &\(\sim\), bomber radar wing bombers crash & 0.137 & 4 & 1-5, 26-30 & \(\sim\), space control motor standard development & 0.085\\ \hline
+5 & 1-5, 31-35 &\(\sim\), airbus airports operations jet helicopter & 0.189 & 5 & 1-5, 31-35 & \(\sim\), film range light using available & -0.002\\ \hline
+6 & 1-5, 36-40 &\(\sim\), squadrons base flown havilland crew & 0.088 & 6 & 1-5, 36-40 & \(\sim\), wing powered wheel weight launch & 0.087\\ \hline
+7 & 1-5, 41-45 & \(\sim\), combat luftwaffe aerodrome carrier fokker & 0.159 & 7 & 1-5, 41-45 & \(\sim\), developed low test ford cylinder & 0.007\\ \hline
+8 & 1-5, 46-50 &\(\sim\), planes fly engine takeoff fleet & 0.186 & 8 & 1-5, 46-50 & \(\sim\), equipment side pilot hp aviation & 0.091\\ \hline
+9 & 1-5, 51-55 &\(\sim\), fuselage helicopters aviator naval aero & 0.157 & 9 & 1-5, 51-55 & \(\sim\), systems us sold body drive & -0.051\\ \hline
+10 & 1-5, 56-60 &\(\sim\), glider command training balloon faa & 0.166 & 10 & 1-5, 56-60 & \(\sim\), gear introduced class safety seat & 0.069\\ \hline
+\(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\) & \(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
+18 & 1-5, 96-100 &\(\sim\), scheduled carriers military curtiss biplane &0.131 & 18 & 1-5, 96-100 & \(\sim\), transmission special replaced limited different & 0.059\\ \hline
+19 & 1-5, 101-105 &\(\sim\), accident engines iaf albatross rcaf &0.068 & 19 & 1-5, 101-105 & \(\sim\), features machine nuclear even unit & 0.011\\ \hline
+\end{tabular}
+}
+\label{tbl:NPMIDetails}
+\end{table}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Experiment Settings}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Experimental Results}	
+\begin{table}
+\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
+\setlength{\belowcaptionskip}{0.cm}
+\centering
+\caption{Category-Level Topics extracted from knowledge base and the corresponding topics on microblog stream learned from CTrans-LDA.
+The words in \textbf{\textit{bold}} font are newly learned on the microblog stream by the transfer learning.}
+\scalebox{0.55}{
+\begin{tabular}{|cc|cc|cc|cc|cc|cc|}
+\hline
+\multicolumn{2}{|c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Middle East}} & \multicolumn{2}{c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Mobile Phones}}\\
+\begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} & \begin{tabular}[c]{@{}c@{}}Knowledge\\ Base\end{tabular} & \begin{tabular}[c]{@{}c@{}}Microblog\\ Stream\end{tabular} \\
+\hline
+aircraft & air & health & weight & al & \textbf{\textit{\#syria}} & army & killed & android & iphone\\ 
+air & plane & patients & loss & israel & \textbf{\textit{\#bahrain}} & military & news & mobile & apple \\ 
+airport & flight & medical & diet & iran & people & air & \textbf{\textit{\#libya}} & nokia & android \\ 
+flight & time & disease & health & arab & israel & command & libya & ios & app \\
+airline & airlines & treatment & cancer & israeli & police & force & rebels & phone & ipad \\
+airlines & news & hospital & lose & egypt & \textbf{\textit{\#libya}} & regiment & people & samsung & samsung \\
+aviation & boat & patient & fat & egyptian & \#egypt & forces & police & game & mobile\\
+flying & airport & clinical & tips & ibn & news & squadron & war & app & blackberry \\
+pilot & force & symptoms & treatment & jerusalem & \textbf{\textit{\#israel}} & infantry & libyan & iphone & tablet \\
+squadron & fly & cancer & body & syria & world & battle & attack & htc & apps\\
+\hline
+\end{tabular}
+}
+\label{tbl:historyStates}
+\end{table}
+\end{frame}
+
+\begin{frame}
+\frametitle{Experimental Results}	
+\begin{table}[h]
+\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
+\setlength{\belowcaptionskip}{0.cm}
+\centering
+\caption{Overall Performance on Event Detection}
+
+\scriptsize
+\scalebox{0.75}{
+\begin{threeparttable}
+
+\begin{tabular}{|c|c|c|c|c|c|c|}
+    \hline
+    Method & \begin{tabular}[c]{@{}c@{}}Number of\\Events to \\ be Evaluated \end{tabular} & \begin{tabular}[c]{@{}c@{}}Recall@ \\ Benchmark1\end{tabular}& \begin{tabular}[c]{@{}c@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}c@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}c@{}}F@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}c@{}}DERate\tnote{a}\ \ (Duplicate\\ Event Rate)@\\ Benchmark2\end{tabular} \\ \hline
+    LSH & 500 & 0.704 & 0.788 & 0.651 & 0.713 & 0.348 \\ \hline
+    TimeUserLDA & 100 & 0.370 & 0.790 & 0.177 & 0.289 & 0.114 \\ \hline
+    Twevent & 375 &  0.741 & 0.808 & 0.658 & 0.725 & 0.142 \\ \hline
+    EDCoW & 349 & 0.556 & 0.748 & 0.511 & 0.607 & 0.226 \\ \hline
+    BurstyBTM & 200 & 0.667 & 0.825 & 0.384 & 0.497 & \textbf{0.079} \\ \hline
+    \textsc{TransDetector} & 457 & \textbf{0.889} & \textbf{0.912} & \textbf{0.876} & \textbf{0.894} & 0.170 \\ \hline
+    \end{tabular}
+
+\begin{tablenotes}  
+\item[a] DERate = (the number of duplicate events) / (the total number of detected realistic events)
+\end{tablenotes}  
+\end{threeparttable}  
+}
+\label{tbl:overall}
+\end{table}
+\end{frame}
+
+\begin{frame}
+\frametitle{Experimental Results}	
+\begin{figure}[h]
+	\setlength{\abovecaptionskip}{0.cm}
+	\setlength{\belowcaptionskip}{0.cm}
+        \centering
+        \includegraphics[width=1.0\columnwidth]{../img/barchartOnBenchmark1.pdf}
+        \caption{The relation between the recall and the event size}
+        \label{fig:Benchmark1}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+\frametitle{Experimental Results}	
+\begin{table}
+\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
+\setlength{\belowcaptionskip}{0.cm}
+\centering
+\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-28}
+\label{my-label}
+\scalebox{0.6}{
+\begin{threeparttable}  
+\begin{tabular}{|c|l|l|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Date} & \multirow{2}{*}{Event key words} & \multirow{2}{*}{Representative event tweet} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular}} & \multicolumn{6}{c|}{Methods\tnote{a}} \\ \cline{5-10}
+ &  &  &  & L & TU & TW & E & B & TD \\ \hline
+7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb\\ ripped through government offices in Oslo \\and a gunman...
+http://dlvr.it/cLbk8\end{tabular} & 557 & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\ \hline
+7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller\\ Rink http://dlvr.it/cLcTH\end{tabular} & 43 & - & - & \checkmark &  \checkmark & - & \checkmark \\ \hline
+7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by\\ Afghan suicide bomber: The mayor of \\Kandahar, the biggest city in south \_\end{tabular} & 47 & \checkmark & - & \checkmark & \checkmark & - & \checkmark \\ \hline
+7/28/11 & Ft., Hood, attack & \begin{tabular}[c]{@{}l@{}} Possible Ft. Hood Attack Thwarted\\ http://t.co/BSJ33hk\end{tabular} & 52 & - & - & - & - & - & \checkmark \\ \hline
+7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 & - & - & - & - & - & \checkmark \\ \hline
+\end{tabular}
+
+\begin{tablenotes}  
+\item[a] L=LSH, TU=TimeUserLDA, TW=Twevent, E=EDCoW, B=BurstyBTM, TD=\textsc{TransDetector}.
+\end{tablenotes}  
+\end{threeparttable}  
+}
+\end{table}
+
+\end{frame}
+
+\begin{frame}
+%\frametitle{A first slide}
+
+\begin{center}
+\Huge Thanks!
+\end{center}
+
+\begin{center}
+\Huge Q\&A
+\end{center}
+
+%\begin{figure}[h]
+%	\setlength{\abovecaptionskip}{0.cm}
+%	\setlength{\belowcaptionskip}{0.cm}
+%        \centering
+%        \includegraphics[width=0.3\columnwidth]{code.png}
+%\end{figure}
+
+\footnotetext{This slide and more data are available at \url{http://q-r.to/bajx8I}}
 

### 2017-03-24 paper/presentation/DASFAA_presentation.tex
use tikz and textblock for beamer

@@
+% arara: pdflatex
+% !arara: indent: {overwrite: on}
 \documentclass{beamer}
@@
 
+%-chage foot part-------------------------------
+\makeatother
+\setbeamertemplate{footline}
+{
+  \leavevmode%
+  \hbox{%
+  \begin{beamercolorbox}[wd=.17\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
+    \usebeamerfont{author in head/foot}\insertshortauthor
+  \end{beamercolorbox}%
+  \begin{beamercolorbox}[wd=.46\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
+    \usebeamerfont{title in head/foot}\insertshorttitle
+  \end{beamercolorbox}%
+  \begin{beamercolorbox}[wd=.37\paperwidth,ht=2.25ex,dp=1ex,center]{date in head/foot}% 
+  \insertdate \hspace{0.2cm}
+    \insertframenumber{} / \inserttotalframenumber\hspace*{1ex}
+  \end{beamercolorbox}}%
+  \vskip0pt%
+}
+\makeatletter
+\setbeamertemplate{navigation symbols}{}
+%--------------------------------
+
+%-chage titlepage's font-------------------------------
 \setbeamercolor{title}{bg=red!65!black,fg=white}
 \usepackage{bm}
+\usepackage{comment}
 \usepackage{graphics} % used for scalebox
@@
 \usepackage{threeparttable} % used for footnotes in table
+
+%---set tikz highlighter------------------------
+\usepackage{multirow, booktabs, dcolumn, color} % Tables
+\usepackage[beamer,customcolors]{hf-tikz}
+\usetikzlibrary{calc}
+% To set the hypothesis highlighting boxes red.
+\tikzset{hl/.style={
+    set fill color=red!80!black!40,
+    set border color=red!80!black,
+  },
+}
+%-----------------------------------------------
+
+%---set tikz marker-----------------------------
+\usepackage{tikz}
+\usetikzlibrary{positioning}
+\tikzset{>=stealth}
+
+\newcommand{\tikzmark}[3][]{\tikz[overlay,remember picture,baseline] \node [anchor=base,#1](#2) {#3};}
+%-----------------------------------------------
+
+%---set textblock----------------------------
+\usepackage[absolute,overlay]{textpos}
+%--------------------------------------------------------
 
@@
 
-\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
-\author{Weijing Huang, Tengjiao Wang, Wei Chen, Yazhou Wang}
+\title[Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection]{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
+\author[Weijing Huang, et,al.]{Weijing Huang, Tengjiao Wang, Wei Chen, Yazhou Wang}
 \institute[EECS, Peking University]{School of Electronics Engineering and Computer Science, Peking University}
@@
 \frametitle{Challenges (2/2)}	
-Statistics of some labeled events on Edinburgh twitter corpus.
+\tikzmark{comment18}\,
+
 \intextsep=5pt plus 3pt minus 1pt % 调整表格与正文的上间距
@@
 \centering
-\caption{My caption}
+\caption{Statistics of labeled events on Edinburgh twitter corpus.}
 \label{my-label}
@@
 ... & ... & ... \\ \hline
-Indian and Bangladesh sign a border pact         & 06/09/2011 & 25       \\ \hline
+\tikzmarkin<1>[hl]{bH1}Indian and Bangladesh sign a border pact         & 06/09/2011 & 25       \\ \hline
 Flight 4896 crash                                & 13/07/2011 & 21       \\ \hline
@@
 three men die in riots in england                & 10/08/2011 & 16       \\ \hline
-rebels capture interational tripoli airport      & 21/08/2011 & 13       \\ \hline
+rebels capture interational tripoli airport      & 21/08/2011 & 13       \tikzmarkend{bH1} \\ \hline
 \end{tabular}
@@
 \end{table}
+
+ \begin{textblock}{0.1}(14,12)
+  \footnotesize{Small events with fewer tweets}
+ \end{textblock}
+
 \end{frame}
 
+%\begin{comment}
 %------------------------------
@@
 
+%\end{comment}
+
 \end{document}

### 2017-03-24 paper/presentation/DASFAA_presentation.tex
finish the first page

@@
 
-The conditional probability \(p(w|d)\) is the combination of \textbf{word-topic distribution} \(p(w|t_i)\) and \textbf{topic-document distribution} \(p(t_i|d)\).
-\begin{equation}
-\label{eq:tm}
-	p(w|d)=\sum_{i=1}^{K} p(w|t_i)p(t_i|d)
-\end{equation}
+Many Web applications need the \textbf{accurate event detection} technique on microblog stream, including:
+\begin{enumerate}
+	\item public opinion analysis [Chen, SIGIR 2013]
+	\item public security [Li, ICDE 2012], [Imran, WWW 2014]
+	\item disaster response [Sakaki,WWW2010]
+	\item breaking news report\footnote{\url{http://www.theverge.com/2016/12/1/13804542/reuters-algorithm-breaking-news-twitter}}
+\end{enumerate}	
+\vfill
 
-Equation (\ref{eq:tm}) equals to the following form:
-\begin{equation}
-\label{eq:nnv_tm}
-p(w|d)=\phi(w) \theta^T(d)
-\end{equation}
-, where \(\phi(w)\) is the row vector \textbf{word-topic distribution} \([p(w|t_1), \cdots, p(w|t_K)]\), and \(\theta(d)\) is the row vector \textbf{topic-document distribution} \([p(t_1|d), \cdots, p(t_K|d)]\).
-
+But detecting events on twitter stream accurately is still challenging.
 \end{frame}
@@
 What we maybe know, but didn't pay much attention:
-
-In equation (\ref{eq:nnv_tm}), the distributions \(\phi(w)\) and \(\theta(d)\) have the following explanation:
-\begin{enumerate}
-	\item \(\phi(w)\) functions as the look-up layer for words with the \textbf{sigmoid} activation functions.
-	\item \(\theta(d)\) functions as the look-up layer for documents with the \textbf{softmax} activation function. 
-\end{enumerate}
 

### 2017-03-24 paper/presentation/DASFAA_presentation.tex
first three pages

@@
 
+%use bold arrow
+\usepackage{marvosym}
+
 \setbeamertemplate{sidebar right}
@@
 \frametitle{Challenges (1/2)}
-What we have already known:
+According to [Huang, WWW 2016], the challenges include,
+\begin{enumerate}
+\item fast changing
+\item high noise
+\item short length
+\end{enumerate}
 
-What we maybe know, but didn't pay much attention:
+\vfill
+
+And, we found another key factor, 
+\begin{enumerate}
+\item Small events with fewer tweets \MVRightarrow \ \ Hard to trade off between precision and recall. 
+\end{enumerate}
 
@@
 \frametitle{Challenges (2/2)}	
-\tikzmark{comment18}\,
+Exploratory study on the on Edinburgh twitter corpus: 11/29 events contains less than 50 tweets.
 
@@
 \centering
-\caption{Statistics of labeled events on Edinburgh twitter corpus.}
+\caption{Statistics of labeled events.}
 \label{my-label}
@@
 
- \begin{textblock}{0.1}(14,12)
-  \footnotesize{Small events with fewer tweets}
+ \begin{textblock}{0.1}(13.5,11.7)
+  \footnotesize{11 Small events with fewer tweets}
  \end{textblock}

### 2017-03-24 paper/presentation/DASFAA_presentation.tex
finish related works

@@
 \frametitle{Challenges (2/2)}	
-Exploratory study on the on Edinburgh twitter corpus: 11/29 events contains less than 50 tweets.
+Exploratory study on the \textit{Edinburgh twitter corpus}: 11/29 events contain less than 50 tweets.
 
@@
 \begin{frame}
-\frametitle{How about existing methods on dealing with challenges?}
+\frametitle{How about existing methods? (1/2)}
+Event detection methods \textit{without extra information}, such as
+\begin{enumerate}
+\item clustering articles
+\begin{itemize}
+	\item LSH[Petrovic, NAACL 2010]
+	\item need to set threshold to determine whether new article represents a new event.
+\end{itemize}
+\item analyzing word frequencies
+\begin{itemize}
+	\item EDCoW[Weng, ICWSM 2011]
+	\item treat the word as the basic unit in analysis, without regarding polysemy words (words have different meanings, e.g. ``apple")
+\end{itemize}
+\item finding bursty topics via topic modeling
+\begin{itemize}
+	\item TimeUserLDA[Diao, ACL 2012], BurstyBTM[Yan, AAAI 2015]
+	\item detects the ``large" events but may ignore the ``small" ones. 
+\end{itemize}
+\end{enumerate}
+\end{frame}
 
+\begin{frame}
+\frametitle{How about existing methods? (2/2)}
+Event detection methods \textit{by leveraging extra information}
+\begin{enumerate}
+	\item typical one: Twevent[Li, CIKM 2012]
+	\begin{itemize}
+		\item divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia
+		\item detects the bursty segments and cluster these segments into candidate events
+		\item still have to trade off between precision and recall
+	\end{itemize}
+\end{enumerate}
 \end{frame}

### 2017-03-24 paper/presentation/DASFAA_presentation.tex
finish the example, [todo] add the explain to the example

@@
 \usepackage{marvosym}
+
+%used for aligning the figure to left
+\usepackage[export]{adjustbox}
 
@@
 		\item detects the bursty segments and cluster these segments into candidate events
-		\item still have to trade off between precision and recall
+		\item still has to trade off between precision and recall
 	\end{itemize}
@@
 \begin{frame}
+Much easier to detect the event on the time series of word "hood" related to \textit{Military}.
 \frametitle{An Example}	
@@
         \caption{The comparison of the time series between the raw word \textit{hood} and the \textit{Military} related word \textit{hood}, computed on the \textit{Edinburgh twitter corpus}.
-The rise of document frequency on July 28th, 2011 is corresponding to the event mentioned in \url{https://en.wikipedia.org/wiki/Fort_Hood\#2011_attack_plot}.}
+Refer the event to \url{https://en.wikipedia.org/wiki/Fort_Hood\#2011_attack_plot}.}
         \label{fig:hood}
+\end{figure}
+
+\begin{figure}[h]
+		\setlength{\abovecaptionskip}{0.cm}
+        \setlength{\belowcaptionskip}{0.cm}
+        \centering
+        \includegraphics[width=0.5\columnwidth, left]{Fort_Hood.pdf}
 \end{figure}

### 2017-03-25 paper/presentation/DASFAA_presentation.tex
finish the example, [todo] overview of our solution

@@
 \usepackage[export]{adjustbox}
+
+%used for colored block
+\usepackage[listings,theorems]{tcolorbox}
 
@@
 \begin{frame}
-Much easier to detect the event on the time series of word "hood" related to \textit{Military}.
+\textbf{Much easier} to detect the event on the time series of word ``hood" related to \textit{Military}, \textbf{without adjusting the threshold}.
 \frametitle{An Example}	
@@
 \frametitle{The insights on the example}	
+\begin{columns}[onlytextwidth, t]
+\column{0.48\linewidth}
+    \begin{tcolorbox}[colback=red!5,colframe=red!5]
+    Knowledge Base
+        \begin{itemize}
+            \item Well organized
+            \item Constructed elaborately
+            \item full of rich information
+        \end{itemize}
+    \end{tcolorbox}
+
+\column{0.48\linewidth}
+    \begin{tcolorbox}[colback=red!5,colframe=red!5]
+    Microblog stream
+        \begin{itemize}
+            \item Short length
+            \item Fast changing
+            \item High noise
+        \end{itemize}
+    \end{tcolorbox}
+\end{columns}
+
+\begin{tcolorbox}[colback=red!5,colframe=red!75!black]
+The benefit of \textbf{enriching the semantics} and \textbf{filtering out noise} by Knowledge Base for microblogs is attractive.
+\\~\\
+But it's expensive to retrieve every word of tweets in the Knowledge Base.
+\end{tcolorbox}
 
@@
 \begin{frame}
-\frametitle{Overview of our method}
+\frametitle{Overview of our solution}
 
@@
 
+\begin{comment}
 %------------------------------
@@
 
-%\end{comment}
+\end{comment}
 

### 2017-03-25 paper/presentation/DASFAA_presentation.tex
presentation 0.9

@@
 
+%used for algorithm
+\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
+\usepackage{algorithmic}
+
 \setbeamertemplate{sidebar right}
@@
 \frametitle{Challenges (2/2)}	
-Exploratory study on the \textit{Edinburgh twitter corpus}: 11/29 events contain less than 50 tweets.
+Exploratory study on the \textit{Edinburgh twitter corpus}: 11/27 events contain less than 50 tweets.
 
@@
 \begin{frame}
-\frametitle{Overview of our solution}
+\frametitle{Our solution}	
+\textsc{TransDetector}: a novel category-level transfer learning method
+\begin{itemize}
+	\item transfer KB's \textbf{category-level info} into microblog stream
+	\item balance the performance and the cost of leveraging knowledge base for event detection
+\end{itemize}
 
+\intextsep=5pt plus 3pt minus 1pt % 调整表格与正文的上间距
 \begin{figure}[h]
@@
         \centering
-        \includegraphics[width=0.5\columnwidth]{../img/NSDetectorExample.pdf}
-        \caption{\textsc{TransDetector}'s processing flow, taking \textit{Military} related events in microblogs as an example.}
+        \includegraphics[width=0.43\columnwidth]{../img/NSDetectorExample.pdf}
+        \caption{\textsc{TransDetector}'s processing flow, in 3 phases.}
         \label{fig:hood}
@@
 
-\begin{comment}
+\begin{frame}
+\frametitle{\textsc{TransDetector}: Phase 1 (Extracting Category-Level Topics in KB)}	
+There is a three fold hierarchical structure in Knowledge Base.
+\begin{enumerate}
+	\item \textbf{Taxonomy Graph \(G^{(0)}\)}. The directed edges in \(G^{(0)}\) represent the \textit{class}\(\rightarrow\)\textit{subclass} relations in KB. 
+		\begin{itemize}
+			\item e.g., \textit{Main topic classifications} \(\rightarrow\) \textit{Society}
+		\end{itemize}
+	\item \textbf{Category-Page Bipartite Graph \(G^{(1)}\)}. The directed edges in \(G^{(1)}\) represent the \textit{class}\(\rightarrow\)\textit{instance} relations in KB.
+		\begin{itemize}
+			\item e.g., \textit{Military} \(\rightarrow\) \textit{page: Armed Forces}
+		\end{itemize}
+	\item \textbf{Page-Content Map \(G^{(2)}\)}. 
+For a specific Wikipedia dumps version, the edges  \textit{page} \(\rightarrow\)\textit{content} in \(G^{(2)}\) define a one-to-one mapping.
+		\begin{itemize}
+			\item e.g., \textit{page: Armed Forces} \(\rightarrow\) \textit{content(20170325version): ``The armed forces of a country are its government-sponsored defense, fighting forces, and organizations..."}
+		\end{itemize}
+\end{enumerate}
+\end{frame}
+
+\begin{frame}
+\frametitle{\textsc{TransDetector}: Phase 1 (Extracting Category-Level Topics in KB)}
+\begin{algorithm}[H]
+\scriptsize
+\caption{Extraction of Category-Level Topics in Knowledge Base}
+\label{alg:normalStatesInit}
+
+\KwIn{Taxonomy's Graph \(G^{(0)}\), Category-Page Bipartite Graph \(G^{(1)}\), Page-Content Bipartite Graph \(G^{(2)}\), topic related category node \(c\)}
+\KwOut{\(c\)'s category-level topic in knowledge base \(\bm{h}_c\)}
+\(Pages(c)\leftarrow \varnothing\), \(\bm{h}_c \leftarrow \varnothing\)\\
+DAG \(G^{(0)'} \leftarrow\) Remove Cycles of \(G^{(0)}\) by nodes' HITS-PageRank scores. \label{alg:line2inNormalStatesInit}\\
+\(SuccessorNodes(c) \leftarrow \) Breadth-first-traverse(\(G^{(0)'},c\))\label{alg:line3inNormalStatesInit}\\
+\For{\(node \in SuccessorNodes(c)\)}{
+    \(Pages(c) \leftarrow Pages(c) \cup G^{(1)}.neighbours(node)\) \label{alg:line5inNormalStatesInit}\\
+}
+Word frequency table \(n(c,.) \leftarrow \) do word count on the text contents of \(Pages(c)\) \\
+Word frequency table \(n(All,.) \leftarrow \) do word count on the text contents of all pages in \(G^{(2)}\).\\
+\For{word \(w\) in WordFrequencyTable(All).keys()}{
+    \(chi(c,w) \leftarrow \) \(w\)'s chi-square statistics on \(WordFrequencyTable(c)\) and \(WordFrequencyTable(All)\).\\
+    \(h_{c,w} \leftarrow chi(c,w)\) \label{alg:line10inNormalStatesInit}\\
+}
+\Return{\(\bm{h}_c\)}
+\end{algorithm}
+
+\end{frame}
+
+%\begin{comment}
 %------------------------------
@@
 \begin{frame}
-\frametitle{\textsc{TransDetector}: Phrase 1}	
+\frametitle{\textsc{TransDetector}: Phase 1 (Extracting Category-Level Topics in KB) (1/3)}	
+Taking the category \textit{Military} as an example, we extract \textit{Military}'s category-level topic \(\bm{h_{Military}}\).
 \begin{figure}[h]
@@
         \centering
-        \includegraphics[width=0.5\columnwidth]{../img/initializationExample.pdf}
+        \includegraphics[width=0.45\columnwidth]{../img/initializationExample.pdf}
         \caption{Extracting Category-Level Topics in Knowledge Base via its three fold hierarchical structure, taking \textit{Military} as an example.}
@@
 \begin{frame}
-\frametitle{\textsc{TransDetector}: Phrase 2}
+\frametitle{\textsc{TransDetector}: Phase 2 (Transferring Category-Level Info into Microblog Stream) (2/3)}	
+Transfer KB's Category-Level Topics \(\{\bm{h_c}\}_{c=1}^{K_{KB}}\) into microblogs stream: CTrans-LDA.
+\begin{figure}[h]
+		\setlength{\abovecaptionskip}{0.cm}
+        \setlength{\belowcaptionskip}{0.cm}
+        \centering
+        \includegraphics[width=0.6\columnwidth]{../model/lda_tikz.pdf}
+        \caption{Diagram of CTrans-LDA.}
+        \label{fig:hood}
+\end{figure}
+
+In CTrans-LDA, \(\{\bm{h_c}\}_{c=1}^{K_{KB}}\) is used as prior information:
+\setlength{\abovedisplayskip}{0pt}
+\setlength{\belowdisplayskip}{0pt}
+\begin{scriptsize}
+\begin{equation}
+\label{eq:wikiPrior}
+\begin{aligned}
+\tau_{kv}=
+\left\{ \begin{aligned}
+\lambda \frac{h_{kv}}{\sum_{v\in S_{k}}h_{kv}} &,v\in S_{k}\ and  \ k \leq K_{\bm{KB}} \\
+0&,v \notin S_{k} \ or \ k > K_{\bm{KB}} \\
+\end{aligned}\right.
+\end{aligned}
+\end{equation}
+\end{scriptsize}
+\end{frame}
+
+\begin{frame}
+\frametitle{\textsc{TransDetector}: Phase 2 (Transferring Category-Level Info into Microblog Stream) (3/3)}	
+We use Gibbs Sampling for solving CTrans-LDA.
+\begin{itemize}
+	\item The initialization probability \(\hat{q}_{k|v}\) makes sure that the learned topics are aligned to the pre-defined category-level topic.
+\setlength{\abovedisplayskip}{0pt}
+\setlength{\belowdisplayskip}{0pt}
+\begin{scriptsize} 
+\begin{equation}
+\label{eq:initProbability}
+\begin{aligned}
+\hat{q}_{k|v}=
+\left\{ \begin{aligned}
+\frac{\tau_{kv}}{\sum_{k=1}^{K}\tau_{kv}} &,\sum_{k}\tau_{kv}>0 & (a)\\
+0&, \sum_{k}\tau_{kv}=0 \ and \ k \leq K_{\bm{KB}} & (b)\\
+1/(K-K_{\bm{KB}})&,\sum_{k}\tau_{kv}=0 \ and \ k > K_{\bm{KB}} & (c)
+\end{aligned}\right.
+\end{aligned}
+\end{equation}
+\end{scriptsize}
+\item Conditional probability in gibbs sampling:
+\(p(z_{dn}=k|.)\propto (n^{(d)}_{dk}+\alpha m_k)(n^{(w)}_{kv}+\tau_{kv}+\beta)/(n^{(w)}_{k,.}+\tau_{k,.}+V\beta)\).
+\end{itemize}
 
@@
 \begin{frame}
-\frametitle{\textsc{TransDetector}: Phrase 3}
+\frametitle{\textsc{TransDetector}: Phase 3 (Detecting Events on Category-Level Word Time Series) (1/2)}	
+After transfer learning, we conduct analysis on category-level word time series, and detect events in microblog stream.
+\begin{figure}[h]
+		\setlength{\abovecaptionskip}{0.cm}
+        \setlength{\belowcaptionskip}{0.cm}
+        \centering
+        \includegraphics[width=.99\columnwidth]{../img/screenShot.png}
+        \caption{Visualizing Category-Level Word Time Series in Microblog Stream on Edinburgh Twitter Corpus (20110711-20110915), taking \textit{Military} as an example.}
+        \label{fig:hood}
+\end{figure}
+\end{frame}
 
+\begin{frame}
+\frametitle{\textsc{TransDetector}: Phase 3 (Detecting Events on Category-Level Word Time Series) (2/2)}
+With richer semantics, and fewer noise, we detect events more accurately, in all the following granularities.(see more technique details in our paper)
+\begin{enumerate}
+	\item events' candidate words
+	\begin{itemize}
+		\item e.g., \textit{Ft.}, \textit{Hood}, \textit{attack}.
+	\end{itemize}
+	\item event phrases
+	\begin{itemize}
+		\item e.g., \textit{Ft. Hood attack}.
+	\end{itemize}
+	\item events' representative microblogs
+	\begin{itemize}
+		\item e.g., \textit{Possible Ft. Hood Attack Thwarted \url{http://t.co/BSJ33hk}}.
+	\end{itemize}
+\end{enumerate}
+\end{frame}
+
+\begin{frame}
+\frametitle{Experiment Settings}
+\textbf{Dataset}
+\begin{itemize}
+	\item Knowledge Base.
+Wikipedia dumps\footnote{\url{https://dumps.wikimedia.org/enwiki/latest/enwiki-latest-categorylinks.sql.gz}}\footnote{\url{https://dumps.wikimedia.org/enwiki/latest/enwiki-latest-pages-articles.xml.bz2}}
+	\item Microblog Stream. Edinburgh twitter corpus\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/fsd_corpus.tar.gz}}
+\end{itemize}
+
+\textbf{Baseline Methods}
+\begin{itemize}
+	\item Twevent, BurstyBTM, LSH, EDCoW, and TimeUserLDA
+\end{itemize}
+\textbf{Ground Truth}
+\begin{itemize}
+	\item Benchmark1 is labeled events in previous study.
+	\item Benchmark2 is our manually checked events based on Twevent, BurstyBTM, LSH, EDCoW, TimeUserLDA and \textsc{TransDetector}.
+\end{itemize}
 \end{frame}
@@
 \frametitle{Experimental Results}
-\begin{figure}[h]
-	\setlength{\abovecaptionskip}{0.cm}
-	\setlength{\belowcaptionskip}{0.cm}
-        \centering
-        \includegraphics[width=1.0\columnwidth]{../img/NPMI.pdf}
-        \caption{More topics are compared at the NPMI metrics between our method and LightLDA}
-        \label{fig:NPMI}
-\end{figure}
-\end{frame}
-
-\begin{frame}
-\frametitle{some}
+Evaluation on Categroy-Level Topics in Knowledge Base. On \textit{Aviation} topic, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Röder, WSDM 2015].
 
@@
 \begin{frame}
-\frametitle{Experiment Settings}
-
+\frametitle{Experimental Results}	
+Evaluation on Categroy-Level Topics in Knowledge Base.
+On more topics, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Röder, WSDM 2015]. 
+\begin{figure}[h]
+	\setlength{\abovecaptionskip}{0.cm}
+	\setlength{\belowcaptionskip}{0.cm}
+        \centering
+        \includegraphics[width=1.0\columnwidth]{../img/NPMI.pdf}
+        \caption{More topics are compared at the NPMI metrics between our method and LightLDA}
+        \label{fig:NPMI}
+\end{figure}
 \end{frame}
@@
 \frametitle{Experimental Results}	
+Effectiveness of transferring category-level topics into the microblog stream, and finding more new words in the stream which is not stored in the knowledge base.
+
 \begin{table}
@@
 \begin{frame}
+\frametitle{Conclusions}	
+\begin{itemize}
+	\item Knowledge base is constructed elaborately and contains rich information, which can benefit the not-well-organized microblog stream. 
+	\item We propose \textsc{TransDetector} method, and
+	\begin{itemize}
+		\item use category-level topic in knowledge base as the prior knowledge,
+		\item transfer abundant knowledge from knowledge base into microblog stream
+		\item enrich the semantics of microblogs and further enhances the accuracy of microblogs event detection
+	\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}
 %\frametitle{A first slide}
@@
 
-\end{comment}
+%\end{comment}
 

### 2017-03-26 paper/presentation/DASFAA_presentation.tex
presentation 1.0

@@
 	\item public security [Li, ICDE 2012], [Imran, WWW 2014]
-	\item disaster response [Sakaki,WWW2010]
+	\item disaster response [Sakaki,WWW 2010]
 	\item breaking news report\footnote{\url{http://www.theverge.com/2016/12/1/13804542/reuters-algorithm-breaking-news-twitter}}
@@
 \begin{frame}
-\frametitle{\textsc{TransDetector}: Phase 1 (Extracting Category-Level Topics in KB)}	
+\frametitle{\textsc{TransDetector}: Phase 1 (Extracting Category-Level Topics in KB) (1/3)}	
 There is a three fold hierarchical structure in Knowledge Base.
@@
 \begin{frame}
-\frametitle{\textsc{TransDetector}: Phase 1 (Extracting Category-Level Topics in KB)}
+\frametitle{\textsc{TransDetector}: Phase 1 (Extracting Category-Level Topics in KB) (2/3)}
 \begin{algorithm}[H]
@@
 \begin{frame}
-\frametitle{\textsc{TransDetector}: Phase 1 (Extracting Category-Level Topics in KB) (1/3)}	
+\frametitle{\textsc{TransDetector}: Phase 1 (Extracting Category-Level Topics in KB) (3/3)}	
 Taking the category \textit{Military} as an example, we extract \textit{Military}'s category-level topic \(\bm{h_{Military}}\).
@@
 \begin{frame}
-\frametitle{\textsc{TransDetector}: Phase 2 (Transferring Category-Level Info into Microblog Stream) (2/3)}	
+\frametitle{\textsc{TransDetector}: Phase 2 (Transferring Category-Level Info into Microblog Stream) (1/2)}	
 Transfer KB's Category-Level Topics \(\{\bm{h_c}\}_{c=1}^{K_{KB}}\) into microblogs stream: CTrans-LDA.
@@
 \begin{frame}
-\frametitle{\textsc{TransDetector}: Phase 2 (Transferring Category-Level Info into Microblog Stream) (3/3)}	
+\frametitle{\textsc{TransDetector}: Phase 2 (Transferring Category-Level Info into Microblog Stream) (2/2)}	
 We use Gibbs Sampling for solving CTrans-LDA.
@@
 \frametitle{Experimental Results}	
+Effectiveness of event detection:
+\begin{enumerate}
+	\item \textsc{TransDetector} performs better in terms of the precision and the recall.
+	\item only sacrificing in the DERate slightly because an event could be grouped into multiple categories.
+	\begin{itemize}
+		\item the event \textit{``S\&P downgrade US credit rating"}, related to \textit{politics} and  \textit{financial} simultaneously.
+	\end{itemize}
+\end{enumerate}
+
 \begin{table}[h]
@@
 \frametitle{Experimental Results}
+To understand why \textsc{TransDetector} performs better.
+\vfill
+Show the relationship between the recall and the event size.
 \begin{figure}[h]
@@
 \frametitle{Experimental Results}	
+To understand why \textsc{TransDetector} performs better.\\
+Show the relationship between the recall and the event size, taking the \textit{military}-related events as an example.
 \begin{table}

### 2017-03-26 paper/presentation/DASFAA_presentation.tex
add example for page 6
add "hood" picture
fix page 18

@@
 \usetheme{CambridgeUS}
+
+\usepackage{subfigure}
 
@@
 		\item still has to trade off between precision and recall
+		\begin{itemize}
+			\item e.g., the bursty segment in the not-so-popular event ``\textit{first artificial organ transplant}" is missed
+		\end{itemize}
 	\end{itemize}
@@
 	\centering
-        \includegraphics[width=0.5\columnwidth, left]{Fort_Hood.pdf}
+        \subfigure[]{
+                \includegraphics[height=2.12cm]{Hood(headgear)-Wikipedia.pdf}
+        }
+        \subfigure[]{
+                \includegraphics[height=2.12cm]{Fort_Hood.pdf}
+        }
 \end{figure}
+
 \end{frame}
@@
 \frametitle{Experimental Results}
-Evaluation on Categroy-Level Topics in Knowledge Base. On \textit{Aviation} topic, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Röder, WSDM 2015].
+Evaluation on Categroy-Level Topics in Knowledge Base.
+On \textit{Aviation} topic, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Röder, WSDM 2015]\footnote{\url{https://github.com/AKSW/Palmetto}}.
 
@@
 Evaluation on Categroy-Level Topics in Knowledge Base.
-On more topics, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Röder, WSDM 2015]. 
+On more topics, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Roder, WSDM 2015]. 
 \begin{figure}[h]
@@
 	\end{itemize}
+
 \end{itemize}

### 2017-03-27 paper/presentation/DASFAA_presentation.tex
some fix

@@
 Evaluation on Categroy-Level Topics in Knowledge Base.
-On \textit{Aviation} topic, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Röder, WSDM 2015]\footnote{\url{https://github.com/AKSW/Palmetto}}.
+On \textit{Aviation} topic, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Roder, WSDM 2015]\footnote{\url{https://github.com/AKSW/Palmetto}}.
 
